### 2021-05-07 Article/Article.Rmd
Commit paper and raw data for the first time

---
title: "Primate Cognition and the Red Queen Hypothesis"
# date: "`r format(Sys.time(), '%B %d, %Y')`"

#I follow: https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown for author display
author: 
  - name: Benjamin Robira
    email: benjamin.robira@normalesup.org
    institute: [CEFE, MH]
    correspondence: true
  - name: Benoit Perez-Lamarque
    institute: [ENS, MNHN]
institute:
  - CEFE: Centre d’Ecologie Fonctionnelle et Evolutive, Université de Montpellier & CNRS, Montpellier, France.
  - MH: Anthropologie et Ethnobiologie, Centre National de la Recherche Scientifique/Muséum National d'Histoire Naturelle, University Paris Diderot, Sorbonne Paris Cité, Musée de l'Homme, Paris, France
  - ENS: Institut de Biologie de l’Ecole Normale Supérieure (IBENS), Ecole Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France
  - MNHN: Institut de Systématique, Evolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France

output: 
 #      - '--lua-filter=scholarly-metadata.lua'
 #      - '--lua-filter=author-info-blocks.lua'
 bookdown::pdf_book:
 #bookdown::word_document2:
   number_sections: false
   toc: false
   #citation_package: natbib
   latex_engine: pdflatex
   fig_caption: true
   pandoc_args:
     - '--lua-filter=scholarly-metadata.lua'
     - '--lua-filter=author-info-blocks.lua'

bibliography: bibliographyarticlepackage.bib
csl: science.csl
#biblio-style: apa

urlcolor: blue
fontsize: 12pt

header-includes:
  - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
  - \usepackage{lineno} # For line numbering
  - \linenumbers # For line numbering
  - \usepackage{setspace}\doublespacing
  - \setlength{\parskip}{0em} #to remove line gaps
  - \DeclareUnicodeCharacter{2212}{-}
  - \usepackage{caption}
  - \captionsetup[figure]{font=small}
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(include=FALSE, echo=FALSE, message=FALSE)
knitr::opts_chunk$set(dpi=300) # Figure resolution and size out.width = '100%', 
knitr::opts_chunk$set(fig.pos = 'p'#, fig.align = 'center'
                      ) # Places figures on pages separate from text, centered
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R figure caption
```

```{r, echo=FALSE, results= 'hide'}
#Import librairies

library(readr)

#Plot
library(RColorBrewer)
library(tidyr)
library(stringr)
library(svMisc)
library(plotrix)
library(circlize)

#Spatial
library(rworldmap) # World map
library(cleangeo) #to clean it otherwise issues with intersection
library(maps)
library(rgeos) #for readOGR; gArea/gCentroid...
library(sf) #for intersection
library(rgdal)
library(geosphere)

#Phylogeny
library(phytools)
library(ape)

#Import own function
source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R", local = knitr::knit_global())

#Create citation fusion between articles and package (based on toolbox function)
citeR(
bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticle.bib",
bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticlepackage.bib",
rgeos,
geosphere,
phytools,
geiger,
RPANDA,
caper,
neurobase,
misc3d
)

#Load environments
load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Data_spatial_primate.RData")
load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/geography_traits_biogeobears.RData")

```

\captionsetup{list=no}

<!-- The front page -->
<!-- \centering -->
<!-- \raggedright -->
<!-- \newpage -->
<!-- \tableofcontents -->
\newpage

```{r,  warning = FALSE, message = FALSE}
#For the moment because this was not run: to delete after
repetitionTrees=50
repetitionModels=30
repetitionBootstrap=2000

repetition=7#length(frugivoryThresholdVector)*length(folivoryThresholdVector)*length(geographicThresholdVector)*randomSampling - 1
checkSampleFruit <- rep(NA, times=repetition)
checkSampleLeaf <- rep(NA, times=repetition)
checkSampleRange <- rep(NA, times=repetition)
checkSampleBrain <-  rep(NA, times=repetition)
checkSampleEQ <-  rep(NA, times=repetition)
checkSampleNeocortex <-  rep(NA, times=repetition)
checkSampleHippocampus <- rep(NA, times=repetition)
checkSampleCerebellum <- rep(NA, times=repetition)
checkSampleStriatum <- rep(NA, times=repetition)
checkSampleMOB <- rep(NA, times=repetition)

for(i in 0:repetition){

  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)

  checkSampleFruit[i] <- length(summaryDataOfInterest$DietaryGuild[summaryDataOfInterest$DietaryGuild=="Fruit"])
  checkSampleLeaf[i]  <- length(summaryDataOfInterest$DietaryGuild[summaryDataOfInterest$DietaryGuild=="Leaf"])
  checkSampleRange[i]  <- length(summaryDataOfInterest$geographicCode[!is.na(summaryDataOfInterest$geographicCode)])
  checkSampleBrain[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&summaryDataOfInterest$DietaryGuild=="Fruit",])
  checkSampleEQ[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Bodymass)&summaryDataOfInterest$DietaryGuild=="Fruit",])
  checkSampleNeocortex[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Neocortex)&summaryDataOfInterest$DietaryGuild=="Fruit",]) 
  checkSampleHippocampus[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Hippocampus)&summaryDataOfInterest$DietaryGuild=="Fruit",])
  checkSampleCerebellum[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Cerebellum)&summaryDataOfInterest$DietaryGuild=="Fruit",])
  checkSampleStriatum[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Striatum)&summaryDataOfInterest$DietaryGuild=="Fruit",])
  checkSampleMOB[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$MOB)&summaryDataOfInterest$DietaryGuild=="Fruit",])

}

#Min values
minFruit <- min(checkSampleFruit)
minLeaf <- min(checkSampleLeaf)
minRange <- min(checkSampleRange)
minBrain <- min(checkSampleBrain)
minEQ <- min(checkSampleEQ)
minNeocortex <- min(checkSampleNeocortex)
minHippocampus <- min(checkSampleHippocampus)
minCerebellum <- min(checkSampleCerebellum)
minStriatum <- min(checkSampleStriatum)
minMOB <- min(checkSampleMOB)

minAllAreas <- min(
minEQ,
minNeocortex,
minHippocampus,
minCerebellum,
minStriatum,
minMOB
)

#Max values
maxFruit <- max(checkSampleFruit)
maxLeaf <- max(checkSampleLeaf)
maxRange <- max(checkSampleRange)
maxBrain <- max(checkSampleBrain)
maxEQ <- max(checkSampleEQ)
maxNeocortex <- max(checkSampleNeocortex)
maxHippocampus <- max(checkSampleHippocampus)
maxCerebellum <- max(checkSampleCerebellum)
maxStriatum <- max(checkSampleStriatum)
maxMOB <- max(checkSampleMOB)

maxAllAreas <- max(
maxEQ,
maxNeocortex,
maxHippocampus,
maxCerebellum,
maxStriatum,
maxMOB
)

```

**Abstract:** The diversity in animal cognition raises the question of its underlying evolutionary drivers. Cognitive selection can stem from interactions of individuals with their environment (*Ecological Intelligence Hypothesis*), with conspecifics within the social unit (*Social Intelligence Hypothesis*) or between social units (*Napoleonic Intelligence Hypothesis*), or even among generations (*Cultural Intelligence Hypothesis*). Yet, one species rarely occupies an area alone: space is a shared place between many species that can interact directly or indirectly. These interactions could represent additional cues and/or noise to find resource or escape predator(s), henceforth stimulate cognition. To test whether species co-occurrence shaped current patterns of cognition, we used Primates (N$_{min-max}$=`r minAllAreas`-`r maxAllAreas`) as a study example and retraced the evolutionary history of species whole brain - or specific area – relative size, using standard phylogenetic models or competitive phylogenetic models. Then we fitted phylogenetic regressions to test for variation in brain size and current co-occurrence pattern correlations. We found that the evolution of the relative size of areas involved in foraging, information processing and/or retention is better described by models accounting for species co-occurrence within dietary guilds which lead to increased relative sizes of these areas. This suggests that cognition is subject to an arms race among species (*Red Queen Intelligence Hypothesis*) and shall explain why specific abilities particularly boomed for some lineages, as for instance with Primates.

**Keywords:** "Brain size - Species co-occurrence - Intelligence evolution - Cooperation - Competition"

```{r}
#My toolbox with several functions
source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R", local = knitr::knit_global())

words <- RmdWords("Article.Rmd")
```

<!-- TC:ignore -->
**Word Count:** `r words$num_words` \newline
<!-- Character Count: `r words$num_char` -->
<!-- TC:endignore -->

\newpage

To grasp the rationale of current hypotheses that aim to describe the evolution of animal cognition [@van2006some; @dunbar2017there], consider an animal foraging for food. This focal is not looking for any type of food but specific one. This can for instance be fruits. Finding fruits for an animal is not an easy task. In fact, fruits are the archetype of a hard-to-find resource likely to promote cognitive development because fruit trees are rare, dispersed, and do not produce constantly along the year nor between years, albeit their fruiting period remains nonetheless predictable [@janmaat2016spatio]. Additionally, they are energy-rich, allowing expansion of costly tissues such as brain tissues [@clutton1980primates]. Where the example focal stands there is no food that is immediately perceived, and the focal must move beyond its sensory range if it is to feed. Moving at random could mean travelling unnecessary long distances to finally rich a potentially void tree. Hence, for the focal, being capable of processing immediate cues and clues to know where specifically to find fruit trees [@dall2005information; @grove2013evolution] and whether it is probable that these trees currently yield fruits [@dall2005information; @robirainreview; @janmaat2016spatio] would be a considerable advantage. Provided it has the appropriate cognitive machinery, this could lead to avoiding costly detours and time recursions to food patches adequately. This simple picture draws the basis of the *Ecological Intelligence Hypothesis* [@clutton1980primates; @milton1981distribution; @rosati2017foraging] which stipulates that cognition was selected as a way to buffer the spatio-temporal complexity of the environment (e.g. @van2012large). In its quest, however, the focal might not be alone: there might be a few conspecifics foraging on its side, each looking for a signal leading to food sources. With these conspecifics, the focal forms a social group: they spend considerable time together, have established bounds and constantly share information. It is thus collectively that they must find a fruiting tree. To do so, being able to process signals emitted by others would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian]. This therefore means plenty of additional stimuli to process, and constitutes the socle of the *Social Intelligence Hypothesis* [@dunbar2017there]. In the focal group, however, all individuals are not equally knowledgeable: perhaps because some have more experience than others do, such as the oldest would be more experienced than the youths. It is possible that these young individuals learn from the elderly individuals [@laland2004social]. For instance, they may learn how to process a specific tool to access a hidden comestible part as for nuts [@boesch1994nut]. In other words, there is vertical transmission that passes by over generations and knowledge thereby accumulates: this is the *Cultural Intelligence Hypothesis* [@whiten2007evolution, reader2002social], also known as the *Vygotskian Intelligence Hypothesis* in humans [@herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social]. Finally, while the focal’s group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild]. The neighbouring groups might indeed be competitors for food, mates or actually any resource that it might be essential to preserve, and as much as it is advantageous to be able to read through the environment and intra-group conspecifics, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g. group size), a view brought by the *Napoleonic Intelligence Hypothesis* [@ashton2020interactions].

|   In this overly simplistic picture, we moved from a unique individual to a group of individuals and then to multiple groups. Never was it question of multiple species: all hypothesized individuals belonged to a singular common species. Yet, a species rarely occupies a given area alone. Space is a shared place between a plethora of species, some of them occupying a same ecological niche. This partial niche overlap could contribute to impoverishing food density and increasing its spatio-temporal variance, hence reinforcing the selective pressure towards advanced cognition to maintain sufficient foraging success. In another perspective, two species sharing common food targets might benefit from being able to process cues of passage or presence of the other, to infer where and when to find ripe resource. To sum up, species co-occurrence might contribute into shaping animal cognition: the more species, the more advanced the cognition because the more noise or stimuli. In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in brain size among species, what we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example.

\hfill

|   Recent tools have been developed to infer the effect of species interaction on trait evolution, either by modelling divergence of the trait in co-occurring species from a same guild (e.g. dietary guild) (Matching Competition: MC models), or due to a density dependence of the evolutionary cladogenesis rate (linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating) on the number of lineages within the guild. After reconstructing the range history based on `r minRange` to `r maxRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs. folivory; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, $EQ$, as a proxy for `r minEQ` to `r maxEQ` frugivorous, depending on how frugivory was assessed, see Dietary guild), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure. \@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming non effect of species interactions, like the pure drift; Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g. stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, REF), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence. Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion (AIC) corrected for small samples (AICc) when considering all five models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Evolutionary models in methods). Non-competitive models were the most likely in describing the evolutionary history of the $EQ$ or the striatum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), an area specifically involved in XXX, used here as a control area. By contrast, competitive models were most supported in areas involved in sensory abilities (the main olfactory bulb, MOB), immediate information processing (i.e. working memory, with the neocortex), or long-term spatio-temporal information retention (hippocampus), (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)). When density-dependent models were the best fit, the positive rate (b or r, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity.

|   To understand the directionality of the selection gradient shaped by co-occurrence (i.e. selection for “bigger” brain or “smaller” brain the more species), we fitted phylogenetic regressions (see Phylogenetic models; phylogenetic regressions in methods). In these linear regressions, the predicted variable was the relative brain size values of areas for which we observed interspecific competition effect. we considered the average surface of the frugivorous species range overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.  Despite considerable noise induced by recent increase extinction and spatial range reduction due to anthropogenic disturbances (REF), it shows that XXXXXXXXXX

\hfill

|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond). The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g. in primates: @milham2018open), or with standardized behaviourally explicit comparisons (e.g. on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time. In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species. Further, biases might be limited by considering measurement variability [@logan2018beyond] or the mosaic structure of the brain [@barton2000mosaic; @decasien2019primate]. In this case, we indeed see that the evolutionary history between specific brain regions differ, while the $EQ$ was not affected by greater lineage diversity. The effect of between-species interaction is indeed only evidenced for specific areas, more particularly those involved in immediate information processing based on senses (%area%), in areas involved in a working memory (%area%), or in a long-term memory of spatio-temporal information (%area%). All these areas have thus in common to be potentially (but not only) used when foraging, suggesting that species with larger brains would be at competitive advantage with sympatric species with similar food preference.

|   Competition is generally the first-thought mechanism to describe community structures [e.g. @rocha2015role]. The idea of such an arms race in cognition should be best illustrated considering predator-prey interactions, in which a bigger brain could rhyme in absolute with higher chance of escaping a predator, but also relatively to other prey species, with a lower probability to be targeted by the predator at first [@shultz2006chimpanzee]. In this study example, however, competition should take the form of scramble competition, indirectly affecting individuals’ fitness through food depletion. Logically, species co-occurrence should correlate with diminished shared food density and lowered temporal predictability (as a drawback of more intense depletion), both these factors playing on the selective pressure on foraging cognition [@grove2013evolution; @janmaat2016spatio]. Possibly indeed, because niche overlap among species is not perfect, the depletion rate for the shared resource would be higher than if a species was occupying a space alone. An oversimplified proof of principle of this assumption would consider a two consumers and three resource types system. Both consumers share only one (essential) resource in common while are limited in population size by respectively the two others. The common resource would therefore be consumed more than it would be if the system considered only one species. Hence, in this competitive view, it seems to be mainly density rather than diversity itself that should particularly shape cognition (REF). Yet, an arms race does not necessarily need to imply competition: one might keep pace with someone it cooperates with.

|   In an analogous situation to direct cooperation, more species sharing overlapping diet would equate to more, and diverse, cues to infer where and when to find food. Hence, not only should animals gain benefits into decoding their own conspecific presence trace or behaviour, but they might as well benefit from decoding those of other species, what matches current behavioural observations. To settle to new coral reefs, fishes use pops and clicks of other fishes as an honest signal for resourcefulness there [@gordon2019acoustic], mangabeys follow calls from hornbills to locate fruiting trees [@olupot1998fruit], and interactions even happen across kingdoms, with migratory birds interpreting phenological cues as synonymous of insect availability [@mcgrath2009flower].  Would the fishes, monkeys or birds truly rely on these signals to reach high foraging success, shall then the individuals be selected based on their ability to process these stimuli. These stimuli might actually be in perpetual change throughout time, as a consequence of the evolution of the emitter species, and thus, so would be the selective pressure on cognitive abilities of species relying on it to make movement decisions.

|   In the end, the inter-specific effect on cognition was here viewed under the prism of foraging, yet, without further evidence, it is as likely to hold in other contexts, such as the social environment. In fact, the general hypotheses on cognition evolution, discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; pepperberg2002allospecific]. As Alice said “'It's a great huge game of chess that's being played—all over the world” (Carroll, Chapter II, Through the Looking Glass) and all individuals are just pieces to play with or against, no matter the species.

# Methods

Data processing, analyses, and plots were computed with R software version 4.0.3 [@Rsoftware]. Used datasets and codes will be made freely available upon publication. They can also be provided during the reviewing process for verification of missed coding errors, or any further investigation by the reviewers.

## Data Collection

Note that in all these analyses, we discarded *Homo sapiens*. A summary of available data per species is presented in Supplementary Figure \@ref(fig:figmap).

### Phylogeny

We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 28/01/2020, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses. The trees contain `r length(phylo_init$tip.label)` primate species.

### Brain data

Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (cerebellum, hippocampus, main olfactory bulb (MOB), neocortex, striatum) , @powell2017re and @powell2019maternal for whole brain, cerebellum and neocortex size, @todorov2019primate for hippocampus and neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, cerebellum, hippocampus and striatum size. They were freely available in the main manuscript or supplementary materials. If the species was represented multiple times in the dataset, we obtained a unique attribute by averaging it. From the global endocranial brain volume, we obtained the Encephalization Quotient (*EQ*, (N$_{max}$=`r maxEQ`)) as follows [@decasien2017primate]

\hfill

\begin{center}

$EQ=1.036 \times Brainvolume/ (0.085 \times Body mass^{0.775})$

\end{center}

\hfill

with the brain volume in cm$^{3}$, 1.036 g/cm$^{3}$ being the assumed homogeneous brain density, and the body mass in g. Encephalization Quotient indicates whether the brain size ranges above (>1) or below (<1) expected given the body mass. Body mass was obtained from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.
The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{max}$=`r maxMOB`), in movement and/or associate immediate information processing and retention (Neocortex, N$_{max}$=`r maxNeocortex`, REF; Cerebellum, N$_{max}$=`r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), long-term spatio-temporal memory (Hippocampus, N$_{max}$=`r maxHippocampus`, @burgess2002human). The striatum (N$_{max}$=`r maxStriatum`), which supports information processing during social interaction (i.e. social reward assessment; @izuma2008processing), was chosen so as to serve as a comparative “null” area. To investigate their evolutionary history, we used the ratio between their volume and that of the whole brain.

### Diet and body mass data

Percentage of frugivory and/or folivory was obtained based on freely available dataset from @decasien2017primate and @powell2017re for the frugivory and folivory rate, or @willems2013collective for the folivory rate. Body mass data were available from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.

### Ranging Data

Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list (downloaded on the 19/01/2021, REF). Ranging data were available for `r nrow(matrixRangingSensitivity[!is.na(matrixRangingSensitivity[,1]),])` species among the `r length(phylo_init$tip.label)` represented in the 10kTrees primate phylogeny.

## Primate species co-occurrence

One to multiple large-scale geographic areas were assigned to each species as soon as the species current range overlapped in surface at `r geographicThresholdVector[1]` (low threshold) or `r geographicThresholdVector[2]`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]`% because on present data, a species could occupy as far as three areas) with the individual geographic area (Figure \@ref(fig:figmap); “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to obtain the overlapping area, “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area calculation). These geographic areas were manually delimited using Google earth pro (version X.X, REF) as a combination of the environment topology and geographic regionalization relative to the primate taxonomy [@kamilar2009environmental]. Based on the structure (i.e. number of species and their phylogenetic relationship) of primate communities at different field sites, @kamilar2009environmental determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates. The considered geographic areas are represented in Figure \@ref(fig:figmap). The chosen scale for the areas is large because (1) retracing history of a large number of areas necessitates considerable computational means. In addition, this drastically increases computational time of phylogenetic model of brain trait evolution too. Furthermore (2), all species and particularly primate species particularly suffer from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unpreceeding speed rate. Finer geographic characterization would therefore give too much weight to this recent anthropogenic effect that recently altered species distribution (e.g. evidenced on the North American fauna in @pineda2021mammal).  Finally, note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography]. Hence, *Macaca Sylvanus* is not considered in this study.
	We retraced the history of the lineage ranges based on current observation of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic]. This algorithm aims to fit, among others, non-time-stratified dispersal-extinction-cladogenesis (DEC) models (used here), specifically suiting analysis of ranging data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events). To reconstruct the evolution of species range, WE fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas. A too high number of areas that can be occupied simultaneously drastically increases computational time. Here, we therefore chose three areas since it offers the possibility to occupy a complete mainland continent. Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models), such as it allowed me to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Evolutionary Models (b)).

## Dietary guild

We classified species as either frugivorous, folivorous or “other” based on the availability of frugivorous rate and folivorous rate, prioritizing fruvigory over folivory. First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold). If this was not the case, or frugivory rate was unavailable, a species could be classified as folivorous if the folivory rate was at least above `r folivoryThresholdVector[1]` (low threshold) or `r folivoryThresholdVector[2]`% (high threshold). Otherwise, @decasien2017primate gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria. Whenever the rate was not available, we referred to this classification. In any other cases, the species was classified as “other”.
	Frugivory rate was prioritized over, folivory, because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed. Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons. First, such static rate does not reflect potential seasonality in fruit eating [e.g. @masi2009western], which is generally shorter, hence a lower overall frugivory rate. Second, frugivory rate is likely to be underestimated in part because primates generally spend more time eating leaves than fruits, while rates are often based on eating relative feeding time, or observation frequency at the individual or group unit of feeding event. Finally, because the methodology to obtain this rate could additionally vary (e.g. in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves), We used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
Considering diet as a categorical variable (frugivory vs folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e. at the root) but with no prior on the transition matrix. Again, the obtained character history is in no case certain. Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models), such as it allowed me to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Evolutionary Models (b)).

## Phylogenetic models

### Evolutionary models: does interspecific interactions shape brain size evolution?

\hfill

(a)	Fitting evolutionary models

\hfill

We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic model of $EQ$ - or relative size of a specific brain area – evolution with and without species competitions. Models were fitted on different sample sizes due to non availability of some data. Specifically, models using $EQ$ included `r minEQ` to `r maxEQ` frugivorous species. Other models included more reduced sample sizes (in species number): striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), neocortex (`r minNeocortex` to `r maxNeocortex`), hippocampus (`r minHippocampus` to `r maxHippocampus`), cerebellum (`r minCerebellum` to `r maxCerebellum`). Prior fitting, trait parameters were log-transformed in case the distribution was skewed (i.e. for brain and MOB ratio) to reach more symmetrical distributions. Models without competition, Brownian motion (i.e. BM, pure drift model), Orstein-Uhlenbeck process (i.e. OU, model with stabilizing selection), or Early-Burst model (i.e. EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5]. Using the evolutionary history of species distribution (Primate co-occurrence paragraph) and of diet (Dietary guild paragraph), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA]. These competitive models notably account for interaction matrices that are build on the evolutionary history of species co-occurrence and diet. These interaction matrices retrace, along the phylogenetic tree, which lineages (species or ancestors) of a same dietary guild were present within the same geographic areas (see @drury2016estimating). We fitted three different competitive models. The matching competition model (MC) considers divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits [@drury2016estimating]. Here, that would mean that co-occurring species would tend to have either extremely low or high $EQ$ or relative brain size. Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity]. Density-dependence means that the evolutionary rate $\lambda$ varies either positively or negatively as a function f of the number of co-occurring lineages sharing the same diet such as

\begin{center}

\hfill

$f_{lin}(\lambda)=\lambda_{0}N^{−r}$

$f_{exp}(\lambda)=\lambda_{0}(1 − N/K)$

\hfill

\end{center}

where $\lambda_{0}$ corresponds to the initial cladogenesis tree, $N$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the exponential dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes), and $K$ is generally considered as a “carrying capacity” [@rabosky2008density], that is the upper limit of lineages that are viable when at equilibrium.
	All these models were repeated `r numberSimulations` times, using `r randomSampling` different combination of the evolutionary history of ranging and diet. They were then compared within an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion (AIC) corrected for small samples (AICc) when considering all five models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU). The model weight then depicts the probability that it best describe the observed evolutionary pattern.

\hfill

(b) Dealing with data uncertainty and parameter sensitivity

\hfill

In this analysis, uncertainty can stem from two sources. First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference. Therefore, the downloaded trees provided by the 10kTrees project might vary depending on the run. Similarly, the estimated evolutionary history of the diet and ranging might vary as well. Second, for each species, trait estimates could vary slightly among datasets (see Supplementary Figure 2). Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Supplementary Figure 2), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset. In addition this study is based on several arbitrary thresholds, namely (i) to assess species co-occurence (see Supplementary Figure 3) and (ii) to assess the species dietary guild (see Supplementary Figure 2) which can cause sensitivity of the results to the chosen parameters.

|   To account for these three sources of variability we refitted several times the five evolutionary model types (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeographic and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e. equal probability for each possible value to be selected) and (3) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence. we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1 000 possible trees estimated by Bayesian inference, because the evolutionary models take a long time to run and we could not fit the model several times with different trees. Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.

### Phylogenetic regression: determining the direction of the selection gradient shaped by interspecific competition

\hfill

(a)	Model dataset and formula

\hfill

To determine the direction of the selection, we fitted Gaussian phylogenetic regressions (i.e. accounting for a variance-covariance matrix based on phylogenetic distances) specifically for each brain region for frugivorous species only. To describe phylogenetic relationships among lineages, we used a consensus tree based on a block of 1 000 trees from the 10kTrees project, but we assessed sensitivity to phylogeny uncertainty using `r repetitionTrees` random trees from the block of trees.
To categorize species as frugivorous or folivorous, we here considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%. If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous vs. folivorous” (i.e. could be either of the two), it was considered as frugivorous nonetheless.

|    The response variable was the relative size of areas shown as better described by competitive phylogenetic scenario (see above). Since the exact value of this output could vary depending on the dataset from which it was extracted (e.g. whole brain size could be extracted from @decasien2017primate, @powell2017re, @grueter2015home or @navarrete2018primate), we took the mean of the possible values but assessed the sensitivity using non-averaged values (see below). In this model, the covariates (i.e. continuous predictors) were the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species (both were square rooted, to reach symmetrical distribution). For a given species A, sympatry with another species B was considered when species B range overlapped on more than 10% of the range of species A. This was done to reduce noise induced by coarse identification of species range.

\hfill

(b)	Model implementation

\hfill

Models were fitted using the “pgls” function from the *caper* package [@caper], with the lambda parameter (i.e. indicating whether the trait is subject to selection if $\lambda$ > 1) estimated by maximum-likelihood (argument “model” set to “lambda”; i.e. fits the Pagel’s lambda model, a derivative of the Brownian Motion model (REF)). Bootstrapping over `r repetitionBootstrap` independent replicates was done so as to obtain confidence intervals. Other function parameters were set to default. Prior fitting, if skewed, covariates were transformed with deemed appropriate functions to reach more symmetrical distribution (e.g. we faced X skewed distributions that were X transformed, REF). Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Supplementary Figure X). We did not observe correlation issue among predictors either (max VIF < XX, REF).

\hfill

(c)	Model robustness

\hfill

To assess model stability with regards to singular points, we discarded one observation at a time and quantified model sensitivity using various predictors relying on (Dffits, dfbetas, cook distance, and leverage, REF; Supplementary Table 1). These controls did not point out important variability.
To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10 000 possible trees from the 10kTrees project. For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple value (e.g. if body mass was provided by different datasets etc.). The results of this sensitivity analysis are shown in Supplementary Table 2 and emphasizes that there is no major effect.

# Acknowledgements

We considerably value the help provided by Jonathan Drury in making some scripts available but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for helping in trying to make the analysis run on the CEFE cluster. We thank Simon Benhamou and Manon Clairbaux for discussion and advices on spatial projections too. Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and Alexandra R. DeCasien and collaborators, Lauren E. Powell, Orlin S. Todorov and collaborators, Erik P. Willems and collaborators, Fiona Pearce and collaborators, Navarrete and collaborators, and Cyril C. Grueter who do not know us, but provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J. Matzke for available algorithm scripts allowing us to implement and better understand the methods. Their indirect input is therefore tremendous.

|   Both authors were supported by a doctoral grant from the *Ecole Normale Supérieure*, Paris. BR received logistic support from the *Centre d’Ecologie Fonctionnelle et Evolutive*, Montpellier and the *Musée de l'Homme*, Paris. BP-L received logistic support from the *Ecole Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.

```{r }
#Reimport areas with cropping
centroid <- matrix(NA, ncol=2, nrow=length(areaName))
for(i in 1:length(areaName)){
  areaTransitory <- readOGR(dsn=paste("T:/IUCN_data_primate/Geographic_areas/Shapefiles/",areaName[i],".shp",sep=""))
  areaTransitory = clgeo_Clean(areaTransitory)
  areaTransitory <- spTransform(areaTransitory, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
  #Have mercator for intersection
  areaTransitory <- spTransform(areaTransitory, CRS("+proj=merc +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
  areaTransitory <- gIntersection(areaTransitory, worldMap_mercator, byid=FALSE)
  areaTransitory = clgeo_Clean(areaTransitory)
  #Reunite polygon in case
  areaTransitory <- gBuffer(areaTransitory, byid=F, width=0)

  #back transform to long/lat
  areaTransitory <- spTransform(areaTransitory, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
  assign(paste("area", i, sep="_"), areaTransitory)
  if(i==1){
    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] + 5, summary(areaTransitory)$bbox[2,1]) 
  }
  else if (i==2){
    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] - 5, summary(areaTransitory)$bbox[2,1] - 5) 
  }
  else{
    centroid[i,] <- geosphere::centroid(areaTransitory)
  }
}
#warnings()
```

```{r figmap, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap=paste("(Left) Current frugivorous primate co-occurrence pattern and phylogeny (Right) Geographic areas used for ancestral range reconstruction | (Left) Primate phylogeny from a consensus tree of 1 000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name. The corresponding non-abbreviated names can be found using Supplementary Figure X. Co-occurring frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by lightgray lines. The geographic area occupied by a species is depicted by the coloured rectangles. Presence was assed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1], "%. (Right) Depicted is the equirectangular projection of the world. Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands. Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography]. Hence, *Macaca Sylvanus* is not considered in this study.", sep="")}

#Just to see the difference as pinpointed by the warning
# geosphere::areaPolygon(areaTransitory)
# gArea(areaTransitory)
# really false
# geosphere::centroid(areaTransitory)
# gCentroid(areaTransitory)
#ok

layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)

####
## Fig interaction
####

#Import data
summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)

#Tree
tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Tree/Tree_diet.nex")

#Create geography df
geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
colnames(geoBinary) <- c("SpeciesPhylo", "Loc")

#Create species ID
hc = as.hclust(tree)#bird.orders)
labels = hc$labels  # name of birds

labels.tordc <- as.data.frame(labels)
colnames(labels.tordc) <- "Name"
labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")

labels.rdc <- apply(labels.tordc, 1, function(x){
  if(!is.na(x[3])){
    paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
  } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
  }
}
)

#Match to have right order for geography
locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
colLoc <- colourArea

#Match to have diet
dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]

#Getting species labels abbreviated
speciesLabels <- hc$labels#Should be in the tree order

#Create the circos plot linking species based on their diet and geography
circos.clear()
circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
circos.initialize(speciesLabels, xlim = c(0, 1))

#Species name + area it belongs to
circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
             panel.fun = function(x, y) {
               i=CELL_META$sector.numeric.index
               circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
                           facing = "clockwise", niceFacing = TRUE,
                           col = "black", cex = 0.35, font=3)

              geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
              for(g in 1:length(geo)){
                if(geo[g]==1){
                  #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
                  circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
                }
              }
             })

#Plot the geographic links
for(i in 1:length(speciesLabels)){
  #locI <- which(strsplit(locationSpecies[i], "")==1)
  for(j in i:length(speciesLabels)){
    #locJ <- which(strsplit(locationSpecies[j], "")==1)
    product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
    if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
      #Do nothing
    }
    else{
      if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
        # colour <- as.data.frame(table(colLoc[which(product==1)]))
        # if(is.finite(max(colour$Freq))){
        # }else{
        #   print(c(i,j))
        # }
        # colour <- colour[colour$Freq==max(colour$Freq),1][1]
        circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
      }
      else{
        #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
      }
    }
  }
}
circos.clear()

#Plot the phylogenetic tree in a new circular plot
n = length(labels)  # number of species
dend = as.dendrogram(hc)

par(new = TRUE) # <- magic
circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
circos.initialize("a", xlim = c(0, n)) # only one sector
# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
#              panel.fun = function(x, y) {
#                for(i in seq_len(n)) {
#                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
#                              facing = "clockwise", niceFacing = TRUE,
#                              col = "black", cex = 0.2, font=3)
#                }
#              })

#suppressPackageStartupMessages(library(dendextend))
#dend = color_branches(dend, k = 6, col = 1:6)
dend_height = attr(dend, "height")
circos.track(ylim = c(0, dend_height), bg.border = NA,
             track.height = 0.95, panel.fun = function(x, y) {
               circos.dendrogram(dend)
             })
circos.clear()

####
## Fig map
####

#Create the map of the geographic area
#Have background
maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))

# addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
#

for(i in 1:length(areaName)){
  plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
}
#Have borders
#plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
# for(i in 1:length(areaName)){
#   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
# }
points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))

```

```{r figbrain, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap=paste("(Left) Brain area location (Right) EQ or relative brain size value among frugivorous primates | (Left) A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]) together with the studied brain area. The neocortex was not represented for readability since it corresponds to the external layer of the cerebral hemisphere. In short, the MOB is involved in immediate olfactory information processing, the neocortex and the cerebellum support a working memory and memory consolidation processes [@koziol2014consensus; @sokolov2017cerebellum], and the hippocampus a long-term spatio-temporal memory [@burgess2002human]. The striatum, involved in social information processing [@izuma2008processing], acts as a comparative “null” area. (Right) The circular rows are indicated by the colours which match a specific brain area. The mean value (after scaling and based on one random sampling among possible values, but see Supplementary Figure 2 for visualization of measure variability) for the Encephalization Quotient ($EQ$, see Data collection; Brain data for further details on calculation) or relative size of brain parts, when available, is depicted by a plain circle for frugivorous species. The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%. The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.", sep="")}

library(RColorBrewer)
colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")

###
## Fig brain values / circular
###

summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain

#Brain data
relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])

library(circlize)
circos.clear()
circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
circos.initialize(speciesLabels, xlim = c(0, 1))

#Species name
circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
             panel.fun = function(x, y) {
               i=CELL_META$sector.numeric.index
               circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
                           facing = "clockwise", niceFacing = TRUE,
                           col = "black", cex = 0.35, font=3)
             })

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
}, track.height = 1/15)

library(plotrix)
#Main circle
for(i in 1:13){
  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
}

#increment of 0.5
for(i in 1:26){
  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
}

#Value

#EQ
absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueEQ[i])){}  else{
    if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
    }
    else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueEQ[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
    }
    else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
    }
    else{}
  }
}, track.height = 0.1)

#Striatum
absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueStriatum[i])){}  else{
    if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
    }
    else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueStriatum[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
    }
    else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

#MOB
absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueMOB[i])){}  else{
    if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
    }
    else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueMOB[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
    }
    else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

#Neocortex
absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueNeocortex[i])){}  else{
    if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
    }
    else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueNeocortex[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
    }
    else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
    }
    else{}
  }
}, track.height = 0.1)

#Hippocampus
absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueHippocampus[i])){}  else{
    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
    }
    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueHippocampus[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
    }
    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
    }
    else{}
  }
}, track.height = 0.1)

#Cerebellum
absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueCerebellum[i])){}  else{
    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
    }
    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueCerebellum[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
    }
    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
    }
    else{}
  }
}, track.height = 0.1)

```

```{r figresultsevolution, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap="AICc weights of fitted evolutionary models for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models. The points represent the average AICc weight obtained (when considering the five models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see Phylogenetic models, Evolutionary Models (b)). (1) Whole brain (EQ) (2) Striatum (3) MOB (4) Neocortex (5) Hippocampus (6) Cerebellum."}

plot(0, 0, type="n")

```

# Literature cited

<div id="refs"></div>

\newpage

# (APPENDIX) Appendix {-}

```{r figdata, include=TRUE, warning = FALSE, message = FALSE, fig.width=20, fig.height=25, fig.cap="Supplementary Figure. Data availability | Black boxes indicate data availability while grey boxes indicate absence of data."}
# 
# plot(
#   x=0, y=0, xlab="", ylab="", cex.sub=1.6,
#   xlim=c(-10,ncol(dataForSample)-1), ylim=c(0,nrow(dataForSample)),
#   las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
#   xaxt="n",xaxs="i",yaxs="i", yaxt="n")
# 
# text(x=rep(-2, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$SpeciesForPhylo, xpd=TRUE, cex=0.4)
# text(x=rep(-0, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$Species, xpd=TRUE, cex=0.4)
# text(x=3:ncol(dataForSample)-1.5, y=rep(nrow(dataForSample)+3, times=length(3:ncol(dataForSample))), labels=colnames(dataForSample)[3:ncol(dataForSample)], xpd=TRUE, cex=0.4, srt=45)
# 
# for(i in 1:nrow(dataForSample)){
#   for(j in 3:ncol(dataForSample)){
#     if(!is.na(dataForSample[i,j])&dataForSample[i,j]==1){
#       rect(
#         xleft=j-2,
#         xright=j-1,
#         ybottom=i-1,
#         ytop=i,
#         border="black",
#         col="black"
#       )
#     } else{
#       rect(
#         xleft=j-2,
#         xright=j-1,
#         ybottom=i-1,
#         ytop=i,
#         border="lightgrey",
#         col="lightgrey"
#       )
#     }
#   }
# }
# 
# addGrid(xmin=1, xmax=ncol(dataForSample), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
# 
# 
# 
# plot(
#   x=0, y=0, xlab="", ylab="", cex.sub=1.6,
#   xlim=c(-10,ncol(dataForSample)-1), ylim=c(0,nrow(dataForSample)),
#   las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
#   xaxt="n",xaxs="i",yaxs="i", yaxt="n")
# 
# text(x=rep(-2, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$SpeciesForPhylo, xpd=TRUE, cex=0.4)
# text(x=rep(-0, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$Species, xpd=TRUE, cex=0.4)
# text(x=3:ncol(dataForSample)-1.5, y=rep(nrow(dataForSample)+3, times=length(3:ncol(dataForSample))), labels=colnames(dataForSample)[3:ncol(dataForSample)], xpd=TRUE, cex=0.4, srt=45)
# 
# for(i in 1:nrow(dataForSample)){
#   for(j in 3:ncol(dataForSample)){
#     if(!is.na(dataForSample[i,j])&dataForSample[i,j]==1){
#       rect(
#         xleft=j-2,
#         xright=j-1,
#         ybottom=i-1,
#         ytop=i,
#         border="black",
#         col="black"
#       )
#     } else{
#       rect(
#         xleft=j-2,
#         xright=j-1,
#         ybottom=i-1,
#         ytop=i,
#         border="lightgrey",
#         col="lightgrey"
#       )
#     }
#   }
# }
# 
# addGrid(xmin=1, xmax=ncol(dataForSample), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)

nbPlot=4

layout(mat=t(c(1:nbPlot)), widths=rep(5, times=nbPlot), heights=c(5*nbPlot))
par(mar=c(0, 0, 3, 0), mgp=c(2, 0.5, 0), xpd=TRUE)

for(p in 1:nbPlot){
  dataForSample_rdcplot <- dataForSample[(1+(p-1)*nrow(dataForSample)/nbPlot):(1+(p)*nrow(dataForSample)/nbPlot),]
  plot(
    x=0, y=0, xlab="", ylab="", cex.sub=1.6,
    xlim=c(-10,ncol(dataForSample_rdcplot)-1), ylim=c(0,nrow(dataForSample_rdcplot)+3),
    las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
    xaxt="n",xaxs="i",yaxs="i", yaxt="n")

  text(x=rep(-5, times=nrow(dataForSample_rdcplot)), y=1:nrow(dataForSample_rdcplot)-0.5, labels=dataForSample_rdcplot$SpeciesForPhylo, xpd=TRUE, cex=1.1)
  text(x=rep(-0.5, times=nrow(dataForSample_rdcplot)), y=1:nrow(dataForSample_rdcplot)-0.5, labels=dataForSample_rdcplot$Species, xpd=TRUE, cex=1.1)
  text(x=3:ncol(dataForSample_rdcplot)-1.5, y=rep(nrow(dataForSample_rdcplot)+2, times=length(3:ncol(dataForSample_rdcplot))), labels=colnames(dataForSample_rdcplot)[3:ncol(dataForSample_rdcplot)], xpd=TRUE, cex=1.1, srt=45)

  for(i in 1:nrow(dataForSample_rdcplot)){
    for(j in 3:ncol(dataForSample_rdcplot)){
      if(!is.na(dataForSample_rdcplot[i,j])&dataForSample_rdcplot[i,j]==1){
        rect(
          xleft=j-2,
          xright=j-1,
          ybottom=i-1,
          ytop=i,
          border="black",
          col="black"
        )
      } else{
        rect(
          xleft=j-2,
          xright=j-1,
          ybottom=i-1,
          ytop=i,
          border="lightgrey",
          col="lightgrey"
        )
      }
    }
  }

  addGrid(xmin=1, xmax=ncol(dataForSample_rdcplot), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample_rdcplot), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
  #cat('\r\n\r\n') #Allows to consider plot as a new figure at each step of the loop
}

```

```{r figvariabilitydata, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Supplementary Figure. Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug. indicates the frugivory rate and Fol. indicates the folivory rate. (A) Correlation: The points depict the coefficient of correlation while the bar depicts the 95% confidence interval. Sample sizes are indicated above the upper value of the confidence interval. (B) Variability: The points depict the average of the mean ratio m of the absolute of differences with paired values; If we reduce the equation, we have $m=|(v_{1}^{2}-v_{2}^{2})|/(2v_{1}v_{2})$, where $v_{1}$ and $v_{2}$ are the two paired values from two different datasets and are different from 0. If equal $v_{1}$ and $v_{2}$ 0, then $m=0$. If $v_{1}$ or $v_{2}$ equals 0 (case for the diet rates), then we fixed $m$ to the non-null value. The bar depicts the min-max interval. Sample sizes are indicated above the max value."}

layout(mat=t(c(1,2)), widths=c(5,5), heights=c(5))
par(mar=c(4, 3, 1, 1), mgp=c(2, 0.5, 0), xpd=TRUE)

###------
### CORRELATION

#Vectors to save results
barLower <- rep(NA, times=length(colNumTest))
barUpper <- rep(NA, times=length(colNumTest))
meanCoeff <- rep(NA, times=length(colNumTest))
N <- rep(NA, times=length(colNumTest))

for (i in 1:length(colNumTest)){
  test <- #abs(as.numeric(as.character(summaryData[,colNumTest[i]])) - as.numeric(as.character(summaryData[,colNumToCompare[i]])))
    cor.test(as.numeric(as.character(summaryData[,colNumTest[i]])), 
                   as.numeric(as.character( summaryData[,colNumToCompare[i]])), method="pearson")
  barLower[i] <- test$conf.int[1]
  barUpper[i] <- test$conf.int[2]
  meanCoeff[i] <- test$estimate[1]
  N[i] <- nrow(summaryData[!is.na(summaryData[,colNumTest[i]])&!is.na(summaryData[,colNumToCompare[i]]),])
}

plot(
  x=0, y=0, xlab="", ylab="Coefficient of correlation", 
  xlim=c(0,length(meanCoeff)+1), ylim=c(0.6,1),
  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
  xaxt="n",xaxs="i",yaxs="i", yaxt="n")

addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0.6, ymax=1, yintsmall=0.025, yintbig=0.1, axisPlot=FALSE)
axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25)
addLabel(x=0.05, y=0.075, label="A", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")

#Comparison
whatCompared <- c(
  rep("Brain", times=10),
  "Hippocampus",
  "Hippocampus",
  "Hippocampus",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Cerebellum",
  "Cerebellum",
  "Cerebellum",
  "Striatum",
  rep("Body", times=6),
  "Frug.",
  "Fol."
)

#Plot legend of what is compared in coloured rectangles
whereToPlot <- as.data.frame(table(whatCompared))
whereToPlot$loc <- whereToPlot$Freq/2

colourWhatCompared <- c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")

#Colour rectangle to indicate what is compared
refLoc=0
for (i in 1:length(whatCompared)){
rect(xleft=i-1,
     xright=i,
     ybottom=0.6-0.05*0.4,#-0.05,
     ytop=0.6,#0,
     border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
     col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
     xpd=TRUE
)
errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
        xpd=TRUE)
text(x=i-0.5, y=barUpper[i]+0.015, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.6,xpd=TRUE)

if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
  refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
  if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
    segments(x0=refLoc, x1=refLoc, y0=0.6-0.025*0.4,#-0.025,
             y1=0.6-0.075*0.4,#-0.075,
             col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
    text(x=refLoc, y=0.6-0.1*0.4,#-0.1, 
         labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.4, xpd=TRUE)
  }
  else{
    text(x=refLoc, y=0.6-0.025*0.4,#-0.025, 
         labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=0.3, xpd=TRUE)
  }
  refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
}
}

###------
### VARIABILITY

#cbind(colnames(summaryData[colNumTest]), colnames(summaryData[colNumToCompare]))
#Vectors to save results
barLower <- rep(NA, times=length(colNumTest))
barUpper <- rep(NA, times=length(colNumTest))
meanCoeff <- rep(NA, times=length(colNumTest))
N <- rep(NA, times=length(colNumTest))

for (i in 1:length(colNumTest)){
  transitoryinit <- as.data.frame(cbind(as.numeric(as.character(summaryData[,colNumTest[i]])),as.numeric(as.character(summaryData[,colNumToCompare[i]]))))
  transitoryinit <- transitoryinit[!is.na(transitoryinit[,1])&!is.na(transitoryinit[,2]),]
  transitory <- apply(transitoryinit, 1, function(v){abs(v[1]**2 - v[2]**2)/2/v[1]/v[2]}) #note= (abs((v1-v2))/v1 + abs((v2-v1))/v2)/2

  #When rate is 0 for both, gives NA, so to transform to 0
  transitory[is.na(transitory)] <- 0

  transitory[!is.finite(transitory)] <- apply(transitoryinit[!is.finite(transitory),], 1, max)

  barLower[i] <- min(transitory)
  barUpper[i] <- max(transitory)
  meanCoeff[i] <- mean(transitory)
  N[i] <- length(transitory)
}

ymax <- round((barUpper)/10)*10

plot(
  x=0, y=0, xlab="", ylab="Variability", 
  xlim=c(0,length(meanCoeff)+1), ylim=c(0,1),
  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
  xaxt="n",xaxs="i",yaxs="i", yaxt="n")

addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
addLabel(x=0.05, y=0.075, label="B", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")

#Comparison
whatCompared <- c(
  rep("Brain", times=10),
  "Hippocampus",
  "Hippocampus",
  "Hippocampus",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Neocortex",
  "Cerebellum",
  "Cerebellum",
  "Cerebellum",
  "Striatum",
  rep("Body", times=6),
  "Frug.",
  "Fol."
)
#Plot legend of what is compared in coloured rectangles
whereToPlot <- as.data.frame(table(whatCompared))
whereToPlot$loc <- whereToPlot$Freq/2

colourWhatCompared <- c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")

#Colour rectangle to indicate what is compared
refLoc=0
for (i in 1:length(whatCompared)){
  rect(xleft=i-1,
       xright=i,
       ybottom=-0.05,
       ytop=0,
       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
       xpd=TRUE
  )
  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
         xpd=TRUE)
  text(x=i-0.5, y=barUpper[i]+0.05, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.6,xpd=TRUE)

  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
      segments(x0=refLoc, x1=refLoc, y0=-0.025,
               y1=-0.075,
               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
      text(x=refLoc, y=-0.1, 
           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.4, xpd=TRUE)
    }
    else{
      text(x=refLoc, y=-0.025, 
           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=0.3, xpd=TRUE)
    }
    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
  }
}

```

```{r figcomparison, include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap=paste("Supplementary Figure. Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2, "% threshold. ", geographicThresholdVector[2]/2, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2], "%. ", geographicThresholdVector[2], "% was chosen as the maximum because based on current observations, a species occupied at best three different biogeographic areas.", sep="")}

plot(
  x=0, y=0, xlab="Overlap threshold", ylab="Variation percent (relative to 15%)", 
  xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
  xaxt="n",xaxs="i",yaxs="i", yaxt="n")

addGrid(xmin=5/100, xmax=30/100, xintsmall=2.5/200, xintbig=5/100, ymin=0, ymax=0.4, yintsmall=0.01, yintbig=0.1, axisPlot=FALSE)
axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=1, tcl=-0.25)
axis(side=1, at=thresholdPresenceRange, labels=thresholdPresenceRange, las=1, tcl=-0.25)

points(x=thresholdPresenceRange, y=howManyDifferent, pch=19, xpd=TRUE)
lines(x=thresholdPresenceRange, y=howManyDifferent)

```

### 2021-05-10 Scripts/Analysis1_competitionsignal/BioGeoBEARSRun.R
Initialise all files for github

@@ -1,0 +1,129 @@
+####---------------------------------
+#### BioGeoBearsRun
+####---------------------------------
+
+# This script allows to fit the biogeobears algorithm to primate ranging data given different threshold to consider that a primate species initially belong to a biogeography area.
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+load("REnvironments/geography_traits.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+##--------
+
+##--------
+#Libraries
+
+#Phylogeny
+library(caper)
+library(MCMCglmm)
+library(RPANDA)
+library(BioGeoBEARS)
+library(phytools)
+library(ape)
+library(geiger)
+library(optimix)
+
+##--------
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+##----
+##Run the biogeobears for speeding up after
+
+##--
+# THE TREE
+
+#Phylogenetic tree: force it to be ultrametric, problem was minor because doesn't change branch length actually
+# phylo_all <-read.nexus("Raw_data/Tree/TreeBlock_10kTrees_Primates_Version3.nex")
+# phylo_init <- phylo_all[[e]]
+
+phylo_all <-read.nexus("Raw_data/Tree/consensusTree_10kTrees_Primates_Version3.nex")
+phylo_init <- phylo_all
+
+phylo <- force.ultrametric(tree=phylo_init, method="extend")#method="nnls")
+is.ultrametric(phylo)
+
+#check if this differ (was done outside the loop and was ok)
+plot(phylo_init$edge.length, phylo$edge.length, xlab="Original tree", ylab="Post-chronos tree", pch=20, bty="n")
+abline(a=0, b=1, col="gray", lwd=0.5)
+
+phylo <- multi2di(phylo)
+is.binary(phylo)
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/DataCleaning.R

@@ -1,0 +1,1058 @@
+####---------------------------------
+#### EvolutionaryHistoryAnalysis
+####---------------------------------
+
+# This script allows pre-processing necessary data for conducting the meta analysis on primate brain size.
+# It will merge, clean, and adjust data relative to 1) primate biogeography (from the IUCN) and 2) data relative to brain size and other attributes (e.g. diet, body mass)
+
+# It is divided into several parts (to be completed):
+
+#1) Ranging data
+#2) Brain data
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+##--------
+
+##--------
+#Libraries
+
+#Plot
+library(RColorBrewer)
+library(tidyr)
+library(stringr)
+library(svMisc)
+library(plotrix)
+library(circlize)
+
+#Spatial
+library(rworldmap) # World map
+library(cleangeo) #to clean it otherwise issues with intersection
+library(maps)
+library(rgeos) #for readOGR; gArea/gCentroid...
+library(sf) #for intersection
+library(rgdal)
+library(geosphere)
+
+#Phylogenetics
+library(caper)
+library(MCMCglmm)
+library(RPANDA)
+library(BioGeoBEARS)
+library(phytools)
+library(ape)
+library(geiger)
+library(optimix)
+
+#Parallelizing
+library(snow)
+library(foreach)
+library(doParallel)
+
+##--------
+
+
+####------------------
+## ANALYSIS
+####------------------
+
+##////
+# Data preparation
+##////
+
+#####
+## Primate ranging
+####
+areaName <- c("Madagascar_east", "Madagascar_west", "Africa_west", "Africa_central", "Africa_south_east", 
+              "America_central", "America_south_north", "America_south_south", 
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryAnalysis.R

@@ -1,0 +1,1654 @@
+####---------------------------------
+#### EvolutionaryHistoryAnalysis
+####---------------------------------
+
+# This script allows processing the result of the estimation with different evolutionary scenario of primate brain size evolution. It is still in construction and is therefore a huge mess.
+
+# It is divided into several parts (to be completed):
+
+#1) Creation of the map and phylogenetic interaction tree
+#2) Creation of the brain + raw data figure
+#3) Creation of the model fit figure
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+##--------
+
+##--------
+#Libraries
+
+#Plot
+library(RColorBrewer)
+library(tidyr)
+library(stringr)
+library(svMisc)
+library(plotrix)
+library(circlize)
+
+#Spatial
+library(rworldmap) # World map
+library(cleangeo) #to clean it otherwise issues with intersection
+library(maps)
+library(rgeos) #for readOGR; gArea/gCentroid...
+library(sf) #for intersection
+library(rgdal)
+library(geosphere)
+
+#Phylogenetics
+library(caper)
+library(MCMCglmm)
+library(RPANDA)
+library(BioGeoBEARS)
+library(phytools)
+library(ape)
+library(geiger)
+library(optimix)
+
+#Parallelizing
+library(snow)
+library(foreach)
+library(doParallel)
+
+##--------
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###----------------------
+## Plotting results of phylogenetic history
+###----------------------
+
+tree <-read.nexus("Raw_data/Tree/TreeBlock_10kTrees_Primates_Version3.nex")
+tree <- tree[[1]]
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R

@@ -1,0 +1,809 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+ 
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
+# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+load("geography_traits_biogeobears.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+
+##--------
+
+##--------
+#Libraries
+
+#Phylogenetics
+library(caper)
+library(ape)
+library(phytools)
+library(geiger)
+library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#??
+library(ellipsis)
+
+#Parallelizing
+# library(snow)
+# library(foreach)
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2.R

@@ -1,0 +1,801 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
+# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+load("geography_traits_biogeobears.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+
+##--------
+
+##--------
+#Libraries
+
+#Phylogenetics
+library(caper)
+library(ape)
+library(phytools)
+library(geiger)
+library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#??
+library(ellipsis)
+
+#Parallelizing
+# library(snow)
+# library(foreach)
+# library(doParallel)
+library(parallel)
+
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1.R

@@ -1,0 +1,801 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
+# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+load("geography_traits_biogeobears.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+
+##--------
+
+##--------
+#Libraries
+
+#Phylogenetics
+library(caper)
+library(ape)
+library(phytools)
+library(geiger)
+library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#??
+library(ellipsis)
+
+#Parallelizing
+# library(snow)
+# library(foreach)
+# library(doParallel)
+library(parallel)
+
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2.R

@@ -1,0 +1,809 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
+# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+load("geography_traits_biogeobears.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+
+##--------
+
+##--------
+#Libraries
+
+#Phylogenetics
+library(caper)
+library(ape)
+library(phytools)
+library(geiger)
+library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#??
+library(ellipsis)
+
[…]

### 2021-05-10 Scripts/Analysis2_competitiondirection/PGLSdirectionSelection.R

@@ -1,0 +1,885 @@
+####---------------------------------
+#### PGLSdirectionSelection
+####---------------------------------
+
+# This script allows to perform PGLS analysis to assess the correlation of brain size with spatial co-occurrence data, specifically in areas for which competitive models were shown to fit the best.
+
+# THIS IS STILL IN PROGRESS; FURTHER CLEANING/COMPLETION NEEDED
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+load("Data_spatial_primate.RData")
+load("geography_traits.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/diagnostic_fcns.R")
+
+##--------
+
+##--------
+#Libraries
+
+library(ape)
+library(phylolm)
+library(phytools)
+library(caper)
+
+##--------
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+################
+# Fitting linear models
+
+#####---------------
+#Fixing data
+#####---------------
+
+summaryData$Family<- NA
+summaryData$DietaryGuild <- NA
+summaryData$FrugivoryPercent <- NA
+summaryData$FolivoryPercent <- NA
+summaryData$Brain <- NA
+summaryData$Neocortex <- NA 
+summaryData$Cerebellum <- NA
+summaryData$Hippocampus <- NA
+summaryData$Striatum <- NA
+summaryData$MOB <- NA 
+summaryData$Optic.Tract <- NA 
+summaryData$Bodymass <- NA
+
+for(i in 1:nrow(summaryData)){
+  #Frugivory 
+  value <- max(c(summaryData$Diet_frug_powell[summaryData$Species_abbrv==summaryData$Species_abbrv[i]],
[…]

### 2021-05-10 Scripts/Analysis2_competitiondirection/SpatialProcessingSympatry.R

@@ -1,0 +1,378 @@
+####---------------------------------
+#### SpatialProcessingSympatry
+####---------------------------------
+
+# This script allows processing the IUCN data to investigate (1) number of sympatric species (2) average overlap. It will save the environment but also create an output txt file.
+
+# Note to discuss with Benoit: on a MAD team meeting where Sophie Monsarrat presented her work, she spoke about the Phylocine database that allowed to consider reconstructed ranging data so to avoid biases with recent extinction/ range shrinkage.
+# Worth checking?
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+load("REnvironments/geography_traits.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+##--------
+
+##--------
+#Libraries
+
+#Phylogeny
+library(ape)
+
+#Plot
+library(stringr)
+library(svMisc)
+
+#Spatial
+library(rgdal)
+library(raster)
+library(rgeos)
+library(cleangeo) #to clean it otherwise issues with intersection
+
+##--------
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+#diet table
+resultsDiet <- matrix(NA, ncol=90, nrow=nrow(summaryData))
+
+frugivoryThresholdVector <- seq(from=10, to=30, by=10)
+folivoryThresholdVector <- seq(from=50, to=70, by=10)
+
+for(a in 1:length(frugivoryThresholdVector)){
+  
+  frugivoryThreshold=frugivoryThresholdVector[a]
+  
+  for(b in 1:length(folivoryThresholdVector)){
+    
+    folivoryThreshold=folivoryThresholdVector[b] 
+    
+    for( r in 1:10){
+      for(i in 1:nrow(summaryData)){
+        #Frugivory 
[…]

### 2021-05-10 Scripts/Analysis3_diversification/diversification/script_ClaDS_f67.jl

@@ -1,0 +1,56 @@
+##/usr/local/src/julia-1.4.2/bin/julia
+
+cd("/users/biodiv/bperez/appli/ClaDS_Julia/")
+
+import Pkg
+Pkg.add("RCall") 
+Pkg.add("RDatasets")
+Pkg.add("StatsBase")
+Pkg.add("Distributions")
+Pkg.add("BenchmarkTools")
+Pkg.add("JLD2")
+Pkg.add("DataFrames")
+Pkg.add("DataFramesMeta")
+Pkg.add("CSV")
+
+using DataFrames
+using RCall
+using DataFramesMeta
+using CSV
+
+cd("/users/biodiv/bperez/appli/ClaDS_Julia/")
+
+include("/users/biodiv/bperez/appli/ClaDS_Julia/load_ClaDS2_functions.jl")
+
+cd("/users/biodiv/bperez/data/others/Benji/diversification/")
+
+R"library(RPANDA)"
+
+
+name="primate_complete"
+
+@rput name
+
+
+# assume 504 species based on https://advances.sciencemag.org/content/3/1/e1600946/tab-pdf
+# sampling fraction 367/504
+
+
+R"tree <- read.tree(paste0('tree_',name,'.tre'))"
+
+
+@rget tree     #load it in Julia
+tree = ape2Tree(tree)    # and make it a Julia Tree
+
+Random.seed!(813)
+n_iter = 400
+
+sample_fraction = 0.67
+sampler = run_ClaDS2(tree, n_iter,plot_tree = 0,
+    print_state = Int64(n_iter/4), plot_chain = false,
+    f=sample_fraction, ltt_steps = 250)
+
+sampler_to_Rdata(tree, sampler, join(["ClaDS2_tree_", name, "_f67.Rdata"]) ; sample_fraction = sample_fraction, max_it_number = 2_500)
+result = (tree, sampler, sample_fraction)
+@save join(["ClaDS2_tree_", name, "_f67.jld2"]) result
+

### 2021-05-10 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R

@@ -1,0 +1,491 @@
+
+##################  Step 1: Prepare primate tree ###################################################
+
+# from Dos Reis 2018
+# set the MRCA at 74 Myr 
+
+library(ape)
+
+setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/diversification/")
+
+tree <- read.tree("host_tree_primate_complete.tre")
+
+tree$edge.length <- tree$edge.length/max(node.depth.edgelength(tree))*74
+
+plot(tree)
+tree <- ladderize(tree)
+
+tree$edge.length
+tree$tip.label
+
+is.binary(tree)
+is.rooted(tree)
+is.ultrametric(tree)
+
+write.tree(tree, "tree_primate_complete.tre")
+
+
+# run using Julia on the cluster
+
+
+##################  Step 2: Results ClaDS ###################################################
+
+rm(list=ls())
+
+library(RPANDA)
+library(coda)
+
+plot_ClaDS_phylo <- function (phylo, rates, rates2 = NULL, same.scale = T, main = NULL, lwd = 2, log = T, show.tip.label = F, ...) {
+  Colors = colorRampPalette(c("steelblue2", "paleturquoise3", 
+                              "palegreen2", "yellow2", "salmon1", "darkorange", "red", 
+                              "red4"))(100)
+  if (is.null(rates2)) {
+    if (log) 
+      rates = log(rates)
+    if (isTRUE(all.equal(rep(as.numeric(rates[1]), length(rates)), 
+                         as.numeric(rates)))) {
+      col = rep(1, length(rates))
+      plot(phylo, edge.color = Colors[col], show.tip.label = show.tip.label, 
+           main = main, edge.width = lwd, ...)
+      if (log) {
+        fields::image.plot(z = c(exp(rates[1]), 2 * exp(rates[1])), 
+                           col = Colors, horizontal = T, legend.only = T)
+      }
+      else {
+        fields::image.plot(z = c(rates[1], 2 * rates[1]), col = Colors, 
+                           horizontal = T, legend.only = T)
+      }
+    }
+    else {
+      col = round((rates - min(rates))/diff(range(rates)) * 
+                    99) + 1
+      plot(phylo, edge.color = Colors[col], show.tip.label = show.tip.label, 
+           main = main, edge.width = lwd, ...)
+      if (log) {
+        min = min(rates)
+        max = max(rates)
+        m10 = floor(min/log(10))
+        M10 = ceiling(max/log(10))
[…]

### 2021-05-10 Scripts/Analysis3_diversification/script_diversification_primates.R

@@ -1,0 +1,502 @@
+
+
+####---------------------------------
+#### PGLSdirectionSelection
+####---------------------------------
+
+# This script allows to fit diversification analysis (i.e. checking whether the evolutionary rate change with clades) based on the ClaDS algorithm.
+# It is divided into three parts:
+
+#1) Preparing the phylogenetic tree 
+#2) Running the ClaDS algorithm
+#3) Visual summarization 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+##################  Step 1: Prepare primate tree ###################################################
+
+# from Dos Reis 2018
+# set the MRCA at 74 Myr 
+
+###Set working directory
+setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/diversification/")
+
+library(ape)
+
+tree <- read.tree("host_tree_primate_complete.tre")
+
+tree$edge.length <- tree$edge.length/max(node.depth.edgelength(tree))*74
+
+plot(tree)
+tree <- ladderize(tree)
+
+tree$edge.length
+tree$tip.label
+
+is.binary(tree)
+is.rooted(tree)
+is.ultrametric(tree)
+
+write.tree(tree, "tree_primate_complete.tre")
+
+# run using Julia on the cluster
+
+##################  Step 2: Results ClaDS ###################################################
+
+rm(list=ls())
+
+library(RPANDA)
+library(coda)
+
+plot_ClaDS_phylo <- function (phylo, rates, rates2 = NULL, same.scale = T, main = NULL, lwd = 2, log = T, show.tip.label = F, ...) {
+  Colors = colorRampPalette(c("steelblue2", "paleturquoise3", 
+                              "palegreen2", "yellow2", "salmon1", "darkorange", "red", 
+                              "red4"))(100)
+  if (is.null(rates2)) {
+    if (log) 
+      rates = log(rates)
+    if (isTRUE(all.equal(rep(as.numeric(rates[1]), length(rates)), 
+                         as.numeric(rates)))) {
+      col = rep(1, length(rates))
+      plot(phylo, edge.color = Colors[col], show.tip.label = show.tip.label, 
+           main = main, edge.width = lwd, ...)
+      if (log) {
[…]

### 2021-05-10 Scripts/Functions.R

@@ -1,0 +1,971 @@
+####---------------------------------
+#### Function script
+####---------------------------------
+
+
+# This script resumes the necessary functions for running the meta-analyses to investigate whether between species competition (direct or indirect), exploitation or cooperation better describe evolutionary scenarios of brain size evolution.
+# It includes:
+
+##---
+#runBioGeoBearsandBSM_DEC
+
+# This function allows to run the BioGeoBears algorithm (version DEC) so as to compute the history of primate biogeography
+
+##---
+#runComparisonModelsCompetition
+
+# Runs the different evolutionary models excluding for competition (BM, OU, EB), or including competition (MC, DDlin, DDexp)
+
+##---
+#cleanTree
+
+# Allows cleaning tree (looking for abnormalities with branch length, etc...)
+
+
+##------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
+runBioGeoBearsandBSM_DEC <- 
+  function(
+    ###################
+    ## Run the BioGeoBears analysis followed by stocchastic mapping as described in http://phylo.wikidot.com/biogeobears#script. It uses the DEC algotrithm, non-stratified. This can be freely adapted to DEC+J etc...
+    ###################
+    
+    pathToTree,
+    pathToGeo,
+    maxCooccurrenceGeo,
+    mapNumber,
+    coreNumber,
+    pathToSaveRdata,
+    pathToSaveFigureGeo,
+    pathToBSMMapList,
+    pathToBSMoutput,
+    pathToFileStockingPdfForBSMAnalysis
+  ){
+
+#######################################################
+# Installing BioGeoBEARS
+#######################################################
+
+# Install optimx
+#install.packages("optimx", dependencies=TRUE, repos="http://cran.rstudio.com")
+library(optimx)
+
+# Also get snow (for parallel processing)
+#install.packages("snow")
+library(snow)
+
+# Install phylobase
+#install.packages("phylobase", dependencies=TRUE, repos="http://cran.rstudio.com")
+
+library(devtools)
+#Intasll BioGeoBEARS:
+#devtools::install_github(repo="nmatzke/BioGeoBEARS")
+
+#Load necessary libraries
+library(rexpokit)
+library(cladoRcpp)
+library(BioGeoBEARS)
+# Load the package (after installation, see above).
+library(GenSA)    # GenSA is better than optimx (although somewhat slower)
[…]

### 2021-05-10 Scripts/OLD/Data_analysis_main_updated_occurrence.R

@@ -1,0 +1,3433 @@
+# install.packages(c("RColorBrewer",
+# "rworldmap",
+# "cleangeo",
+# "rgdal",
+# "ape",
+# "stringr",
+# "svMisc",
+# "rgeos",
+# "tidyr",
+# "RPANDA",
+# "ape",
+# "caper",
+# "MCMCglmm",
+# "phytools",
+# "BioGeoBEARS",
+# "geosphere"), dependencies=TRUE)
+
+
+###
+#Libraries
+#Plot
+library(RColorBrewer)
+library(tidyr)
+library(stringr)
+library(svMisc)
+library(plotrix)
+library(circlize)
+#Spatial
+library(rworldmap) # World map
+library(cleangeo) #to clean it otherwise issues with intersection
+library(maps)
+library(rgeos) #for readOGR; gArea/gCentroid...
+library(sf) #for intersection
+library(rgdal)
+library(geosphere)
+#Phylogenetics
+library(caper)
+library(MCMCglmm)
+library(RPANDA)
+library(BioGeoBEARS)
+library(phytools)
+library(ape)
+library(geiger)
+library(optimix)
+#Parallelizing
+library(snow)
+library(foreach)
+library(doParallel)
+###
+
+
+###
+#Functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+
+#Capitalize first letter
+firstup <- function(x) {
+  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
+  x
+}
+###
+
+
+####------------------
+## ANALYSIS
+####------------------
+
+
+##////
+# Data preparation
+##////
+
+#####
+## Primate ranging
+####
+areaName <- c("Madagascar_east", "Madagascar_west", "Africa_west", "Africa_central", "Africa_south_east", 
+              "America_central", "America_south_north", "America_south_south", 
+              "Asia_west", "Asia_central_east",  "Asia_south", "Asia_island")
+ 
+
+colourArea <- brewer.pal(n = 12, name="Paired")
+
+#Select only the terrestrial area, because was roughly drawn with google earth
[…]

### 2021-05-10 Scripts/OLD/Rscript.R

@@ -1,0 +1,4097 @@
+
+areaName <- c("Madagascar_east", "Madagascar_west", "Africa_west", "Africa_central", "Africa_south_east", 
+              "America_central", "America_south_north", "America_south_south", 
+              "Asia_west", "Asia_central_east",  "Asia_south", "Asia_island")
+ 
+library(RColorBrewer)
+colourArea <- brewer.pal(n = 12, name="Paired")
+
+#Select only the terrestrial area, because was roughly drawn with google earth
+
+#+Note the shapefile were transformed from kml using: https://products.aspose.app/gis/conversion/kml-to-shapefile
+
+library(rworldmap) # World map 
+worldMap <- getMap()
+library(cleangeo) #to clean it otherwise issues with intersection
+worldMap = clgeo_Clean(worldMap)
+
+library(rgeos) #for readOGR; gArea/gCentroid...
+library(sf) #for intersection
+library(rgdal)
+centroid <- matrix(NA, ncol=2, nrow=length(areaName))
+for(i in 1:length(areaName)){
+  areaTransitory <- readOGR(dsn=paste("T:/IUCN_data_primate/Geographic_areas/Shapefiles/",areaName[i],".shp",sep=""))
+  areaTransitory = clgeo_Clean(areaTransitory)
+  areaTransitory <- spTransform(areaTransitory, CRS(proj4string(worldMap)))
+  areaTransitory <- gIntersection(areaTransitory, worldMap)
+  assign(paste("area", i, sep="_"), areaTransitory)
+  if(i==1){
+    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] + 5, summary(areaTransitory)$bbox[2,1]) 
+  }
+  else if (i==2){
+    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] - 5, summary(areaTransitory)$bbox[2,1] - 5) 
+  }
+  else{
+    centroid[i,] <- gCentroid(areaTransitory)@coords
+  }
+}
+warnings()
+
+
+#Create the map of the geographic area
+
+#Have background
+library(maps)
+map("world", fill=TRUE, col="lightgray", bg="white", border=NA, ylim=c(-60, 50))
+
+for(i in 1:length(areaName)){
[…]

### 2021-05-10 Scripts/OLD/Script_for_cluster_run.R

@@ -1,0 +1,522 @@
+##############################
+## BRAIN EVOLUTIONARY HISTORY
+##############################
+
+#---------------------------------
+##This part only runs the (non-)competitive models of brain size evolution in frugivorous primates.
+#---------------------------------
+
+setwd("//10.8.4.232/shared-2/robira/Metaanalysescognition/Evolutionary_history")
+
+###----
+##Load data
+
+load("geography_traits_biogeobears.RData")
+
+##-----
+## Run the different evolutionary models
+
+for(a in 1:length(frugivoryThresholdVector)){
+  
+  frugivoryThreshold=frugivoryThresholdVector[a]
+  
+  for(b in 1:length(folivoryThresholdVector)){
+    
+    folivoryThreshold=folivoryThresholdVector[b] 
+    
+    for(c in 1:length(geographicThresholdVector)){
+      
+      ###------------------
+      ##Adding the co-occurence
+      ###------------------
+      
+      summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
+      
+      load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
+      
+      ##--------
+      #for(e in 1:numberTrees){
+      
+      #Parallelizing loop
+      
+      #for(d in 1:randomSampling){
+      cores=detectCores()
+      cl <- makeCluster(cores[1]-2) #not to overload your computer
+      registerDoParallel(cl)
+      foreach(d=1:randomSampling#, .packages=c('caper',
+              #'RPANDA',
+              #'BioGeoBEARS',
+              #'phytools',
+              #'ape',
+              #'phytools')
+              ) %dopar% {
+                
+                setwd("//10.8.4.232/shared-2/robira/Metaanalysescognition/Evolutionary_history")
+                number= (a-1)*randomSampling + (b-1)*randomSampling + (c-1)*randomSampling + d-1
+                
+                #Source functions & packages
+                
+                ###
+                #Functions
+                #To source all phylogenetics functions (biogeobears + models of evolution)
+                source("//10.8.4.232/shared-2/robira/Metaanalysescognition/Evolutionary_history/Functions.R")
+                
+                #My toolkit
+                source("//10.8.4.232/shared-2/robira/Metaanalysescognition/Evolutionary_history/toolbox.R")
+                
[…]

### 2021-05-10 Scripts/OLD/Script_jonathan_drury.R

@@ -1,0 +1,125 @@
+########################################################################################################################################
+#                                                  SCRIPT FOR JONATHAN DRURY
+########################################################################################################################################
+
+#This scripts will lead to the error as encountered. Further details below.
+
+##---------------
+##NOTE
+
+#To make the script work, load the result of the biogeobears (BSM_output_file.RData)
+#Run the simmap
+#Run the function for evolutionary models. The error that will be printed is mine: it will indicate which model failed. I provide another file "function_RPANDA", where I copied
+#functions from RPANDA to track down the error. These functions include the corrections I have mentioned in my first email.
+
+##--------------
+
+##--------------
+## Libraries
+library(caper)
+library(phytools)
+library(BioGeoBEARS)
+library(RPANDA)
+##--------------
+
+##--------------
+##Functions
+
+#To: run biogeobears, clean trees, run evolutionary models
+source("Functions.R")
+
+##--------------
+
+##--------------
+## Environments
+
+#Biogeobearsoutput
+load("BSM_output_file2.Rdata")
+##--------------
+
+##--------------
+#Load data table (reduced for including only variables of interest, so as to be the clearest possible. Please email me for further details.
+
+data.df <- read.delim("table_data_rdc_jonathan_drury.txt")
+
+
+##------------------------------------------------------------------------------------------------
+
+################
+## ANALYSIS
+################
+
+##--------------
+#Run simmap
+
+#data vector
+vectorDiet <-  data.df$Guild
+names(vectorDiet) <-  data.df$SpeciesForPhylogeny
+vectorDiet <- vectorDiet[vectorDiet!="Other"&!is.na(data.df$geographicCode)]
+
+# #Load and save tree corresponding to species with diet
+# phylo_all <-read.nexus("consensusTree_10kTrees_Primates_Version3.nex")
+# phylo_init <- phylo_all
+# 
+# #ultrametric?
+# phylo <- force.ultrametric(tree=phylo_init, method="extend")#method="nnls")
+# is.ultrametric(phylo)
[…]

### 2021-05-10 Scripts/OLD/function_RPANDA.R

@@ -1,0 +1,616 @@
+
+
+full.phylo=tree
+ana.events=ana_events_tables[[i]]
+clado.events=clado_events_tables[[i]]
+stratified=FALSE
+map=group.map2
+data=M
+trim.class=subgroup
+model="MC"
+par=NULL
+method="Nelder-Mead"
+bounds=NULL
+
+
+fit_t_comp_subgroup<-function(full.phylo,ana.events,clado.events,stratified=FALSE,map,data,trim.class,model=c("MC","DDexp","DDlin"),par=NULL,method="Nelder-Mead",bounds=NULL){
+  
+  if(is.null(names(data))){stop("data missing taxa names")}
+  if(!is.null(dim(data))){stop("data needs to be a single trait")}
+  is_tip <- full.phylo$edge[,2] <= length(full.phylo$tip.label)
+  if(sum(diff(full.phylo$edge[is_tip, 2])<0)>0){ stop('fit_t_comp_subgroup cannot be used with ladderized full.phylogenies')}
+  
+  if(is.null(bounds[["lower"]]) & is.null(bounds[["upper"]])){
+    bounds$lower = -Inf
+    bounds$upper = Inf
+  }
+  
+  GeoByClassObject<-CreateGeobyClassObject(full.phylo,map,trim.class,ana.events,clado.events,stratified=stratified)
+  
+  phylo<-GeoByClassObject$map
+  
+  root.trimmed.phylo<-max(nodeHeights(phylo))
+  root.data<-max(nodeHeights(drop.tip.simmap(phylo,phylo$tip.label[which(!phylo$tip.label%in%names(data))])))
+  
+  if(round(root.trimmed.phylo,5)!=round(root.data,5)){stop("error where root of trimmed simmap and root of target clade don't match")}
+  #if this above error is triggered, need to use scripts written by JPD using JC mvMORPH approach in summer 2018
+  
+  if(!is.null(phylo$node.label)){phylo$node.label<-NULL}
+  geo.object<-GeoByClassObject$geo.object
+  #geo.sorted<-.resortGeoObject(phylo,geo.object) 
+  
+  if(length(geo.object$geography.object)<phylo$Nnode){stop("geography object cannot have more or fewer components than internode intervals in phylo")}
+  if(length(data)>length(phylo$tip.label)){stop("error: some tips missing from pruned simmap")}
[…]

### 2021-05-10 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R
Update EvolutionaryHistoryClusterRun_a1b1.R

@@ -366,7 +366,6 @@ for(c in 1:length(geographicThresholdVector)){
     
     summaryData <- summaryData_init 
     
-    number= (a-1)*randomSampling*4 + (b-1)*randomSampling*2 + (c-1)*randomSampling + d-1
     
     #Source functions & packages
     

### 2021-05-11 Article/Article.Rmd
Correct typos in script/redaction

@@
  #      - '--lua-filter=author-info-blocks.lua'
- bookdown::pdf_book:
- #bookdown::word_document2:
+ #bookdown::pdf_book:
+ bookdown::word_document2:
    number_sections: false
@@
 #Load environments
-load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Data_spatial_primate.RData")
-load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/geography_traits_biogeobears.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsData_spatial_primate.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsgeography_traits_biogeobears.RData")
 

### 2021-05-11 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2.R

@@ -358,8 +358,6 @@ for(c in 1:length(geographicThresholdVector)){
     
     summaryData <- summaryData_init 
     
-    number= (a-1)*randomSampling*4 + (b-1)*randomSampling*2 + (c-1)*randomSampling + d-1
-    
     #Source functions & packages
     
     #Capitalize first letter

### 2021-05-11 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2.R

@@ -366,8 +366,6 @@ for(c in 1:length(geographicThresholdVector)){
     
     summaryData <- summaryData_init 
     
-    number= (a-1)*randomSampling*4 + (b-1)*randomSampling*2 + (c-1)*randomSampling + d-1
-    
     #Source functions & packages
     
     #Capitalize first letter

### 2021-05-11 Scripts/Analysis3_diversification/script_diversification_primates.R

@@ -1,5 +1,3 @@
-
-
 ####---------------------------------
 #### PGLSdirectionSelection
 ####---------------------------------

### 2021-05-12 Article/Article.Rmd
Update after rerun biogeobears due to data loss - new download 10kTrees

@@
 citeR(
-bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticle.bib",
-bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticlepackage.bib",
+bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticle.bib",
+bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticlepackage.bib",
 rgeos,
@@
 #Load environments
-load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsData_spatial_primate.RData")
-load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsgeography_traits_biogeobears.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/Data_spatial_primate.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/geography_traits_biogeobears.RData")
 
@@
 
-  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)
+  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)
 
@@
 
-We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 28/01/2020, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses.
+We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses.
 The trees contain `r length(phylo_init$tip.label)` primate species.
@@
 #Import data
-summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
+summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
 
 #Tree
-tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Tree/Tree_diet.nex")
+tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
 

### 2021-05-12 Scripts/Analysis1_competitionsignal/DataCleaning.R

@@ -19,7 +19,7 @@ rm(list=ls())
 ##--------
 #Home made functions
 #To source all phylogenetics functions (biogeobears + models of evolution)
-source("~/PhD/Meta_analysis/Cognition_metaanalysis/Functions.R")
+source("Scripts/Functions.R")
 
 #My toolkit
 source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
@@ -129,7 +129,7 @@ speciesGeo <- gsub(" ", "_",  speciesGeo)
 
 #Extract name of phylogeny
 
-treeForName <-read.nexus("~/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Tree/consensusTree_10kTrees_Primates_Version3.nex")
+treeForName <-read.nexus("/Raw_data/Tree/consensusTree_10kTrees_Primates_Version3.nex")
 speciesLabels <-  as.data.frame(treeForName$tip.label)
 
 #Determine the belonging geographic area based on overlap
@@ -362,48 +362,48 @@ lines(x=thresholdPresenceRange, y=howManyDifferent)
 
 options(warn=1)
 #Powell
-Data_powell <- read.delim("~/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Powell/Data_powell.txt")
-Data_powell_mosaic <- read.delim("~/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Powell/Data_powell_mosaic.txt")
-Data_powell2 <- read.delim("~/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Powell/Data_powell2.txt")
+Data_powell <- read.delim("Raw_data/Powell/Data_powell.txt")
+Data_powell_mosaic <- read.delim("Raw_data/Powell/Data_powell_mosaic.txt")
+Data_powell2 <- read.delim("Raw_data/Powell/Data_powell2.txt")
 Data_powell2<- Data_powell2[Data_powell2$MSW05_Order=="Primates",]
 
 #Todorov
-Data_todorov <-  read.delim("~/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Todorov/data.txt")
+Data_todorov <-  read.delim("Raw_data/Todorov/data.txt")
 
 #Willems
[…]

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R

@@ -366,10 +366,6 @@ for(c in 1:length(geographicThresholdVector)){
     
     summaryData <- summaryData_init 
     
-<<<<<<< HEAD
-=======
-    
->>>>>>> b7ad3650c1b4a01e06b3753dfd32c2f755841d78
     #Source functions & packages
     
     #Capitalize first letter

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R
minor

@@ -17,7 +17,7 @@
 ###Set working directory
 # scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
 # setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
-setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
 dir.create(file.path("extdata"), showWarnings = FALSE)
@@ -30,7 +30,7 @@ load("geography_traits_biogeobears.RData")
 ##--------
 #Home made functions
 #To source all phylogenetics functions (biogeobears + models of evolution)
-source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+source("Functions.R")
 
 ##--------
 
@@ -805,3 +805,4 @@ for(c in 1:length(geographicThresholdVector)){
 ##--
 ## Saving environment
 save.image("geography_trait_models1.RData")
+

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1.R

@@ -9,7 +9,7 @@
 ###Set working directory
 # scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
 # setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
-setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
 dir.create(file.path("extdata"), showWarnings = FALSE)
@@ -22,7 +22,7 @@ load("geography_traits_biogeobears.RData")
 ##--------
 #Home made functions
 #To source all phylogenetics functions (biogeobears + models of evolution)
-source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+source("Functions.R")
 
 ##--------
 

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2.R

@@ -17,7 +17,7 @@
 ###Set working directory
 # scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
 # setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
-setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
 dir.create(file.path("extdata"), showWarnings = FALSE)
@@ -30,7 +30,7 @@ load("geography_traits_biogeobears.RData")
 ##--------
 #Home made functions
 #To source all phylogenetics functions (biogeobears + models of evolution)
-source("/users/biodiv/bperez/data/others/Benji/Evolutionary_history//Functions.R")
+source("Functions.R")
 
 ##--------
 

### 2021-05-12 toolbox.R
Toolbox addition // update biogeobears

@@ -1,0 +1,1045 @@
+#########################
+## TOOLBOX
+#########################
+
+##What is it?
+
+#This toolbox gathers many handmade functions (of my own, or burrowed, and potentially modified from the Internet!) that were created because repeatedly used. 
+#Note that I have plenty of others linked to movement analyses specifically (in case you need).
+#How each function work is described, please enjoy!
+
+
+## OH NO! :( AN ERROR!
+#Found a mistake or an error? I am sad (really, this is my highest fright), and I truly hope this is no big deal. 
+#Please contact me at benjamin.robira@normalesup.org so we can solve it together!
+
+##--------------------------------------------------
+#Function list:
+
+##----
+###Data processing
+##----
+#firstup
+#as.numcharac
+#'%nin%'
+#getmode 
+#cbind.fill
+
+##----
+###P-value related
+##----
+#pvalueToText
+#pvalueRound 
+#textTestOneVar
+#textEstOneVar
+#roundIntelligent
+
+##----
+###Linear models
+##----
+#reportGamSmooth
+#mainResults
+#stabResults 
+#diagnostics.plot.dharma
+
+##----
+###Graphic related
+##----
+#addImg
+#pastellize 
+#addGrid
+#addCorner 
+#errorBars
+#addLabel
+#patternLayer
+#patternLayerCoordinates
+
+##----
+### R markdown
+##----
+# RmdWords
+# citeR
+##--------------------------------------------------
+
+##################
+## Data processing
+##################
+
+##-------------
+# firstup
+##-------------
+
+#Capitalize the first letter of a string
+
+firstup <- function(x) {
+  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
+  x
+}
+
+#--
+
+##-------------
+# as.numcharac
+##-------------
+
+#This function allows to combine as.numeric and as.character
+
+as.numcharac <- function(x){
+	return(as.numeric(as.character(x)))
+}
+
+#--
+
+
+##-------------
+# %nin%
+##-------------
+
+#This function allows to select what is not included in a given variable
+
+
+'%nin%' <- Negate('%in%')
+
+#--
+
+##-------------
+# getmode
+##-------------
+
[…]

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R
minor

@@ -22,6 +22,7 @@ setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
 dir.create(file.path("extdata"), showWarnings = FALSE)
 dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
 
 #Import environment
 rm(list=ls())
@@ -588,7 +589,7 @@ for(c in 1:length(geographicThresholdVector)){
     }
 
     #SaveDataGeneral
-    write.table(summaryData, paste("Dataplot", a, "_", b, "_", c, "_", d,".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    write.table(summaryData, paste("Dataplot/Dataplot", a, "_", b, "_", c, "_", d,".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
     write.table(length(summaryData$DietaryGuild[summaryData$DietaryGuild=="Fruit"]), 
                 paste("Sample_size/checkSampleFruit", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")

### 2021-05-12 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1.R

@@ -14,6 +14,7 @@ setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
 dir.create(file.path("extdata"), showWarnings = FALSE)
 dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
 
 #Import environment
 rm(list=ls())
@@ -580,7 +581,7 @@ for(c in 1:length(geographicThresholdVector)){
     }
     
     #SaveDataGeneral
-    write.table(summaryData, paste("Dataplot", a, "_", b, "_", c, "_", d,".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    write.table(summaryData, paste("Dataplot/Dataplot", a, "_", b, "_", c, "_", d,".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
     write.table(length(summaryData$DietaryGuild[summaryData$DietaryGuild=="Fruit"]), 
                 paste("Sample_size/checkSampleFruit", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")

### 2021-05-13 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R
log transfo EQ, Hippo, Neo

@@ -655,7 +655,7 @@ for(c in 1:length(geographicThresholdVector)){
     #summaryData$ratioBrain.log <- log(summaryData$ratioBrain)
     
     hist(summaryData$EQ)
-    #summaryData$EQ.log <- log(summaryData$EQ)
+    summaryData$EQ.log <- log(summaryData$EQ)
     #hist(summaryData$EQ.log)
     
     hist(summaryData$Brain)
@@ -690,25 +690,25 @@ for(c in 1:length(geographicThresholdVector)){
       data=summaryData[!is.na(summaryData$EQ)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="EQ",
+      trait="EQ.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
     write.table(resultEQFrugivory, paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
-    
     #Neocortex
     print("Neocortex")
     summaryData$ratioNeocortex <- summaryData$Neocortex/ summaryData$Brain
     hist(summaryData$ratioNeocortex )
-
+    summaryData$ratioNeocortex.log <- log(summaryData$ratioNeocortex)
+    
     resultNeocortexFrugivory <- runComparisonModelsCompetition(
       simmap=simmapdiet1,
       data=summaryData[!is.na(summaryData$ratioNeocortex)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="ratioNeocortex",
+      trait="ratioNeocortex.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
@@ -719,13 +719,14 @@ for(c in 1:length(geographicThresholdVector)){
     print("ratioHippocampus")
     summaryData$ratioHippocampus <- summaryData$Hippocampus/ summaryData$Brain
     hist(summaryData$ratioHippocampus )
[…]

### 2021-05-13 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1.R

@@ -647,7 +647,7 @@ for(c in 1:length(geographicThresholdVector)){
     #summaryData$ratioBrain.log <- log(summaryData$ratioBrain)
     
     hist(summaryData$EQ)
-    #summaryData$EQ.log <- log(summaryData$EQ)
+    summaryData$EQ.log <- log(summaryData$EQ)
     #hist(summaryData$EQ.log)
     
     hist(summaryData$Brain)
@@ -682,25 +682,25 @@ for(c in 1:length(geographicThresholdVector)){
       data=summaryData[!is.na(summaryData$EQ)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="EQ",
+      trait="EQ.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
     write.table(resultEQFrugivory, paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
-    
     #Neocortex
     print("Neocortex")
     summaryData$ratioNeocortex <- summaryData$Neocortex/ summaryData$Brain
     hist(summaryData$ratioNeocortex )
+    summaryData$ratioNeocortex.log <- log(summaryData$ratioNeocortex)
     
     resultNeocortexFrugivory <- runComparisonModelsCompetition(
       simmap=simmapdiet1,
       data=summaryData[!is.na(summaryData$ratioNeocortex)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="ratioNeocortex",
+      trait="ratioNeocortex.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
@@ -711,13 +711,14 @@ for(c in 1:length(geographicThresholdVector)){
     print("ratioHippocampus")
     summaryData$ratioHippocampus <- summaryData$Hippocampus/ summaryData$Brain
     hist(summaryData$ratioHippocampus )
[…]

### 2021-05-13 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2.R

@@ -655,7 +655,7 @@ for(c in 1:length(geographicThresholdVector)){
     #summaryData$ratioBrain.log <- log(summaryData$ratioBrain)
     
     hist(summaryData$EQ)
-    #summaryData$EQ.log <- log(summaryData$EQ)
+    summaryData$EQ.log <- log(summaryData$EQ)
     #hist(summaryData$EQ.log)
     
     hist(summaryData$Brain)
@@ -690,25 +690,25 @@ for(c in 1:length(geographicThresholdVector)){
       data=summaryData[!is.na(summaryData$EQ)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="EQ",
+      trait="EQ.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
     write.table(resultEQFrugivory, paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
-    
     #Neocortex
     print("Neocortex")
     summaryData$ratioNeocortex <- summaryData$Neocortex/ summaryData$Brain
     hist(summaryData$ratioNeocortex )
+    summaryData$ratioNeocortex.log <- log(summaryData$ratioNeocortex)
     
     resultNeocortexFrugivory <- runComparisonModelsCompetition(
       simmap=simmapdiet1,
       data=summaryData[!is.na(summaryData$ratioNeocortex)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
       subgroup="Fruit",
       numberMaps=numberSimulations,
-      trait="ratioNeocortex",
+      trait="ratioNeocortex.log",
       tree=phylo,
       ana_events_tables=BSM_output$RES_ana_events_tables,
       clado_events_tables=BSM_output$RES_clado_events_tables
@@ -719,13 +719,14 @@ for(c in 1:length(geographicThresholdVector)){
     print("ratioHippocampus")
     summaryData$ratioHippocampus <- summaryData$Hippocampus/ summaryData$Brain
     hist(summaryData$ratioHippocampus )
[…]

### 2021-05-21 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1.R
update

@@ -131,6 +131,7 @@ for(c in 1:length(geographicThresholdVector)){
 
   parrallel_run <- function(d){
     
+    set.seed(d)
     
     runComparisonModelsCompetition <- function(
       
@@ -672,6 +673,7 @@ for(c in 1:length(geographicThresholdVector)){
     
     colnames(summaryData)[colnames(summaryData)=="DietaryGuild"] <- "Guild"
 
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
     print("Brain")
     resultBrainFrugivory <- runComparisonModelsCompetition(
       simmap=simmapdiet1,
@@ -684,7 +686,9 @@ for(c in 1:length(geographicThresholdVector)){
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
     write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    }
     
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
     print("EQ")
     resultEQFrugivory <- runComparisonModelsCompetition(
       simmap=simmapdiet1,
@@ -697,8 +701,10 @@ for(c in 1:length(geographicThresholdVector)){
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
     write.table(resultEQFrugivory, paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    }
     
     #Neocortex
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_Neocortex", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
     print("Neocortex")
     summaryData$ratioNeocortex <- summaryData$Neocortex/ summaryData$Brain
     hist(summaryData$ratioNeocortex )
@@ -715,8 +721,10 @@ for(c in 1:length(geographicThresholdVector)){
       clado_events_tables=BSM_output$RES_clado_events_tables
     )
[…]

### 2021-05-21 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2.R

@@ -123,6 +123,8 @@ for(c in 1:length(geographicThresholdVector)){
   
   parrallel_run <- function(d){
     
+    set.seed(d)
+    
     
     runComparisonModelsCompetition <- function(
       
@@ -664,123 +666,134 @@ for(c in 1:length(geographicThresholdVector)){
     
     colnames(summaryData)[colnames(summaryData)=="DietaryGuild"] <- "Guild"
     
-    print("Brain")
-    resultBrainFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
-      data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
-      subgroup="Fruit",
-      numberMaps=numberSimulations,
-      trait="Brain.log",
-      tree=phylo,
-      ana_events_tables=BSM_output$RES_ana_events_tables,
-      clado_events_tables=BSM_output$RES_clado_events_tables
-    )
-    write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
+      print("Brain")
+      resultBrainFrugivory <- runComparisonModelsCompetition(
+        simmap=simmapdiet1,
+        data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
+        subgroup="Fruit",
+        numberMaps=numberSimulations,
+        trait="Brain.log",
+        tree=phylo,
+        ana_events_tables=BSM_output$RES_ana_events_tables,
+        clado_events_tables=BSM_output$RES_clado_events_tables
+      )
+      write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    }
     
-    print("EQ")
-    resultEQFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
[…]

### 2021-05-21 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1.R

@@ -123,6 +123,8 @@ for(c in 1:length(geographicThresholdVector)){
   
   parrallel_run <- function(d){
     
+    set.seed(d)
+    
     
     runComparisonModelsCompetition <- function(
       
@@ -664,123 +666,134 @@ for(c in 1:length(geographicThresholdVector)){
     
     colnames(summaryData)[colnames(summaryData)=="DietaryGuild"] <- "Guild"
     
-    print("Brain")
-    resultBrainFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
-      data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
-      subgroup="Fruit",
-      numberMaps=numberSimulations,
-      trait="Brain.log",
-      tree=phylo,
-      ana_events_tables=BSM_output$RES_ana_events_tables,
-      clado_events_tables=BSM_output$RES_clado_events_tables
-    )
-    write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
+      print("Brain")
+      resultBrainFrugivory <- runComparisonModelsCompetition(
+        simmap=simmapdiet1,
+        data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
+        subgroup="Fruit",
+        numberMaps=numberSimulations,
+        trait="Brain.log",
+        tree=phylo,
+        ana_events_tables=BSM_output$RES_ana_events_tables,
+        clado_events_tables=BSM_output$RES_clado_events_tables
+      )
+      write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    }
     
-    print("EQ")
-    resultEQFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
[…]

### 2021-05-21 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2.R

@@ -131,6 +131,8 @@ for(c in 1:length(geographicThresholdVector)){
   
   parrallel_run <- function(d){
     
+    set.seed(d)
+    
     
     runComparisonModelsCompetition <- function(
       
@@ -672,123 +674,134 @@ for(c in 1:length(geographicThresholdVector)){
     
     colnames(summaryData)[colnames(summaryData)=="DietaryGuild"] <- "Guild"
     
-    print("Brain")
-    resultBrainFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
-      data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
-      subgroup="Fruit",
-      numberMaps=numberSimulations,
-      trait="Brain.log",
-      tree=phylo,
-      ana_events_tables=BSM_output$RES_ana_events_tables,
-      clado_events_tables=BSM_output$RES_clado_events_tables
-    )
-    write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
+      print("Brain")
+      resultBrainFrugivory <- runComparisonModelsCompetition(
+        simmap=simmapdiet1,
+        data=summaryData[!is.na(summaryData$Brain.log)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
+        subgroup="Fruit",
+        numberMaps=numberSimulations,
+        trait="Brain.log",
+        tree=phylo,
+        ana_events_tables=BSM_output$RES_ana_events_tables,
+        clado_events_tables=BSM_output$RES_clado_events_tables
+      )
+      write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_Brain", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+    }
     
-    print("EQ")
-    resultEQFrugivory <- runComparisonModelsCompetition(
-      simmap=simmapdiet1,
[…]

### 2021-05-23 Article/Article.Rmd

@@
 #biblio-style: apa
+always_allow_html: true
 
@@
 
-#Just to see the difference as pinpointed by the warning
-# geosphere::areaPolygon(areaTransitory)
-# gArea(areaTransitory)
-# really false
-# geosphere::centroid(areaTransitory)
-# gCentroid(areaTransitory)
-#ok
-
-layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-####
-## Fig interaction
-####
-
-#Import data
-summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
-
-#Tree
-tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
-
-#Create geography df
-geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
-colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
-
-#Create species ID
-hc = as.hclust(tree)#bird.orders)
-labels = hc$labels  # name of birds
-
-labels.tordc <- as.data.frame(labels)
-colnames(labels.tordc) <- "Name"
-labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
-
-labels.rdc <- apply(labels.tordc, 1, function(x){
-  if(!is.na(x[3])){
-    paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
-  } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
-  }
-}
-)
-
-#Match to have right order for geography
-locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
-colLoc <- colourArea
-
-#Match to have diet
-dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
-
-#Getting species labels abbreviated
-speciesLabels <- hc$labels#Should be in the tree order
-
-#Create the circos plot linking species based on their diet and geography
-circos.clear()
-circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
-circos.initialize(speciesLabels, xlim = c(0, 1))
-
-#Species name + area it belongs to
-circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
-             panel.fun = function(x, y) {
-               i=CELL_META$sector.numeric.index
-               circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
-                           facing = "clockwise", niceFacing = TRUE,
-                           col = "black", cex = 0.35, font=3)
-
-              geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-              for(g in 1:length(geo)){
-                if(geo[g]==1){
-                  #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
-                  circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
-                }
-              }
-             })
-
-#Plot the geographic links
-for(i in 1:length(speciesLabels)){
-  #locI <- which(strsplit(locationSpecies[i], "")==1)
-  for(j in i:length(speciesLabels)){
-    #locJ <- which(strsplit(locationSpecies[j], "")==1)
-    product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-    if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
-      #Do nothing
-    }
-    else{
-      if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
-        # colour <- as.data.frame(table(colLoc[which(product==1)]))
-        # if(is.finite(max(colour$Freq))){
-        # }else{
-        #   print(c(i,j))
-        # }
-        # colour <- colour[colour$Freq==max(colour$Freq),1][1]
-        circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
-      }
-      else{
-        #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
-      }
-    }
-  }
-}
-circos.clear()
-
-#Plot the phylogenetic tree in a new circular plot
-n = length(labels)  # number of species
-dend = as.dendrogram(hc)
-
-par(new = TRUE) # <- magic
-circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
-circos.initialize("a", xlim = c(0, n)) # only one sector
-# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
+# #Just to see the difference as pinpointed by the warning
+# # geosphere::areaPolygon(areaTransitory)
+# # gArea(areaTransitory)
+# # really false
+# # geosphere::centroid(areaTransitory)
+# # gCentroid(areaTransitory)
+# #ok
+# 
+# layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
+# par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+# 
+# ####
+# ## Fig interaction
+# ####
+# 
+# #Import data
+# summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
+# 
+# #Tree
+# tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
+# 
+# #Create geography df
+# geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
+# colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
+# 
+# #Create species ID
+# hc = as.hclust(tree)#bird.orders)
+# labels = hc$labels  # name of birds
+# 
+# labels.tordc <- as.data.frame(labels)
+# colnames(labels.tordc) <- "Name"
+# labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
+# 
+# labels.rdc <- apply(labels.tordc, 1, function(x){
+#   if(!is.na(x[3])){
+#     paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
+#   } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
+#   }
+# }
+# )
+# 
+# #Match to have right order for geography
+# locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
+# colLoc <- colourArea
+# 
+# #Match to have diet
+# dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
+# 
+# #Getting species labels abbreviated
+# speciesLabels <- hc$labels#Should be in the tree order
+# 
+# #Create the circos plot linking species based on their diet and geography
+# circos.clear()
+# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
+# circos.initialize(speciesLabels, xlim = c(0, 1))
+# 
+# #Species name + area it belongs to
+# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
 #              panel.fun = function(x, y) {
-#                for(i in seq_len(n)) {
-#                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
+#                i=CELL_META$sector.numeric.index
+#                circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
 #                            facing = "clockwise", niceFacing = TRUE,
-#                              col = "black", cex = 0.2, font=3)
+#                            col = "black", cex = 0.35, font=3)
+#                
+#               geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
+#               for(g in 1:length(geo)){
+#                 if(geo[g]==1){
+#                   #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
+#                   circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
+#                 }
 #               }
 #              })
-
-#suppressPackageStartupMessages(library(dendextend))
-#dend = color_branches(dend, k = 6, col = 1:6)
-dend_height = attr(dend, "height")
-circos.track(ylim = c(0, dend_height), bg.border = NA,
-             track.height = 0.95, panel.fun = function(x, y) {
-               circos.dendrogram(dend)
-             })
-circos.clear()
-
-####
-## Fig map
-####
-
-#Create the map of the geographic area
-#Have background
-maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))
-
-# addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
-#
-
-for(i in 1:length(areaName)){
-  plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
-}
-#Have borders
-#plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
+# 
+# #Plot the geographic links
+# for(i in 1:length(speciesLabels)){
+#   #locI <- which(strsplit(locationSpecies[i], "")==1)
+#   for(j in i:length(speciesLabels)){
+#     #locJ <- which(strsplit(locationSpecies[j], "")==1)
+#     product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
+#     if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
+#       #Do nothing
+#     }
+#     else{
+#       if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
+#         # colour <- as.data.frame(table(colLoc[which(product==1)]))
+#         # if(is.finite(max(colour$Freq))){
+#         # }else{
+#         #   print(c(i,j))
+#         # }
+#         # colour <- colour[colour$Freq==max(colour$Freq),1][1]
+#         circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
+#       }
+#       else{
+#         #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
+#       }
+#     }
+#   }
+# }
+# circos.clear()
+# 
+# #Plot the phylogenetic tree in a new circular plot
+# n = length(labels)  # number of species
+# dend = as.dendrogram(hc)
+# 
+# par(new = TRUE) # <- magic
+# circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
+# circos.initialize("a", xlim = c(0, n)) # only one sector
+# # circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
+# #              panel.fun = function(x, y) {
+# #                for(i in seq_len(n)) {
+# #                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
+# #                              facing = "clockwise", niceFacing = TRUE,
+# #                              col = "black", cex = 0.2, font=3)
+# #                }
+# #              })
+# 
+# 
+# #suppressPackageStartupMessages(library(dendextend))
+# #dend = color_branches(dend, k = 6, col = 1:6)
+# dend_height = attr(dend, "height")
+# circos.track(ylim = c(0, dend_height), bg.border = NA,
+#              track.height = 0.95, panel.fun = function(x, y) {
+#                circos.dendrogram(dend)
+#              })
+# circos.clear()
+# 
+# ####
+# ## Fig map
+# ####
+# 
+# #Create the map of the geographic area
+# #Have background
+# maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))
+# 
+# # addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
+# # 
+# 
 # for(i in 1:length(areaName)){
-#   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
-# }
-points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
-points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
-text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))
+#   plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
+# }
+# #Have borders
+# #plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
+# # for(i in 1:length(areaName)){
+# #   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
+# # }
+# points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
+# points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
+# text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))
 
@@
 
-library(RColorBrewer)
-colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
-colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
-
-###
-## Fig brain values / circular
-###
-
-summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
-summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
-summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
-summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
-summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
-summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain
-
-#Brain data
-relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
-relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-
-library(circlize)
-circos.clear()
-circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
-circos.initialize(speciesLabels, xlim = c(0, 1))
-
-#Species name
-circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
-             panel.fun = function(x, y) {
-               i=CELL_META$sector.numeric.index
-               circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
-                           facing = "clockwise", niceFacing = TRUE,
-                           col = "black", cex = 0.35, font=3)
-             })
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
-}, track.height = 1/15)
-
-library(plotrix)
-#Main circle
-for(i in 1:13){
-  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
-}
-
-#increment of 0.5
-for(i in 1:26){
-  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
-}
-
-#Value
-
-#EQ
-absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueEQ[i])){}  else{
-    if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-    }
-    else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueEQ[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
-    }
-    else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Striatum
-absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueStriatum[i])){}  else{
-    if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
-    }
-    else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueStriatum[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
-    }
-    else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#MOB
-absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueMOB[i])){}  else{
-    if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
-    }
-    else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueMOB[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
-    }
-    else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Neocortex
-absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueNeocortex[i])){}  else{
-    if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
-    }
-    else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueNeocortex[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
-    }
-    else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Hippocampus
-absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Cerebellum
-absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
-    }
-    else{}
-  }
-}, track.height = 0.1)
+# library(RColorBrewer)
+# colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
+# colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
+# colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
+# 
+# ###
+# ## Fig brain values / circular
+# ###
+# 
+# summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
+# summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
+# summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
+# summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
+# summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
+# summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain
+# 
+# #Brain data
+# relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
+# relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+# relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+# relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+# relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+# relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+# 
+# 
+# library(circlize)
+# circos.clear()
+# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
+# circos.initialize(speciesLabels, xlim = c(0, 1))
+# 
+# #Species name
+# circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
+#              panel.fun = function(x, y) {
+#                i=CELL_META$sector.numeric.index
+#                circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
+#                            facing = "clockwise", niceFacing = TRUE,
+#                            col = "black", cex = 0.35, font=3)
+#              })
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
+# }, track.height = 1/15)
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
+# }, track.height = 1/15)
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
+# }, track.height = 1/15)
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
+# }, track.height = 1/15)
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
+# }, track.height = 1/15)
+# 
+# #Background
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
+# }, track.height = 1/15)
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+#   circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
+# }, track.height = 1/15)
+# 
+# 
+# library(plotrix)
+# #Main circle
+# for(i in 1:13){
+#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
+# }
+# 
+# #increment of 0.5
+# for(i in 1:26){
+#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
+# }
+# 
+# #Value
+# 
+# 
+# 
+# #EQ
+# absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueEQ[i])){}  else{
+#     if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+#     }
+#     else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueEQ[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
+#     }
+#     else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# #Striatum
+# absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueStriatum[i])){}  else{
+#     if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+#     }
+#     else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueStriatum[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+#     }
+#     else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# #MOB
+# absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueMOB[i])){}  else{
+#     if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+#     }
+#     else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueMOB[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+#     }
+#     else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# #Neocortex
+# absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueNeocortex[i])){}  else{
+#     if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+#     }
+#     else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueNeocortex[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+#     }
+#     else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# #Hippocampus
+# absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueHippocampus[i])){}  else{
+#     if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
+#     }
+#     else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueHippocampus[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
+#     }
+#     else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# #Cerebellum
+# absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+#   if(is.na(relativeValueCerebellum[i])){}  else{
+#     if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
+#     }
+#     else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+#       circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
+# 
+# 
+# circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
+#   i=CELL_META$sector.numeric.index
+#   if(is.na(relativeValueCerebellum[i])){}  else{
+#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+#     if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
+#     }
+#     else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
+#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+#       circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
+#     }
+#     else{}
+#   }
+# }, track.height = 0.1)
 

### 2021-05-25 Article/Article.Rmd
Article modified after Benoit's comments

@@
  #      - '--lua-filter=author-info-blocks.lua'
- #bookdown::pdf_book:
- bookdown::word_document2:
+ bookdown::pdf_book:
+ #bookdown::word_document2:
    number_sections: false
@@
 **Abstract:** The diversity in animal cognition raises the question of its underlying evolutionary drivers.
-Cognitive selection can stem from interactions of individuals with their environment (*Ecological Intelligence Hypothesis*), with conspecifics within the social unit (*Social Intelligence Hypothesis*) or between social units (*Napoleonic Intelligence Hypothesis*), or even among generations (*Cultural Intelligence Hypothesis*).
-Yet, one species rarely occupies an area alone: space is a shared place between many species that can interact directly or indirectly.
-These interactions could represent additional cues and/or noise to find resource or escape predator(s), henceforth stimulate cognition.
-To test whether species co-occurrence shaped current patterns of cognition, we used Primates (N$_{min-max}$=`r minAllAreas`-`r maxAllAreas`) as a study example and retraced the evolutionary history of species whole brain - or specific area – relative size, using standard phylogenetic models or competitive phylogenetic models.
-Then we fitted phylogenetic regressions to test for variation in brain size and current co-occurrence pattern correlations.
-We found that the evolution of the relative size of areas involved in foraging, information processing and/or retention is better described by models accounting for species co-occurrence within dietary guilds which lead to increased relative sizes of these areas.
+Selection upon more advanced cognitive abilities can stem from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*), among generations (*Cultural Intelligence Hypothesis*), between social units (*Napoleonic Intelligence Hypothesis*), or with the rest of their environment (*Ecological Intelligence Hypothesis*).
+These hypotheses were limited to within-species scenarios.
+Yet, one species rarely occupies an area alone: space is a place shared between many species that can interact directly or indirectly.
+For species occupying a same ecological niche, interspecific competition is particularly expected in this case, but interactions could also represent additional cues and/or noise to cognitively process to find resource or escape predator(s) more efficiently.
+To test whether species co-occurrence shaped current patterns of cognition, we used Primates as a study example and retraced the evolutionary history and diversification of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
+We found that the evolution of the relative size of areas involved in foraging-related information processing and/or retention is better described by models accounting for species co-occurrence within dietary guilds which lead to increased relative sizes of these areas.
 This suggests that cognition is subject to an arms race among species (*Red Queen Intelligence Hypothesis*) and shall explain why specific abilities particularly boomed for some lineages, as for instance with Primates.
@@
 
-To grasp the rationale of current hypotheses that aim to describe the evolution of animal cognition [@van2006some; @dunbar2017there], consider an animal foraging for food.
-This focal is not looking for any type of food but specific one.
-This can for instance be fruits.
-Finding fruits for an animal is not an easy task.
+To grasp the rationale of current hypotheses that aim to describe the evolution of animal cognition [@van2006some; @dunbar2017there], consider a primate individual foraging for food.
+Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for assessing human evolution [@byrne2000evolution].
+The chosen focal is not looking for any type of food but specific one, as for instance, most primate species often look for fruits.
+Finding fruits for a primate is not an easy task.
 In fact, fruits are the archetype of a hard-to-find resource likely to promote cognitive development because fruit trees are rare, dispersed, and do not produce constantly along the year nor between years, albeit their fruiting period remains nonetheless predictable [@janmaat2016spatio].
 Additionally, they are energy-rich, allowing expansion of costly tissues such as brain tissues [@clutton1980primates].
-Where the example focal stands there is no food that is immediately perceived, and the focal must move beyond its sensory range if it is to feed.
-Moving at random could mean travelling unnecessary long distances to finally rich a potentially void tree.
+Overall, primates thus show remarkable abilities to navigate precisely and target fruit trees likely to yield ripe resource despite they are out of their sensory range [@trapanese2019review], in part because of advanced spatio-temporal information retention [e.g.
+spatial knowledge: @normand2009forest; @robiraroute, temporal knowledge: @janmaat2006evidence; @janmaat2013chimpanzees; @janmaat2013tai].
+
+|	When the resource is out of sight, moving at random could mean travelling unnecessary long distances to finally reach a potentially void tree.
 Hence, for the focal, being capable of processing immediate cues and clues to know where specifically to find fruit trees [@dall2005information; @grove2013evolution] and whether it is probable that these trees currently yield fruits [@dall2005information; @robirainreview; @janmaat2016spatio] would be a considerable advantage.
-Provided it has the appropriate cognitive machinery, this could lead to avoiding costly detours and time recursions to food patches adequately.
+Having appropriate cognitive machinery may avoid costly detours and time recursions to food patches adequately.
 This simple picture draws the basis of the *Ecological Intelligence Hypothesis* [@clutton1980primates; @milton1981distribution; @rosati2017foraging] which stipulates that cognition was selected as a way to buffer the spatio-temporal complexity of the environment (e.g.
 @van2012large).
-In its quest, however, the focal might not be alone: there might be a few conspecifics foraging on its side, each looking for a signal leading to food sources.
-With these conspecifics, the focal forms a social group: they spend considerable time together, have established bounds and constantly share information.
-It is thus collectively that they must find a fruiting tree.
-To do so, being able to process signals emitted by others would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian].
+
+|	In its quest for food, however, the focal might not be alone: for instance, primates often form social groups [@kappeler2002evolution] where group members spend considerable time together, have established bounds and constantly share information.
+Thus, they might altogether look for, and process, cues and clues leading to food sources.
+To do so, being able to process signals emitted by other maneuvers would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian].
 This therefore means plenty of additional stimuli to process, and constitutes the socle of the *Social Intelligence Hypothesis* [@dunbar2017there].
-In the focal group, however, all individuals are not equally knowledgeable: perhaps because some have more experience than others do, such as the oldest would be more experienced than the youths.
-It is possible that these young individuals learn from the elderly individuals [@laland2004social].
+
+|   In the focal group, however, all individuals are not equally knowledgeable: perhaps because some have more experience than others do, such as the oldest would be more experienced than the youths.
+It is possible that these young individuals learn from the elderly ones [@laland2004social].
 For instance, they may learn how to process a specific tool to access a hidden comestible part as for nuts [@boesch1994nut].
 In other words, there is vertical transmission that passes by over generations and knowledge thereby accumulates: this is the *Cultural Intelligence Hypothesis* [@whiten2007evolution, reader2002social], also known as the *Vygotskian Intelligence Hypothesis* in humans [@herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social].
-Finally, while the focal’s group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild].
-The neighbouring groups might indeed be competitors for food, mates or actually any resource that it might be essential to preserve, and as much as it is advantageous to be able to read through the environment and intra-group conspecifics, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g.
+
+|   Finally, while the group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild].
+The neighboring groups might indeed be competitors for food, mates or any essential resource, and as much as it is advantageous to be able to read through the environment and intra-group companions, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g.
 group size), a view brought by the *Napoleonic Intelligence Hypothesis* [@ashton2020interactions].
@@
 Never was it question of multiple species: all hypothesized individuals belonged to a singular common species.
-Yet, a species rarely occupies a given area alone.
-Space is a shared place between a plethora of species, some of them occupying a same ecological niche.
-This partial niche overlap could contribute to impoverishing food density and increasing its spatio-temporal variance, hence reinforcing the selective pressure towards advanced cognition to maintain sufficient foraging success.
-In another perspective, two species sharing common food targets might benefit from being able to process cues of passage or presence of the other, to infer where and when to find ripe resource.
-To sum up, species co-occurrence might contribute into shaping animal cognition: the more species, the more advanced the cognition because the more noise or stimuli.
-In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in brain size among species, what we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example.
-
-\hfill
-
-|   Recent tools have been developed to infer the effect of species interaction on trait evolution, either by modelling divergence of the trait in co-occurring species from a same guild (e.g.
-dietary guild) (Matching Competition: MC models), or due to a density dependence of the evolutionary cladogenesis rate (linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating) on the number of lineages within the guild.
-After reconstructing the range history based on `r minRange` to `r maxRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs.
+Yet, space is a place shared between a plethora of species, some of them occupying a same ecological niche.
+As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from an other species with similar ecological preferences, for instance with regards to diet.
+As such, co-occurrence of species from the same guild might contribute into shaping animal cognition: the more species, the more selective pressure for advanced the cognition .
+In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in cognitive abilities among species - approximated by the size of the whole or specific regions of the brain - that we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example.
+
+\hfill
+
+|   Recent tools have been developed to infer the effect of species interactions on trait evolution, either by modelling trait divergence in co-occurring species from a same guild (e.g.
+dietary guild) (Matching Competition: MC models) or considering that the evolutionary rate depends on the on the number of lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
+After reconstructing the biogeography history based on `r minRange` to `r maxRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs.
 folivory; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, $EQ$, as a proxy for `r minEQ` to `r maxEQ` frugivorous, depending on how frugivory was assessed, see Dietary guild), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
-\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming non effect of species interactions, like the pure drift; Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
+\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming non effect of species interactions, like the simple Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
 stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, REF), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion (AIC) corrected for small samples (AICc) when considering all five models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Evolutionary models in methods).
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Evolutionary models in methods).
 Non-competitive models were the most likely in describing the evolutionary history of the $EQ$ or the striatum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), an area specifically involved in XXX, used here as a control area.
@@
 working memory, with the neocortex), or long-term spatio-temporal information retention (hippocampus), (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-When density-dependent models were the best fit, the positive rate (b or r, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity.
+When density-dependent models were the best fit, the positive rate (r, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity.
 
@@
 In these linear regressions, the predicted variable was the relative brain size values of areas for which we observed interspecific competition effect.
-we considered the average surface of the frugivorous species range overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
+We considered the average surface of the frugivorous species range overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
 Despite considerable noise induced by recent increase extinction and spatial range reduction due to anthropogenic disturbances (REF), it shows that XXXXXXXXXX
@@
 Used datasets and codes will be made freely available upon publication.
-They can also be provided during the reviewing process for verification of missed coding errors, or any further investigation by the reviewers.
+Used codes and data are freely available at XXXXX.
 
@@
 
-We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses.
+We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1,000 trees for the subsequent phylogenetic analyses.
 The trees contain `r length(phylo_init$tip.label)` primate species.
@@
 They were freely available in the main manuscript or supplementary materials.
-If the species was represented multiple times in the dataset, we obtained a unique attribute by averaging it.
+When the species was represented multiple times in the dataset, we obtained a unique attribute by averaging it.
 From the global endocranial brain volume, we obtained the Encephalization Quotient (*EQ*, (N$_{max}$=`r maxEQ`)) as follows [@decasien2017primate]
@@
 Finally, note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-Hence, *Macaca Sylvanus* is not considered in this study.
-	We retraced the history of the lineage ranges based on current observation of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
-This algorithm aims to fit, among others, non-time-stratified dispersal-extinction-cladogenesis (DEC) models (used here), specifically suiting analysis of ranging data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
-To reconstruct the evolution of species range, WE fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas.
+Hence, *Macaca sylvanus* is not considered in this study.
+	We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+This algorithm aims to fit, among others, non-time-stratified dispersal-extinction-cladogenesis (DEC) models (used here), specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
+To reconstruct the evolution of species range, we fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas.
 A too high number of areas that can be occupied simultaneously drastically increases computational time.
-Here, we therefore chose three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models), such as it allowed me to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Evolutionary Models (b)).
+Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
+Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Evolutionary Models (b)).
 
@@
 
-We classified species as either frugivorous, folivorous or “other” based on the availability of frugivorous rate and folivorous rate, prioritizing fruvigory over folivory.
+We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate, prioritizing fruvigory over folivory.
 First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold).
@@
 Whenever the rate was not available, we referred to this classification.
-In any other cases, the species was classified as “other”.
-	Frugivory rate was prioritized over, folivory, because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed.
+In any other cases, the species was discarded.
+	Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed.
 Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
@@
 Finally, because the methodology to obtain this rate could additionally vary (e.g.
-in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves), We used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
-Considering diet as a categorical variable (frugivory vs folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
+in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves).
+We used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
+Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
 at the root) but with no prior on the transition matrix.
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models), such as it allowed me to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Evolutionary Models (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Evolutionary Models (b)).
 
@@
 We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic model of $EQ$ - or relative size of a specific brain area – evolution with and without species competitions.
-Models were fitted on different sample sizes due to non availability of some data.
+Models were fitted on different sample sizes due to non-availability of some data.
 Specifically, models using $EQ$ included `r minEQ` to `r maxEQ` frugivorous species.
@@
 Prior fitting, trait parameters were log-transformed in case the distribution was skewed (i.e.
-for brain and MOB ratio) to reach more symmetrical distributions.
+for brain, EQ, and MOB ratio) to reach more symmetrical distributions.
 Models without competition, Brownian motion (i.e.
-BM, pure drift model), Orstein-Uhlenbeck process (i.e.
+BM), Orstein-Uhlenbeck process (i.e.
 OU, model with stabilizing selection), or Early-Burst model (i.e.
@@
 Using the evolutionary history of species distribution (Primate co-occurrence paragraph) and of diet (Dietary guild paragraph), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These competitive models notably account for interaction matrices that are build on the evolutionary history of species co-occurrence and diet.
-These interaction matrices retrace, along the phylogenetic tree, which lineages (species or ancestors) of a same dietary guild were present within the same geographic areas (see @drury2016estimating).
+These competitive models notably account for interaction matrices that are built on the evolutionary history of species co-occurrence and diet.
+These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see @drury2016estimating).
 We fitted three different competitive models.
-The matching competition model (MC) considers divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits [@drury2016estimating].
-Here, that would mean that co-occurring species would tend to have either extremely low or high $EQ$ or relative brain size.
+The matching competition model (MC) may consider divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
+Here, that would mean that co-occurring species would tend to have either lower or higher $EQ$ or relative brain size.
 Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
@@
 
-where $\lambda_{0}$ corresponds to the initial cladogenesis tree, $N$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the exponential dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes), and $K$ is generally considered as a “carrying capacity” [@rabosky2008density], that is the upper limit of lineages that are viable when at equilibrium.
+where $\lambda_{0}$ corresponds to the value of the initial ancestor, $N$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the exponential dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes), and $K$ is generally considered as a “carrying capacity” [@rabosky2008density], that is the upper limit of lineages that are viable when at equilibrium.
 	All these models were repeated `r numberSimulations` times, using `r randomSampling` different combination of the evolutionary history of ranging and diet.
-They were then compared within an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion (AIC) corrected for small samples (AICc) when considering all five models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU).
-The model weight then depicts the probability that it best describe the observed evolutionary pattern.
+They were then compared within an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
+The model weight then depicts the probability that it best describes the observed evolutionary pattern among the tested models.
 
@@
 In this analysis, uncertainty can stem from two sources.
-First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference.
-Therefore, the downloaded trees provided by the 10kTrees project might vary depending on the run.
-Similarly, the estimated evolutionary history of the diet and ranging might vary as well.
+First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1 000 possible estimated trees.
+
+|	Similarly, the estimated evolutionary history of the diet and ranging might vary as well.
 Second, for each species, trait estimates could vary slightly among datasets (see Supplementary Figure 2).
 Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Supplementary Figure 2), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
-In addition this study is based on several arbitrary thresholds, namely (i) to assess species co-occurence (see Supplementary Figure 3) and (ii) to assess the species dietary guild (see Supplementary Figure 2) which can cause sensitivity of the results to the chosen parameters.
-
-|   To account for these three sources of variability we refitted several times the five evolutionary model types (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeographic and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
+In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Supplementary Figure 3) and (ii) to assess the species dietary guild (see Supplementary Figure 2) which can cause sensitivity of the results to the chosen parameters.
+To account for these three sources of variability we refitted several times the six evolutionary model types (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeographic and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
 equal probability for each possible value to be selected) and (3) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence.
-we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1 000 possible trees estimated by Bayesian inference, because the evolutionary models take a long time to run and we could not fit the model several times with different trees.
-Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
-
-### Phylogenetic regression: determining the direction of the selection gradient shaped by interspecific competition
-
-\hfill
-
-(a)	Model dataset and formula
-
-\hfill
-
-To determine the direction of the selection, we fitted Gaussian phylogenetic regressions (i.e.
-accounting for a variance-covariance matrix based on phylogenetic distances) specifically for each brain region for frugivorous species only.
-To describe phylogenetic relationships among lineages, we used a consensus tree based on a block of 1 000 trees from the 10kTrees project, but we assessed sensitivity to phylogeny uncertainty using `r repetitionTrees` random trees from the block of trees.
-To categorize species as frugivorous or folivorous, we here considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
-If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous vs.
-folivorous” (i.e.
+
+|	Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
+
+### Phylogenetic regressions
+
+\hfill
+
+(a)	Determining the direction of the selection gradient shaped by interspecific competition
+
+\hfill
+
+To determine the direction of the selection of species co-occurrence on size of brain regions for which competitive models fitted the best, we fitted Gaussian phylogenetic regressions (i.e.
+accounting for a variance-covariance matrix based on phylogenetic distances) for each brain region individually and for frugivorous species only.
+We here considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
+If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
 could be either of the two), it was considered as frugivorous nonetheless.
@@
 |    The response variable was the relative size of areas shown as better described by competitive phylogenetic scenario (see above).
-Since the exact value of this output could vary depending on the dataset from which it was extracted (e.g.
-whole brain size could be extracted from @decasien2017primate, @powell2017re, @grueter2015home or @navarrete2018primate), we took the mean of the possible values but assessed the sensitivity using non-averaged values (see below).
+Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see below).
 In this model, the covariates (i.e.
@@
 
-(b)	Model implementation
+(b)	Diversification analysis
+
+TO BE COMPLETED
+
+(c)	Model implementation
 
@@
 
-(c)	Model robustness
+(d)	Model robustness
 
@@
 These controls did not point out important variability.
-To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10 000 possible trees from the 10kTrees project.
+To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10,000 possible trees from the 10kTrees project.
 For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple value (e.g.
@@
 The results of this sensitivity analysis are shown in Supplementary Table 2 and emphasizes that there is no major effect.
+Note that the main model was fitted with the consensus tree.
 
@@
 
-We considerably value the help provided by Jonathan Drury in making some scripts available but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for helping in trying to make the analysis run on the CEFE cluster.
+We considerably value the help provided by Jonathan Drury in making some scripts available but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for assistance for using the CEFE cluster.
 We thank Simon Benhamou and Manon Clairbaux for discussion and advices on spatial projections too.
@@
 BR received logistic support from the *Centre d’Ecologie Fonctionnelle et Evolutive*, Montpellier and the *Musée de l'Homme*, Paris.
-BP-L received logistic support from the *Ecole Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.
+BP-L received support from the *Ecole Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.
 

### 2021-05-25 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R
diversification

@@ -4,9 +4,11 @@
 # from Dos Reis 2018
 # set the MRCA at 74 Myr 
 
+rm(list=ls())
+
 library(ape)
 
-setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/diversification/")
+setwd("/Users/bperez/Documents/GitHub/Meta_analysis_cognition_primates/Scripts/Analysis3_diversification/diversification/")
 
 tree <- read.tree("host_tree_primate_complete.tre")
 
@@ -267,6 +269,8 @@ for (f in c( "95", "90", "80", "70", "60", "67")){
   colnames(speciation_rates) <- c("Species","Speciation_rate")
   speciation_rates$Speciation_rate <- as.numeric(as.character(speciation_rates$Speciation_rate))
   
+  speciation_rates$Diversification_rate <- speciation_rates$Speciation_rate*(1-MAPS[3])
+  
   write.table(speciation_rates, paste0("MAPS_speciation_rates_tips_",name,".csv"), sep=";",row.names=F,quote=F)
   
   # density
@@ -296,24 +300,6 @@ for (f in c( "95", "90", "80", "70", "60", "67")){
   colnames(table_mean_rates) <- c("time","speciation_rates")
   write.table(table_mean_rates,paste0("mean_speciation_rates_trought_time_",name,".csv"),sep=";",quote=F,row.names = F)
   
-  # index <- 1:12
-  # 
-  # for (rep in index){
-  #   load(paste0("ClaDS2_tree_GMYC_units_LSU_replicate_",rep,"_f",f,".Rdata"))
-  #   
-  #   # density
-  #   MAPS <- c()
-  #   for (i in 1:length(mr[[1]][[1]])){
-  #     D=density(sapply(1:length(mr), function(k) sapply(floor(length(mr[[1]])*0.3):length(mr[[1]]), function(j) mr[[k]][[j]][i])))
-  #     MAPS <- c(MAPS, D[[1]][which.max(D[[2]])])
-  #   }
-  #   plot(MAPS)
-  #   table_MAPS_rates <- cbind(seq(-505,0,length.out = length(mr[[1]][[1]])), MAPS)
-  #   colnames(table_MAPS_rates) <- c("time","speciation_rates")
[…]

### 2021-05-25 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R
update

@@ -328,6 +328,7 @@ for (f in c( "95", "90", "80", "70", "60", "67")){
 
 rm(list=ls())
 
+library(phytools)
 
 # setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history/")
 # load("geography_traits_biogeobears_2.RData")
@@ -337,9 +338,9 @@ setwd("/Users/bperez/Documents/GitHub/Meta_analysis_cognition_primates/Scripts/A
 
 tree <- read.tree("tree_primate_complete.tre")
 
-summaryData <- read.table("../results/Evolutionary_history/Dataplot.txt", header=TRUE, sep="\t")
+summaryData <- read.table("../../../Processed_data/Dataplot.txt", header=TRUE, sep="\t")
 
-nrow(summaryData) # 428 species
+nrow(summaryData) # 425 species
 Ntip(tree) # 367 species 
 table(summaryData$SpeciesForPhylogeny %in% tree$tip.label)
 
@@ -373,6 +374,7 @@ table(summaryData$SpeciesForPhylogeny %in% tree$tip.label)
 summaryData$Brain.log <- log(summaryData$Brain)
 summaryData$ratioBrain <- summaryData$Brain*1.036*(10**-3)/summaryData$Bodymass #Following decasien for multiplication by 1.036
 summaryData$EQ <- summaryData$Brain*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775) #Following decasien, according to #Jerison, H. J. Evolution of the Brain and Intelligence (Academic, 1973).
+summaryData$EQ.log <- log(summaryData$EQ)
 summaryData$ratioNeocortex <- summaryData$Neocortex/ summaryData$Brain
 summaryData$ratioHippocampus <- summaryData$Hippocampus/ summaryData$Brain
 summaryData$ratioCerebellum <- summaryData$Cerebellum/ summaryData$Brain
@@ -392,20 +394,89 @@ for (f in c(60, 67, 70, 80, 90, 95)){
   table_MAPS_rates <- read.table(paste0("MAPS_speciation_rates_tips_ClaDS2_tree_primate_complete_f",f,".csv"), sep=";",header=T)
   
   summaryData_div$speciation_rate <- NA
+  summaryData_div$diversification_rate <- NA
   for (i in 1:nrow(summaryData_div)){
[…]

### 2021-05-25 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R
Update script_diversification_primates.R

@@ -409,49 +409,49 @@ for (f in c(60, 67, 70, 80, 90, 95)){
   x <- summaryData_omit$Brain.log
   names(x) <- summaryData_omit$SpeciesForPhylogeny
   dotTree(tree_plot,x,ftype="i",legend=F, standardize=T)
-  text(0,0, "Brain.log")
+  text(10,0, "Brain.log")
   
   summaryData_omit<- summaryData_div[-which(is.na(summaryData_div$EQ.log)),]
   tree_plot <- drop.tip(tree,tip=tree$tip.label[!tree$tip.label %in% summaryData_omit$SpeciesForPhylogeny])
   x <- summaryData_omit$EQ.log
   names(x) <- summaryData_omit$SpeciesForPhylogeny
   dotTree(tree_plot,x,ftype="i",legend=F, standardize=T)
-  text(0,0, "EQ.log")
+  text(10,0, "EQ.log")
   
   summaryData_omit<- summaryData_div[-which(is.na(summaryData_div$ratioNeocortex)),]
   tree_plot <- drop.tip(tree,tip=tree$tip.label[!tree$tip.label %in% summaryData_omit$SpeciesForPhylogeny])
   x <- summaryData_omit$ratioNeocortex
   names(x) <- summaryData_omit$SpeciesForPhylogeny
   dotTree(tree_plot,x,ftype="i",legend=F, standardize=T)
-  text(0,0, "ratioNeocortex")
+  text(10,0, "ratioNeocortex")
   
   summaryData_omit<- summaryData_div[-which(is.na(summaryData_div$ratioHippocampus)),]
   tree_plot <- drop.tip(tree,tip=tree$tip.label[!tree$tip.label %in% summaryData_omit$SpeciesForPhylogeny])
   x <- summaryData_omit$ratioHippocampus
   names(x) <- summaryData_omit$SpeciesForPhylogeny
   dotTree(tree_plot,x,ftype="i",legend=F, standardize=T)
-  text(0,0, "ratioHippocampus")
+  text(10,0, "ratioHippocampus")
   
   summaryData_omit<- summaryData_div[-which(is.na(summaryData_div$ratioCerebellum)),]
   tree_plot <- drop.tip(tree,tip=tree$tip.label[!tree$tip.label %in% summaryData_omit$SpeciesForPhylogeny])
   x <- summaryData_omit$ratioCerebellum
[…]

### 2021-05-26 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
update

@@ -1,0 +1,902 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+ 
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
+# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+load("geography_traits_biogeobears.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("Functions.R")
+
+##--------
+
+##--------
+#Libraries
+
+#Phylogenetics
+library(caper)
+library(ape)
+library(phytools)
+library(geiger)
+library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#??
+library(ellipsis)
+
+#Parallelizing
+# library(snow)
+# library(foreach)
[…]

### 2021-05-26 Scripts/Analysis3_diversification/diversification/script_ClaDS_f73.jl

@@ -45,12 +45,12 @@ tree = ape2Tree(tree)    # and make it a Julia Tree
 Random.seed!(813)
 n_iter = 400
 
-sample_fraction = 0.67
+sample_fraction = 0.73
 sampler = run_ClaDS2(tree, n_iter,plot_tree = 0,
     print_state = Int64(n_iter/4), plot_chain = false,
     f=sample_fraction, ltt_steps = 250)
 
-sampler_to_Rdata(tree, sampler, join(["ClaDS2_tree_", name, "_f67.Rdata"]) ; sample_fraction = sample_fraction, max_it_number = 2_500)
+sampler_to_Rdata(tree, sampler, join(["ClaDS2_tree_", name, "_f73.Rdata"]) ; sample_fraction = sample_fraction, max_it_number = 2_500)
 result = (tree, sampler, sample_fraction)
-@save join(["ClaDS2_tree_", name, "_f67.jld2"]) result
+@save join(["ClaDS2_tree_", name, "_f73.jld2"]) result
 

### 2021-05-26 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R

@@ -248,9 +248,9 @@ plot_ClaDS_phylo <- function (phylo, rates, rates2 = NULL, same.scale = T, main 
 
 setwd("/users/biodiv/bperez/data/others/Benji/diversification/")
 
-f="60"
+f="73"
 
-for (f in c( "95", "90", "80", "70", "60", "67")){
+for (f in c( "95", "90", "80", "70", "60", "73")){
   
   print(f)
   name=paste0("ClaDS2_tree_primate_complete_f",f)

### 2021-05-26 Scripts/Analysis3_diversification/diversification/script_diversification_primates.R
Update script_diversification_primates.R

@@ -385,7 +385,7 @@ summaryData$ratioMOB.log <- log(summaryData$ratioMOB)
 
 f=67
 
-for (f in c(60, 67, 70, 80, 90, 95)){
+for (f in c(60, 73, 70, 80, 90, 95)){
   
   print(f)
   

### 2021-05-31 Article/Article.Rmd
Update main text: biblio/intro

@@
 header-includes:
-  - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
+  - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
   - \usepackage{lineno} # For line numbering
@@
 neurobase,
-misc3d
+misc3d,
+phylolm,
+nlme,
+pgls
 )
@@
 repetitionModels=30
-repetitionBootstrap=2000
+repetitionBootstrap=200
 
@@
 For species occupying a same ecological niche, interspecific competition is particularly expected in this case, but interactions could also represent additional cues and/or noise to cognitively process to find resource or escape predator(s) more efficiently.
-To test whether species co-occurrence shaped current patterns of cognition, we used Primates as a study example and retraced the evolutionary history and diversification of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
+To test whether species co-occurrence shaped current patterns of cognition, we used Primates as a study example and retraced the evolutionary history of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
 We found that the evolution of the relative size of areas involved in foraging-related information processing and/or retention is better described by models accounting for species co-occurrence within dietary guilds which lead to increased relative sizes of these areas.
@@
 To grasp the rationale of current hypotheses that aim to describe the evolution of animal cognition [@van2006some; @dunbar2017there], consider a primate individual foraging for food.
-Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for assessing human evolution [@byrne2000evolution].
+Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
 The chosen focal is not looking for any type of food but specific one, as for instance, most primate species often look for fruits.
@@
 Yet, space is a place shared between a plethora of species, some of them occupying a same ecological niche.
-As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from an other species with similar ecological preferences, for instance with regards to diet.
-As such, co-occurrence of species from the same guild might contribute into shaping animal cognition: the more species, the more selective pressure for advanced the cognition .
-In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in cognitive abilities among species - approximated by the size of the whole or specific regions of the brain - that we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example.
+As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from another species with similar ecological preferences, for instance with regards to diet.
+As such, co-occurrence of species from the same guild might contribute into shaping animal cognition: the more species, the more selective pressure for advanced cognition.
+In this line, because the cognitive abilities would rhyme with ecological success (REF), thus inducing higher population size which ultimately would spur speciations and reduce extinction risk, these cognitively advanced species are expected to "boom", what would be translated into increased species diversification rates.
+In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in cognitive abilities among species - approximated by the size of the whole or specific regions of the brain - that we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example, and assess how this might have affected the evolutionary success of the Primate lineage.
 
@@
 folivory; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, $EQ$, as a proxy for `r minEQ` to `r maxEQ` frugivorous, depending on how frugivory was assessed, see Dietary guild), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
-\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming non effect of species interactions, like the simple Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
+\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming no effect of species interactions, like the simple Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
 stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, REF), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Evolutionary models in methods).
+The use of specific region size relatively to the whole brain size [see @deaner2000comparative for further consideration of scaling methods], and not raw size, rather depicts the evolutionary evolution of cognitive abilities in terms of allocation rather than abilities per se [although it is vividly discussed whether raw measure are anything informative on that point too @logan2018beyond].
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Models of trait evolution in methods).
 Non-competitive models were the most likely in describing the evolutionary history of the $EQ$ or the striatum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), an area specifically involved in XXX, used here as a control area.
@@
 |   To understand the directionality of the selection gradient shaped by co-occurrence (i.e.
-selection for “bigger” brain or “smaller” brain the more species), we fitted phylogenetic regressions (see Phylogenetic models; phylogenetic regressions in methods).
+selection for “bigger” brain or “smaller” brain if the more species), we fitted phylogenetic regressions (see (Phylogenetic regressions) a)).
 In these linear regressions, the predicted variable was the relative brain size values of areas for which we observed interspecific competition effect.
 We considered the average surface of the frugivorous species range overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
-Despite considerable noise induced by recent increase extinction and spatial range reduction due to anthropogenic disturbances (REF), it shows that XXXXXXXXXX
+
+|   Next, we investigated how brain evolution was related to evolutionary successes, assumed proportional to diversification rate, by using birth-death models of species diversification.
+Present-day diversification rates were estimated using ClaDS [@maliet2019model].
+
+They were positively correlated with XXXX suggesting that XXX.
+However, when accounting for phylogenetic dependence between primate species, the correlations were no longer significant: because advanced cognitive abilities only evolved in a limited number of primate clades (XXX), we thus cannot conclude whether advanced cognitive abilities generally enhance species diversification.
+ClaDS’ estimates of diversification rates through times also suggested that primates diversified faster in the last XXX Myr (as previously shown in XXX), which correlatively mirrored their increased of cognitive abilities.
 
@@
 |   In the end, the inter-specific effect on cognition was here viewed under the prism of foraging, yet, without further evidence, it is as likely to hold in other contexts, such as the social environment.
-In fact, the general hypotheses on cognition evolution, discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; pepperberg2002allospecific].
+In fact, the general hypotheses on cognition evolution, discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
 As Alice said “'It's a great huge game of chess that's being played—all over the world” (Carroll, Chapter II, Through the Looking Glass) and all individuals are just pieces to play with or against, no matter the species.
@@
 Used datasets and codes will be made freely available upon publication.
-Used codes and data are freely available at XXXXX.
+Used codes and data are freely available at [https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency](https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency).
 
@@
 
-Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (cerebellum, hippocampus, main olfactory bulb (MOB), neocortex, striatum) , @powell2017re and @powell2019maternal for whole brain, cerebellum and neocortex size, @todorov2019primate for hippocampus and neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, cerebellum, hippocampus and striatum size.
+Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (cerebellum, hippocampus, main olfactory bulb (MOB), neocortex, striatum), @powell2017re and @powell2019maternal for whole brain, cerebellum and neocortex size, @todorov2019primate for hippocampus and neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, cerebellum, hippocampus and striatum size.
 They were freely available in the main manuscript or supplementary materials.
@@
 Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Evolutionary Models (b)).
+Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Models of trait evolution (b)).
 
@@
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Evolutionary Models (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Models of trait evolution (b)).
 
@@
 
-### Evolutionary models: does interspecific interactions shape brain size evolution?
-
-\hfill
-
-(a)	Fitting evolutionary models
+### Models of trait evolution: does interspecific interactions shape brain size evolution?
+
+\hfill
+
+(a)	Fitting models of trait evolution
 
@@
 for brain, EQ, and MOB ratio) to reach more symmetrical distributions.
-Models without competition, Brownian motion (i.e.
+Models without competition, Brownian Motion (i.e.
 BM), Orstein-Uhlenbeck process (i.e.
@@
 
-$f_{lin}(\lambda)=\lambda_{0}N^{−r}$
-
-$f_{exp}(\lambda)=\lambda_{0}(1 − N/K)$
+$f_{lin}(\lambda)=\lambda_{0}(1 − N/K)$
+
+$f_{exp}(\lambda)=\lambda_{0}N^{−r}$
 
@@
 In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Supplementary Figure 3) and (ii) to assess the species dietary guild (see Supplementary Figure 2) which can cause sensitivity of the results to the chosen parameters.
-To account for these three sources of variability we refitted several times the six evolutionary model types (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeographic and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
+To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeography and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
 equal probability for each possible value to be selected) and (3) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence.
@@
 
+### Models of species diversification
+
+We investigated how the Primate taxon diversified over time.
+Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
+Particularly, we used *ClaDS2*, the model with constant turnover (i.e.
+constant ratio between extinction and speciation rates).
+This Bayesian approach considers speciation rate heterogeneity by modeling small shifts in this rate at speciation events.
+In other words, the daughter lineage is assumed to inherit new speciation rates that is sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the parental speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
+Three independent chains were run and their respective convergence was checked using a Gelman-Rubin diagnostic criterion.
+The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
+This latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
+
+|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of "known" taxa among all possibles ones.
+@estrada2017impending estimated that, given current knowledge, the primate lineage should be composed of 504 species.
+This means that the current sampling fraction is around 73%.
+We thus parameterized the *ClaDS* algorithm with this value for the estimate sampling fraction.
+Yet, given that the extant number of primate species is subject to controversy, and also because the estimated sampling fraction affects diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
+At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each primate species, as well as the mean rate (given all lineages) through time.
+
 ### Phylogenetic regressions
@@
 
-To determine the direction of the selection of species co-occurrence on size of brain regions for which competitive models fitted the best, we fitted Gaussian phylogenetic regressions (i.e.
-accounting for a variance-covariance matrix based on phylogenetic distances) for each brain region individually and for frugivorous species only.
-We here considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
+To determine the direction of the selection of species co-occurrence on size of brain regions for which competitive models fitted the best, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
+a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients but its diagonal multiplied by lambda) for each brain region individually and for frugivorous species only.
+We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we specifically focused on brain areas for which the evolutionary history was best described by competitive models.
+Here specifically, we considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
 If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
@@
 |    The response variable was the relative size of areas shown as better described by competitive phylogenetic scenario (see above).
-Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see below).
+Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see Model Robustness).
 In this model, the covariates (i.e.
@@
 
-TO BE COMPLETED
+\hfill
+
+In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different brain traits against the diversification rate (i.e.
+accounting for both, speciation and extinction) estimated for each species by the *ClaDS* algorithm.
+Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values in this case.
+
+\hfill
 
@@
 
-Models were fitted using the “pgls” function from the *caper* package [@caper], with the lambda parameter (i.e.
-indicating whether the trait is subject to selection if $\lambda$ > 1) estimated by maximum-likelihood (argument “model” set to “lambda”; i.e.
-fits the Pagel’s lambda model, a derivative of the Brownian Motion model (REF)).
+Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (i.e.
+indicating whether the trait is subject to selection, or corresponds to Brownian Motion, if $\lambda$ tends towards 1) estimated by maximum-likelihood (argument “model” set to “lambda”).
 Bootstrapping over `r repetitionBootstrap` independent replicates was done so as to obtain confidence intervals.
 Other function parameters were set to default.
-Prior fitting, if skewed, covariates were transformed with deemed appropriate functions to reach more symmetrical distribution (e.g.
-we faced X skewed distributions that were X transformed, REF).
-Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Supplementary Figure X).
-We did not observe correlation issue among predictors either (max VIF < XX, REF).
+Prior fitting, the covariates were square-rooted to reach more symmetrical distribution.
+Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Supplementary Material).
+We did not observe correlation issue among predictors either [max VIF < 2, @mundry2014statistical].
 
@@
 
-To assess model stability with regards to singular points, we discarded one observation at a time and quantified model sensitivity using various predictors relying on (Dffits, dfbetas, cook distance, and leverage, REF; Supplementary Table 1).
-These controls did not point out important variability.
+To assess model stability with regards to singular points, we computed the dfbetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree.
 To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10,000 possible trees from the 10kTrees project.
@@
 if body mass was provided by different datasets etc.).
-The results of this sensitivity analysis are shown in Supplementary Table 2 and emphasizes that there is no major effect.
-Note that the main model was fitted with the consensus tree.
+For the diversification analysis specifically, we also assessed the sensitivity to changes in hypothesized fraction of known primate taxon by refitting the models for values ranging between 60 to 95% (as specified before) using the "standard" dataset and the consensus tree.
+The results of these assessment (min-max of estimates) are shown in Supplementary Material. It emphasizes weak sensitivity of the results.
 
@@
 DeCasien and collaborators, Lauren E.
-Powell, Orlin S.
+Powell and collaborators, Orlin S.
 Todorov and collaborators, Erik P.
 Willems and collaborators, Fiona Pearce and collaborators, Navarrete and collaborators, and Cyril C.
-Grueter who do not know us, but provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J.
+Grueter who provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J.
 Matzke for available algorithm scripts allowing us to implement and better understand the methods.
@@
 
-```{r figresultsevolution, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap="AICc weights of fitted evolutionary models for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
-The points represent the average AICc weight obtained (when considering the five models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see Phylogenetic models, Evolutionary Models (b)).
+```{r figresultsevolution, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap="AICc weights of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
+The points represent the average AICc weight obtained (when considering the five models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see Phylogenetic models, Models of trait evolution (b)).
 (1) Whole brain (EQ) (2) Striatum (3) MOB (4) Neocortex (5) Hippocampus (6) Cerebellum."}
@@
 ```
+
+# Authors' contribution
+
+BR conceived the study, collected, cleaned and analyzed the data, and wrote the first version of the manuscript and subsequently revised it.
+BP-L helped with analyses, adapted them for, and ran them on, the cluster, and revised the manuscript multiple times.
+The authors declare having no conflict of interests.
+All authors gave final approval for publication and agree to be held accountable for the work performed therein.
 
@@
 
-nbPlot=4
+nbPlot=2
 
@@
   addGrid(xmin=1, xmax=ncol(dataForSample_rdcplot), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample_rdcplot), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
-  #cat('\r\n\r\n') #Allows to consider plot as a new figure at each step of the loop
+  #if(p==2){cat('\r\n\r\n')} #Allows to consider plot as a new figure at each step of the loop
 }

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
new

@@ -2,7 +2,7 @@
 #### EvolutionaryHistoryClusterRun
 ####---------------------------------
 
-# This script allows running one the ENS cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
 # This is the example script for low frugivory and low folivory threshold i.e.:
  
 # a=1
@@ -50,8 +50,6 @@ library(BioGeoBEARS)
 library(optimx)
 library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
-#??
-library(ellipsis)
 
 #Parallelizing
 # library(snow)
@@ -126,8 +124,8 @@ for(c in 1:length(geographicThresholdVector)){
   load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
   
   summaryData_init <- summaryData
-  source("Functions.R")
-  source("toolbox.R")
+  # source("Functions.R")
+  # source("toolbox.R")
 
   parrallel_run <- function(d){
     
@@ -195,7 +193,7 @@ for(c in 1:length(geographicThresholdVector)){
         }
         
         tryCatch(
-          {o2<-fitContinuous(subtree,M,model="BM")#, ncores=1)
+          {o2<-fitContinuous(subtree,M,model="BM", ncores=1)
           BM.log_lik<-o2$opt$lnL
           BM.sig2<-o2$opt$sigsq
           BM.z0<-o2$opt$z0
@@ -213,7 +211,7 @@ for(c in 1:length(geographicThresholdVector)){
         
         tryCatch(
           {
-            o3<-fitContinuous(subtree,M,model="OU")#, ncores=1)
+            o3<-fitContinuous(subtree,M,model="OU", ncores=1)
             OU.log_lik<-o3$opt$lnL
             OU.sig2<-o3$opt$sigsq
             OU.alpha<-o3$opt$alpha
@@ -233,7 +231,7 @@ for(c in 1:length(geographicThresholdVector)){
 
         tryCatch(
           {
-            o32<-fitContinuous(subtree,M,model="EB")#, ncores=1)
+            o32<-fitContinuous(subtree,M,model="EB", ncores=1)
             EB.log_lik<-o32$opt$lnL
             EB.sig2<-o32$opt$sigsq
[…]

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
Update EvolutionaryHistoryClusterRun_a1b1_new.R

@@ -127,6 +127,7 @@ for(c in 1:length(geographicThresholdVector)){
   # source("Functions.R")
   # source("toolbox.R")
 
+
   parrallel_run <- function(d){
     
     set.seed(d)

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
Update EvolutionaryHistoryClusterRun_a1b1_new.R

@@ -4,7 +4,7 @@
 
 # This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
 # This is the example script for low frugivory and low folivory threshold i.e.:
- 
+
 # a=1
 # frugivoryThreshold=frugivoryThresholdVector[a]
 
@@ -15,8 +15,6 @@
 ##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
 ###Set working directory
-# scp -r /Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/* bperez@jord.biologie.ens.fr:/users/biodiv/bperez/data/others/Benji/Evolutionary_history/
-# setwd("/Users/bperez/ownCloud/Recherche/These/ENS/Autres/Benjamin/Evolutionary_history/")
 setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
 
 dir.create(file.path("Sample_size"), showWarnings = FALSE)
@@ -26,36 +24,29 @@ dir.create(file.path("Dataplot"), showWarnings = FALSE)
 
 #Import environment
 rm(list=ls())
-load("geography_traits_biogeobears.RData")
 
-##--------
-#Home made functions
-#To source all phylogenetics functions (biogeobears + models of evolution)
-source("Functions.R")
+#load("geography_traits_biogeobears.RData")
 
-##--------
 
-##--------
 #Libraries
 
-#Phylogenetics
-library(caper)
-library(ape)
-library(phytools)
-library(geiger)
-library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
-library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
-library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
-library(BioGeoBEARS)
-library(optimx)
-library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+# require(devtools)
+# install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
 
+# Phylogenetics
+# library(caper)
+# library(ape)
+library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
[…]

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_raw.R
add simmap

@@ -585,9 +585,9 @@ for(c in 1:length(geographicThresholdVector)){
     
     colnames(summaryData)[colnames(summaryData)=="DietaryGuild"] <- "Guild"
     
-    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
+    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_BrainRaw", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
       print("Brain")
-      summaryData$ratioBrain <-  summaryData$Brain/summaryData$Bodymass
+      summaryData$ratioBrain <-  summaryData$Brain
       hist(summaryData$ratioBrain )
       summaryData$ratioBrain.log <- log(summaryData$ratioBrain)
       resultBrainFrugivory <- runComparisonModelsCompetition(
@@ -600,28 +600,13 @@ for(c in 1:length(geographicThresholdVector)){
         ana_events_tables=BSM_output$RES_ana_events_tables,
         clado_events_tables=BSM_output$RES_clado_events_tables
       )
-      write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
+      write.table(resultBrainFrugivory, paste("OutputEvolModel/Output_evolutionary_history_BrainRaw", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     }
+
     
-    if (!file.exists(paste("OutputEvolModel/Output_evolutionary_history_EQ", a, "_", b, "_", c, "_", d, ".txt", sep=""))){
-      print("EQ")
-      resultEQFrugivory <- runComparisonModelsCompetition(
-        simmap=simmapdiet1,
-        data=summaryData[!is.na(summaryData$EQ)&!is.na(summaryData$geographicCode)&summaryData$SpeciesForPhylogeny%in%phylo$tip.label,],
-        subgroup="Fruit",
-        numberMaps=numberSimulations,
-        trait="EQ.log",
-        tree=phylo,
-        ana_events_tables=BSM_output$RES_ana_events_tables,
-        clado_events_tables=BSM_output$RES_clado_events_tables
[…]

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2_new.R

@@ -69,7 +69,7 @@ progression=0
 a=1
 frugivoryThreshold=frugivoryThresholdVector[a]
 
-b=1
+b=2
 folivoryThreshold=folivoryThresholdVector[b] 
 
 ##------------

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1_new.R

@@ -66,7 +66,7 @@ progression=0
 ##--------
 
 # Set the frugivory and folivory threshold to consider:
-a=1
+a=2
 frugivoryThreshold=frugivoryThresholdVector[a]
 
 b=1

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2_new.R

@@ -5,10 +5,10 @@
 # This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
 # This is the example script for low frugivory and low folivory threshold i.e.:
 
-# a=1
+# a=2
 # frugivoryThreshold=frugivoryThresholdVector[a]
 
-# b=1
+# b=2
 # folivoryThreshold=folivoryThresholdVector[b] 
 
 

### 2021-05-31 Scripts/Analysis1_competitionsignal/EvolutionaryHistory_make_simmap.R

@@ -1,0 +1,386 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+setwd("/Users/bperez/Documents/GitHub/Meta_analysis_cognition_primates/Processed_data/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+
+load("../BioGeoBEARS/geography_traits_biogeobears.RData")
+
+
+#Libraries
+
+# require(devtools)
+# install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
+
+# Phylogenetics
+# library(caper)
+# library(ape)
+library(phytools)
+# library(geiger)
+# library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA)
+# library(BioGeoBEARS)
+# library(optimx)
+# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#Parallelizing
+# library(parallel)
+
+##--------
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
[…]

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2_raw.R
new raw scripts

@@ -1,0 +1,723 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+
+load("geography_traits_biogeobears.RData")
+
+
+#Libraries
+
+# require(devtools)
+# install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
+
+# Phylogenetics
+# library(caper)
+# library(ape)
+library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
+# library(geiger)
+# library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+# library(BioGeoBEARS)
+# library(optimx)
+# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#Parallelizing
+# library(parallel)
+
+##--------
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
[…]

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1_raw.R

@@ -1,0 +1,723 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+
+load("geography_traits_biogeobears.RData")
+
+
+#Libraries
+
+# require(devtools)
+# install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
+
+# Phylogenetics
+# library(caper)
+# library(ape)
+library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
+# library(geiger)
+# library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+# library(BioGeoBEARS)
+# library(optimx)
+# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#Parallelizing
+# library(parallel)
+
+##--------
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
[…]

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2_raw.R

@@ -1,0 +1,723 @@
+####---------------------------------
+#### EvolutionaryHistoryClusterRun
+####---------------------------------
+
+# This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
+# This is the example script for low frugivory and low folivory threshold i.e.:
+
+# a=1
+# frugivoryThreshold=frugivoryThresholdVector[a]
+
+# b=1
+# folivoryThreshold=folivoryThresholdVector[b] 
+
+
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+###Set working directory
+setwd("/users/biodiv/bperez/data/others/Benji/Evolutionary_history_2/")
+
+dir.create(file.path("Sample_size"), showWarnings = FALSE)
+dir.create(file.path("extdata"), showWarnings = FALSE)
+dir.create(file.path("OutputEvolModel"), showWarnings = FALSE)
+dir.create(file.path("Dataplot"), showWarnings = FALSE)
+
+#Import environment
+rm(list=ls())
+
+load("geography_traits_biogeobears.RData")
+
+
+#Libraries
+
+# require(devtools)
+# install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
+
+# Phylogenetics
+# library(caper)
+# library(ape)
+library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
+# library(geiger)
+# library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
+# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
+# library(BioGeoBEARS)
+# library(optimx)
+# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+
+#Parallelizing
+# library(parallel)
+
+##--------
+##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
[…]

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
results

@@ -26,6 +26,7 @@ dir.create(file.path("Dataplot"), showWarnings = FALSE)
 rm(list=ls())
 
 load("geography_traits_biogeobears.RData")
+#load("../BioGeoBEARS/geography_traits_biogeobears.RData")
 
 
 #Libraries
@@ -104,17 +105,16 @@ checkSampleRange <- rep(NA, times=repetition)
 
 for(c in 1:length(geographicThresholdVector)){
   
-
+  ## Adding the co-occurence
+  
+  summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
+  
+  load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
+  
+  summaryData_init <- summaryData
+  
+  
   parrallel_run <- function(d){
-    
-    
-    ## Adding the co-occurence
-    
-    summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
-    
-    load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
-    
-    summaryData_init <- summaryData
 
     base::set.seed(d)
     base::set.seed(d)
@@ -145,7 +145,7 @@ for(c in 1:length(geographicThresholdVector)){
       data.grouped<-subset(data, Guild==subgroup)
       mass<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
       names(mass)<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
-      nc<-name.check(tree,mass)
+      nc<-geiger::name.check(tree,mass)
       data.grouped.tree<-drop.tip(tree,nc$tree_not_data)
       subdata<-data.grouped[which(data.grouped$SpeciesForPhylogeny%in%data.grouped.tree$tip.label),]
       
@@ -177,7 +177,7 @@ for(c in 1:length(geographicThresholdVector)){
         names(M)<-subdata$SpeciesForPhylogeny
         M<-subset(M,M!='NA')
         
-        nc<-name.check(subtree,M)
[…]

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b1_new.R

@@ -145,7 +145,7 @@ for(c in 1:length(geographicThresholdVector)){
       data.grouped<-subset(data, Guild==subgroup)
       mass<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
       names(mass)<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
-      nc<-name.check(tree,mass)
+      nc<-geiger::name.check(tree,mass)
       data.grouped.tree<-drop.tip(tree,nc$tree_not_data)
       subdata<-data.grouped[which(data.grouped$SpeciesForPhylogeny%in%data.grouped.tree$tip.label),]
       
@@ -177,7 +177,7 @@ for(c in 1:length(geographicThresholdVector)){
         names(M)<-subdata$SpeciesForPhylogeny
         M<-subset(M,M!='NA')
         
-        nc<-name.check(subtree,M)
+        nc<-geiger::name.check(subtree,M)
         if(is.list(nc)){
           subtree<-drop.tip(subtree,nc$tree_not_data)
         }

### 2021-06-01 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
Update EvolutionaryHistoryClusterRun_a1b1_new.R

@@ -36,15 +36,15 @@ load("geography_traits_biogeobears.RData")
 
 # Phylogenetics
 # library(caper)
-# library(ape)
-library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
+library(ape)
+library(phytools) #, lib.loc = "/users/biodiv/bperez/packages/")
 # library(geiger)
 # library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
-# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
 library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
-# library(BioGeoBEARS)
-# library(optimx)
-# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
 #Parallelizing
 # library(parallel)
@@ -205,7 +205,9 @@ for(c in 1:length(geographicThresholdVector)){
         EB.z0<-o32$opt$z0
         EB.aicc<-o32$opt$aicc
         EB.conv<-as.numeric(tail(o32$res[,length(o32$res[1,])],n=1))
+
         
+        print(group.map2)
         
         o4<-fit_t_comp_subgroup(full.phylo=tree,
                                 ana.events=ana_events_tables[[i]],
@@ -555,6 +557,9 @@ for(c in 1:length(geographicThresholdVector)){
     #simmapdiet1 <- make.simmap(tree=phylo, vectorDiet, model="ARD", pi="estimated", nsim=numberSimulations)#inequal and not symmetrical rate of transition from folivory to frugivory etc...
     
     load(file=paste("Simmap/Output_simmap_transition", a, "_", b, "_", c, "_", d, ".Rdata", sep=""))
+    
+    
+    print(simmapdiet1)
     
     write.table(as.vector(simmapdiet1[[1]]$Q[,1]), paste("OutputEvolModel/Output_simmap_transition", a, "_", b, "_", c, "_", d, ".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
Update EvolutionaryHistoryClusterRun_a1b1_new.R

@@ -35,10 +35,10 @@ load("geography_traits_biogeobears.RData")
 # install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
 
 # Phylogenetics
-# library(caper)
+library(caper)
 library(ape)
 library(phytools) #, lib.loc = "/users/biodiv/bperez/packages/")
-# library(geiger)
+library(geiger)
 # library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
 library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
 library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
@@ -47,7 +47,7 @@ library(optimx)
 library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
 #Parallelizing
-# library(parallel)
+library(parallel)
 
 ##--------
 ##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -110,6 +110,7 @@ for(c in 1:length(geographicThresholdVector)){
   summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
   
   load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
+  # load(paste("../BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
   
   summaryData_init <- summaryData
   
@@ -118,8 +119,18 @@ for(c in 1:length(geographicThresholdVector)){
 
     base::set.seed(d)
     base::set.seed(d)
+    rm(.Random.seed)
+    base::set.seed(d)
+    base::set.seed(d)
     
     print(runif(1))
+    
+    
+    for (rep in 1:1000){
+      print(runif(1))
+    }
+    
+    print("end")
 
     runComparisonModelsCompetition <- function(
       
@@ -142,11 +153,30 @@ for(c in 1:length(geographicThresholdVector)){
       
       #isolate data from subgroup of interest 
       group.map<-simmap
[…]

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b1_new.R
update

@@ -123,15 +123,7 @@ for(c in 1:length(geographicThresholdVector)){
     base::set.seed(d)
     base::set.seed(d)
     
-    print(runif(1))
-    
-    
-    for (rep in 1:1000){
-      print(runif(1))
-    }
-    
-    print("end")
-
+   
     runComparisonModelsCompetition <- function(
       
       #######################
@@ -153,30 +145,13 @@ for(c in 1:length(geographicThresholdVector)){
       
       #isolate data from subgroup of interest 
       group.map<-simmap
-      
-      
-      print(nrow(data))
-      print(table(data$Guild))
-      
       data.grouped<-data[which(data$Guild==subgroup),]
-      
-      print(table(data.grouped$Guild))
-      
-      print(nrow(data.grouped))
       
       mass<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
       names(mass)<-data.grouped[,which(colnames(data.grouped)=="SpeciesForPhylogeny")]
       nc<-geiger::name.check(tree,mass)
+      
       data.grouped.tree<-drop.tip(tree,nc$tree_not_data)
-      
-      # test
-      if (Ntip(data.grouped.tree)!=nrow(data.grouped)){
-        data.grouped.tree<-drop.tip(data.grouped.tree,tip = data.grouped.tree$tip.label[which(!data.grouped.tree$tip.label %in% data.grouped$SpeciesForPhylogeny)])
-      }
-      
-      print(nrow(data.grouped))
-      print(Ntip(data.grouped.tree))
-      
       subdata<-data.grouped[which(data.grouped$SpeciesForPhylogeny%in%data.grouped.tree$tip.label),]
       
       #set up analyses
@@ -236,14 +211,6 @@ for(c in 1:length(geographicThresholdVector)){
         EB.aicc<-o32$opt$aicc
         EB.conv<-as.numeric(tail(o32$res[,length(o32$res[1,])],n=1))
 
-        
-        print(Ntip(tree))
-        print(nrow(ana_events_tables[[i]]))
-        print(group.map2)
-        print(nrow(group.map2))
-        print(M)
-        print(length(M))
-        
         o4<-fit_t_comp_subgroup(full.phylo=tree,
                                 ana.events=ana_events_tables[[i]],
                                 clado.events=clado_events_tables[[i]],
[…]

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2_new.R

@@ -26,6 +26,7 @@ dir.create(file.path("Dataplot"), showWarnings = FALSE)
 rm(list=ls())
 
 load("geography_traits_biogeobears.RData")
+#load("../BioGeoBEARS/geography_traits_biogeobears.RData")
 
 
 #Libraries
@@ -34,19 +35,19 @@ load("geography_traits_biogeobears.RData")
 # install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
 
 # Phylogenetics
-# library(caper)
-# library(ape)
-library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
-# library(geiger)
+library(caper)
+library(ape)
+library(phytools) #, lib.loc = "/users/biodiv/bperez/packages/")
+library(geiger)
 # library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
-# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
 library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
-# library(BioGeoBEARS)
-# library(optimx)
-# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
 #Parallelizing
-# library(parallel)
+library(parallel)
 
 ##--------
 ##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -104,23 +105,25 @@ checkSampleRange <- rep(NA, times=repetition)
 
 for(c in 1:length(geographicThresholdVector)){
   
-
+  ## Adding the co-occurence
+  
+  summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
+  
+  load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
[…]

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a1b2_raw.R

@@ -26,6 +26,7 @@ dir.create(file.path("Dataplot"), showWarnings = FALSE)
 rm(list=ls())
 
 load("geography_traits_biogeobears.RData")
+#load("../BioGeoBEARS/geography_traits_biogeobears.RData")
 
 
 #Libraries
@@ -34,19 +35,19 @@ load("geography_traits_biogeobears.RData")
 # install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
 
 # Phylogenetics
-# library(caper)
-# library(ape)
-library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
-# library(geiger)
+library(caper)
+library(ape)
+library(phytools) #, lib.loc = "/users/biodiv/bperez/packages/")
+library(geiger)
 # library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
-# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
 library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
-# library(BioGeoBEARS)
-# library(optimx)
-# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
 #Parallelizing
-# library(parallel)
+library(parallel)
 
 ##--------
 ##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -104,23 +105,25 @@ checkSampleRange <- rep(NA, times=repetition)
 
 for(c in 1:length(geographicThresholdVector)){
   
-
+  ## Adding the co-occurence
+  
+  summaryData$geographicCode <- matrixRangingSensitivity[match(summaryData$SpeciesForPhylogeny,matrixRangingSensitivity$SpeciesForPhylogeny),which(thresholdPresenceRange==geographicThresholdVector[c])]   
+  
+  load(paste("BioGeoBEARS/BSM_output_file", c, ".Rdata", sep=""))
[…]

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryClusterRun_a2b2_new.R

@@ -5,10 +5,10 @@
 # This script allows running one the cluster the different scenario (non-competitive vs. competitive) of brain size evolution in frugivorous primates. 
 # This is the example script for low frugivory and low folivory threshold i.e.:
 
-# a=2
+# a=1
 # frugivoryThreshold=frugivoryThresholdVector[a]
 
-# b=2
+# b=1
 # folivoryThreshold=folivoryThresholdVector[b] 
 
 
@@ -26,6 +26,7 @@ dir.create(file.path("Dataplot"), showWarnings = FALSE)
 rm(list=ls())
 
 load("geography_traits_biogeobears.RData")
+#load("../BioGeoBEARS/geography_traits_biogeobears.RData")
 
 
 #Libraries
@@ -34,19 +35,19 @@ load("geography_traits_biogeobears.RData")
 # install_version("phytools", version = "0.6.99", repos = "http://cran.us.r-project.org", lib="/users/biodiv/bperez/packages/")
 
 # Phylogenetics
-# library(caper)
-# library(ape)
-library(phytools, lib.loc = "/users/biodiv/bperez/packages/")
-# library(geiger)
+library(caper)
+library(ape)
+library(phytools) #, lib.loc = "/users/biodiv/bperez/packages/")
+library(geiger)
 # library(MCMCglmm, lib.loc = "/users/biodiv/bperez/packages/")
-# library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
+library(ellipsis, lib.loc = "/users/biodiv/bperez/packages/")
 library(RPANDA, lib.loc = "/users/biodiv/bperez/packages/")
-# library(BioGeoBEARS)
-# library(optimx)
-# library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
+library(BioGeoBEARS)
+library(optimx)
+library(svMisc, lib.loc = "/users/biodiv/bperez/packages/")
 
 #Parallelizing
-# library(parallel)
+library(parallel)
 
 ##--------
 ##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -66,10 +67,10 @@ progression=0
 ##--------
 
 # Set the frugivory and folivory threshold to consider:
[…]

### 2021-06-02 Scripts/Analysis1_competitionsignal/EvolutionaryHistory_make_simmap.R

@@ -123,6 +123,10 @@ for(c in 1:length(geographicThresholdVector)){
     
     base::set.seed(d)
     base::set.seed(d)
+    rm(.Random.seed)
+    base::set.seed(d)
+    base::set.seed(d)
+    
     
     #####  To run with different d values 
     
@@ -346,8 +350,11 @@ for(c in 1:length(geographicThresholdVector)){
     #save data for plotting
     if(a==1&b==1&c==1&d==1){
       summaryDataForPlot <- summaryData
-      #write.table(summaryData, "Dataplot.txt", row.names=FALSE, col.names=TRUE, sep="\t")
+      write.table(summaryData, "Dataplot.txt", row.names=FALSE, col.names=TRUE, sep="\t")
     }
+    
+    #SaveDataGeneral
+    write.table(summaryData, paste("Dataplot/Dataplot", a, "_", b, "_", c, "_", d,".txt", sep=""), row.names=FALSE, col.names=TRUE, sep="\t")
     
 
     ##--------

### 2021-06-25 Article/Article.Rmd
Update analysis diversification (Bayesian) + finish writing

@@
 ---
-title: "Primate Cognition and the Red Queen Hypothesis"
+title: \Huge \textbf{Species sympatry constrains brain size evolution in Primates}
 # date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 author: 
-  - name: Benjamin Robira
+  - name: \textit{Benjamin Robira}
     email: benjamin.robira@normalesup.org
@@
     correspondence: true
-  - name: Benoit Perez-Lamarque
+  - name: \textit{Benoit Perez-Lamarque}
+    email: benoit.perez@ens.psl.eu
     institute: [ENS, MNHN]
+    correspondence: true
 institute:
-  - CEFE: Centre d’Ecologie Fonctionnelle et Evolutive, Université de Montpellier & CNRS, Montpellier, France.
+  - CEFE: Centre d’Écologie Fonctionnelle et Évolutive, Université de Montpellier & CNRS, Montpellier, France.
   - MH: Anthropologie et Ethnobiologie, Centre National de la Recherche Scientifique/Muséum National d'Histoire Naturelle, University Paris Diderot, Sorbonne Paris Cité, Musée de l'Homme, Paris, France
-  - ENS: Institut de Biologie de l’Ecole Normale Supérieure (IBENS), Ecole Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France
-  - MNHN: Institut de Systématique, Evolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France
+  - ENS: Institut de Biologie de l’École Normale Supérieure (IBENS), École Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France
+  - MNHN: Institut de Systématique, Évolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France
 
@@
 always_allow_html: true
+link-citations: yes
 
@@
 header-includes:
-  - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
+# - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
   - \usepackage{lineno} # For line numbering
@@
   - \captionsetup[figure]{font=small}
+  - \newcommand{\beginsupplement}{
+      \setcounter{table}{0}  
+      \renewcommand{\thetable}{S\arabic{table}} 
+      \setcounter{figure}{0} 
+      \renewcommand{\thefigure}{S\arabic{figure}}
+    }
 ---
@@
 library(ape)
+library(phylolm)
+
+#Segmentation
+library(strucchange)
 
@@
 nlme,
-pgls
+MCMCglmm,
+coda,
+strucchange
 )
@@
 load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/geography_traits_biogeobears.RData")
+
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/PGLSdiversification_withautocorr.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/PGLSdirectionSelection.RData")
 
@@
 
-```{r,  warning = FALSE, message = FALSE}
-#For the moment because this was not run: to delete after
-repetitionTrees=50
-repetitionModels=30
-repetitionBootstrap=200
-
-repetition=7#length(frugivoryThresholdVector)*length(folivoryThresholdVector)*length(geographicThresholdVector)*randomSampling - 1
+**Abstract:** The diversity in animal cognition raises the question of its underlying evolutionary drivers.
+Selection upon more advanced cognitive abilities can stem from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*), among generations (*Cultural Intelligence Hypothesis*), between social units (*Napoleonic Intelligence Hypothesis*), or with the rest of their environment (*Ecological Intelligence Hypothesis*).
+These hypotheses were limited to within-species scenarios.
+Yet, one species rarely occupies an area alone: Space is a place shared between many species that can interact directly or indirectly.
+For species occupying a same dietary niche, interspecific competition could induce a cognitive evolutionary arms race, so as to outperform competitors.
+Furthermore, all species act upon the spatio-temporal distribution of resources, hence contribute to increasing the uncertainty for a third species to infer resource location and availability.
+This would ultimately shape the cognitive machinery involved to allow sufficient harvesting.
+In addition, sympatric species can leave traces of passage and of resource presence that can be cognitively processed by a third species to find it more efficiently.
+As such, to test whether species co-occurrence shaped current patterns of cognition, we used primates as a study example and retraced the evolutionary history of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
+We found that the evolution of the relative size of areas involved in foraging-related information processing and/or retention, as well as in areas related to processing social information, are better described by models accounting for species co-occurrence within dietary guilds.
+More precisely for these brain areas, species co-occurrence was associated to a decrease, and never to an increase, of their relative size.
+Coherently with the observed wide variability in sympatry rate and intensity, the degree of encephalisation was unrelated to the evolutionary success of a lineage (i.e.
+its diversification rate).
+Overall, this comparative study suggests that species co-occurrence stands as a brake to positive selection towards larger cognitive abilities, yet leaves open the question of the underlying ecological mechanisms at play.
+
+<!-- subject to an arms race among species (*Red Queen Intelligence Hypothesis*).  -->
+
+**Keywords:** "Brain size - Cognition - Cooperation - Competition - Intelligence evolution - Primates - Species co-occurrence"
+
+<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
+
+```{r wordCount}
+words <- RmdWords("Article.Rmd")
+```
+
+<!-- TC:ignore -->
+**Word Count:** `r words$num_words` \newline
+<!-- Character Count: `r words$num_char` -->
+<!-- TC:endignore -->
+
+\newpage
+
+# Introduction
+
+On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@dunbar2017there].
+It remains puzzling why humans have a brain that is that large, relatively to body size, compared to other animals, or why primate brain architecture, in general, is much more complex than observed in other taxa.
+Overall, the evolution of the brain is the consequence of constraints [e.g.
+energetic limitations, @navarrete2011energetics], but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
+
+|   To grasp the rationale of current hypotheses that aim to describe the evolution of cognition [@van2006some; @dunbar2017there], consider a primate individual foraging for food.
+Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
+The chosen focal is not looking for any type of food but specific one, as for instance, most primate species often look for fruits.
+Finding fruits for a primate is not an easy task.
+In fact, fruits are the archetype of a hard-to-find resource likely to promote cognitive development because fruit trees are rare, dispersed, and do not produce constantly along the year nor between years, albeit their fruiting period remains nonetheless predictable [@janmaat2016spatio].
+Additionally, they are energy-rich, allowing expansion of costly tissues such as brain tissues [@clutton1980primates].
+Overall, primates thus show remarkable abilities to navigate precisely and target fruit trees likely to yield ripe resource despite they are out of their sensory range [@trapanese2019review], in part because of advanced spatio-temporal information retention [e.g.
+spatial knowledge: @normand2009forest; @robiraroute, temporal knowledge: @janmaat2006evidence; @janmaat2013chimpanzees; @janmaat2013tai].
+
+|   When the resource is out of sight, moving at random could mean travelling unnecessary long distances to finally reach a potentially void tree.
+Hence, for the focal, being capable of processing immediate environmental cues and clues to know where specifically to find fruit trees [@dall2005information; @grove2013evolution] and whether it is probable that these trees currently yield fruits [@dall2005information; @robirainreview; @janmaat2016spatio] would be a considerable advantage.
+Having an appropriate cognitive machinery may avoid costly detours and time recursions to food patches adequately.
+This simple picture draws the basis of the *Ecological Intelligence Hypothesis* [@clutton1980primates; @milton1981distribution; @rosati2017foraging] which stipulates that cognition was selected as a way to buffer the spatio-temporal complexity of the environment (e.g.
+@van2012large).
+
+|   In its quest for food, however, the focal might not be alone: For instance, primates often form social groups [@kappeler2002evolution] in which group members spend considerable time together, have established bounds and constantly share information.
+Thus, they might altogether look for, and process, cues and clues leading to food sources.
+To do so, being able to process signals emitted by other maneuvers would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian].
+This therefore means plenty of additional information to process, and constitutes the socle of the *Social Intelligence Hypothesis* [@dunbar2017there].
+
+|   In the focal group, however, all individuals are not equally knowledgeable: Perhaps because some have more experience than others, such as the elderly ones would be more experienced than the youths, with the latter thus learning from the former [@laland2004social].
+For instance, young individuals may progressively learn how to process a specific tool to access a hidden comestible part as for nuts [@boesch1994nut] by observing and reproducing, or possibly being teached (learning ways detailed in @estienne2019acquisition).
+In other words, there is vertical transmission that passes by over generations and knowledge thereby accumulates: This is the *Cultural Intelligence Hypothesis* [@whiten2007evolution; @reader2002social], also known as the *Vygotskian Intelligence Hypothesis* in humans [@herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social].
+
+|   Finally, while the group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild].
+The neighboring groups might indeed be competitors for food, mates or any essential resource, and as much as it is advantageous to be able to read through the environment and intra-group companions, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g.
+group size), a view brought by the *Napoleonic Intelligence Hypothesis* [@ashton2020interactions].
+
+|   Yet, in this overly simplistic picture, we moved from a unique individual to a group of individuals and then to multiple groups.
+Never was it question of multiple species.
+Yet, space is a place shared between a plethora of species, some of them occupying a same ecological niche.
+As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from another species with similar ecological preferences, for instance with regards to diet.
+As such, co-occurrence of species from the same guild might contribute into shaping animal cognition.
+On the one side, the presence of sympatric species with overlapping diet could contribute in reinforcing selective pressures for advanced cognition because (i, competition) species would compete for food access (i.e.
+Red Queen paradigm, [@van1973new]).
+Co-occurrence would increase the environmental complexity due to impoverishment of food and addition of noise to the spatio-temporal availability signal because of unforeseen depletion.
+(ii, cooperation/exploitation) sympatric species presence cues could also represent additional information to process to infer resource location and availability.
+Logically then, species with higher brain size would be the most evolutionary successful, thus “booming” and intensively diversifying as for hominins [@melchionna2020macroevolutionary].
+On the other side, (i) the increase in environmental complexity could be such that advanced cognition is no longer adaptive (see for instance [@grove2013evolution] and [@robirainreview] for the limit of the adaptiveness of spatial and temporal cognition respectively), or (ii) the additional cues provided by other species presence would not add, but replace, and perhaps be more easily interpreted than, environmental cues of food availability.
+In this latter case, selective pressure on cognitive abilities would be relaxed, inducing a decrease in brain size in sympatric species compared to lonely species.
+Following this rationale, species living in co-occurrence or not with other species would not face the same evolutionary fate despite initially similar environmental conditions.
+Thus, the evolutionary success of specific lineages would end up unrelated to brain size.
+In this study, we therefore aimed to test how species co-occurrence contributed to shaping the evolutionary history of the encephalisation of the whole, or part of, the brain, and whether this induced a "boom" or a "brake" to cognitive abilities and associated evolutionary success by focusing on frugivorous primates as a study example.
+
+\hfill
+
+```{r sampleCalculation,  warning = FALSE, message = FALSE}
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+repetition=2*2*2*10#length(frugivoryThresholdVector)*length(folivoryThresholdVector)*length(geographicThresholdVector)*randomSampling
+
 checkSampleFruit <- rep(NA, times=repetition)
@@
 checkSampleMOB <- rep(NA, times=repetition)
-
-for(i in 0:repetition){
-
-  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)
-
-  checkSampleFruit[i] <- length(summaryDataOfInterest$DietaryGuild[summaryDataOfInterest$DietaryGuild=="Fruit"])
-  checkSampleLeaf[i]  <- length(summaryDataOfInterest$DietaryGuild[summaryDataOfInterest$DietaryGuild=="Leaf"])
-  checkSampleRange[i]  <- length(summaryDataOfInterest$geographicCode[!is.na(summaryDataOfInterest$geographicCode)])
-  checkSampleBrain[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-  checkSampleEQ[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Bodymass)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-  checkSampleNeocortex[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Neocortex)&summaryDataOfInterest$DietaryGuild=="Fruit",]) 
-  checkSampleHippocampus[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Hippocampus)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-  checkSampleCerebellum[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Cerebellum)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-  checkSampleStriatum[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$Striatum)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-  checkSampleMOB[i]  <- nrow(summaryDataOfInterest[!is.na(summaryDataOfInterest$Brain)&!is.na(summaryDataOfInterest$MOB)&summaryDataOfInterest$DietaryGuild=="Fruit",])
-
-}
+checkSampleRange <- rep(NA, times=repetition)
+
+counter=0
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        counter=counter+1
+        tryCatch(
+        {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleFruit",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+         checkSampleFruit[counter] <- toAdd[1]
+        }, error=function(e){
+          #Do nothing
+        }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleLeaf",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleLeaf[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleRange",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleRange[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleBrain",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleBrain[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleEQ",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleEQ[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleNeocortex",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleNeocortex[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleHippocampus",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleHippocampus[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleCerebellum",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleCerebellum[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleStriatum",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleStriatum[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleMOB",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+           checkSampleMOB[counter] <- toAdd[1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+checkSampleFruit <- unlist(checkSampleFruit)
+checkSampleLeaf <- unlist(checkSampleLeaf)
+checkSampleRange <- unlist(checkSampleRange)
+checkSampleBrain <-  unlist(checkSampleBrain)
+checkSampleEQ <-  unlist(checkSampleEQ)
+checkSampleNeocortex <-  unlist(checkSampleNeocortex)
+checkSampleHippocampus <- unlist(checkSampleHippocampus)
+checkSampleCerebellum <- unlist(checkSampleCerebellum)
+checkSampleStriatum <- unlist(checkSampleStriatum)
+checkSampleMOB <- unlist(checkSampleMOB)
 
@@
 
-**Abstract:** The diversity in animal cognition raises the question of its underlying evolutionary drivers.
-Selection upon more advanced cognitive abilities can stem from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*), among generations (*Cultural Intelligence Hypothesis*), between social units (*Napoleonic Intelligence Hypothesis*), or with the rest of their environment (*Ecological Intelligence Hypothesis*).
-These hypotheses were limited to within-species scenarios.
-Yet, one species rarely occupies an area alone: space is a place shared between many species that can interact directly or indirectly.
-For species occupying a same ecological niche, interspecific competition is particularly expected in this case, but interactions could also represent additional cues and/or noise to cognitively process to find resource or escape predator(s) more efficiently.
-To test whether species co-occurrence shaped current patterns of cognition, we used Primates as a study example and retraced the evolutionary history of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
-We found that the evolution of the relative size of areas involved in foraging-related information processing and/or retention is better described by models accounting for species co-occurrence within dietary guilds which lead to increased relative sizes of these areas.
-This suggests that cognition is subject to an arms race among species (*Red Queen Intelligence Hypothesis*) and shall explain why specific abilities particularly boomed for some lineages, as for instance with Primates.
-
-**Keywords:** "Brain size - Species co-occurrence - Intelligence evolution - Cooperation - Competition"
-
-```{r}
-#My toolbox with several functions
-source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R", local = knitr::knit_global())
-
-words <- RmdWords("Article.Rmd")
-```
-
-<!-- TC:ignore -->
-**Word Count:** `r words$num_words` \newline
-<!-- Character Count: `r words$num_char` -->
-<!-- TC:endignore -->
-
-\newpage
-
-To grasp the rationale of current hypotheses that aim to describe the evolution of animal cognition [@van2006some; @dunbar2017there], consider a primate individual foraging for food.
-Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
-The chosen focal is not looking for any type of food but specific one, as for instance, most primate species often look for fruits.
-Finding fruits for a primate is not an easy task.
-In fact, fruits are the archetype of a hard-to-find resource likely to promote cognitive development because fruit trees are rare, dispersed, and do not produce constantly along the year nor between years, albeit their fruiting period remains nonetheless predictable [@janmaat2016spatio].
-Additionally, they are energy-rich, allowing expansion of costly tissues such as brain tissues [@clutton1980primates].
-Overall, primates thus show remarkable abilities to navigate precisely and target fruit trees likely to yield ripe resource despite they are out of their sensory range [@trapanese2019review], in part because of advanced spatio-temporal information retention [e.g.
-spatial knowledge: @normand2009forest; @robiraroute, temporal knowledge: @janmaat2006evidence; @janmaat2013chimpanzees; @janmaat2013tai].
-
-|	When the resource is out of sight, moving at random could mean travelling unnecessary long distances to finally reach a potentially void tree.
-Hence, for the focal, being capable of processing immediate cues and clues to know where specifically to find fruit trees [@dall2005information; @grove2013evolution] and whether it is probable that these trees currently yield fruits [@dall2005information; @robirainreview; @janmaat2016spatio] would be a considerable advantage.
-Having appropriate cognitive machinery may avoid costly detours and time recursions to food patches adequately.
-This simple picture draws the basis of the *Ecological Intelligence Hypothesis* [@clutton1980primates; @milton1981distribution; @rosati2017foraging] which stipulates that cognition was selected as a way to buffer the spatio-temporal complexity of the environment (e.g.
-@van2012large).
-
-|	In its quest for food, however, the focal might not be alone: for instance, primates often form social groups [@kappeler2002evolution] where group members spend considerable time together, have established bounds and constantly share information.
-Thus, they might altogether look for, and process, cues and clues leading to food sources.
-To do so, being able to process signals emitted by other maneuvers would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian].
-This therefore means plenty of additional stimuli to process, and constitutes the socle of the *Social Intelligence Hypothesis* [@dunbar2017there].
-
-|   In the focal group, however, all individuals are not equally knowledgeable: perhaps because some have more experience than others do, such as the oldest would be more experienced than the youths.
-It is possible that these young individuals learn from the elderly ones [@laland2004social].
-For instance, they may learn how to process a specific tool to access a hidden comestible part as for nuts [@boesch1994nut].
-In other words, there is vertical transmission that passes by over generations and knowledge thereby accumulates: this is the *Cultural Intelligence Hypothesis* [@whiten2007evolution, reader2002social], also known as the *Vygotskian Intelligence Hypothesis* in humans [@herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social].
-
-|   Finally, while the group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild].
-The neighboring groups might indeed be competitors for food, mates or any essential resource, and as much as it is advantageous to be able to read through the environment and intra-group companions, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g.
-group size), a view brought by the *Napoleonic Intelligence Hypothesis* [@ashton2020interactions].
-
-|   In this overly simplistic picture, we moved from a unique individual to a group of individuals and then to multiple groups.
-Never was it question of multiple species: all hypothesized individuals belonged to a singular common species.
-Yet, space is a place shared between a plethora of species, some of them occupying a same ecological niche.
-As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from another species with similar ecological preferences, for instance with regards to diet.
-As such, co-occurrence of species from the same guild might contribute into shaping animal cognition: the more species, the more selective pressure for advanced cognition.
-In this line, because the cognitive abilities would rhyme with ecological success (REF), thus inducing higher population size which ultimately would spur speciations and reduce extinction risk, these cognitively advanced species are expected to "boom", what would be translated into increased species diversification rates.
-In this study, we therefore propose to test for the existence of such an arms race [@van1973new] in cognitive abilities among species - approximated by the size of the whole or specific regions of the brain - that we naturally term the *Red Queen Intelligence Hypothesis*, building on frugivorous primates as a study example, and assess how this might have affected the evolutionary success of the Primate lineage.
-
-\hfill
+# Results
 
 |   Recent tools have been developed to infer the effect of species interactions on trait evolution, either by modelling trait divergence in co-occurring species from a same guild (e.g.
-dietary guild) (Matching Competition: MC models) or considering that the evolutionary rate depends on the on the number of lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
-After reconstructing the biogeography history based on `r minRange` to `r maxRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs.
-folivory; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, $EQ$, as a proxy for `r minEQ` to `r maxEQ` frugivorous, depending on how frugivory was assessed, see Dietary guild), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
-\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species) as well as the likelihoods of simpler models assuming no effect of species interactions, like the simple Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
-stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, REF), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence.
-The use of specific region size relatively to the whole brain size [see @deaner2000comparative for further consideration of scaling methods], and not raw size, rather depicts the evolutionary evolution of cognitive abilities in terms of allocation rather than abilities per se [although it is vividly discussed whether raw measure are anything informative on that point too @logan2018beyond].
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see Phylogenetic models; Models of trait evolution in methods).
-Non-competitive models were the most likely in describing the evolutionary history of the $EQ$ or the striatum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), an area specifically involved in XXX, used here as a control area.
-By contrast, competitive models were most supported in areas involved in sensory abilities (the main olfactory bulb, MOB), immediate information processing (i.e.
-working memory, with the neocortex), or long-term spatio-temporal information retention (hippocampus), (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-When density-dependent models were the best fit, the positive rate (r, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity.
-
-|   To understand the directionality of the selection gradient shaped by co-occurrence (i.e.
-selection for “bigger” brain or “smaller” brain if the more species), we fitted phylogenetic regressions (see (Phylogenetic regressions) a)).
-In these linear regressions, the predicted variable was the relative brain size values of areas for which we observed interspecific competition effect.
-We considered the average surface of the frugivorous species range overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
-
-|   Next, we investigated how brain evolution was related to evolutionary successes, assumed proportional to diversification rate, by using birth-death models of species diversification.
-Present-day diversification rates were estimated using ClaDS [@maliet2019model].
-
-They were positively correlated with XXXX suggesting that XXX.
-However, when accounting for phylogenetic dependence between primate species, the correlations were no longer significant: because advanced cognitive abilities only evolved in a limited number of primate clades (XXX), we thus cannot conclude whether advanced cognitive abilities generally enhance species diversification.
-ClaDS’ estimates of diversification rates through times also suggested that primates diversified faster in the last XXX Myr (as previously shown in XXX), which correlatively mirrored their increased of cognitive abilities.
-
-\hfill
+dietary guild; Matching Competition: MC models) or considering that the evolutionary rate depends on the number of lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
+After reconstructing primate biogeography history when considering `r length(areaName)` biogeographic areas following [@kamilar2009environmental] based on `r minRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs.
+folivory; @bollback2006simmap.
+The classification varied depending on how frugivory/folivory was assessed, see [Dietary guild]), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy for `r minEQ` to `r maxEQ` frugivorous), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
+\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species).
+The use of specific region size relatively to the body mass (see @deaner2000comparative for further consideration of scaling methods), and not raw size, rather depicts the evolutionary evolution of cognitive abilities in terms of allocation rather than abilities per se (although it is vividly discussed whether raw measures are anything informative on "abilities" too @logan2018beyond).
+We also estimated the likelihoods of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
+stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, @blomberg2003testing), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence.
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does interspecific interactions shape brain size evolution?]).
+Non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
+By contrast, competitive models were most supported in areas involved in sensory abilities (the main olfactory bulb, MOB), short-term working memory and long-term spatio-temporal information retention (Hippocampus, @burgess2002human), and the Striatum an area that is involved in information processing during social interaction (i.e.
+social reward assessment; @izuma2008processing) (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and Striatum, but a slow down for the MOB.
+
+```{r samplecooccurrence}
+
+minNspeciesCoocc <- round(min(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
+maxNspeciesCoocc <- round(max(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
+meanNspeciesCoocc <- round(mean(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
+seNspeciesCoocc <- round(sd(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE)/sqrt(length(dataRangePrimate$Number_species_cooccurrence[!is.na(dataRangePrimate$Number_species_cooccurrence)])), digit=2)
+
+whichSpeciesMinNCoocc <- paste(sort(dataRangePrimate$Species[which(round(dataRangePrimate$Number_species_cooccurrence, digit=2)==minNspeciesCoocc)]), collapse=", ")
+whichSpeciesMaxNCoocc <- paste(sort(dataRangePrimate$Species[which(round(dataRangePrimate$Number_species_cooccurrence, digit=2)==maxNspeciesCoocc)]), collapse=", ")
+whichSpeciesMinNCoocc <- gsub("_", " ", whichSpeciesMinNCoocc)
+whichSpeciesMaxNCoocc <- gsub("_", " ", whichSpeciesMaxNCoocc)
+
+minOverlapSpecies <- round(min(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
+maxOverlapSpecies <- round(max(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
+meanOverlap <- round(mean(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
+seOverlap <- round(sd(dataRangePrimate$Overlap_average, na.rm=TRUE)/sqrt(length(dataRangePrimate$Overlap_average[!is.na(dataRangePrimate$Overlap_average)])), digit=2)
+
+whichSpeciesMinOverlap <- paste(dataRangePrimate$Species[which(round(dataRangePrimate$Overlap_average, digit=2)==minOverlapSpecies)], collapse=", ")
+whichSpeciesMaxOverlap <- paste(dataRangePrimate$Species[which(round(dataRangePrimate$Overlap_average, digit=2)==maxOverlapSpecies)], collapse=", ")
+whichSpeciesMinOverlap <- gsub("_", " ", whichSpeciesMinOverlap)
+whichSpeciesMaxOverlap <- gsub("_", " ", whichSpeciesMaxOverlap)
+
+```
+
+```{r estimateRegGradient, error=TRUE, include=TRUE}
+
+#Hippocampus
+model <- get(paste("modelBrain", traitName[3], sep="_"))
+
+estimateGradientHippocampus <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+testGradientHippocampus <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+
+#Striatum
+model <- get(paste("modelBrain", traitName[6], sep="_"))
+
+estimateGradientStriatum <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+testGradientStriatum <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+
+#MOB
+model <- get(paste("modelBrain", traitName[7], sep="_"))
+
+estimateGradientMOB <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+testGradientMOB <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+```
+
+|   Next, to understand the directionality of the selection gradient shaped by co-occurrence (i.e.
+selection for “bigger” or “smaller” brain if the more species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
+For these linear regressions, the predicted variable was the relative brain size values of the different areas.
+We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
+On average ($\pm$ SE), the considered primate species had `r meanNspeciesCoocc` in their distribution range ($\pm$ `r seNspeciesCoocc`).
+That ranged from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
+On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
+That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
+The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
+The percentage of range shared on average with other species was coherently assessed as significantly correlated, or as a trend, with the relative size of areas which evolutionary history was better described with competitive models: the Hippocampus, the MOB and the Striatum (Hippocampus: $t$`r testGradientHippocampus`;  MOB: $t$`r testGradientMOB`; Striatum: $t$`r testGradientStriatum`).
+The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`;  MOB: `r estimateGradientMOB`; Striatum: `r estimateGradientStriatum`), which means that higher overlap rhymes with lower relative size, insensitive to data and the phylogeny variability (Table \@ref(tab:tabledfsensitivity)).
+Thus, it suggests that sympatric species are subject to less stringent selection on advanced cognitive abilities.
+
+```{r estimateRegDiversification, error=TRUE, include=TRUE}
+
+#print(traitName)
+# increaseHippocampus <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
+# averageDivRateHippocampus <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
+# estimateHippocampus <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+# testHippocampus <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+# 
+# #Neocortex
+# model <- get(paste("modelBrainDiversification", traitName[4], sep="_"))
+# 
+# increaseNeocortex <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
+# averageDivRateNeocortex <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
+# estimateNeocortex <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+# testNeocortex <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+#   
+# #Striatum
+# model <- get(paste("modelBrainDiversification", traitName[6], sep="_"))
+# 
+# increaseStriatum <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
+# averageDivRateStriatum <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
+# estimateStriatum <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
+# testStriatum <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
+
+#print(c(increaseStriatum, averageDivRateStriatum, estimateStriatum, testStriatum))
+
+```
+
+```{r determineBoomTime}
+###-----
+## Diversification evolution over time
+fraction.v <- c(60, 70, 80, 90, 95)
+table_MAPS_rates_time <- c()
+for (f in fraction.v){
+  table_MAPS_rates_time_transitory <- read.table(paste0("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Scripts/Analysis3_diversification/diversification/MAPS_speciation_rates_trought_time_ClaDS2_tree_primate_complete_f",f,".csv"),sep=";",header=T)###Hahah nice English Benoit, trought ;)
+  table_MAPS_rates_time_transitory$f <- f
+  table_MAPS_rates_time <- rbind(table_MAPS_rates_time, table_MAPS_rates_time_transitory)
+}
+
+aggregatedSpeciationTime.mean <- aggregate(table_MAPS_rates_time$speciation_rates, by = list(table_MAPS_rates_time$time), FUN = mean)
+aggregatedSpeciationTime.sd <- aggregate(table_MAPS_rates_time$speciation_rates, by = list(table_MAPS_rates_time$time), FUN = sd)
+
+colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
+colnames(aggregatedSpeciationTime.sd) <- c("Time", "Diversification")
+
+bp.resp <- breakpoints(Diversification ~ Time, data=aggregatedSpeciationTime.mean, breaks=2)
+ci.resp <- confint(bp.resp)
+dates <- as.data.frame(breakdates(ci.resp))
+dateFirstRupt <- as.numeric(round((1-dates[1,])*(max(aggregatedSpeciationTime.mean$Time) - min(aggregatedSpeciationTime.mean$Time)), digit=2))
+dateSecondRupt <- as.numeric(round((1-dates[2,])*(max(aggregatedSpeciationTime.mean$Time) - min(aggregatedSpeciationTime.mean$Time)), digit=2))
+
+```
+
+|   Finally, we investigated how brain evolution was related to evolutionary success, assumed proportional to diversification rate (i.e.
+speciation minus extinction rate), by using birth-death models of species diversification [@maliet2019model].
+Overall, diversification, estimated based on molecular phylogeny without fossil records, increased over time (Figure \@ref(fig:figdiversificationTime), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
+Visual inspection clearly suggested positive relationship between diversification rate and the size of brain areas (Figure \@ref(fig:figRegressionDiversification)).
+Yet, accounting for phylogenetic dependence erased such pattern: In fitted Bayesian regressions, the size of brain size was never significantly associated with an increase in diversification rate (Table \@ref(tab:tableRegDiversification); see robustness in Table \@ref(tab:tabledfsensitivity2)).
+
+# Discussion
 
@@
 Further, biases might be limited by considering measurement variability [@logan2018beyond] or the mosaic structure of the brain [@barton2000mosaic; @decasien2019primate].
-In this case, we indeed see that the evolutionary history between specific brain regions differ, while the $EQ$ was not affected by greater lineage diversity.
-The effect of between-species interaction is indeed only evidenced for specific areas, more particularly those involved in immediate information processing based on senses (%area%), in areas involved in a working memory (%area%), or in a long-term memory of spatio-temporal information (%area%).
-All these areas have thus in common to be potentially (but not only) used when foraging, suggesting that species with larger brains would be at competitive advantage with sympatric species with similar food preference.
+We did both.
+Although it existed a variability in the data (phylogenetic and on traits), results were robust.
+In addition, we saw that the evolutionary history between specific brain regions did not equally depend on the number of lineages living in sympatry.
+The effect of between-species interaction was indeed only evidenced for specific areas, more particularly those involved in immediate information processing based on senses (Main Olfactory Bulb, MOB), in a working memory or in a long-term memory of spatio-temporal information (Hippocampus) and in processing social cues (Striatum).
+These areas thus imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates.
+This supports the general discussion on the importance of social vs.
+ecological factors to explain primate cognition evolution and diversity [@decasien2017primate; @powell2017re].
+Using a modelling approach including metabolic, life-history and game theories, @gonzalez2018inference emphasized that ecological challenges were preponderant (equating around 60% of challenges faced) to explain current human brain size, which then was also substantially promoted by the occurrence of social challenges (equating around 30% of challenges faced).
+Here, we highlighted that the cognitive function allowing processing sociological or ecological cues are both affected by species sympatry.
+
+```{r calculationValueDiscussion}
+#Import data
+summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
+
+summaryDataForPlot <- summaryDataForPlot[!is.na(summaryDataForPlot$geographicCode),]
+# summaryDataForPlot <- summaryDataForPlot[summaryDataForPlot$DietaryGuild=="Fruit",]
+
+summaryDataForPlot$Family <- Data_powell2$MSW05_Family[match(summaryDataForPlot$Species_abbrv,Data_powell2$Species_abbrv)]#summaryData$Family[match(summaryDataForPlot$Species_abbrv, summaryData$Species_abbrv)]
+
+summaryDataForPlot[is.na(summaryDataForPlot$Family ),c(1,2,3)]
+#summaryDataForPlot$SpeciesForPhylogeny[which(is.na(summaryDataForPlot$Family))]
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Galagoides_demi"]<-"Galagonidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Macaca_munz"]<-"Cercopithecidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Microcebus_mitt"]<-"Cheirogaleidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Mirza_zaza"]<-"Lorisidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Nycticebus_java"]<-"Galagonidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Tarsius_lari"]<-"Tarsiidae"
+
+lemuriformes.v <- 
+c(  
+"Daubentoniidae",
+"Lemuridae",
+"Indriidae",
+"Cheirogaleidae",
+"Lepilemuridae"
+)
+
+platyrrhini.v <- c(
+"Atelidae",   
+"Aotidae",
+"Pitheciidae",
+"Cebidae"
+)
+
+meanseMOBlemu <- round(c(
+  mean(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v &
+                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseMOBother <- round(c(
+  mean(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v &
+                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseStriatumplaty <- round(c(
+  mean(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v &
+                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseStriatumother <- round(c(
+  mean(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v &
+                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+# summaryDataForPlot[order(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+# summaryDataForPlot[order(summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+# summaryDataForPlot[order(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+
+```
+
+<!-- From small to long range ( < few km) primates might rely on sensory abilities to decide where to go [@dominy2001sensory].
+They are known as visual mammals.
+In particular, frugivorous species highly benefit from a trichromatic vision that enables them to distinguish fruits within the dense foliage [@osorio1996colour].
+Yet, in tropical forests, visual range is easily impeded, being barely greater than a hundred of meters.
+On the contrary olfactory cues are of longer distance.
+-->
+
+|   Although primates are microsmatic species and better known as visual foragers [@dominy2001sensory; @osorio1996colour], frugivorous species also benefit from olfactory cues processing.
+Fruits can be highly odorous: The produced ethanol and other chemical compounds can be smelled so as to identify fruit ripeness, but also the location of fruit trees with ripe fruit, although current evidence for this latter case is weak [@nevo2015led].
+The Lemuriformes, that are known to prioritize smell compared to other primate species, indeed have the largest relative MOB size (i.e.
+pondered by body size) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
+When worthy targets are out of the perceptual range, primates might rely on internal memories of the resource distribution in space, and of their availability period, to forage efficiently [@janson2007wild; @trapanese2019review].
+In this system, the Hippocampus occupies a key position: It hosts (inter)neurons that encode for spatial location and orientation (known as place, grid or head cells, @grieves2017representation) and is home of episodic memory [@ranganath2016hippocampus].
+In addition, when foraging, environmental cues might be complemented by social cues, which processing can involve the Striatum.
+Platyrrhini, and callitrichine in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+It has been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging].
+A lesser scrutinized function of the Striatum is also that of supporting goal-directed behaviour and planning abilities [@johnson2007integrating].
+Overall, we expect the size of brain areas involved in dissecting socio-environmental cues to be under strong positive selection [@decasien2017primate; @barton2006olfactory].
+Here, on the contrary, we showed that species co-occurrence acts as a brake to such positive selection since the size of these areas were negatively associated with species co-occurence.
+This was the result of a slow down of the evolutionary rate for the MOB, but an accelration (thus towards lower size) of the evolutionary rate for the Hippocampus and Striatum.
 
@@
 @rocha2015role].
-The idea of such an arms race in cognition should be best illustrated considering predator-prey interactions, in which a bigger brain could rhyme in absolute with higher chance of escaping a predator, but also relatively to other prey species, with a lower probability to be targeted by the predator at first [@shultz2006chimpanzee].
-In this study example, however, competition should take the form of scramble competition, indirectly affecting individuals’ fitness through food depletion.
-Logically, species co-occurrence should correlate with diminished shared food density and lowered temporal predictability (as a drawback of more intense depletion), both these factors playing on the selective pressure on foraging cognition [@grove2013evolution; @janmaat2016spatio].
-Possibly indeed, because niche overlap among species is not perfect, the depletion rate for the shared resource would be higher than if a species was occupying a space alone.
-An oversimplified proof of principle of this assumption would consider a two consumers and three resource types system.
-Both consumers share only one (essential) resource in common while are limited in population size by respectively the two others.
-The common resource would therefore be consumed more than it would be if the system considered only one species.
-Hence, in this competitive view, it seems to be mainly density rather than diversity itself that should particularly shape cognition (REF).
-Yet, an arms race does not necessarily need to imply competition: one might keep pace with someone it cooperates with.
-
-|   In an analogous situation to direct cooperation, more species sharing overlapping diet would equate to more, and diverse, cues to infer where and when to find food.
-Hence, not only should animals gain benefits into decoding their own conspecific presence trace or behaviour, but they might as well benefit from decoding those of other species, what matches current behavioural observations.
+Following the principle of an arms race between species (Red Queen scenario, @van1973new), it would have been logical to see species co-occurrence as an additional positive driver towards increase size.
+A multi-species case stands yet as a peculiar situation.
+In particular, inter-species site exclusion in primates has been observed only in gibbons [@suwanvecho2012interspecific].
+Thus, given that primates restrain their space-use to a limited area, their home range, they will suffer from more intense depletion (and consequently unpredictability), of their environment.
+If this latter is too important, this could alleviate the benefices purported by foraging cognition [@grove2013evolution; @robirainreview]: The environment would be too complex to read through it, and conspecifics might be thus be too error-prone to rely on them.
+Positive selection for "bigger" areas supporting foraging efficiency would be relaxed, and, given the functioning and maintenance cost of the brain [@raichle2006brain], this could even turn into a selection for "smaller" sizes of brain areas related to socio-ecological cue processing.
+
+|   Yet, as much as social species could exploit cues provided by conspecifics, a species might also benefit from using cues of other species.
 To settle to new coral reefs, fishes use pops and clicks of other fishes as an honest signal for resourcefulness there [@gordon2019acoustic], mangabeys follow calls from hornbills to locate fruiting trees [@olupot1998fruit], and interactions even happen across kingdoms, with migratory birds interpreting phenological cues as synonymous of insect availability [@mcgrath2009flower].
-Would the fishes, monkeys or birds truly rely on these signals to reach high foraging success, shall then the individuals be selected based on their ability to process these stimuli.
-These stimuli might actually be in perpetual change throughout time, as a consequence of the evolution of the emitter species, and thus, so would be the selective pressure on cognitive abilities of species relying on it to make movement decisions.
-
-|   In the end, the inter-specific effect on cognition was here viewed under the prism of foraging, yet, without further evidence, it is as likely to hold in other contexts, such as the social environment.
+These signals should not involve true social reading, thus should be processed by areas such as the Neocortex which process such sensory cues [@barton1996neocortex].
+This could explain why the size of this area was actually better described by evolutionary models with stabilizing selection and did not follow the pace of the three aforementionned areas.
+Despite a potential increase load of stimuli (due to the cues provided by other species), the Neocortex size however did not correlate positively with sympatry rate.
+Perhaps the inter-specific cues do not add, but simply replace other used cues.
+In addition, given that areas affected by sympatry are far smaller than those that are not, there is no surprise that the deficit in allocation to these areas, potentially to the benefits of the Neocortex, is not observed through an increase of the Neocortex size.
+
+|   Finally, we observed that primate diversification rate increased along time particularly around -`r dateFirstRupt[2]` and -`r dateSecondRupt[2]` Myr.
+This corroborates previous findings about diversity boom in primate lineages early and late Miocene as a consequence of a sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography].
+Given the observed effect of species co-occurrence on brain size selection trends, species living in areas with or without competitive species would thus not be under the same selective regime.
+This would explain why we did not observe a link between the size of brain areas negatively affected by sympatry and their evolutionary success, approximated by their diversification rate.
+Why, nonetheless, the whole brain size is not correlated to diversification rate, while it is unaffected by the density of sympatric species, remains puzzling given that higher cognitive abilities are associated with higher ecological success since they act as a "cognitive buffer" to environmental challenges [@sol2007big].
+For these reasons, larger brain size is indeed associated with higher diversification in birds [@sayol2019larger].
+To sum up, these results suggest that the encephalisation boom observed in primates shall not be explained by a global, or area-restricted, encephalization increase, as suggested for Hominins [@melchionna2020macroevolutionary].
+
+# Conclusion
+
+In the end, the inter-specific effect on cognition was here mainly viewed under the prism of foraging and was limited to within primates.
+Without further evidence, it is as likely to hold if considering all potential competitors, that is not limited to an arbitrary taxa (see evidence of primate and non-primate interactions, reviewed in @heymann2015unlike), and in other contexts, such as the social environment.
 In fact, the general hypotheses on cognition evolution, discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
-As Alice said “'It's a great huge game of chess that's being played—all over the world” (Carroll, Chapter II, Through the Looking Glass) and all individuals are just pieces to play with or against, no matter the species.
+As Alice said “'It's a great huge game of chess that's being played—all over the world” (@Carroll, Chapter II) and all individuals are just pieces to play with or against, no matter the species.
 
@@
 Data processing, analyses, and plots were computed with R software version 4.0.3 [@Rsoftware].
-Used datasets and codes will be made freely available upon publication.
 Used codes and data are freely available at [https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency](https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency).
@@
 
-Note that in all these analyses, we discarded *Homo sapiens*. A summary of available data per species is presented in Supplementary Figure \@ref(fig:figmap).
+Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*, this latter being too geographically isolated.
+A summary of available data per species is presented in Appendix Figure \@ref(fig:figmap).
 
@@
 
-We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1,000 trees for the subsequent phylogenetic analyses.
+We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
 The trees contain `r length(phylo_init$tip.label)` primate species.
@@
 
-Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (cerebellum, hippocampus, main olfactory bulb (MOB), neocortex, striatum), @powell2017re and @powell2019maternal for whole brain, cerebellum and neocortex size, @todorov2019primate for hippocampus and neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, cerebellum, hippocampus and striatum size.
+Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size.
 They were freely available in the main manuscript or supplementary materials.
-When the species was represented multiple times in the dataset, we obtained a unique attribute by averaging it.
-From the global endocranial brain volume, we obtained the Encephalization Quotient (*EQ*, (N$_{max}$=`r maxEQ`)) as follows [@decasien2017primate]
+When the species was represented multiple times within dataset, we obtained a unique attribute by averaging it.
+From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
 
@@
 
-$EQ=1.036 \times Brainvolume/ (0.085 \times Body mass^{0.775})$
+$\mathrm{EQ}=1.036 \times \mathrm{Brainvolume}/ (0.085 \times \mathrm{Body mass}^{0.775})$
 
@@
 with the brain volume in cm$^{3}$, 1.036 g/cm$^{3}$ being the assumed homogeneous brain density, and the body mass in g.
-Encephalization Quotient indicates whether the brain size ranges above (>1) or below (<1) expected given the body mass.
+EQ indicates whether the brain size ranges above (> 1) or below (< 1) expected given the body mass.
 Body mass was obtained from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.
-The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{max}$=`r maxMOB`), in movement and/or associate immediate information processing and retention (Neocortex, N$_{max}$=`r maxNeocortex`, REF; Cerebellum, N$_{max}$=`r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), long-term spatio-temporal memory (Hippocampus, N$_{max}$=`r maxHippocampus`, @burgess2002human).
-The striatum (N$_{max}$=`r maxStriatum`), which supports information processing during social interaction (i.e.
+The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or associate information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, @wiltgen2004new; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, @burgess2002human).
+The Striatum (N$_{Striatum,max}$ = `r maxStriatum`), which supports information processing during social interaction (i.e.
 social reward assessment; @izuma2008processing), was chosen so as to serve as a comparative “null” area.
-To investigate their evolutionary history, we used the ratio between their volume and that of the whole brain.
+To investigate their evolutionary history, we used the ratio between their volume and
+<!-- that of the whole brain.  -->
 
@@
 
-Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list (downloaded on the 19/01/2021, REF).
+Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list [@IUCN].
 Ranging data were available for `r nrow(matrixRangingSensitivity[!is.na(matrixRangingSensitivity[,1]),])` species among the `r length(phylo_init$tip.label)` represented in the 10kTrees primate phylogeny.
@@
 
-One to multiple large-scale geographic areas were assigned to each species as soon as the species current range overlapped in surface at `r geographicThresholdVector[1]` (low threshold) or `r geographicThresholdVector[2]`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]`% because on present data, a species could occupy as far as three areas) with the individual geographic area (Figure \@ref(fig:figmap); “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to obtain the overlapping area, “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area calculation).
-These geographic areas were manually delimited using Google earth pro (version X.X, REF) as a combination of the environment topology and geographic regionalization relative to the primate taxonomy [@kamilar2009environmental].
+One to multiple large-scale geographic areas were assigned to each species as soon as the species current range overlapped in surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas; Figure \@ref(fig:figmap)).
+Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlap contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
+These geographic areas were initially, manually delimited using Google earth professional (v7.3.3) as a combination of the environment topology and geographic regionalization relative to the primate taxonomy [@kamilar2009environmental].
 Based on the structure (i.e.
@@
 In addition, this drastically increases computational time of phylogenetic model of brain trait evolution too.
-Furthermore (2), all species and particularly primate species particularly suffer from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unpreceeding speed rate.
-Finer geographic characterization would therefore give too much weight to this recent anthropogenic effect that recently altered species distribution (e.g.
+Furthermore (2), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unpreceeding speed rate.
+Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
 evidenced on the North American fauna in @pineda2021mammal).
@@
 Hence, *Macaca sylvanus* is not considered in this study.
-	We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+
+|   We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
 This algorithm aims to fit, among others, non-time-stratified dispersal-extinction-cladogenesis (DEC) models (used here), specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
@@
 Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral range estimations (see Phylogenetic models, Models of trait evolution (b)).
+Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
 
@@
 In any other cases, the species was discarded.
-	Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed.
+
+```{r transitionMatrix}
+
+transitionMatrix <- matrix(NA, nrow=repetition, ncol=2)
+
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        start=which(is.na(transitionMatrix[,1]))[1]
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_simmap_transition",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+          transitionMatrix[start,1] <- toAdd[1,1]
+          transitionMatrix[start,2] <- toAdd[2,1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+minProba.v <- apply(abs(transitionMatrix), 2, min)
+maxProba.v <- apply(abs(transitionMatrix), 2, max)
+
+```
+
+|   Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed.
 Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
@@
 @masi2009western], which is generally shorter, hence a lower overall frugivory rate.
-Second, frugivory rate is likely to be underestimated in part because primates generally spend more time eating leaves than fruits, while rates are often based on eating relative feeding time, or observation frequency at the individual or group unit of feeding event.
-Finally, because the methodology to obtain this rate could additionally vary (e.g.
+Second, frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding event.
+Finally, the methodology to obtain this rate could additionally vary (e.g.
 in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves).
-We used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
+For all these reasons, we used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
 Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
@@
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting (Phylogenetic models) to account for uncertainty of these ancestral diet estimations (see Phylogenetic models, Models of trait evolution (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting [Phylogenetic models] to account for uncertainty of these ancestral diet estimations (see [Phylogenetic models, Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
 
@@
 
-We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic model of $EQ$ - or relative size of a specific brain area – evolution with and without species competitions.
+We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic model of EQ - or relative size of a specific brain area – evolution with and without species competitions.
 Models were fitted on different sample sizes due to non-availability of some data.
-Specifically, models using $EQ$ included `r minEQ` to `r maxEQ` frugivorous species.
-Other models included more reduced sample sizes (in species number): striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), neocortex (`r minNeocortex` to `r maxNeocortex`), hippocampus (`r minHippocampus` to `r maxHippocampus`), cerebellum (`r minCerebellum` to `r maxCerebellum`).
-Prior fitting, trait parameters were log-transformed in case the distribution was skewed (i.e.
-for brain, EQ, and MOB ratio) to reach more symmetrical distributions.
+Specifically, models using EQ included `r minEQ` to `r maxEQ` frugivorous species.
+Other models included more reduced sample sizes (in species number): Striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), Neocortex (`r minNeocortex` to `r maxNeocortex`), Hippocampus (`r minHippocampus` to `r maxHippocampus`), Cerebellum (`r minCerebellum` to `r maxCerebellum`).
+Prior fitting, trait parameters were log-transformed to reach more symmetrical distributions.
 Models without competition, Brownian Motion (i.e.
@@
 EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (Primate co-occurrence paragraph) and of diet (Dietary guild paragraph), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+Using the evolutionary history of species distribution (see [Primate species co-occurrence]) and of diet (see [Dietary guild]), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
 These competitive models notably account for interaction matrices that are built on the evolutionary history of species co-occurrence and diet.
@@
 The matching competition model (MC) may consider divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
-Here, that would mean that co-occurring species would tend to have either lower or higher $EQ$ or relative brain size.
+Here, that would mean that co-occurring species would tend to have either lower or higher EQ or relative brain size.
 Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
-Density-dependence means that the evolutionary rate $\lambda$ varies either positively or negatively as a function f of the number of co-occurring lineages sharing the same diet such as
+Density-dependence means that the evolutionary rate $\lambda$ varies either positively or negatively as a function $f$ of the number of co-occurring lineages sharing the same diet such as
 
@@
 
-$f_{lin}(\lambda)=\lambda_{0}(1 − N/K)$
-
-$f_{exp}(\lambda)=\lambda_{0}N^{−r}$
+$f_{lin}(\lambda)=\lambda_{0}(1 + r)$
+
+$f_{exp}(\lambda)=\lambda_{0}\exp(rL)$
 
@@
 
-where $\lambda_{0}$ corresponds to the value of the initial ancestor, $N$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the exponential dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes), and $K$ is generally considered as a “carrying capacity” [@rabosky2008density], that is the upper limit of lineages that are viable when at equilibrium.
+where $\lambda_{0}$ corresponds to the value of the initial ancestor, $L$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
 	All these models were repeated `r numberSimulations` times, using `r randomSampling` different combination of the evolutionary history of ranging and diet.
@@
 In this analysis, uncertainty can stem from two sources.
-First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1 000 possible estimated trees.
+First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees.
 
 |	Similarly, the estimated evolutionary history of the diet and ranging might vary as well.
-Second, for each species, trait estimates could vary slightly among datasets (see Supplementary Figure 2).
-Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Supplementary Figure 2), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
-In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Supplementary Figure 3) and (ii) to assess the species dietary guild (see Supplementary Figure 2) which can cause sensitivity of the results to the chosen parameters.
+Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
+Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
+In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Appendix Figure \@fig(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
 To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeography and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
@@
 
-We investigated how the Primate taxon diversified over time.
+We investigated how the primate taxon diversified over time.
 Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
@@
 In other words, the daughter lineage is assumed to inherit new speciation rates that is sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the parental speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
-Three independent chains were run and their respective convergence was checked using a Gelman-Rubin diagnostic criterion.
+Three independent chains were run until their respective convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
 The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
@@
 
+(i)	Direction of the selection gradient shaped by interspecific competition
+
+\hfill
                                                                                                                                                                            Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (i.e.
@@
 Prior fitting, the covariates were square-rooted to reach more symmetrical distribution.
-Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Supplementary Material).
+Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
 We did not observe correlation issue among predictors either [max VIF < 2, @mundry2014statistical].
@@
 
+(ii)	Diversification analysis
+
+\hfill
+
+We could not compute phylogenetic regressions to link diversification and brain traits using a frequentist approach because it lead to violation of homoscedasticity.
+Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
+Each chain was based on a burnin period of `r burnin` iterations, among a total of `r nitt` iterations, and was sampled every `r thin` iterations.
+We used the least informative priors.
+Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
+Prior on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
+We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion [max value < `r round(max(gelmanRubinValues), digit=2)`; @gelman1992inference], as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
+In Appendix [Model assumptions], we present trace and distributions of posterior estimates.
+We further checked the quality of the posterior by visually assessing the Q-Q plot of the posterior with that of a Gaussian distribution of mean 0 and sd 1 (see Appendix [Model assumptions]).
+We present the estimate together with the 95% credibility interval centered on the mode (Highest Density Posterior, HDP), together with a MCMC p-value (pMCMC) that corresponds to the probability that the estimate ($\beta$) is positive if the mean estimate ($\hat{\beta}$) is negative (i.e.
+$P(\beta>0|\hat{\beta}<0)$), or if the mean estimate is positive, the probability that the estimate is negative (i.e.
+$P(\beta<0|\hat{\beta}>0)$).
+
+\hfill
+
 (d)	Model robustness
@@
 
-To assess model stability with regards to singular points, we computed the dfbetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree.
-To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10,000 possible trees from the 10kTrees project.
+To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree.
+
+|   To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10000 possible trees from the 10kTrees project.
 For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple value (e.g.
@@
 For the diversification analysis specifically, we also assessed the sensitivity to changes in hypothesized fraction of known primate taxon by refitting the models for values ranging between 60 to 95% (as specified before) using the "standard" dataset and the consensus tree.
-The results of these assessment (min-max of estimates) are shown in Supplementary Material. It emphasizes weak sensitivity of the results.
+
+|   The results of these assessment (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes weak sensitivity of the results.
 
@@
 
-We considerably value the help provided by Jonathan Drury in making some scripts available but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for assistance for using the CEFE cluster.
-We thank Simon Benhamou and Manon Clairbaux for discussion and advices on spatial projections too.
+We considerably value the help provided by Jonathan Drury in making some scripts available, but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for assistance for using the CEFE cluster.
+We thank Simon Benhamou and Manon Clairbaux for discussion and advices on spatial projections, and M.
+Quéroué, V.
+Lauret, A.
+Caizergues and C.
+Teplistky for feedback on Bayesian computations too.
 Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and Alexandra R.
@@
 
-|   Both authors were supported by a doctoral grant from the *Ecole Normale Supérieure*, Paris.
-BR received logistic support from the *Centre d’Ecologie Fonctionnelle et Evolutive*, Montpellier and the *Musée de l'Homme*, Paris.
-BP-L received support from the *Ecole Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.
-
-```{r }
+|   Both authors were supported by a doctoral grant from the *École Normale Supérieure*, Paris.
+BR received support from the *Centre d’Écologie Fonctionnelle et Évolutive*, Montpellier and the *Musée de l'Homme*, Paris.
+BP-L received support from the *École Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.
+
+# Authors' contribution
+
+BR conceived the study, collected, cleaned and analyzed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
+BP-L implemented the ClaDS algorithm with our data, helped with other analyses, adapted them for, and ran them on, the cluster, and revised the manuscript multiple times.
+The authors declare having no conflict of interest.
+All authors gave final approval for publication and agree to be held accountable for the work performed therein.
+
+\newpage
+
+```{r tableRegGradient, include=TRUE}
+
+knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the selection gradient direction | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+The brain area (as well as the associated sample size) are indicated prior each list of estimates.
+The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
+  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold) %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down") #%>%
+  #kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r}
+#Round numbers table
+results.df_diversification[seq(from=4, to=nrow(results.df_diversification), by=4),c(2,3,4)] <-apply(results.df_diversification[seq(from=4, to=nrow(results.df_diversification), by=4),c(2,3,4)], 2, function(x){roundIntelligent(as.numcharac(x), digit=2)})
+
+results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1] <- gsub("\\(log\\) ", "", results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1])
+results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1]  <- gsub("\\(\\/bodymass, log\\) ", "", results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1])
+
+```
+\newpage
+
+```{r tableRegDiversification, include=TRUE}
+
+knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the diversification pattern | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+samp.=Effective sample (adjusted for autocorrelation).
+The brain area (as well as the associated sample size) are indicated prior each list of estimates.
+The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
+  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification) %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down") #%>%
+  #kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+\newpage
+
+```{r prepareMap}
 #Reimport areas with cropping
@@
 }
-#warnings()
-```
-
-```{r figmap, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap=paste("(Left) Current frugivorous primate co-occurrence pattern and phylogeny (Right) Geographic areas used for ancestral range reconstruction | (Left) Primate phylogeny from a consensus tree of 1 000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
-The corresponding non-abbreviated names can be found using Supplementary Figure X.
-Co-occurring frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by lightgray lines.
-The geographic area occupied by a species is depicted by the coloured rectangles.
-Presence was assed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1], "%.
-(Right) Depicted is the equirectangular projection of the world.
+warnings()
+```
+```{r figmap, include=TRUE, warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction | Depicted is the Natural Earth projection of the world.
 Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
@@
 
-# #Just to see the difference as pinpointed by the warning
-# # geosphere::areaPolygon(areaTransitory)
-# # gArea(areaTransitory)
-# # really false
-# # geosphere::centroid(areaTransitory)
-# # gCentroid(areaTransitory)
-# #ok
-# 
-# layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
-# par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-# 
-# ####
-# ## Fig interaction
-# ####
-# 
-# #Import data
-# summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
-# 
-# #Tree
-# tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
-# 
-# #Create geography df
-# geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
-# colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
-# 
-# #Create species ID
-# hc = as.hclust(tree)#bird.orders)
-# labels = hc$labels  # name of birds
-# 
-# labels.tordc <- as.data.frame(labels)
-# colnames(labels.tordc) <- "Name"
-# labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
-# 
-# labels.rdc <- apply(labels.tordc, 1, function(x){
-#   if(!is.na(x[3])){
-#     paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
-#   } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
-#   }
-# }
-# )
-# 
-# #Match to have right order for geography
-# locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
-# colLoc <- colourArea
-# 
-# #Match to have diet
-# dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
-# 
-# #Getting species labels abbreviated
-# speciesLabels <- hc$labels#Should be in the tree order
-# 
-# #Create the circos plot linking species based on their diet and geography
-# circos.clear()
-# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
-# circos.initialize(speciesLabels, xlim = c(0, 1))
-# 
-# #Species name + area it belongs to
-# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
-#              panel.fun = function(x, y) {
-#                i=CELL_META$sector.numeric.index
-#                circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
-#                            facing = "clockwise", niceFacing = TRUE,
-#                            col = "black", cex = 0.35, font=3)
-#                
-#               geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-#               for(g in 1:length(geo)){
-#                 if(geo[g]==1){
-#                   #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
-#                   circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
-#                 }
-#               }
-#              })
-# 
-# #Plot the geographic links
-# for(i in 1:length(speciesLabels)){
-#   #locI <- which(strsplit(locationSpecies[i], "")==1)
-#   for(j in i:length(speciesLabels)){
-#     #locJ <- which(strsplit(locationSpecies[j], "")==1)
-#     product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-#     if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
-#       #Do nothing
-#     }
-#     else{
-#       if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
-#         # colour <- as.data.frame(table(colLoc[which(product==1)]))
-#         # if(is.finite(max(colour$Freq))){
-#         # }else{
-#         #   print(c(i,j))
-#         # }
-#         # colour <- colour[colour$Freq==max(colour$Freq),1][1]
-#         circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
-#       }
-#       else{
-#         #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
-#       }
-#     }
-#   }
-# }
-# circos.clear()
-# 
-# #Plot the phylogenetic tree in a new circular plot
-# n = length(labels)  # number of species
-# dend = as.dendrogram(hc)
-# 
-# par(new = TRUE) # <- magic
-# circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
-# circos.initialize("a", xlim = c(0, n)) # only one sector
-# # circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
-# #              panel.fun = function(x, y) {
-# #                for(i in seq_len(n)) {
-# #                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
-# #                              facing = "clockwise", niceFacing = TRUE,
-# #                              col = "black", cex = 0.2, font=3)
-# #                }
-# #              })
-# 
-# 
-# #suppressPackageStartupMessages(library(dendextend))
-# #dend = color_branches(dend, k = 6, col = 1:6)
-# dend_height = attr(dend, "height")
-# circos.track(ylim = c(0, dend_height), bg.border = NA,
-#              track.height = 0.95, panel.fun = function(x, y) {
-#                circos.dendrogram(dend)
-#              })
-# circos.clear()
-# 
+#abbreviation name are available in https://proj.org/operations/projections/index.html
+#help for graticule: https://rpsychologist.com/working-with-shapefiles-projections-and-world-maps-in-ggplot
+
+proj.map <- "+proj=natearth +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
+
+centroid <- as.data.frame(centroid)
+colnames(centroid) <- c("long", "lat")
+centroid$nudge_y <- 0
+centroid$nudge_y[5] <- -5
+
+library(tidyverse)
+library(ggspatial)
+
+library(rnaturalearth)
+world <- ne_countries(scale = "medium", returnclass = "sf")
+
+# graticule (Robin)
+grat <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_graticules_15")
+grat_df <- fortify(grat)
+
+bbox <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_wgs84_bounding_box")
+bbox_df<- fortify(bbox)
+
+bbox.sf <- sfheaders::sf_polygon(  obj = bbox_df 
+                                         , x = "long"
+                                         , y = "lat"
+                                         , polygon_id = "group"
+)
+sf::st_crs(bbox.sf) <- st_crs(world)
+
+grat_df <- grat_df[,c(1,2,6)]
+colnames(grat_df) <- c("x", "y", "linestring_id")
+grat_df.sf <- sfheaders::sf_line(obj = grat_df)
+
+sf::st_crs(grat_df.sf) <- st_crs(world)
+
+#Main map
+map <- ggplot() +
+  geom_sf(data = bbox.sf, fill=adjustcolor("white", alpha.f=0.45), col="white") +
+  geom_sf(data = grat_df.sf, col="darkgrey", lty=2) +
+  geom_sf(data = world, fill = "black", col = "white") +
+  theme(panel.background=element_rect(fill="white"),
+        panel.grid = element_blank(),
+        axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank()
+  )
+
+#Plot polygons areas
+mergedArea <- c()
+areaNameCorrected <- c(
+  "East Madagascar",
+  "West Madagascar",
+  "West Africa",
+  "Central Africa",
+  "East/South Africa",
+  "Central America",
+  "Northern South America",
+  "Southern South America",
+  "West Asia",
+  "Central/East Asia",
+  "South Asia",
+  "Asian islands")
+
+for(i in 1:length(areaName)){
+  toFortify <- get(paste("area", i, sep="_"))
+  toFortify <- fortify(toFortify)
+
+  toFortify$group <-paste(areaName[i], toFortify$piece)
+  toFortify$colour <- gsub("_", " ", areaName[i],)#areaNameCorrected[i]#colourArea[i]
+  mergedArea <- rbind(mergedArea, toFortify)
+  #add to ggplot
+  #map <- map + geom_polygon(data = toFortify, aes(x = long, y = lat, group = group), col = colourArea[i], fill = colourArea[i])
+}
+
+centroid.sf <- st_as_sf(centroid, coords=c("long", "lat"), crs=st_crs(world))
+library(sfheaders)
+mergedArea.sf <- sfheaders::sf_polygon(  obj = mergedArea
+                                         , x = "long"
+                                         , y = "lat"
+                                         , polygon_id = "group"
+)
+sf::st_crs(mergedArea.sf) <- st_crs(world)
+
+#Readd colour
+mergedArea.sf$colour <- unique(mergedArea[,c(7,8)])[,2]
+
+#   mergedArea, coords=c("long", "lat"), crs=st_crs(world))
+# st_cast(mergedArea.sf, to="POLYGON")
+
+map <- map +
+  geom_sf(data = mergedArea.sf, aes(fill = colour)) +
+  geom_sf_label(data = centroid.sf, aes(label = 1:nrow(centroid)),
+             fill = c(colourArea[11], colourArea[12], rep("white", times=10)),
+             col = c("black", "white", rep("black", times=10)),#colourArea[3:12]),
+             nudge_y=centroid$nudge_y,
+             label.r = unit(0.4, "lines"),
+             size = 2) +
+  coord_sf(crs = proj.map, expand = F) +
+  scale_fill_manual(values = colourArea) +
+  labs(fill = "")  +
+  theme(
+        text = element_text(size = 10),
+        legend.key = element_rect(size = 4),
+        legend.key.size = unit(1, 'lines'),
+        legend.position="bottom")
+map
+
+# # #Just to see the difference as pinpointed by the warning
+# # # geosphere::areaPolygon(areaTransitory)
+# # # gArea(areaTransitory)
+# # # really false
+# # # geosphere::centroid(areaTransitory)
+# # # gCentroid(areaTransitory)
+# # #ok
+# #
+# # layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
+# # par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+# #
+# # Add figure interaction here if needed
 # ####
@@
 # #Have background
-# maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))
+# maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA, mar = c(0, 0, 0, 0))#, ylim=c(-60, 50))
 #
@@
 # # }
-# points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
-# points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
-# text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))
-
-```
-
-```{r figbrain, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap=paste("(Left) Brain area location (Right) EQ or relative brain size value among frugivorous primates | (Left) A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]) together with the studied brain area.
-The neocortex was not represented for readability since it corresponds to the external layer of the cerebral hemisphere.
-In short, the MOB is involved in immediate olfactory information processing, the neocortex and the cerebellum support a working memory and memory consolidation processes [@koziol2014consensus; @sokolov2017cerebellum], and the hippocampus a long-term spatio-temporal memory [@burgess2002human].
-The striatum, involved in social information processing [@izuma2008processing], acts as a comparative “null” area.
-(Right) The circular rows are indicated by the colours which match a specific brain area.
-The mean value (after scaling and based on one random sampling among possible values, but see Supplementary Figure 2 for visualization of measure variability) for the Encephalization Quotient ($EQ$, see Data collection; Brain data for further details on calculation) or relative size of brain parts, when available, is depicted by a plain circle for frugivorous species.
-The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%.
-The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.", sep="")}
-
-# library(RColorBrewer)
-# colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-# colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
-# colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
-# 
-# ###
-# ## Fig brain values / circular
-# ###
-# 
-# summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
-# summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
-# summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
-# summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
-# summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
-# summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain
-# 
-# #Brain data
-# relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
-# relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-# relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-# relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-# relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-# relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-# 
-# 
-# library(circlize)
-# circos.clear()
-# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
-# circos.initialize(speciesLabels, xlim = c(0, 1))
-# 
-# #Species name
-# circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
+# points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.3)
+# points(x=centroid[,1], y=centroid[,2], cex=1.3, col=c("white", "white", rep("black", times=10)))
+# text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.5, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))
+
+```
+
+\newpage
+
+```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Current frugivorous primate co-occurrence pattern and phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
+The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
+Co-occurring frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by lightgray lines.
+The geographic area occupied by a species is depicted by the coloured rectangles.
+Presence was assed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1]*100, "%.", sep="")}
+
+# ####
+# ## Fig interaction
+# ####
+
+#Tree
+tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
+tree <-  drop.tip(tree,
+                      tree $tip.label[
+                        which(tree$tip.label
+                              %nin% summaryDataForPlot$SpeciesForPhylogeny)])
+
+#Create geography df
+geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
+colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
+
+#Create species ID
+hc = as.hclust(tree)#bird.orders)
+labels = hc$labels  # name of birds
+
+labels.tordc <- as.data.frame(labels)
+colnames(labels.tordc) <- "Name"
+labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
+
+labels.rdc <- apply(labels.tordc, 1, function(x){
+  if(!is.na(x[3])){
+    paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
+  } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
+  }
+}
+)
+
+#Match to have right order for geography
+locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
+colLoc <- colourArea
+
+#Match to have diet
+dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
+
+#Getting species labels abbreviated
+speciesLabels <- hc$labels#Should be in the tree order
+
+#Create the circos plot linking species based on their diet and geography
+
+circos.clear()
+circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
+circos.initialize(speciesLabels, xlim = c(0, 1))
+
+# #Add family
+# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
 #              panel.fun = function(x, y) {
 #                i=CELL_META$sector.numeric.index
-#                circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
-#                            facing = "clockwise", niceFacing = TRUE,
-#                            col = "black", cex = 0.35, font=3)
+#                circos.rect(CELL_META$cell.xlim[1],CELL_META$cell.ylim[1], CELL_META$cell.xlim[2],CELL_META$cell.ylim[2], col="white", border=NA)
 #                 })
 #
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
-# }, track.height = 1/15)
+# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
+#              panel.fun = function(x, y) {
+#                i=CELL_META$sector.numeric.index
+#                circos.rect(CELL_META$cell.xlim[1],CELL_META$cell.ylim[1], CELL_META$cell.xlim[2],CELL_META$cell.ylim[2], col="white", border=NA)
+#                 })
 #
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
-# }, track.height = 1/15)
+# for(i in 1:length(unique(summaryDataForPlot$Family))){
+#   speciesForPlotFamily <- speciesLabels[speciesLabels %in% summaryDataForPlot$SpeciesForPhylogeny[summaryDataForPlot$Family %in% unique(summaryDataForPlot$Family)[i]]]
+#   if(length(speciesForPlotFamily) > 0){
+#     highlight.sector(speciesForPlotFamily, track.index = 1, col = adjustcolor("black", alpha.f=0.15), padding = c(0, 0.2, 0, 0),
+#       text = unique(summaryDataForPlot$Family)[i], cex = 0.5, text.col = "white", niceFacing = TRUE)
+#   }
+# }
+
+#Species name + area it belongs to
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
+             panel.fun = function(x, y) {
+               i=CELL_META$sector.numeric.index
+               circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0),
+                           facing = "clockwise", niceFacing = TRUE,
+                           col = "black", cex = 0.75, font=3)
+
+              geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
+              for(g in 1:length(geo)){
+                if(geo[g]==1){
+                  #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
+                  circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
+                }
+              }
+             })
+
+#Plot the geographic links
+for(i in 1:length(speciesLabels)){
+  #locI <- which(strsplit(locationSpecies[i], "")==1)
+  for(j in i:length(speciesLabels)){
+    #locJ <- which(strsplit(locationSpecies[j], "")==1)
+    product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
+    if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
+      #Do nothing
+    }
+    else{
+      if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
+        # colour <- as.data.frame(table(colLoc[which(product==1)]))
+        # if(is.finite(max(colour$Freq))){
+        # }else{
+        #   print(c(i,j))
+        # }
+        # colour <- colour[colour$Freq==max(colour$Freq),1][1]
+        circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col=adjustcolor("black",alpha.f=0.15))#"lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
+      }
+      else{
+        #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
+      }
+    }
+  }
+}
+circos.clear()
+
+#Plot the phylogenetic tree in a new circular plot
+n = length(labels)  # number of species
+dend = as.dendrogram(hc)
+
+par(new = TRUE) # <- magic
+circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
+circos.initialize("a", xlim = c(0, n)) # only one sector
+# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3,
+#              panel.fun = function(x, y) {
+#                for(i in seq_len(n)) {
+#                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5),
+#                              facing = "clockwise", niceFacing = TRUE,
+#                              col = "black", cex = 0.2, font=3)
+#                }
+#              })
+
+#suppressPackageStartupMessages(library(dendextend))
+#dend = color_branches(dend, k = 6, col = 1:6)
+dend_height = attr(dend, "height")
+circos.track(ylim = c(0, dend_height), bg.border = NA,
+             track.height = 0.95, panel.fun = function(x, y) {
+               circos.dendrogram(dend)
+             })
+circos.clear()
+```
+
+\newpage
+
+```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("(Left) EQ or relative brain size value among frugivorous primates (Right) Studied brain areas | (Left) The circular rows are indicated by the colours which match a specific brain area.
+The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.
+The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain parts, when available, is depicted by a plain circle for frugivorous species.
+The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%.
+(Right) A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]).
+The arrows indicate the sagital and frontal axes.
+Studied brain area are coloured, although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere.
+In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation processes [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
+The Striatum is involved in social information processing [@izuma2008processing].", sep="")}
+
+library(RColorBrewer)
+colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
+colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
+colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
+
+###
+## Fig brain values / circular
+###
+
+summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
+summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Bodymass
+summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass
+summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Bodymass
+summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass
+summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Bodymass
+
+#Brain data
+relativeValueEQ <- scale(summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])#runif(length(speciesLabels), -1, 1)
+relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
+
+layout(mat=cbind(c(1,1), c(2,3)), widths=c(35,15), heights=c(15,35))
+par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+
+# plot(0, 0, type="n")
+
+library(circlize)
+circos.clear()
+circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
+circos.initialize(speciesLabels, xlim = c(0, 1))
+
+#Species name
+circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
+             panel.fun = function(x, y) {
+               i=CELL_META$sector.numeric.index
+               circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
+                           facing = "clockwise", niceFacing = TRUE,
+                           col = "black", cex = 0.6, font=3)
+             })
 #
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
-# }, track.height = 1/15)
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
-# }, track.height = 1/15)
-# 
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
-# }, track.height = 1/15)
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
-# }, track.height = 1/15)
-# 
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
-# }, track.height = 1/15)
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
-# }, track.height = 1/15)
-# 
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
-# }, track.height = 1/15)
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
-# }, track.height = 1/15)
-# 
-# #Background
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
-# }, track.height = 1/15)
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-#   circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
-# }, track.height = 1/15)
-# 
-# 
-# library(plotrix)
-# #Main circle
-# for(i in 1:13){
-#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
-# }
-# 
-# #increment of 0.5
-# for(i in 1:26){
-#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
-# }
-# 
-# #Value
-# 
-# 
-# 
-# #EQ
-# absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueEQ[i])){}  else{
-#     if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-#     }
-#     else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueEQ[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
-#     }
-#     else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# #Striatum
-# absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueStriatum[i])){}  else{
-#     if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
-#     }
-#     else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueStriatum[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
-#     }
-#     else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# #MOB
-# absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueMOB[i])){}  else{
-#     if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
-#     }
-#     else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueMOB[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
-#     }
-#     else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# #Neocortex
-# absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueNeocortex[i])){}  else{
-#     if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
-#     }
-#     else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueNeocortex[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
-#     }
-#     else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# #Hippocampus
-# absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueHippocampus[i])){}  else{
-#     if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-#     }
-#     else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueHippocampus[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-#     }
-#     else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# #Cerebellum
-# absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-#   if(is.na(relativeValueCerebellum[i])){}  else{
-#     if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-#     }
-#     else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-#       circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-# 
-# 
-# circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
-#   i=CELL_META$sector.numeric.index
-#   if(is.na(relativeValueCerebellum[i])){}  else{
-#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-#     if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-#     }
-#     else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
-#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-#       circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
-#     }
-#     else{}
-#   }
-# }, track.height = 0.1)
-
-```
-
-```{r figresultsevolution, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=10, fig.cap="AICc weights of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
-The points represent the average AICc weight obtained (when considering the five models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see Phylogenetic models, Models of trait evolution (b)).
-(1) Whole brain (EQ) (2) Striatum (3) MOB (4) Neocortex (5) Hippocampus (6) Cerebellum."}
-
-plot(0, 0, type="n")
-
-```
-
-# Authors' contribution
-
-BR conceived the study, collected, cleaned and analyzed the data, and wrote the first version of the manuscript and subsequently revised it.
-BP-L helped with analyses, adapted them for, and ran them on, the cluster, and revised the manuscript multiple times.
-The authors declare having no conflict of interests.
-All authors gave final approval for publication and agree to be held accountable for the work performed therein.
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
+}, track.height = 1/15)
+
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
+}, track.height = 1/15)
+
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
+}, track.height = 1/15)
+
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
+}, track.height = 1/15)
+
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
+}, track.height = 1/15)
+
+#Background
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
+}, track.height = 1/15)
+
+circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
+}, track.height = 1/15)
+
+library(plotrix)
+#Main circle
+for(i in 1:13){
+  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
+}
+
+#increment of 0.5
+for(i in 1:26){
+  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
+}
+
+#Value
+
+#EQ
+absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueEQ[i])){}  else{
+    if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+    }
+    else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueEQ[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
+    }
+    else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Striatum
+absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueStriatum[i])){}  else{
+    if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+    }
+    else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueStriatum[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+    }
+    else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#MOB
+absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueMOB[i])){}  else{
+    if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+    }
+    else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueMOB[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+    }
+    else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Neocortex
+absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueNeocortex[i])){}  else{
+    if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+    }
+    else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueNeocortex[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+    }
+    else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Hippocampus
+absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueHippocampus[i])){}  else{
+    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
+    }
+    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueHippocampus[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
+    }
+    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Cerebellum
+absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueCerebellum[i])){}  else{
+    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
+    }
+    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueCerebellum[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
+    }
+    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
+      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Empty plot
+par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
+     xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
+
+# #Add brain
+library(png)
+brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/3dplot.png")
+addImg(brainIMG, x = 0.425, y = 0.65, width = 1.3)
+
+#Add circle contour
+draw.circle(x=0.45,y=0.55,0.435, col=NA, border="lightgray", lwd=2)
+draw.circle(x=0.45,y=0.55,0.405, col=NA, border="lightgray", lwd=2)
+
+par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
+     xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
+
+colourHip=colourVector[5]
+colourCereb=colourVector[6]
+colourOlf=colourVector[3]
+colourStri=colourVector[2]
+
+legend(x=0.1, y=0.8, legend = c("EQ", "Striatum", "MOB",  "Hippocampus", "Neocortex", "Cerebellum", "Frugivorous species", "Folivorous species"), cex = 1, fill = c(colourVector, NA, NA), pch=c(NA, NA, NA, NA, NA, NA, 19, 1), border=c("black", "black", "black", "black", "black", "black", "white", "white"), col=c(NA, NA, NA, NA, NA, NA, "black", "black"), bty="n", seg.len=0.75)
+
+```
+
+\newpage
+
+```{r prepfigevolution}
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+
+counter=0
+start=counter
+end=counter
+numberSimulations=10
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        counter=end+1
+        start=counter
+        end=counter + numberSimulations - 1
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
+        }, error=function(e){
+          #Do nothing
+          }
+        )
+
+        tryCatch(
+        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryEQFrugivory[start:end,] <- toAdd
+        }, error=function(e){
+          #Do nothing
+        }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryNeocortexFrugivory[start:end,] <- toAdd
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryHippocampusFrugivory[start:end,] <- toAdd
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryCerebellumFrugivory[start:end,] <- toAdd
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryStriatumFrugivory[start:end,] <- toAdd
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryMOBFrugivory[start:end,] <- toAdd
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
+summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
+summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
+summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
+summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
+summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
+summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
+
+colnames(summaryBrainFrugivory) <- colnames(toAdd)
+colnames(summaryEQFrugivory) <- colnames(toAdd)
+colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
+colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
+colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
+colnames(summaryStriatumFrugivory) <- colnames(toAdd)
+colnames(summaryMOBFrugivory) <- colnames(toAdd)
+
+##----
+
+colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
+
+models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
+colourModels <- brewer.pal(n = 6, name = "Set1")
+
+```
+
+```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="AICc weights of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
+The points represent the average AICc weight obtained (when considering the six models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does interspecific interactions shape brain size evolution?])."}
+
+layout(mat=rbind(c(1,2,3), c(4,5,6)), widths=c(5,5,5), heights=c(5,5))
+par(mar=c(3.5, 3, 2, 0.5), mgp=c(2, 0.5, 0), xpd=TRUE)
+#note: 1= second run for frugivory 20%
+#note: _2= first run for frugivory 20%
+
+## EQ
+
+plot(
+  x=0, y=0, xlab="", ylab="AICc weight", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+
+for(i in 1:6){
+  meanPt <- mean(as.numcharac(summaryEQFrugivory[, ncol(summaryEQFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryEQFrugivory[, ncol(summaryEQFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryEQFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryEQFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryEQFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[1], border=NA)
+text(x=0.3, y=1.1, labels="1", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="EQ", xpd=TRUE, col="black", font=2, cex=1.5)
+
+##-------------
+
+##------------
+#Striatum
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[2])
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8, xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryStriatumFrugivory[, ncol(summaryStriatumFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryStriatumFrugivory[, ncol(summaryStriatumFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryStriatumFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[2], border=NA)
+text(x=0.3, y=1.1, labels="2", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="Striatum", xpd=TRUE, col="black", font=2, cex=1.5)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryStriatumFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryStriatumFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+
+##------------
+
+##-------------
+#MOB
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[3])
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryMOBFrugivory[, ncol(summaryMOBFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryMOBFrugivory[, ncol(summaryMOBFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryMOBFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[3], border=NA)
+text(x=0.3, y=1.1, labels="3", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="MOB", xpd=TRUE, col="black", font=2, cex=1.5)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryMOBFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryMOBFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+##------------
+
+##------------
+
+#Hippocampus
+
+plot(
+  x=0, y=0, xlab="", ylab="AICc weight", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryHippocampusFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[4], border=NA)
+text(x=0.3, y=1.1, labels="6", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="Hippocampus", xpd=TRUE, col="black", font=2, cex=1.5)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryHippocampusFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryHippocampusFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+##------------
+
+##-------------
+#Neocortex
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[5])
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8, xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryNeocortexFrugivory[, ncol(summaryNeocortexFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryNeocortexFrugivory[, ncol(summaryNeocortexFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryNeocortexFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[5], border=NA)
+text(x=0.3, y=1.1, labels="5", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="Neocortex", xpd=TRUE, col="black", font=2, cex=1.5)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryNeocortexFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryNeocortexFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+
+##-------------
+
+##-------------
+#Cerebellum
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[6])
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryCerebellumFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.25, col=colNum[6], border=NA)
+text(x=0.3, y=1.1, labels="7", xpd=TRUE, col="white", font=2)
+text(x=3.5, y=1.1, labels="Cerebellum", xpd=TRUE, col="black", font=2, cex=1.5)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryCerebellumFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryCerebellumFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.75, xpd=TRUE)
+###----------------------
+```
+
+\newpage
+
+<!-- TC:ignore -->
 
@@
 
+\beginsupplement
 \newpage
 
-# (APPENDIX) Appendix {-}
-
-```{r figdata, include=TRUE, warning = FALSE, message = FALSE, fig.width=20, fig.height=25, fig.cap="Supplementary Figure.
-Data availability | Black boxes indicate data availability while grey boxes indicate absence of data."}
+# Appendix
+
+## Data availability
+
+Availability of trait and biogeography range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Figure \@ref(fig:figdata).
+
+## Data variability
+
+We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to bieography ranges, or anatomical/behavioural traits.
+
+### Sensitivity to variation in biogeography range
+
+```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=3.5, fig.height=3.5, fig.cap=paste("Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
+", geographicThresholdVector[2]/2*100, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2]*100, "%.
+", geographicThresholdVector[2]*100, "% was chosen as the maximum because based on current observations, a species occupied at best three different biogeographic areas.", sep="")}
+
+plot(
+  x=0, y=0, xlab="Overlap threshold", ylab="Variation percent (relative to 15%)", 
+  xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=5/100, xmax=30/100, xintsmall=2.5/200, xintbig=5/100, ymin=0, ymax=0.4, yintsmall=0.01, yintbig=0.1, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=1, tcl=-0.25)
+axis(side=1, at=thresholdPresenceRange, labels=thresholdPresenceRange, las=1, tcl=-0.25)
+
+points(x=thresholdPresenceRange, y=howManyDifferent, pch=19, xpd=TRUE)
+lines(x=thresholdPresenceRange, y=howManyDifferent)
+
+```
+
+\newpage
+
+### Sensitivity to variation in trait value
+
+```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Supplementary Figure.
+Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
+indicates the frugivory rate and Fol.
+indicates the folivory rate.
+(A) Correlation: The points depict the coefficient of correlation while the bar depicts the 95% confidence interval (CI).
+(B) Variability: The points depict the average of the mean ratio $m$ of the absolute of differences with paired values; If we reduce the equation, we have $m=|(v_{1}^{2}-v_{2}^{2})|/(2v_{1}v_{2})$, where $v_{1}$ and $v_{2}$ are the two paired values from two different datasets and are different from 0.
+If $v_{1}$ and $v_{2}$ equal 0, then $m=0$.
+If $v_{1}$ or $v_{2}$ equals 0 (case for the diet rates constrained between [0,1]), then we fixed the null value to 0.01.
+The bar depicts the standard error.
+(C) Repeatability: Repeatability was assessed for traits that were included in at least three datasets.
+Prior calculation, traits were pondered *within* species by the *within* species max value.
+The point represents the mean repeatability $r$ calculated as $V_{between}/(V_{between}+V_{within})$, with the $V_{between}$ and $V_{within}$ corresponding the variance *between* or *within* species.
+The bar depicts the standard error.
+For all graphics, sample sizes are indicated above the upper value of the CI/error interval.
+"}
+
+layout(mat=t(c(1,2,3)), widths=c(5,5,3), heights=c(5))
+par(mar=c(4, 3, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
+
+cexText <-  c(
+  rep(0.8, times=10),
+  rep(0.4, times=3),
+  rep(0.8, times=6),
+  rep(0.4, times=3),
+  rep(1, times=1),
+  rep(0.8, times=6),
+  rep(1, times=1),
+  rep(1, times=1)
+)
+
+addToY <- c(
+  rep(0, times=10),
+  rep(0, times=3),
+  rep(0, times=6),
+  rep(0, times=3),
+  rep(0, times=1),
+  rep(0, times=6),
+  rep(-0.05, times=1),
+  rep(0, times=1)
+)
+
+colourWhatCompared <-  c("gray", brewer.pal(n = 9, name = "Pastel1")[c(1:5)], "black", brewer.pal(n = 9, name = "Pastel1")[7])#c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
+
+###------
+### CORRELATION
+
+#Vectors to save results
+barLower <- rep(NA, times=length(colNumTest))
+barUpper <- rep(NA, times=length(colNumTest))
+meanCoeff <- rep(NA, times=length(colNumTest))
+N <- rep(NA, times=length(colNumTest))
+
+for (i in 1:length(colNumTest)){
+  test <- #abs(as.numeric(as.character(summaryData[,colNumTest[i]])) - as.numeric(as.character(summaryData[,colNumToCompare[i]])))
+    cor.test(as.numeric(as.character(summaryData[,colNumTest[i]])), 
+             as.numeric(as.character( summaryData[,colNumToCompare[i]])), method="pearson")
+  barLower[i] <- test$conf.int[1]
+  barUpper[i] <- test$conf.int[2]
+  meanCoeff[i] <- test$estimate[1]
+  N[i] <- nrow(summaryData[!is.na(summaryData[,colNumTest[i]])&!is.na(summaryData[,colNumToCompare[i]]),])
+}
+
+plot(
+  x=0, y=0, xlab="", ylab="Coefficient of correlation", 
+  xlim=c(0,length(meanCoeff)+1), ylim=c(0.6,1),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0.6, ymax=1, yintsmall=0.025, yintbig=0.1, axisPlot=FALSE)
+axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25)
+addLabel(x=0.05, y=0.075, label="A", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
+
+#Comparison
+whatCompared <- c(
+  rep("Brain", times=10),
+  "Hippocampus",
+  "Hippocampus",
+  "Hippocampus",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Cerebellum",
+  "Cerebellum",
+  "Cerebellum",
+  "Striatum",
+  rep("Body", times=6),
+  "Frug.",
+  "Fol."
+)
+
+#Plot legend of what is compared in coloured rectangles
+whereToPlot <- as.data.frame(table(whatCompared))
+whereToPlot$loc <- whereToPlot$Freq/2
+
+#Colour rectangle to indicate what is compared
+refLoc=0
+for (i in 1:length(whatCompared)){
+  rect(xleft=i-1,
+       xright=i,
+       ybottom=0.6-0.05*0.4,#-0.05,
+       ytop=0.6,#0,
+       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+       xpd=TRUE
+  )
+  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
+  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+         xpd=TRUE)
+  text(x=i-0.5, y=barUpper[i]+0.015, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.8,xpd=TRUE)
+
+  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
+    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
+    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
+      segments(x0=refLoc, x1=refLoc, y0=0.6-0.025*0.4,#-0.025,
+               y1=0.6-0.075*0.4 + addToY[i]*0.4,#-0.075,
+               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
+      text(x=refLoc, y=0.6-0.1*0.4 + addToY[i]*0.4,#-0.1, 
+           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=cexText[i], xpd=TRUE)
+    }
+    else{
+      text(x=refLoc, y=0.6-0.025*0.4,#-0.025, 
+           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=cexText[i], xpd=TRUE)
+    }
+    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
+  }
+}
+
+###------
+### VARIABILITY
+
+#cbind(colnames(summaryData[colNumTest]), colnames(summaryData[colNumToCompare]))
+#Vectors to save results
+barLower <- rep(NA, times=length(colNumTest))
+barUpper <- rep(NA, times=length(colNumTest))
+meanCoeff <- rep(NA, times=length(colNumTest))
+N <- rep(NA, times=length(colNumTest))
+
+for (i in 1:length(colNumTest)){
+  transitoryinit <- as.data.frame(cbind(as.numeric(as.character(summaryData[,colNumTest[i]])),as.numeric(as.character(summaryData[,colNumToCompare[i]]))))
+  transitoryinit <- transitoryinit[!is.na(transitoryinit[,1])&!is.na(transitoryinit[,2]),]
+
+  # transitoryinit <- transitoryinit/max(apply(transitoryinit, 2, max))
+
+  transitory <- apply(transitoryinit, 1, function(v){abs(v[1]**2 - v[2]**2)/2/v[1]/v[2]}) #note= (abs((v1-v2))/v1 + abs((v2-v1))/v2)/2
+
+  #When rate is 0 for both, gives NA, so to transform to 0
+  transitory[is.na(transitory)] <- 0
+
+  transitory[!is.finite(transitory)] <- apply(transitoryinit[!is.finite(transitory),], 1, function(x) abs(max(x)**2 - 1**2)/2/max(x)/1)
+
+  barLower[i] <- mean(transitory) - sd(transitory)/sqrt(length(transitory))#min(transitory)
+  barUpper[i] <- mean(transitory) + sd(transitory)/sqrt(length(transitory))#max(transitory)
+  meanCoeff[i] <- mean(transitory)
+  N[i] <- length(transitory)
+
+}
+
+ymax <- 1#round((barUpper)/10)*10
+
+plot(
+  x=0, y=0, xlab="", ylab="Variability", 
+  xlim=c(0,length(meanCoeff)+1), ylim=c(0,ymax),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25)
+addLabel(x=0.05, y=0.075, label="B", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
+
+#Comparison
+whatCompared <- c(
+  rep("Brain", times=10),
+  "Hippocampus",
+  "Hippocampus",
+  "Hippocampus",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Neocortex",
+  "Cerebellum",
+  "Cerebellum",
+  "Cerebellum",
+  "Striatum",
+  rep("Body", times=6),
+  "Frug.",
+  "Fol."
+)
+
+#Plot legend of what is compared in coloured rectangles
+whereToPlot <- as.data.frame(table(whatCompared))
+whereToPlot$loc <- whereToPlot$Freq/2
+
+#Colour rectangle to indicate what is compared
+refLoc=0
+
+for (i in 1:length(whatCompared)){
+  rect(xleft=i-1,
+       xright=i,
+       ybottom=-0.05,
+       ytop=0,
+       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+       xpd=TRUE
+  )
+  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
+  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+         xpd=TRUE)
+  text(x=i-0.5, y=barUpper[i]+0.05, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.8,xpd=TRUE)
+
+  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
+    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
+    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
+      segments(x0=refLoc, x1=refLoc, y0=-0.025,
+               y1=-0.075 + addToY[i],
+               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
+      text(x=refLoc, y=-0.1  + addToY[i], 
+           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=cexText[i], xpd=TRUE)
+    }
+    else{
+      text(x=refLoc, y=-0.025, 
+           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=cexText[i], xpd=TRUE)
+    }
+    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
+  }
+}
+
+##----
+## Repeatability of measure
+
+colRep <- list(c(4, 14, 17, 22, 23),
+               c(5, 15, 18),
+               c(6, 12, 16, 19),
+               c(7, 13, 20),
+               #c(8, 21),
+               c(24, 25, 26, 27)#,
+               #c(29, 33),
+               #c(30, 34)
+)
+
+ymax <- 1
+
+plot(
+  x=0, y=0, xlab="", ylab="Repeatability", 
+  xlim=c(0,length(colRep)+1), ylim=c(0,ymax),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+addGrid(xmin=0, xmax=length(colRep), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25)
+addLabel(x=0.05*2, y=0.075, label="C", radius=0.75*length(colRep)/length(meanCoeff)*2, circle=TRUE, circle.bg="black", font.col="white")
+
+#Comparison
+whatCompared2 <- c(
+  "Brain",
+  "Hippocampus",
+  "Neocortex",
+  "Cerebellum",
+  #"Striatum",
+  "Body"#,
+  #"Fol.",
+  #"Frug."
+)
+
+for(i in 1:length(colRep)){
+  dataRdc <- summaryData[, colRep[[i]]]
+
+  #Normalise by max for all species (i.e. by row)
+  maxVector <- apply(dataRdc, 1, function(x)max(x, na.rm=TRUE))
+  maxVector[!is.finite(maxVector)] <- NA
+  dataRdc <- apply(dataRdc, 2, function(x) x/maxVector) 
+  dataRdc <- as.data.frame(dataRdc)
+
+  #Create common ID
+  dataRdc$id <- 1:nrow(dataRdc)
+
+  #Switch to 1 row=1value
+  dataRdc <- pivot_longer(dataRdc, col=1:(ncol(dataRdc)-1), names_to="Dataset", values_to="Value")
+
+  #Remove NAs
+  dataRdc <- dataRdc[!is.na(dataRdc$Value),]
+
+  #Keep thos with multiple obs
+  whichKeep <- dataRdc %>% count(id)
+  whichKeep <- whichKeep$id[whichKeep$n > 2]
+
+  dataRdc <- dataRdc[dataRdc$id %in% whichKeep,]
+  dataRdc <- pivot_wider(dataRdc, names_from="Dataset", values_from="Value")
+
+  withinVariance <- apply(dataRdc[,2:ncol(dataRdc)], 1, function(x) var(x, na.rm=TRUE))
+  betweenVariance <- var(apply(dataRdc[,2:ncol(dataRdc)], 1, function(x) mean(x, na.rm=TRUE)), na.rm=TRUE)
+
+  repeatability <- betweenVariance/(betweenVariance + withinVariance)
+
+  #Plot mean +/- SE
+  errorBars(location=i-0.5, meanPt=mean(repeatability),
+            refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=mean(repeatability)+sd(repeatability)/sqrt(length(repeatability)),
+            lowerBarValue=mean(repeatability)-sd(repeatability)/sqrt(length(repeatability)), horiz=FALSE, symmetrical=FALSE)
+
+  points(x=i-0.5, y=mean(repeatability), pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared2[i])],
+         xpd=TRUE)
+  text(x=i-0.5, y=mean(repeatability)+sd(repeatability)/sqrt(length(repeatability))+0.05, labels=length(repeatability), pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared2[i])], cex=0.8, xpd=TRUE)
+
+  # library(rptR)
+  # repeatabilityTest <- rpt(Value ~ (1 | id), grname = "id", data = dataRdc, datatype = "Proportion", 
+  #   nboot = 10, npermut = 0)
+  # Too few data to do that way
+
+}
+
+```
+
+```{r figdata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=20, fig.height=25, fig.cap="Data availability | Black boxes indicate data availability while grey boxes indicate absence of data."}
 # 
@@
 
-nbPlot=2
+dataForSample <- dataForSample[dataForSample$SpeciesForPhylo != "Homo_sapiens",]
+dataForSample <- dataForSample[order(dataForSample$SpeciesForPhylo),]
+
+nbPlot=4
 
@@
 
-```{r figvariabilitydata, include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Supplementary Figure.
-Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
-indicates the frugivory rate and Fol.
-indicates the folivory rate.
-(A) Correlation: The points depict the coefficient of correlation while the bar depicts the 95% confidence interval.
-Sample sizes are indicated above the upper value of the confidence interval.
-(B) Variability: The points depict the average of the mean ratio m of the absolute of differences with paired values; If we reduce the equation, we have $m=|(v_{1}^{2}-v_{2}^{2})|/(2v_{1}v_{2})$, where $v_{1}$ and $v_{2}$ are the two paired values from two different datasets and are different from 0.
-If equal $v_{1}$ and $v_{2}$ 0, then $m=0$.
-If $v_{1}$ or $v_{2}$ equals 0 (case for the diet rates), then we fixed $m$ to the non-null value.
-The bar depicts the min-max interval.
-Sample sizes are indicated above the max value."}
-
-layout(mat=t(c(1,2)), widths=c(5,5), heights=c(5))
-par(mar=c(4, 3, 1, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-###------
-### CORRELATION
-
-#Vectors to save results
-barLower <- rep(NA, times=length(colNumTest))
-barUpper <- rep(NA, times=length(colNumTest))
-meanCoeff <- rep(NA, times=length(colNumTest))
-N <- rep(NA, times=length(colNumTest))
-
-for (i in 1:length(colNumTest)){
-  test <- #abs(as.numeric(as.character(summaryData[,colNumTest[i]])) - as.numeric(as.character(summaryData[,colNumToCompare[i]])))
-    cor.test(as.numeric(as.character(summaryData[,colNumTest[i]])), 
-                   as.numeric(as.character( summaryData[,colNumToCompare[i]])), method="pearson")
-  barLower[i] <- test$conf.int[1]
-  barUpper[i] <- test$conf.int[2]
-  meanCoeff[i] <- test$estimate[1]
-  N[i] <- nrow(summaryData[!is.na(summaryData[,colNumTest[i]])&!is.na(summaryData[,colNumToCompare[i]]),])
-}
-
-plot(
-  x=0, y=0, xlab="", ylab="Coefficient of correlation", 
-  xlim=c(0,length(meanCoeff)+1), ylim=c(0.6,1),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0.6, ymax=1, yintsmall=0.025, yintbig=0.1, axisPlot=FALSE)
-axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25)
-addLabel(x=0.05, y=0.075, label="A", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
-
-#Comparison
-whatCompared <- c(
-  rep("Brain", times=10),
-  "Hippocampus",
-  "Hippocampus",
-  "Hippocampus",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Cerebellum",
-  "Cerebellum",
-  "Cerebellum",
-  "Striatum",
-  rep("Body", times=6),
-  "Frug.",
-  "Fol."
-)
-
-#Plot legend of what is compared in coloured rectangles
-whereToPlot <- as.data.frame(table(whatCompared))
-whereToPlot$loc <- whereToPlot$Freq/2
-
-colourWhatCompared <- c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
-
-#Colour rectangle to indicate what is compared
-refLoc=0
-for (i in 1:length(whatCompared)){
-rect(xleft=i-1,
-     xright=i,
-     ybottom=0.6-0.05*0.4,#-0.05,
-     ytop=0.6,#0,
-     border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-     col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-     xpd=TRUE
-)
-errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
-points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
+\newpage
+
+## Diversification pattern over time
+
+```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
+The grey background depicts the standard deviation.
+The two rupture points, depicted by the plain dots and the vertical dotted bars, were calculated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
+The three fitted regressions are displayed by the dashed lines."}
+
+##Plot diversification in function of time
+xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
+xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
+ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
+ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
+
+plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
+     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
+     las=1, type="n", tcl=-0.25, bty="n",
+     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
      xpd=TRUE)
-text(x=i-0.5, y=barUpper[i]+0.015, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.6,xpd=TRUE)
-
-if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
-  refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
-  if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
-    segments(x0=refLoc, x1=refLoc, y0=0.6-0.025*0.4,#-0.025,
-             y1=0.6-0.075*0.4,#-0.075,
-             col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
-    text(x=refLoc, y=0.6-0.1*0.4,#-0.1, 
-         labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.4, xpd=TRUE)
-  }
-  else{
-    text(x=refLoc, y=0.6-0.025*0.4,#-0.025, 
-         labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=0.3, xpd=TRUE)
-  }
-  refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
-}
-}
-
-###------
-### VARIABILITY
-
-#cbind(colnames(summaryData[colNumTest]), colnames(summaryData[colNumToCompare]))
-#Vectors to save results
-barLower <- rep(NA, times=length(colNumTest))
-barUpper <- rep(NA, times=length(colNumTest))
-meanCoeff <- rep(NA, times=length(colNumTest))
-N <- rep(NA, times=length(colNumTest))
-
-for (i in 1:length(colNumTest)){
-  transitoryinit <- as.data.frame(cbind(as.numeric(as.character(summaryData[,colNumTest[i]])),as.numeric(as.character(summaryData[,colNumToCompare[i]]))))
-  transitoryinit <- transitoryinit[!is.na(transitoryinit[,1])&!is.na(transitoryinit[,2]),]
-  transitory <- apply(transitoryinit, 1, function(v){abs(v[1]**2 - v[2]**2)/2/v[1]/v[2]}) #note= (abs((v1-v2))/v1 + abs((v2-v1))/v2)/2
-
-  #When rate is 0 for both, gives NA, so to transform to 0
-  transitory[is.na(transitory)] <- 0
-
-  transitory[!is.finite(transitory)] <- apply(transitoryinit[!is.finite(transitory),], 1, max)
-
-  barLower[i] <- min(transitory)
-  barUpper[i] <- max(transitory)
-  meanCoeff[i] <- mean(transitory)
-  N[i] <- length(transitory)
-}
-
-ymax <- round((barUpper)/10)*10
-
-plot(
-  x=0, y=0, xlab="", ylab="Variability", 
-  xlim=c(0,length(meanCoeff)+1), ylim=c(0,1),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-addLabel(x=0.05, y=0.075, label="B", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
-
-#Comparison
-whatCompared <- c(
-  rep("Brain", times=10),
-  "Hippocampus",
-  "Hippocampus",
-  "Hippocampus",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Cerebellum",
-  "Cerebellum",
-  "Cerebellum",
-  "Striatum",
-  rep("Body", times=6),
-  "Frug.",
-  "Fol."
-)
-#Plot legend of what is compared in coloured rectangles
-whereToPlot <- as.data.frame(table(whatCompared))
-whereToPlot$loc <- whereToPlot$Freq/2
-
-colourWhatCompared <- c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
-
-#Colour rectangle to indicate what is compared
-refLoc=0
-for (i in 1:length(whatCompared)){
-  rect(xleft=i-1,
-       xright=i,
-       ybottom=-0.05,
-       ytop=0,
-       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       xpd=TRUE
-  )
-  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
-  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-         xpd=TRUE)
-  text(x=i-0.5, y=barUpper[i]+0.05, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.6,xpd=TRUE)
-
-  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
-    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
-      segments(x0=refLoc, x1=refLoc, y0=-0.025,
-               y1=-0.075,
-               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
-      text(x=refLoc, y=-0.1, 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.4, xpd=TRUE)
-    }
-    else{
-      text(x=refLoc, y=-0.025, 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=0.3, xpd=TRUE)
-    }
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
-  }
-}
-
-```
-
-```{r figcomparison, include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap=paste("Supplementary Figure.
-Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2, "% threshold.
-", geographicThresholdVector[2]/2, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2], "%.
-", geographicThresholdVector[2], "% was chosen as the maximum because based on current observations, a species occupied at best three different biogeographic areas.", sep="")}
-
-plot(
-  x=0, y=0, xlab="Overlap threshold", ylab="Variation percent (relative to 15%)", 
-  xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=5/100, xmax=30/100, xintsmall=2.5/200, xintbig=5/100, ymin=0, ymax=0.4, yintsmall=0.01, yintbig=0.1, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=1, tcl=-0.25)
-axis(side=1, at=thresholdPresenceRange, labels=thresholdPresenceRange, las=1, tcl=-0.25)
-
-points(x=thresholdPresenceRange, y=howManyDifferent, pch=19, xpd=TRUE)
-lines(x=thresholdPresenceRange, y=howManyDifferent)
-
-```
+
+#Add grid
+addGrid(
+  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
+  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
+  axisPlot=TRUE, round=TRUE, digit=c(2,2))
+axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
+
+#Add background se
+polygon(
+  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
+  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
+  col=grey(level=0.5, alpha=0.15),
+  border=NA
+)
+
+#Add mean
+lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
+
+library(strucchange)
+## confidence interval
+colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
+
+yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
+ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
+
+# Rupture points and (CI too reduced to be plotted)
+points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
+# errorBars(location=c(yFirst), 
+#          meanPt=c(-dateFirstRupt[2]),
+#          barValue=c(0,0), refUnit=1, 
+#          minValue=-80, maxValue=80, 
+#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
+#          col="black", lty=1, 
+#          horiz=TRUE, symmetrical=FALSE)
+
+#Vertical bars
+segments(
+  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  y0=c(0,0),
+  y1=c(yFirst, ySecond),
+  lty=3
+)
+mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
+
+#three fitted regressions
+fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
+
+reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
+reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
+reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
+
+lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
+```
+
+## Phylogenetic regressions: results, stability and assumption
+
+### Model results
+
+<!-- We present below the visual fit of phylogenetic regressions. -->
+
+(a) Phylogenetic regressions: selection gradient
+
+```{=latex}
+\begin{figure}
+\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf}
+\caption{\footnotesize{Phylogenetic regressions of the size of the different brain areas in function of the number of sympatric species (left) or the percentage of the range overlapping with the range of other species (right) | The numeric labels refer the brain area number of Figure 1.
+Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the range overlaped by sympatric species is averaged, while the right graphics do the opposite.
+Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent gray background.}}\label{fig:figRegressionGradient}
+\end{figure}
+```
+\newpage
+
+(b) Phylogenetic regressions: diversification
+
+```{=latex}
+\begin{figure}
+\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
+\caption{\footnotesize{Phylogenetic regressions of the diversification rate in function of the size of the different brain areas | The numeric labels refer the brain area number of Figure 1.
+Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent gray background.}}\label{fig:figRegressionDiversification}
+\end{figure}
+```
+
+\newpage
+
+### Model stability
+
+We present below statistical indicators related to changes in estimates when re-fitting the model considering sub-samples (i.e.
+DfBetas and Cook's distance), as well as when accounting for data variability (i.e.
+re-sampling among possible values given all datasets) or when using different parameterization (i.e.
+"sampling fraction" of known species for diversification analysis)
+
+```{r correctSensitivityTable}
+#Include true estimator in the min-max range
+
+#1)Change min-max interval
+summarySensitivityGradient[,1:3+2] <- t(apply(summarySensitivityGradient[,1:3+2], 1, function(x){
+  x <- as.numeric(x)
+  if(x[1] > x[2]){
+   x[1] <- x[2] 
+  } else if (x[2] > x[3]){
+    x[3] <- x[2]
+  }else{}
+  return(x)
+}
+)
+)
+
+summarySensitivityGradient[,4:6+2] <- t(apply(summarySensitivityGradient[,4:6+2], 1, function(x){
+  x <- as.numeric(x)
+  if(x[1] > x[2]){
+   x[1] <- x[2] 
+  } else if (x[2] > x[3]){
+    x[3] <- x[2]
+  }else{}
+  return(x)
+}
+)
+)
+
+#2) Re-round intelligent with scientific writing
+summarySensitivityGradient[, 1:6+2] <- t(apply(summarySensitivityGradient[, 1:6+2], 1, function(x)
+roundIntelligent(as.numcharac(x))))
+
+#1)Change min-max interval
+summarySensitivityDiversification[,1:3+2] <- t(apply(summarySensitivityDiversification[,1:3+2], 1, function(x){
+  x <- as.numeric(x)
+  if(x[1] > x[2]){
+   x[1] <- x[2] 
+  } else if (x[2] > x[3]){
+    x[3] <- x[2]
+  }else{}
+  return(x)
+}
+)
+)
+summarySensitivityDiversification[,4:6+2] <- t(apply(summarySensitivityDiversification[,4:6+2], 1, function(x){
+  x <- as.numeric(x)
+  if(x[1] > x[2]){
+   x[1] <- x[2] 
+  } else if (x[2] > x[3]){
+    x[3] <- x[2]
+  }else{}
+  return(x)
+}
+)
+)
+summarySensitivityDiversification[,7:9+2] <- t(apply(summarySensitivityDiversification[,7:9+2], 1, function(x){
+  x <- as.numeric(x)
+  if(x[1] > x[2]){
+   x[1] <- x[2] 
+  } else if (x[2] > x[3]){
+    x[3] <- x[2]
+  }else{}
+  return(x)
+}
+)  
+)
+
+#2) Re-round intelligent with scientific writing
+summarySensitivityDiversification[,-c(1,2)] <- t(apply(summarySensitivityDiversification[,-c(1,2)], 1, function(x) roundIntelligent(as.numcharac(x)))) 
+```
+
+(a) Phylogenetic regressions: selection gradient
+
+```{r tabledfsensitivity, include=TRUE}
+knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE,
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the selection gradient direction | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down") %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
+  kableExtra::add_header_above(c("Regression" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3))
+```
+
+\newpage
+
+(b) Phylogenetic regressions: diversification
+
+```{r tabledfsensitivity2, include=TRUE}
+knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE,
+             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the diversification pattern | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down") %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
+  kableExtra::add_header_above(c("Regression" = 2, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
+```
+
+\newpage
+
+### Model assumptions
+
+We present below the visual assessment of linear modelling assumptions (histogram of residuals, Q-Q plot, and scatterplot of fitted values vs residuals).
+
+(a) Phylogenetic regressions: selection gradient
+
+```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values vs.
+the residuals."}
+for(a in 1:length(traitName)){
+  model <- get(paste("modelBrain", traitName[a], sep="_"))
+
+  diagnostics.plot(model)
+  text(x=0.85, y=0.15, paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
+
+  if(a/2==floor(a/2)){
+    cat('\n') #Break page for new figure
+  }
+}
+```
+
+\newpage
+
+(b) Phylogenetic regressions: diversification
+
+```{r modelAssumption2a, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Trace and density of posteriors"}
+for(a in 1:length(traitName)){
+  model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
+
+  plot(model1$Sol)
+  mtext(paste("Fixed effects: ", traitName[a], sep=""), side = 3, line = -1, outer = TRUE, xpd=TRUE)
+  #cat('\n') #Break page for new figure
+
+  plot(model1$VCV)
+  mtext(paste("Random/residuals: ", traitName[a], sep=""), side = 3, line = -1, outer = TRUE, xpd=TRUE)
+  #text(x=max(fitted(model)) + abs(min(fitted(model))), y=mean(residuals(model)), paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
+  if(a/2==floor(a/2)){
+    cat('\n') #Break page for new figure
+  }
+}
+```
+
+```{r modelAssumption2b, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=10, fig.cap="Q-Q plot of the posterior distribution and the expected Gaussian distribution"}
+
+layout(mat=matrix(1:(2*ceiling(length(traitName)/2)), ncol=2), widths=c(5,5), heights=rep(5, times=2*ceiling(length(traitName)/2)))
+par(mar=c(3, 3, 3, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
+
+for(a in 1:length(traitName)){
+  model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
+
+  posterior <- as.data.frame(model$Sol)
+  qqnorm(posterior$Trait, main=paste("Normal Q-Q Plot of the posterior distribution;\nModel:", traitName[a], sep=" "))
+  qqline(posterior$Trait)
+  #text(x=max(fitted(model)) + abs(min(fitted(model))), y=mean(residuals(model)), paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
+
+  #cat('\n') #Break page for new figure
+}
+```
+
+\newpage
+
+<!-- TC:endignore -->

### 2021-06-25 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryAnalysis.R

@@ -638,7 +638,7 @@ MOB = labs$index[grep("Olfactory_L", labs$name)]
 #labs$index[grep("Occipital", labs$name)], labs$index[grep("Cingulate", labs$name)], labs$index[grep("Insula", labs$name)]) #incomplete
 
 
-colourHip=colourVector[5]
+colourHip=colourVector[4]
 colourCereb=colourVector[6]
 colourOlf=colourVector[3]
 colourStri=colourVector[2]
@@ -681,29 +681,23 @@ arrow3d(p0=c(dtemp[1]/2,dtemp[2]/2,dtemp[3]), p1=c(dtemp[1]/2,dtemp[2]/2,1.17*dt
 #segmentBackFront
 arrow3d(p0=c(dtemp[1]/2,dtemp[2],dtemp[3]/2), p1=c(dtemp[1]/2,1.1*dtemp[2],dtemp[3]/2), type="extrusion")
 
-legend3d(x=0.1, y=0.2, legend = c("Cerebellum", "Hippocampus", "MOB", "Striatum"), fill = c(colourCereb, colourHip, colourOlf, colourStri), cex=1, bty="n", ncol=2)
+#legend3d(x=0.1, y=0.2, legend = c("Cerebellum", "Hippocampus", "MOB", "Striatum"), fill = c(colourCereb, colourHip, colourOlf, colourStri), cex=1, bty="n", ncol=2)
 #rglwidget()
 
 
 #from: https://r-graphics.org/recipe-miscgraph-3d-save
 #rgl.snapshot('3dplot.png', fmt = 'png', top = TRUE, width = 300)
-snapshot3d('3dplot.png', fmt = 'png', top = TRUE, webshot = FALSE, width=32000, height=32000)
+#snapshot3d('Plots/3dplot.png', fmt = 'png', top = TRUE, webshot = FALSE, width=32000, height=32000)
 #rgl.postscript('3dplot.pdf', fmt = 'pdf')
 
 #remotes::install_github("rstudio/chromote")
 #remotes::install_github("rstudio/webshot2")
 
 library(webshot2)
-snapshot3d('3dplot.png', fmt = 'png')
-
+snapshot3d('Plots/3dplot.png', fmt = 'png')
 
 writeASY()
 rgl.postscript('3dplot', fmt="svg")
-
-
-
-, width = 300, height = 300
-
 
 plot(x=0, y=0,
      xlab="", ylab="", 
[…]

### 2021-06-25 Scripts/Analysis2_competitiondirection/PGLSdirectionSelection.R

@@ -42,7 +42,7 @@ library(geiger)
 ################
 # Fitting linear models
 
-repetitionBootstrap=200
+repetitionBootstrap=1000
 
 #####---------------
 #Fixing data
@@ -270,27 +270,60 @@ summaryData$Family<- summaryData$Family[match(summaryData$Species_abbrv,summaryD
 
 #All the potential output predictors:
 
-summaryData$ratioBrain <- summaryData$Brain*1.036*(10**-3)/summaryData$Bodymass #Following decasien for multiplication by 1.036
+##--
+# Ratio body mass
+summaryData$ratioBrain <- summaryData$Brain/summaryData$Bodymass
+summaryData$ratioBrain.log <- log(summaryData$ratioBrain)
+
 summaryData$EQ <- summaryData$Brain*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775) #Following decasien, according to #Jerison, H. J. Evolution of the Brain and Intelligence (Academic, 1973).
 
 summaryData$Brain.log <- log(summaryData$Brain)
 summaryData$EQ.log <- log(summaryData$EQ)
 
-summaryData$ratioNeocortex <- summaryData$Neocortex*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775)#summaryData$Neocortex/summaryData$Brain
+summaryData$ratioNeocortex <- summaryData$Neocortex/summaryData$Bodymass
 summaryData$ratioNeocortex.log  <- log(summaryData$ratioNeocortex)
 
-summaryData$ratioHippocampus <- summaryData$Hippocampus*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775)#summaryData$Hippocampus/summaryData$Brain
+summaryData$ratioHippocampus <- summaryData$Hippocampus/summaryData$Bodymass
 summaryData$ratioHippocampus.log <- log(summaryData$ratioHippocampus)
 
-summaryData$ratioCerebellum <- summaryData$Cerebellum*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775)#summaryData$Cerebellum/summaryData$Brain
+summaryData$ratioCerebellum <- summaryData$Cerebellum/summaryData$Bodymass
[…]

### 2021-06-25 Scripts/Analysis3_diversification/PGLSdiversification.R

@@ -42,6 +42,7 @@ library(phytools)
 library(caper)
 library(nlme)
 library(geiger)
+library(mcmcglmm)
 
 ##--------
 
@@ -54,7 +55,7 @@ library(geiger)
 ################
 # Fitting linear models
 
-repetitionBootstrap=200
+repetitionBootstrap=1000
 
 #####---------------
 #Fixing data
@@ -282,23 +283,25 @@ summaryData$Family<- summaryData$Family[match(summaryData$Species_abbrv,summaryD
 
 #All the potential output predictors:
 
-summaryData$ratioBrain <- summaryData$Brain*1.036*(10**-3)/summaryData$Bodymass #Following decasien for multiplication by 1.036
+summaryData$ratioBrain <- summaryData$Brain/summaryData$Bodymass #Following decasien for multiplication by 1.036
 summaryData$EQ <- summaryData$Brain*1.036*(10**-3)/(0.085*summaryData$Bodymass**0.775) #Following decasien, according to #Jerison, H. J. Evolution of the Brain and Intelligence (Academic, 1973).
 
 summaryData$Brain.log <- log(summaryData$Brain)
 summaryData$EQ.log <- log(summaryData$EQ)
 
-summaryData$ratioNeocortex <- summaryData$Neocortex/summaryData$Brain
+summaryData$ratioNeocortex <- summaryData$Neocortex/summaryData$Bodymass
 summaryData$ratioNeocortex.log  <- log(summaryData$ratioNeocortex)
 
-summaryData$ratioHippocampus <- summaryData$Hippocampus/summaryData$Brain
+summaryData$ratioHippocampus <- summaryData$Hippocampus/summaryData$Bodymass
 summaryData$ratioHippocampus.log <- log(summaryData$ratioHippocampus)
 
-summaryData$ratioCerebellum <- summaryData$Cerebellum/summaryData$Brain
+summaryData$ratioCerebellum <- summaryData$Cerebellum/summaryData$Bodymass
+summaryData$ratioCerebellum.log <- log(summaryData$ratioCerebellum)
 
-summaryData$ratioStriatum <- summaryData$Striatum/summaryData$Brain
+summaryData$ratioStriatum <- summaryData$Striatum/summaryData$Bodymass
+summaryData$ratioStriatum.log <- log(summaryData$ratioStriatum)
 
-summaryData$ratioMOB <- summaryData$MOB/summaryData$Brain
[…]

### 2021-06-26 Scripts/Analysis3_diversification/PGLSdiversification_bayesian.R
Push article pdf + Rscript

@@ -1,0 +1,1316 @@
+############
+## DIVERSIFICATION ANALYSIS
+############
+
+# This script aims to analyse whether diversification rate correlates with brain size measures. Diversification was assessed using the CLADS2 algorithm developed within Helene Morlon's lab by . Maliet.
+# It simply corresponds to correlation analyses (while accounting for phylogeny). The same procedure than in previous scripts is done thus, it is decomposed into three steps:
+# 1) Cumpute the correlation for each brain area
+# 2) Compute the plots
+# 3) Carry on the sensitivity/stability etc... analyses
+
+##--------------
+
+# This script allows to perform PGLS analysis to assess the correlation of brain size with spatial co-occurrence data, specifically in areas for which competitive models were shown to fit the best.
+
+# The frequentist approach suffered from heteroskedasticity. Thus, we favoured Bayesian computation for this analysis. #We thank V. lauret and M. Queroue for discussion on these models.
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+#Import environment
+rm(list=ls())
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/Data_spatial_primate.RData")
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/geography_traits.RData")
+
+##--------
+#Home made functions
+#To source all phylogenetics functions (biogeobears + models of evolution)
+source("~/PhD/Meta_analysis/Meta_analysis_cognition_primates/Scripts/Functions.R")
+
+#My toolkit
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/diagnostic_fcns.R")
+
+##--------
+
+##--------
+#Libraries
+
+library(ape)
+library(phylolm)
+library(phytools)
+library(caper)
+library(nlme)
+library(geiger)
+
+##--------
+
[…]

### 2021-08-11 Article/Article.Rmd
Rerun pgls with correct frugivory threshold and shortened manuscript

@@
 ---
-title: \Huge \textbf{Species sympatry constrains brain size evolution in Primates}
+title: \Huge \textbf{Species sympatry shapes brain size evolution in Primates}
 # date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
     institute: [ENS, MNHN]
-    correspondence: true
 institute:
   - CEFE: Centre d’Écologie Fonctionnelle et Évolutive, Université de Montpellier & CNRS, Montpellier, France.
-  - MH: Anthropologie et Ethnobiologie, Centre National de la Recherche Scientifique/Muséum National d'Histoire Naturelle, University Paris Diderot, Sorbonne Paris Cité, Musée de l'Homme, Paris, France
-  - ENS: Institut de Biologie de l’École Normale Supérieure (IBENS), École Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France
-  - MNHN: Institut de Systématique, Évolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France
+  - MH: Anthropologie et Ethnobiologie, Centre National de la Recherche Scientifique/Muséum National d'Histoire Naturelle, University Paris Diderot, Sorbonne Paris Cité, Musée de l'Homme, Paris, France.
+  - ENS: Institut de Biologie de l’École Normale Supérieure (IBENS), École Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France.
+  - MNHN: Institut de Systématique, Évolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France.
 
@@
 bibliography: bibliographyarticlepackage.bib
-csl: science.csl
+csl: nature.csl
 #biblio-style: apa
@@
 # - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
-  - \usepackage{lineno} # For line numbering
-  - \linenumbers # For line numbering
-  - \usepackage{setspace}\doublespacing
+  #- \usepackage{lineno} # For line numbering
+  #- \linenumbers # For line numbering
+  #- \usepackage{setspace}\doublespacing
+  - \usepackage{fontawesome} #for fa symbols
+  - \usepackage{tcolorbox}
+  - \pagenumbering{gobble} #for no page numbering
   - \setlength{\parskip}{0em} #to remove line gaps
@@
 
-**Abstract:** The diversity in animal cognition raises the question of its underlying evolutionary drivers.
-Selection upon more advanced cognitive abilities can stem from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*), among generations (*Cultural Intelligence Hypothesis*), between social units (*Napoleonic Intelligence Hypothesis*), or with the rest of their environment (*Ecological Intelligence Hypothesis*).
-These hypotheses were limited to within-species scenarios.
-Yet, one species rarely occupies an area alone: Space is a place shared between many species that can interact directly or indirectly.
-For species occupying a same dietary niche, interspecific competition could induce a cognitive evolutionary arms race, so as to outperform competitors.
-Furthermore, all species act upon the spatio-temporal distribution of resources, hence contribute to increasing the uncertainty for a third species to infer resource location and availability.
-This would ultimately shape the cognitive machinery involved to allow sufficient harvesting.
-In addition, sympatric species can leave traces of passage and of resource presence that can be cognitively processed by a third species to find it more efficiently.
-As such, to test whether species co-occurrence shaped current patterns of cognition, we used primates as a study example and retraced the evolutionary history of multiple species brain areas involved in foraging activities or not while considering competitive or non-competitive evolutionary scenarios.
-We found that the evolution of the relative size of areas involved in foraging-related information processing and/or retention, as well as in areas related to processing social information, are better described by models accounting for species co-occurrence within dietary guilds.
-More precisely for these brain areas, species co-occurrence was associated to a decrease, and never to an increase, of their relative size.
-Coherently with the observed wide variability in sympatry rate and intensity, the degree of encephalisation was unrelated to the evolutionary success of a lineage (i.e.
-its diversification rate).
-Overall, this comparative study suggests that species co-occurrence stands as a brake to positive selection towards larger cognitive abilities, yet leaves open the question of the underlying ecological mechanisms at play.
-
-<!-- subject to an arms race among species (*Red Queen Intelligence Hypothesis*).  -->
-
-**Keywords:** "Brain size - Cognition - Cooperation - Competition - Intelligence evolution - Primates - Species co-occurrence"
-
-<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
-
 ```{r wordCount}
@@
 
+\newtcolorbox{graybox}{
+  colback=lightgray!25,
+  colframe=lightgray!25,
+  coltext=black,
+  boxsep=3pt,
+  arc=0pt}
+
+:::: {.graybox data-latex=""}
+
+**Abstract |** In hypotheses related to the evolution of animal intelligence, a particular emphasis was given to the role of intra-species conspecifics.
+Yet, one species rarely occupies an area alone: Space is a place shared between many species.
+These latter can be new competitors to outperform or cooperators to decode and maneuver, thereby stimulating cognition.
+They can also contribute to modifying and depleting the environment such as it overly increases its complexity, thereby alleviating the benefice of cognition.
+Considering brain size as a proxy for cognition, we used primates as a study example to test for the intertwine between species co-occurrence and cognition.
+We retraced the evolutionary history of several brain areas considering competitive or non-competitive evolutionary scenarios.
+We found that competitive evolutionary scenarios best predicted the evolution of some brain areas that were related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
+The whole brain size, as well as the size of areas used in more general contexts were not related to the sympatry rate.
+In any case, the evolutionary success of primate species was unrelated th the relative sizes of brain areas.
+Overall, this comparative study suggests that species co-occurrence contributes to shaping the selective pressure acting upon animal cognition, yet leaves open the question of the underlying ecological mechanisms at play.
+
+\hfill
+
+<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
+
+\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Diversification - Intelligence evolution - Primates - Species co-occurrence
+
 <!-- TC:ignore -->
-**Word Count:** `r words$num_words` \newline
+\faInfoCircle  \hspace{0.01in} **Word Count (main text only):** `r words$num_words` \newline
 <!-- Character Count: `r words$num_char` -->
@@
 
+::::
+
 \newpage
-
-# Introduction
-
-On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@dunbar2017there].
-It remains puzzling why humans have a brain that is that large, relatively to body size, compared to other animals, or why primate brain architecture, in general, is much more complex than observed in other taxa.
-Overall, the evolution of the brain is the consequence of constraints [e.g.
-energetic limitations, @navarrete2011energetics], but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
-
-|   To grasp the rationale of current hypotheses that aim to describe the evolution of cognition [@van2006some; @dunbar2017there], consider a primate individual foraging for food.
-Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
-The chosen focal is not looking for any type of food but specific one, as for instance, most primate species often look for fruits.
-Finding fruits for a primate is not an easy task.
-In fact, fruits are the archetype of a hard-to-find resource likely to promote cognitive development because fruit trees are rare, dispersed, and do not produce constantly along the year nor between years, albeit their fruiting period remains nonetheless predictable [@janmaat2016spatio].
-Additionally, they are energy-rich, allowing expansion of costly tissues such as brain tissues [@clutton1980primates].
-Overall, primates thus show remarkable abilities to navigate precisely and target fruit trees likely to yield ripe resource despite they are out of their sensory range [@trapanese2019review], in part because of advanced spatio-temporal information retention [e.g.
-spatial knowledge: @normand2009forest; @robiraroute, temporal knowledge: @janmaat2006evidence; @janmaat2013chimpanzees; @janmaat2013tai].
-
-|   When the resource is out of sight, moving at random could mean travelling unnecessary long distances to finally reach a potentially void tree.
-Hence, for the focal, being capable of processing immediate environmental cues and clues to know where specifically to find fruit trees [@dall2005information; @grove2013evolution] and whether it is probable that these trees currently yield fruits [@dall2005information; @robirainreview; @janmaat2016spatio] would be a considerable advantage.
-Having an appropriate cognitive machinery may avoid costly detours and time recursions to food patches adequately.
-This simple picture draws the basis of the *Ecological Intelligence Hypothesis* [@clutton1980primates; @milton1981distribution; @rosati2017foraging] which stipulates that cognition was selected as a way to buffer the spatio-temporal complexity of the environment (e.g.
-@van2012large).
-
-|   In its quest for food, however, the focal might not be alone: For instance, primates often form social groups [@kappeler2002evolution] in which group members spend considerable time together, have established bounds and constantly share information.
-Thus, they might altogether look for, and process, cues and clues leading to food sources.
-To do so, being able to process signals emitted by other maneuvers would be an advantage, as well as reading through their mind [@devaine2017reading] in order to plan ahead for collective actions or even outsmart them [@byrne1994machiavellian].
-This therefore means plenty of additional information to process, and constitutes the socle of the *Social Intelligence Hypothesis* [@dunbar2017there].
-
-|   In the focal group, however, all individuals are not equally knowledgeable: Perhaps because some have more experience than others, such as the elderly ones would be more experienced than the youths, with the latter thus learning from the former [@laland2004social].
-For instance, young individuals may progressively learn how to process a specific tool to access a hidden comestible part as for nuts [@boesch1994nut] by observing and reproducing, or possibly being teached (learning ways detailed in @estienne2019acquisition).
-In other words, there is vertical transmission that passes by over generations and knowledge thereby accumulates: This is the *Cultural Intelligence Hypothesis* [@whiten2007evolution; @reader2002social], also known as the *Vygotskian Intelligence Hypothesis* in humans [@herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social].
-
-|   Finally, while the group peacefully forages, it might sense the past or current presence of another group and anticipate its move, such as wild baboons do when prioritizing food likely to be depleted by other troops [@noser2010wild].
-The neighboring groups might indeed be competitors for food, mates or any essential resource, and as much as it is advantageous to be able to read through the environment and intra-group companions, it might be advantageous to be able to decode information relative to other groups’ presence and attribute (e.g.
-group size), a view brought by the *Napoleonic Intelligence Hypothesis* [@ashton2020interactions].
-
-|   Yet, in this overly simplistic picture, we moved from a unique individual to a group of individuals and then to multiple groups.
-Never was it question of multiple species.
-Yet, space is a place shared between a plethora of species, some of them occupying a same ecological niche.
-As much as conspecifics could be competitors, or direct or indirect cooperators, so could be individuals from another species with similar ecological preferences, for instance with regards to diet.
-As such, co-occurrence of species from the same guild might contribute into shaping animal cognition.
-On the one side, the presence of sympatric species with overlapping diet could contribute in reinforcing selective pressures for advanced cognition because (i, competition) species would compete for food access (i.e.
-Red Queen paradigm, [@van1973new]).
-Co-occurrence would increase the environmental complexity due to impoverishment of food and addition of noise to the spatio-temporal availability signal because of unforeseen depletion.
-(ii, cooperation/exploitation) sympatric species presence cues could also represent additional information to process to infer resource location and availability.
-Logically then, species with higher brain size would be the most evolutionary successful, thus “booming” and intensively diversifying as for hominins [@melchionna2020macroevolutionary].
-On the other side, (i) the increase in environmental complexity could be such that advanced cognition is no longer adaptive (see for instance [@grove2013evolution] and [@robirainreview] for the limit of the adaptiveness of spatial and temporal cognition respectively), or (ii) the additional cues provided by other species presence would not add, but replace, and perhaps be more easily interpreted than, environmental cues of food availability.
-In this latter case, selective pressure on cognitive abilities would be relaxed, inducing a decrease in brain size in sympatric species compared to lonely species.
-Following this rationale, species living in co-occurrence or not with other species would not face the same evolutionary fate despite initially similar environmental conditions.
-Thus, the evolutionary success of specific lineages would end up unrelated to brain size.
-In this study, we therefore aimed to test how species co-occurrence contributed to shaping the evolutionary history of the encephalisation of the whole, or part of, the brain, and whether this induced a "boom" or a "brake" to cognitive abilities and associated evolutionary success by focusing on frugivorous primates as a study example.
-
-\hfill
 
@@
 
+# Introduction
+
+On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
+Overall, the evolution of the brain is the consequence of constraints (e.g.
+energetic limitations, @navarrete2011energetics), but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
+Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
+Their cognition can result from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*, @byrne1994machiavellian; @dunbar2017there), among generations (*Cultural Intelligence Hypothesis*, @whiten2007evolution; @reader2002social, also known as the *Vygotskian Intelligence Hypothesis* in humans, @herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social), between social units (*Napoleonic Intelligence Hypothesis*, @ashton2020interactions), or with the rest of their environment (*Ecological Intelligence Hypothesis*; @clutton1980primates; @milton1981distribution; @rosati2017foraging).
+
+|   A particular emphasis was given to the role of intra-species conspecifics in shaping animals cognitive abilities.
+Yet, space is a place shared between a plethora of species that can interact directly or indirectly, in particular if sharing some ecological traits, especially diet [@drury2018contrasting].
+To settle to new coral reefs, fishes use pops and clicks of other fishes as an honest signal for resourcefulness there [@gordon2019acoustic], mangabeys follow calls from hornbills to locate fruiting trees [@olupot1998fruit], and interactions even happen across kingdoms, with migratory birds interpreting phenological cues as synonymous of insect availability [@mcgrath2009flower].
+
+|   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
+Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond).
+Although generally considered as a singular entity, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
+For instance, the Striatum is stimulated during social interaction [@baez2013role].
+Therefore, its size is expected to be positively influenced when contacts with other species increase, for instance in species performing mixed-species groups (e.g.
+in callhitrichine primates, @heymann2015unlike).
+Conversely, the evolution of the Main Olfactory Bulb (MOB), allowing processing olfactory cues, or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], should be linked to environmental complexity faced by a species, in particular when foraging.
+This environmental complexity can increase if space is shared with species with similar dietary habits because it contributes to impoverishing the environment and increasing its unpredictability, thus looping on selective pressure towards cognitive abilities [@grove2013evolution: @robirainreview].
+Given high energetic costs of the brain [@raichle2006brain], it is thus expected that sympatry should induce positive selection on the size of brain areas involved in foraging-related information processing, unless the induced environmental complexity starts being too high for cognitive foraging to be adaptive.
+Given that the Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating], the same scenario might apply as well to the Striatum of species that do not live in mixed-groups, which actually constitute the majority of the primate lineage.
+In between, more generalist areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
+
+|    Recent tools have been developed to infer the effect of species interactions on trait evolution, either by modelling trait divergence in co-occurring species from a same guild (e.g.
+dietary guild; Matching Competition: MC models) or considering that the evolutionary rate depends on the number of co-occurring lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
+After reconstructing primate biogeography history (N$_{species}$ = `r minRange`, @matzke2013probabilistic; @matzke2016stochastic) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); @kamilar2009environmental) and diet evolution (N$_species$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy, N$_{species}$ = `r minEQ` to `r maxEQ`), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
+\@ref(fig:figbrain); N$_{species}$ = `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)`).
+The use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in @deaner2000comparative).
+We also estimated the likelihoods of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
+stabilizing selection; see @blomberg2020beyond for a review) or the Early-Burst model (EB, @blomberg2003testing), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criterions corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does interspecific interactions shape brain size evolution?]).
+
 # Results
 
-|   Recent tools have been developed to infer the effect of species interactions on trait evolution, either by modelling trait divergence in co-occurring species from a same guild (e.g.
-dietary guild; Matching Competition: MC models) or considering that the evolutionary rate depends on the number of lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
-After reconstructing primate biogeography history when considering `r length(areaName)` biogeographic areas following [@kamilar2009environmental] based on `r minRange` primate species (@matzke2013probabilistic; @matzke2016stochastic; Figure \@ref(fig:figmap)) as well as primate diet evolution based on `r minFruit + minLeaf` to `r maxFruit + maxLeaf` species (discrete trait: frugivory vs.
-folivory; @bollback2006simmap.
-The classification varied depending on how frugivory/folivory was assessed, see [Dietary guild]), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy for `r minEQ` to `r maxEQ` frugivorous), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
-\@ref(fig:figbrain); comprising `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)` frugivorous species).
-The use of specific region size relatively to the body mass (see @deaner2000comparative for further consideration of scaling methods), and not raw size, rather depicts the evolutionary evolution of cognitive abilities in terms of allocation rather than abilities per se (although it is vividly discussed whether raw measures are anything informative on "abilities" too @logan2018beyond).
-We also estimated the likelihoods of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) assuming that traits are constrained around on optimal value (e.g.
-stabilizing selection; see @blomberg2020beyond for a review on these approaches) or the Early-Burst model (EB, @blomberg2003testing), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does interspecific interactions shape brain size evolution?]).
-Non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
-By contrast, competitive models were most supported in areas involved in sensory abilities (the main olfactory bulb, MOB), short-term working memory and long-term spatio-temporal information retention (Hippocampus, @burgess2002human), and the Striatum an area that is involved in information processing during social interaction (i.e.
-social reward assessment; @izuma2008processing) (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and Striatum, but a slow down for the MOB.
+|   Non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
+By contrast, competitive models were most supported in areas involved in short-term working memory and long-term spatio-temporal information retention (Hippocampus, @burgess2002human) and in planning, reward assessment, and information processing during social interaction (Striatum, @baez2013role; @johnson2007integrating), while they tended to be so for one involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and the Striatum, but a slowdown for the MOB.
 
@@
 For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire range as covariates.
-On average ($\pm$ SE), the considered primate species had `r meanNspeciesCoocc` in their distribution range ($\pm$ `r seNspeciesCoocc`).
-That ranged from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
+We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates.
 On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
 That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
+In term of distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
 The number of sympatric species never influenced significantly the relative size of the brain or other specific areas  (Table \@ref(tab:tableRegGradient)).
-The percentage of range shared on average with other species was coherently assessed as significantly correlated, or as a trend, with the relative size of areas which evolutionary history was better described with competitive models: the Hippocampus, the MOB and the Striatum (Hippocampus: $t$`r testGradientHippocampus`;  MOB: $t$`r testGradientMOB`; Striatum: $t$`r testGradientStriatum`).
-The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`;  MOB: `r estimateGradientMOB`; Striatum: `r estimateGradientStriatum`), which means that higher overlap rhymes with lower relative size, insensitive to data and the phylogeny variability (Table \@ref(tab:tabledfsensitivity)).
-Thus, it suggests that sympatric species are subject to less stringent selection on advanced cognitive abilities.
+Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas for which the evolutionary history was better described with competitive models: The Hippocampus, the MOB and the Striatum (Hippocampus: $t$`r testGradientHippocampus`;  MOB: $t$`r testGradientMOB`; Striatum: $t$`r testGradientStriatum`).
+The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`;  MOB: `r estimateGradientMOB`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogeny variability (Table \@ref(tab:tabledfsensitivity)).
+Thus, it suggests that sympatric species are either subject to a positive selection for smaller brain, or to a less stringent selection on advanced cognitive abilities.
 
@@
 
+# bp.resp <- breakpoints(Diversification ~ Time, data=aggregatedSpeciationTime.mean)
+# summary(bp.resp)
+# ## the BIC 
+# plot(bp.resp)
+# breakpoints(bp.resp)
+
+#Suggest that 4 is better from stats, visually 2
+
 bp.resp <- breakpoints(Diversification ~ Time, data=aggregatedSpeciationTime.mean, breaks=2)
@@
 
-|   Finally, we investigated how brain evolution was related to evolutionary success, assumed proportional to diversification rate (i.e.
-speciation minus extinction rate), by using birth-death models of species diversification [@maliet2019model].
-Overall, diversification, estimated based on molecular phylogeny without fossil records, increased over time (Figure \@ref(fig:figdiversificationTime), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
-Visual inspection clearly suggested positive relationship between diversification rate and the size of brain areas (Figure \@ref(fig:figRegressionDiversification)).
-Yet, accounting for phylogenetic dependence erased such pattern: In fitted Bayesian regressions, the size of brain size was never significantly associated with an increase in diversification rate (Table \@ref(tab:tableRegDiversification); see robustness in Table \@ref(tab:tabledfsensitivity2)).
+|   Finally, we investigated the evolutionary consequences of brain evolution by evaluating whether brain sizes correlated with species diversification rates (i.e.
+speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
+Overall, species diversification, estimated based on molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
+When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification); see robustness in Table \@ref(tab:tabledfsensitivity2)).
 
 # Discussion
-
-|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond).
-The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
-in primates: @milham2018open), or with standardized behaviourally explicit comparisons (e.g.
-on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time.
-In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species.
-Further, biases might be limited by considering measurement variability [@logan2018beyond] or the mosaic structure of the brain [@barton2000mosaic; @decasien2019primate].
-We did both.
-Although it existed a variability in the data (phylogenetic and on traits), results were robust.
-In addition, we saw that the evolutionary history between specific brain regions did not equally depend on the number of lineages living in sympatry.
-The effect of between-species interaction was indeed only evidenced for specific areas, more particularly those involved in immediate information processing based on senses (Main Olfactory Bulb, MOB), in a working memory or in a long-term memory of spatio-temporal information (Hippocampus) and in processing social cues (Striatum).
-These areas thus imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates.
-This supports the general discussion on the importance of social vs.
-ecological factors to explain primate cognition evolution and diversity [@decasien2017primate; @powell2017re].
-Using a modelling approach including metabolic, life-history and game theories, @gonzalez2018inference emphasized that ecological challenges were preponderant (equating around 60% of challenges faced) to explain current human brain size, which then was also substantially promoted by the occurrence of social challenges (equating around 30% of challenges faced).
-Here, we highlighted that the cognitive function allowing processing sociological or ecological cues are both affected by species sympatry.
 
@@
 
-<!-- From small to long range ( < few km) primates might rely on sensory abilities to decide where to go [@dominy2001sensory].
-They are known as visual mammals.
-In particular, frugivorous species highly benefit from a trichromatic vision that enables them to distinguish fruits within the dense foliage [@osorio1996colour].
-Yet, in tropical forests, visual range is easily impeded, being barely greater than a hundred of meters.
-On the contrary olfactory cues are of longer distance.
--->
-
-|   Although primates are microsmatic species and better known as visual foragers [@dominy2001sensory; @osorio1996colour], frugivorous species also benefit from olfactory cues processing.
-Fruits can be highly odorous: The produced ethanol and other chemical compounds can be smelled so as to identify fruit ripeness, but also the location of fruit trees with ripe fruit, although current evidence for this latter case is weak [@nevo2015led].
-The Lemuriformes, that are known to prioritize smell compared to other primate species, indeed have the largest relative MOB size (i.e.
+The bigger is not necessarily the better.
+The size of the brain is subject to a compromise between the energy it incurs, and the increase of fitness it allows.
+This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ) were best described by the Orstein-Uhlenbeck process, what might suggest a stabilisation towards an optimal size as a result of an equilibrium between costs and benefices.
+As the brain area is regionally specialised [@barton2000mosaic], it was also expected that brain regions could be under different selective pressures.
+For instance, the Lemuriformes, that are known to prioritize smell compared to other primate species, indeed have the largest relative MOB size (i.e.
 pondered by body size) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-When worthy targets are out of the perceptual range, primates might rely on internal memories of the resource distribution in space, and of their availability period, to forage efficiently [@janson2007wild; @trapanese2019review].
-In this system, the Hippocampus occupies a key position: It hosts (inter)neurons that encode for spatial location and orientation (known as place, grid or head cells, @grieves2017representation) and is home of episodic memory [@ranganath2016hippocampus].
-In addition, when foraging, environmental cues might be complemented by social cues, which processing can involve the Striatum.
-Platyrrhini, and callitrichine in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+Similarly, Platyrrhini, and Callitrichine in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+Here, we show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species co-occurrence, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB.
+These areas imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates.
+This supports the general discussion on the importance of social *vs* ecological factors to explain primate cognition evolution and diversity [@decasien2017primate; @powell2017re].
+
+|   The relative size of these brain areas were negatively associated with one index of sympatry intensity, the average overlap of a species distribution range with that of other species.
+Because the ratio of the other brain areas is insensitive to sympatry intensity, it is unlikely that this results from a by-product of a selection on body mass and might thus be a consequence of species direct or indirect interactions.
+In general, competition is the first-thought mechanism to describe community structures [e.g.
+@rocha2015role].
+In primates, it is rare to observe direct competition between species, which should translate into site exclusion.
+In fact, inter-species site exclusion in this taxa has only been observed in gibbons [@suwanvecho2012interspecific].
+For species with overlapping diet, indirect competition for resource might happen.
 It has been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging].
-A lesser scrutinized function of the Striatum is also that of supporting goal-directed behaviour and planning abilities [@johnson2007integrating].
-Overall, we expect the size of brain areas involved in dissecting socio-environmental cues to be under strong positive selection [@decasien2017primate; @barton2006olfactory].
-Here, on the contrary, we showed that species co-occurrence acts as a brake to such positive selection since the size of these areas were negatively associated with species co-occurence.
-This was the result of a slow down of the evolutionary rate for the MOB, but an accelration (thus towards lower size) of the evolutionary rate for the Hippocampus and Striatum.
-
-|   Competition is generally the first-thought mechanism to describe community structures [e.g.
-@rocha2015role].
-Following the principle of an arms race between species (Red Queen scenario, @van1973new), it would have been logical to see species co-occurrence as an additional positive driver towards increase size.
-A multi-species case stands yet as a peculiar situation.
-In particular, inter-species site exclusion in primates has been observed only in gibbons [@suwanvecho2012interspecific].
-Thus, given that primates restrain their space-use to a limited area, their home range, they will suffer from more intense depletion (and consequently unpredictability), of their environment.
-If this latter is too important, this could alleviate the benefices purported by foraging cognition [@grove2013evolution; @robirainreview]: The environment would be too complex to read through it, and conspecifics might be thus be too error-prone to rely on them.
-Positive selection for "bigger" areas supporting foraging efficiency would be relaxed, and, given the functioning and maintenance cost of the brain [@raichle2006brain], this could even turn into a selection for "smaller" sizes of brain areas related to socio-ecological cue processing.
-
-|   Yet, as much as social species could exploit cues provided by conspecifics, a species might also benefit from using cues of other species.
-To settle to new coral reefs, fishes use pops and clicks of other fishes as an honest signal for resourcefulness there [@gordon2019acoustic], mangabeys follow calls from hornbills to locate fruiting trees [@olupot1998fruit], and interactions even happen across kingdoms, with migratory birds interpreting phenological cues as synonymous of insect availability [@mcgrath2009flower].
-These signals should not involve true social reading, thus should be processed by areas such as the Neocortex which process such sensory cues [@barton1996neocortex].
-This could explain why the size of this area was actually better described by evolutionary models with stabilizing selection and did not follow the pace of the three aforementionned areas.
-Despite a potential increase load of stimuli (due to the cues provided by other species), the Neocortex size however did not correlate positively with sympatry rate.
-Perhaps the inter-specific cues do not add, but simply replace other used cues.
-In addition, given that areas affected by sympatry are far smaller than those that are not, there is no surprise that the deficit in allocation to these areas, potentially to the benefits of the Neocortex, is not observed through an increase of the Neocortex size.
-
-|   Finally, we observed that primate diversification rate increased along time particularly around -`r dateFirstRupt[2]` and -`r dateSecondRupt[2]` Myr.
-This corroborates previous findings about diversity boom in primate lineages early and late Miocene as a consequence of a sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography].
-Given the observed effect of species co-occurrence on brain size selection trends, species living in areas with or without competitive species would thus not be under the same selective regime.
-This would explain why we did not observe a link between the size of brain areas negatively affected by sympatry and their evolutionary success, approximated by their diversification rate.
-Why, nonetheless, the whole brain size is not correlated to diversification rate, while it is unaffected by the density of sympatric species, remains puzzling given that higher cognitive abilities are associated with higher ecological success since they act as a "cognitive buffer" to environmental challenges [@sol2007big].
-For these reasons, larger brain size is indeed associated with higher diversification in birds [@sayol2019larger].
-To sum up, these results suggest that the encephalisation boom observed in primates shall not be explained by a global, or area-restricted, encephalization increase, as suggested for Hominins [@melchionna2020macroevolutionary].
+The utilization of these cues should promote cognition until reaching a certain range of environmental complexity [@grove2013evolution; @robirainreview].
+Our results could thus suggest that species sympatry may trigger an important decrease in cues reliability, for instance due to higher and unforeseen depletion rate.
+That would explain a relaxed positive selection for advance cognitive abilities, and conversely, given the cost of brain maintenance [@raichle2006brain], would induce a negative selection towards areas involved in foraging related activities like the Hippocampus, the MOB and the Striatum.
+
+|   Given the context dependence of the direction of selection (towards bigger sizes in the absence of other species, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by inter-species sympatry.
+Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to inter-species sympatry too.
+This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
+The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetical signals (Figure \@ref(fig:figRegressionDiversification)).
+In fact, a sudden encephalisation in primates is clearly associated to a limited number of close-related species [@decasien2017primate; @melchionna2020macroevolutionary].
+This clearly limits the statistical power of our phylogenetically corrected analyses and might thus explain why we did not observe evidence of connivance between brain size and evolutionary success.
+A positive association between brain size and bigger brain was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
+This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in @melchionna2020macroevolutionary remains a likely possibility.
 
@@
 
-In the end, the inter-specific effect on cognition was here mainly viewed under the prism of foraging and was limited to within primates.
-Without further evidence, it is as likely to hold if considering all potential competitors, that is not limited to an arbitrary taxa (see evidence of primate and non-primate interactions, reviewed in @heymann2015unlike), and in other contexts, such as the social environment.
-In fact, the general hypotheses on cognition evolution, discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
-As Alice said “'It's a great huge game of chess that's being played—all over the world” (@Carroll, Chapter II) and all individuals are just pieces to play with or against, no matter the species.
+In conclusion, the use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond).
+The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
+in primates: @milham2018open), or with standardized behaviourally explicit comparisons (e.g.
+on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time to generate large-enough datasets.
+In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species.
+Here, we showed that species sympatry can influence the evolutionary scenario that applies to animals' brain, but the proximate mechanisms at play remain to be elucidated.
+Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: Polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
+As Alice said “It's a great huge game of chess that's being played—all over the world” (@Carroll, Chapter II) and all individuals are just pieces to play with or against, no matter the species.
+
+<!-- TC:ignore -->
+
+\newpage
 
@@
 
-Data processing, analyses, and plots were computed with R software version 4.0.3 [@Rsoftware].
+Data processing, analyses, and plots were computed with R software [`r extractRversion()`, @Rsoftware].
 Used codes and data are freely available at [https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency](https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency).
-
-## Data Collection
-
 Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*, this latter being too geographically isolated.
@@
 
+## Data Collection
+
 ### Phylogeny
@@
 
-### Brain data
+### Trait data
 
@@
 They were freely available in the main manuscript or supplementary materials.
-When the species was represented multiple times within dataset, we obtained a unique attribute by averaging it.
+When a species was represented multiple times within dataset, we obtained a unique attribute by averaging it.
 From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
@@
 Body mass was obtained from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.
-The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or associate information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, @wiltgen2004new; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, @burgess2002human).
-The Striatum (N$_{Striatum,max}$ = `r maxStriatum`), which supports information processing during social interaction (i.e.
-social reward assessment; @izuma2008processing), was chosen so as to serve as a comparative “null” area.
-To investigate their evolutionary history, we used the ratio between their volume and
-<!-- that of the whole brain.  -->
-
-### Diet and body mass data
-
+The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, @wiltgen2004new; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, @burgess2002human).
+The Striatum (N$_{Striatum,max}$ = `r maxStriatum`) supports information processing during social interaction, reward assessment, planning or goal-oriented behaviours [@baez2013role; @johnson2007integrating].
+To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
 Percentage of frugivory and/or folivory was obtained based on freely available dataset from @decasien2017primate and @powell2017re for the frugivory and folivory rate, or @willems2013collective for the folivory rate.
-Body mass data were available from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.
 
@@
 
-One to multiple large-scale geographic areas were assigned to each species as soon as the species current range overlapped in surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas; Figure \@ref(fig:figmap)).
+One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Figure \@ref(fig:figmap)).
 Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlap contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
-These geographic areas were initially, manually delimited using Google earth professional (v7.3.3) as a combination of the environment topology and geographic regionalization relative to the primate taxonomy [@kamilar2009environmental].
 Based on the structure (i.e.
 number of species and their phylogenetic relationship) of primate communities at different field sites, @kamilar2009environmental determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
-The considered geographic areas are represented in Figure \@ref(fig:figmap).
-The chosen scale for the areas is large because (1) retracing history of a large number of areas necessitates considerable computational means.
+We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
+These geographic areas are represented in Figure \@ref(fig:figmap) and correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia and the Asian Islands.
+The chosen scale for the areas is large because (i) retracing history of a large number of areas necessitates considerable computational means.
 In addition, this drastically increases computational time of phylogenetic model of brain trait evolution too.
-Furthermore (2), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unpreceeding speed rate.
+Furthermore (ii), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unprecedented speed rate.
 Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
 evidenced on the North American fauna in @pineda2021mammal).
-Finally, note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-Hence, *Macaca sylvanus* is not considered in this study.
-
-|   We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic] following the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
-This algorithm aims to fit, among others, non-time-stratified dispersal-extinction-cladogenesis (DEC) models (used here), specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
+
+|   We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
 To reconstruct the evolution of species range, we fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas.
@@
 Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models, we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fitting (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
+Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
 
@@
 
-|   Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence on brain selection), even if less consumed.
+|   Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
 Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
-First, such static rate does not reflect potential seasonality in fruit eating [e.g.
-@masi2009western], which is generally shorter, hence a lower overall frugivory rate.
-Second, frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding event.
+First, such static rate does not reflect potential seasonality in fruit eating (e.g.
+@masi2009western), which is generally shorter, hence a lower overall frugivory rate.
+Second, frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
 Finally, the methodology to obtain this rate could additionally vary (e.g.
@@
 For all these reasons, we used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
-Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
+
+|   Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
 at the root) but with no prior on the transition matrix.
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fitting [Phylogenetic models] to account for uncertainty of these ancestral diet estimations (see [Phylogenetic models, Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits [Phylogenetic models] to account for uncertainty of these ancestral diet estimations (see [Phylogenetic models, Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
 
@@
 
-We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic model of EQ - or relative size of a specific brain area – evolution with and without species competitions.
-Models were fitted on different sample sizes due to non-availability of some data.
+We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic models of EQ - or relative size of a specific brain area – evolution with and without species competitions.
+Models were fitted on different sample sizes due to non-availability of some data for some traits.
 Specifically, models using EQ included `r minEQ` to `r maxEQ` frugivorous species.
 Other models included more reduced sample sizes (in species number): Striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), Neocortex (`r minNeocortex` to `r maxNeocortex`), Hippocampus (`r minHippocampus` to `r maxHippocampus`), Cerebellum (`r minCerebellum` to `r maxCerebellum`).
+Nonetheless, for a given set of models (i.e.
+within brain area), the sample was strictly identical, allowing within set comparison.
 Prior fitting, trait parameters were log-transformed to reach more symmetrical distributions.
@@
 
-$f_{exp}(\lambda)=\lambda_{0}\exp(rL)$
+$f_{exp}(\lambda)=\lambda_{0}\exp(rl)$
 
@@
 
-where $\lambda_{0}$ corresponds to the value of the initial ancestor, $L$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
+where $\lambda_{0}$ corresponds to the value of the initial ancestor, $l$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
 All these models were repeated `r numberSimulations` times, using `r randomSampling` different combination of the evolutionary history of ranging and diet.
@@
 
+```{r prepfigevolution}
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+
+counter=0
+start=counter
+end=counter
+numberSimulations=10
+totModelsWorked=c(0,0,0,0,0,0,0)
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        counter=end+1
+        start=counter
+        end=counter + numberSimulations - 1
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
+        totModelsWorked[1]=totModelsWorked[1]+1
+        }, error=function(e){
+          #Do nothing
+          }
+        )
+
+        tryCatch(
+        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryEQFrugivory[start:end,] <- toAdd
+        totModelsWorked[2]=totModelsWorked[2]+1
+        }, error=function(e){
+          #Do nothing
+        }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryNeocortexFrugivory[start:end,] <- toAdd
+        totModelsWorked[3]=totModelsWorked[3]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryHippocampusFrugivory[start:end,] <- toAdd
+        totModelsWorked[4]=totModelsWorked[4]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryCerebellumFrugivory[start:end,] <- toAdd
+        totModelsWorked[5]=totModelsWorked[5]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryStriatumFrugivory[start:end,] <- toAdd
+        totModelsWorked[6]=totModelsWorked[6]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryMOBFrugivory[start:end,] <- toAdd
+        totModelsWorked[7]=totModelsWorked[7]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
+summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
+summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
+summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
+summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
+summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
+summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
+
+colnames(summaryBrainFrugivory) <- colnames(toAdd)
+colnames(summaryEQFrugivory) <- colnames(toAdd)
+colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
+colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
+colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
+colnames(summaryStriatumFrugivory) <- colnames(toAdd)
+colnames(summaryMOBFrugivory) <- colnames(toAdd)
+
+##----
+
+colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
+
+models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
+colourModels <- brewer.pal(n = 6, name = "Set1")
+
+```
+
 (b) Dealing with data uncertainty and parameter sensitivity
@@
 In this analysis, uncertainty can stem from two sources.
-First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees.
+First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
 
@@
 Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
-In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Appendix Figure \@fig(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
-To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) various biogeography and dietary evolutionary history estimations, (2) random samples of the dietary and brain traits in case of multiple values available (i.e.
-equal probability for each possible value to be selected) and (3) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence.
+In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
+To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
+equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence, and (3) various biogeography and dietary evolutionary history reconstructions.
 
 |   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
+We stopped computations when the calculation of the likelihood was excessively long.
+The final sample size thus was of `r min(totModelsWorked[-2])*10` models.
 
@@
 
-We investigated how the primate taxon diversified over time.
+We investigated how primates diversified over time.
 Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
@@
 Three independent chains were run until their respective convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
-The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
+The analysis relied on the use of a consensus tree of primate phylogeny from @dos2018using.
 This latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
 
-|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of "known" taxa among all possibles ones.
+|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
 @estrada2017impending estimated that, given current knowledge, the primate lineage should be composed of 504 species.
@@
 We thus parameterized the *ClaDS* algorithm with this value for the estimate sampling fraction.
-Yet, given that the extant number of primate species is subject to controversy, and also because the estimated sampling fraction affects diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
-At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each primate species, as well as the mean rate (given all lineages) through time.
+Yet, given that the extant number of primate species is subject to controversy, and because the estimated sampling fraction may affect diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
+At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each extant primate species, as well as the mean diversification rate (given all lineages) through time.
 
@@
 
-To determine the direction of the selection of species co-occurrence on size of brain regions for which competitive models fitted the best, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
+To determine the nature of the relationship between species co-occurrence and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
 a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients but its diagonal multiplied by lambda) for each brain region individually and for frugivorous species only.
-We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we specifically focused on brain areas for which the evolutionary history was best described by competitive models.
+We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we it included brain areas for which the evolutionary history was best described by competitive models.
 Here specifically, we considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
@@
 
-In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different brain traits against the diversification rate (i.e.
+In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the diversification rate (i.e.
 accounting for both, speciation and extinction) estimated for each species by the *ClaDS* algorithm.
@@
 Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
-We did not observe correlation issue among predictors either [max VIF < 2, @mundry2014statistical].
+We did not observe correlation issue among predictors either (VIF$_{max}$ < 2, @mundry2014statistical).
 
@@
 
-We could not compute phylogenetic regressions to link diversification and brain traits using a frequentist approach because it lead to violation of homoscedasticity.
+We could not compute phylogenetic regressions to link diversification and brain traits using a frequentist approach because it led to violation of homoscedasticity.
 Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
@@
 Prior on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
-We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion [max value < `r round(max(gelmanRubinValues), digit=2)`; @gelman1992inference], as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
+We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=2)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
 In Appendix [Model assumptions], we present trace and distributions of posterior estimates.
@@
 |   To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10000 possible trees from the 10kTrees project.
-For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple value (e.g.
+For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple values (e.g.
 if body mass was provided by different datasets etc.).
-For the diversification analysis specifically, we also assessed the sensitivity to changes in hypothesized fraction of known primate taxon by refitting the models for values ranging between 60 to 95% (as specified before) using the "standard" dataset and the consensus tree.
+For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before) using the "standard" dataset and the consensus tree.
 
@@
 Their indirect input is therefore tremendous.
-
-|   Both authors were supported by a doctoral grant from the *École Normale Supérieure*, Paris.
-BR received support from the *Centre d’Écologie Fonctionnelle et Évolutive*, Montpellier and the *Musée de l'Homme*, Paris.
-BP-L received support from the *École Normale Supérieure*, Paris and the *Muséum National d’Histoire Naturelle*, Paris.
+Both authors were supported by a doctoral grant from the *École Normale Supérieure*, Paris.
 
@@
 BR conceived the study, collected, cleaned and analyzed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
-BP-L implemented the ClaDS algorithm with our data, helped with other analyses, adapted them for, and ran them on, the cluster, and revised the manuscript multiple times.
+BP-L implemented the ClaDS algorithm for our data, helped with running other analyses, and revised the manuscript multiple times.
 The authors declare having no conflict of interest.
@@
 
+# Literature cited
+
+<div id="refs"></div>
+
+<!-- TC:endignore -->
+
 \newpage
@@
 ```{r tableRegGradient, include=TRUE}
-
+results.df_gradient <- results.df_gradient[-(6:10),]
+rownames(results.df_gradient) <- NULL
 knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the selection gradient direction | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
@@
 The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold) %>%
+  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 ```
+
 \newpage
@@
 ```{r tableRegDiversification, include=TRUE}
-
+results.df_diversification <- results.df_diversification[-(5:8),]
+rownames(results.df_diversification) <- NULL
 knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the diversification pattern | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
@@
 The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification) %>%
+  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 ```
-```{r figmap, include=TRUE, warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction | Depicted is the Natural Earth projection of the world.
-Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
+
+```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction represented on the Natural Earth projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
 Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
@@
   coord_sf(crs = proj.map, expand = F) +
-  scale_fill_manual(values = colourArea) +
+  scale_fill_manual(values = colourArea, labels=c("Central Africa", "South/East Africa", "West Africa", "Central America", "North of South America", "South of South America", "Central/East Asia", "Asian islands", "South Asia", "West Asia", "East Madagascar", "West Madagascar")) +
   labs(fill = "")  +
@@
 In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation processes [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
-The Striatum is involved in social information processing [@izuma2008processing].", sep="")}
+The Striatum is involved in social information processing [@baez2013role].", sep="")}
 
@@
 
-```{r prepfigevolution}
-
-###Set working directory
-setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
-
-summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-
-counter=0
-start=counter
-end=counter
-numberSimulations=10
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        counter=end+1
-        start=counter
-        end=counter + numberSimulations - 1
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
-        }, error=function(e){
-          #Do nothing
-          }
-        )
-
-        tryCatch(
-        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryEQFrugivory[start:end,] <- toAdd
-        }, error=function(e){
-          #Do nothing
-        }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryNeocortexFrugivory[start:end,] <- toAdd
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryHippocampusFrugivory[start:end,] <- toAdd
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryCerebellumFrugivory[start:end,] <- toAdd
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryStriatumFrugivory[start:end,] <- toAdd
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryMOBFrugivory[start:end,] <- toAdd
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
-summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
-summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
-summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
-summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
-summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
-summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
-
-colnames(summaryBrainFrugivory) <- colnames(toAdd)
-colnames(summaryEQFrugivory) <- colnames(toAdd)
-colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
-colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
-colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
-colnames(summaryStriatumFrugivory) <- colnames(toAdd)
-colnames(summaryMOBFrugivory) <- colnames(toAdd)
-
-##----
-
-colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-
-models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
-colourModels <- brewer.pal(n = 6, name = "Set1")
-
-```
-
 ```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="AICc weights of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
@@
 
+```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
+The grey background depicts the standard deviation.
+The two breakpoints, depicted by the plain dots and the vertical dotted bars, were thus estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
+The three fitted regressions are displayed by the dashed lines.
+The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the the Bayesian Information Criterion.
+The identified breakpoints coin with identified sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
+
+##Plot diversification in function of time
+xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
+xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
+ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
+ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
+
+plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
+     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
+     las=1, type="n", tcl=-0.25, bty="n",
+     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
+     xpd=TRUE)
+
+#Add grid
+addGrid(
+  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
+  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
+  axisPlot=TRUE, round=TRUE, digit=c(2,2))
+axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
+
+#Add background se
+polygon(
+  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
+  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
+  col=grey(level=0.5, alpha=0.15),
+  border=NA
+)
+
+#Add mean
+lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
+
+library(strucchange)
+## confidence interval
+colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
+
+yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
+ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
+
+# Rupture points and (CI too reduced to be plotted)
+points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
+# errorBars(location=c(yFirst), 
+#          meanPt=c(-dateFirstRupt[2]),
+#          barValue=c(0,0), refUnit=1, 
+#          minValue=-80, maxValue=80, 
+#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
+#          col="black", lty=1, 
+#          horiz=TRUE, symmetrical=FALSE)
+
+#Vertical bars
+segments(
+  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  y0=c(0,0),
+  y1=c(yFirst, ySecond),
+  lty=3
+)
+mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
+
+#three fitted regressions
+fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
+
+reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
+reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
+reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
+
+lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
+```
+
 <!-- TC:ignore -->
 
-# Literature cited
-
-<div id="refs"></div>
-
 \beginsupplement
-\newpage
+
+\clearpage
 
@@
 
-Availability of trait and biogeography range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Figure \@ref(fig:figdata).
+Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Figure \@ref(fig:figdata).
 
@@
 
-We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to bieography ranges, or anatomical/behavioural traits.
-
-### Sensitivity to variation in biogeography range
-
-```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=3.5, fig.height=3.5, fig.cap=paste("Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
+We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to distribution ranges, or anatomical/behavioural traits.
+
+### Sensitivity to variation in distribution range
+
+```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4, fig.height=4, fig.cap=paste("Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
 ", geographicThresholdVector[2]/2*100, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2]*100, "%.
@@
 Prior calculation, traits were pondered *within* species by the *within* species max value.
-The point represents the mean repeatability $r$ calculated as $V_{between}/(V_{between}+V_{within})$, with the $V_{between}$ and $V_{within}$ corresponding the variance *between* or *within* species.
+The point represents the mean repeatability $r$ calculated as $\\sigma^{2}_{between}/(\\sigma^{2}_{between}+\\sigma^{2}_{within})$, with the $\\sigma^{2}_{between}$ and $\\sigma^{2}_{within}$ corresponding the variance *between* or *within* species.
 The bar depicts the standard error.
-For all graphics, sample sizes are indicated above the upper value of the CI/error interval.
-"}
+For all graphics, sample sizes are indicated above the upper value of the CI/error interval."}
 
@@
 
-## Diversification pattern over time
-
-```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
-The grey background depicts the standard deviation.
-The two rupture points, depicted by the plain dots and the vertical dotted bars, were calculated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
-The three fitted regressions are displayed by the dashed lines."}
-
-##Plot diversification in function of time
-xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
-xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
-ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
-ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
-
-plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
-     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
-     las=1, type="n", tcl=-0.25, bty="n",
-     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
-     xpd=TRUE)
-
-#Add grid
-addGrid(
-  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
-  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
-  axisPlot=TRUE, round=TRUE, digit=c(2,2))
-axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
-
-#Add background se
-polygon(
-  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
-  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
-  col=grey(level=0.5, alpha=0.15),
-  border=NA
-)
-
-#Add mean
-lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
-
-library(strucchange)
-## confidence interval
-colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
-
-yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
-ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
-
-# Rupture points and (CI too reduced to be plotted)
-points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
-# errorBars(location=c(yFirst), 
-#          meanPt=c(-dateFirstRupt[2]),
-#          barValue=c(0,0), refUnit=1, 
-#          minValue=-80, maxValue=80, 
-#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
-#          col="black", lty=1, 
-#          horiz=TRUE, symmetrical=FALSE)
-
-#Vertical bars
-segments(
-  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  y0=c(0,0),
-  y1=c(yFirst, ySecond),
-  lty=3
-)
-mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
-
-#three fitted regressions
-fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
-
-reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
-reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
-reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
-
-lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
-```
-
 ## Phylogenetic regressions: results, stability and assumption
@@
 \centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf}
-\caption{\footnotesize{Phylogenetic regressions of the size of the different brain areas in function of the number of sympatric species (left) or the percentage of the range overlapping with the range of other species (right) | The numeric labels refer the brain area number of Figure 1.
-Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the range overlaped by sympatric species is averaged, while the right graphics do the opposite.
+\caption{\scriptsize{Phylogenetic regressions of relative brain size in function of sympatry intensity indices | Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the distribution range overlapped by sympatric species is averaged, while the right graphics do the opposite.
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
@@
 \begin{figure}
-\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
-\caption{\footnotesize{Phylogenetic regressions of the diversification rate in function of the size of the different brain areas | The numeric labels refer the brain area number of Figure 1.
-Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+\centering\includegraphics[width=0.7\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
+\caption{\scriptsize{Phylogenetic regressions of the diversification rate in function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
 The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent gray background.}}\label{fig:figRegressionDiversification}
@@
 DfBetas and Cook's distance), as well as when accounting for data variability (i.e.
-re-sampling among possible values given all datasets) or when using different parameterization (i.e.
-"sampling fraction" of known species for diversification analysis)
+re-sampling among possible values given all datasets) or when using different parameterisation (i.e.
+"sampling fraction" of known species for diversification analysis).
 
@@
 
+\hfill
+
 (a) Phylogenetic regressions: selection gradient
@@
 ```{r tabledfsensitivity, include=TRUE}
-knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the selection gradient direction | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+summarySensitivityGradient <- summarySensitivityGradient[-(1:4),]
+rownames(summarySensitivityGradient) <- NULL
+knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between speies co-occurrence and relative brain sizes | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 ```{r tabledfsensitivity2, include=TRUE}
-knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the diversification pattern | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
+summarySensitivityDiversification <- summarySensitivityDiversification[-(1:3),]
+rownames(summarySensitivityDiversification) <- NULL
+knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
+             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the relationship between species diversifition and relative brain sizes| Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 
-```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values vs.
-the residuals."}
+```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
 for(a in 1:length(traitName)){
+  if(a!=2){#Remove brain
     model <- get(paste("modelBrain", traitName[a], sep="_"))
@@
   }
+}
 ```
@@
 for(a in 1:length(traitName)){
+  if(a!=2){#Remove brain
     model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))

### 2021-08-11 Scripts/Analysis1_competitionsignal/EvolutionaryHistoryAnalysis.R

@@ -659,15 +659,15 @@ view3d(userMatrix = um)
 contour3d(template, x=1:dtemp[1], y=1:dtemp[2], z=1:dtemp[3], level = cut, alpha = 0.03, draw = TRUE)
 
 mask = remake_img(vec = img %in% hippocampus, img = img)
-contour3d(mask, level = c(0.5), alpha = c(0.4), add = TRUE, color=colourHip)
+contour3d(mask, level = c(0.5), alpha = c(0.7), add = TRUE, color=colourHip)
 mask = remake_img(vec = img %in% cerebellum, img = img)
-contour3d(mask, level = c(0.5), alpha = c(0.4), add = TRUE, color=colourCereb)
+contour3d(mask, level = c(0.5), alpha = c(0.7), add = TRUE, color=colourCereb)
 mask = remake_img(vec = img %in% MOB, img = img)
-contour3d(mask, level = c(0.5), alpha = c(0.4), add = TRUE, color=colourOlf)
+contour3d(mask, level = c(0.5), alpha = c(0.7), add = TRUE, color=colourOlf)
 #mask = remake_img(vec = img %in% neocortex, img = img)
 #contour3d(mask, level = c(0.5), alpha = c(0.4), add = TRUE, color=c("orange"))
 mask = remake_img(vec = img %in% striatum, img = img)
-contour3d(mask, level = c(0.5), alpha = c(0.4), add = TRUE, color=colourStri)
+contour3d(mask, level = c(0.5), alpha = c(0.7), add = TRUE, color=colourStri)
 
 
 ### add text
@@ -684,6 +684,14 @@ arrow3d(p0=c(dtemp[1]/2,dtemp[2],dtemp[3]/2), p1=c(dtemp[1]/2,1.1*dtemp[2],dtemp
 #legend3d(x=0.1, y=0.2, legend = c("Cerebellum", "Hippocampus", "MOB", "Striatum"), fill = c(colourCereb, colourHip, colourOlf, colourStri), cex=1, bty="n", ncol=2)
 #rglwidget()
 
+# save in eps format
+rgl.snapshot('3dplot.png', fmt = 'png')
+rgl.postscript("3dplot_test.eps")
+
+# convert to png
+cmd <- 
+  "gs -dSAFER -dBATCH -dNOPAUSE -dEPSCrop -sDEVICE=png16m -r600 -sOutputFile=randu.png randu.eps"
+system(cmd)
[…]

### 2021-08-11 Scripts/Analysis2_competitiondirection/PGLSdirectionSelection.R

@@ -542,142 +542,150 @@ for(a in 1:length(traitToStudy)){
 #1) create layout + matrix for all plots
 
 #finish the plot part:write for overlap + adjust axis and color + add regression
-pdf("Plots/selectionGradientPGLS.pdf", height=25, width=18)
-
-layout(mat=cbind(seq(from=1, to=length(traitToStudy), by=2), seq(from=2, to=length(traitToStudy)+1, by=2)),
-       widths=c(5,5), heights=rep(5, times=length(traitToStudy)))
+pdf("Plots/selectionGradientPGLS.pdf", height=40, width=18)
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+layout(mat=cbind(seq(from=1, to=(length(traitToStudy)-1)*2, by=2), seq(from=2, to=(length(traitToStudy)-1)*2+1, by=2)),
+       widths=c(5,5), heights=rep(5, times=(length(traitToStudy)-1)))
 par(mar=c(3.5, 3.5, 1, 1), mgp=c(2.5, 0.5, 0), xpd=TRUE, cex=1.2)
 
+countLabel=0
 for(i in 1:length(traitToStudy)){ 
-  
-  #Matching the brain trait to the dataset with predictors
-  dataRangePrimate$Trait <- summaryData[match(dataRangePrimate$Species,summaryData$SpeciesForPhylogeny), which(colnames(summaryData)==traitToStudy[i])]
-  dataRangePrimate_rdc <- dataRangePrimate[!is.na(dataRangePrimate[,2])&!is.na(dataRangePrimate[,3])&!is.na(dataRangePrimate[,4]),]
-  rownames(dataRangePrimate_rdc) <- dataRangePrimate_rdc$Species
-  
-  #Readjust phylo tree
-  phyloConsensus <- drop.tip(phylo,
-                             phylo$tip.label[
-                               which(phylo$tip.label
-                                     %nin%dataRangePrimate_rdc$Species)])
-  
-  # #Create data for phylogenetic regression
-  # comp_data <- comparative.data(phy = phyloConsensus, data= dataRangePrimate_rdc,
-  #                               names.col = Species, vcv = TRUE)
-  # 
[…]

### 2021-08-11 Scripts/Analysis2_competitiondirection/SpatialProcessingSympatry.R

@@ -47,8 +47,8 @@ library(cleangeo) #to clean it otherwise issues with intersection
 #diet table
 resultsDiet <- matrix(NA, ncol=90, nrow=nrow(summaryData))
 
-frugivoryThresholdVector <- seq(from=10, to=30, by=10)
-folivoryThresholdVector <- seq(from=50, to=70, by=10)
+frugivoryThresholdVector <- seq(from=20, to=40, by=20)
+folivoryThresholdVector <- seq(from=40, to=60, by=20)
 
 for(a in 1:length(frugivoryThresholdVector)){
   

### 2021-08-11 Scripts/Analysis3_diversification/PGLSdiversification_bayesian.R

@@ -369,7 +369,7 @@ dataRangePrimate <- dataRangePrimate[-grep("Homo", dataRangePrimate$Species), ]
 
 ##----
 ## Run analysis for each trait
-
+set.seed(26)
 traitToStudy=c("EQ.log", "ratioBrain", "ratioHippocampus.log", "ratioNeocortex.log", "ratioCerebellum.log", "ratioStriatum.log", "ratioMOB.log")
 traitName=c("EQ (log)", "Brain (/bodymass, log)", "Hippocampus (/bodymass, log)", "Neocortex (/bodymass, log)", "Cerebellum (/bodymass, log)", "Striatum (/bodymass, log)", "MOB (/bodymass, log)")
 vifVector <- rep(NA, times=length(traitName))  
@@ -504,104 +504,108 @@ save.image("REnvironments/PGLSdiversification.RData")
 #finish the plot part:write for overlap + adjust axis and color + add regression
 pdf("Plots/diversificationPGLS.pdf", height=25, width=18)
 
-numberPlots = ifelse(length(traitToStudy)/2==floor(length(traitToStudy)/2), length(traitToStudy), length(traitToStudy) + 1)#if odd number, readjust
+numberPlots = ifelse((length(traitToStudy)-1)/2==floor((length(traitToStudy)-1)/2), (length(traitToStudy)-1), (length(traitToStudy)-1) + 1)#if odd number, readjust
 
 layout(mat=matrix(1:numberPlots, ncol=2),
-       widths=c(5,5), heights=rep(5, times=length(traitToStudy)))
+       widths=c(5,5), heights=rep(5, times=numberPlots/2))
 par(mar=c(3.5, 3.5, 1, 1), mgp=c(2.5, 0.5, 0), xpd=TRUE, cex=1.2)
 
+countLabel=0
 for(i in 1:length(traitToStudy)){ 
-  
-  #Matching the brain trait to the dataset with predictors
-  dataRangePrimate$Trait <- summaryData[match(dataRangePrimate$Species,summaryData$SpeciesForPhylogeny), which(colnames(summaryData)==traitToStudy[i])]
-  dataRangePrimate$Diversification_rate <-  summaryData$Diversification_rate[match(dataRangePrimate$Species,summaryData$SpeciesForPhylogeny)]
[…]

### 2021-08-19 Article/Article.Rmd
Update following benoit's correction + putting right frugivory threshold + filtering frugivorous correctly + adding sympatry vs diversification

@@
 header-includes:
+  - \usepackage{lettrine}
 # - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
@@
 
+<!-- ------------------------------------------------------------------- -->
+<!-- ---------------------      LAYOUT       --------------------------- -->
+<!-- ------------------------------------------------------------------- -->
+
+<!-- TO PUT THE LETTRINE -->
+
+\newcommand{\initial}[1]{%
+	\lettrine[lraise=0, loversize=0.5,nindent=0em]{
+		\color{black}
+     		{\textsc{#1}}}{}}
+
+<!-- TO CREATE GRAY BOX -->
+
+\newtcolorbox{graybox}{
+  colback=lightgray!25,
+  colframe=lightgray!25,
+  coltext=black,
+  boxsep=3pt,
+  arc=0pt}
+
+<!-- ------------------------------------------------------------------- -->
+<!-- ------------------------------------------------------------------- -->
+<!-- ------------------------------------------------------------------- -->
+
 ```{r setup, include=FALSE, echo=FALSE, message=FALSE}
@@
 ```
+
+<!-- TC:ignore -->
 
@@
 load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/PGLSdirectionSelection.RData")
-
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/PGLSdiversificationAndSympatry.RData")
 ```
@@
 \captionsetup{list=no}
-
-<!-- The front page -->
-<!-- \centering -->
-<!-- \raggedright -->
-<!-- \newpage -->
-<!-- \tableofcontents -->
 \newpage
@@
 
-\newtcolorbox{graybox}{
-  colback=lightgray!25,
-  colframe=lightgray!25,
-  coltext=black,
-  boxsep=3pt,
-  arc=0pt}
-
 :::: {.graybox data-latex=""}
 
-**Abstract |** In hypotheses related to the evolution of animal intelligence, a particular emphasis was given to the role of intra-species conspecifics.
-Yet, one species rarely occupies an area alone: Space is a place shared between many species.
-These latter can be new competitors to outperform or cooperators to decode and maneuver, thereby stimulating cognition.
-They can also contribute to modifying and depleting the environment such as it overly increases its complexity, thereby alleviating the benefice of cognition.
-Considering brain size as a proxy for cognition, we used primates as a study example to test for the intertwine between species co-occurrence and cognition.
+**Abstract |** Hypotheses related to animal intelligence evolution highlight the role of intra-species conspecifics.
+Yet, one species rarely occupies an area alone: Space is a place often occupied by many species, sometimes belonging to the same ecological guild.
+These species can act as competitors to outperform or cooperators to decode and maneuver, thereby stimulating cognition.
+They can also contribute to modifying and depleting the environment such as it overly increases depletion intensity and makes it poorly predictable, thereby alleviating the benefice of cognition.
+Considering brain size as a proxy for cognition, we used primates as a study example to test for the intertwine between species sympatry and cognition.
 We retraced the evolutionary history of several brain areas considering competitive or non-competitive evolutionary scenarios.
-We found that competitive evolutionary scenarios best predicted the evolution of some brain areas that were related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
+We found that competitive evolutionary scenarios best predicted the evolution of brain areas related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
 The whole brain size, as well as the size of areas used in more general contexts were not related to the sympatry rate.
-In any case, the evolutionary success of primate species was unrelated th the relative sizes of brain areas.
-Overall, this comparative study suggests that species co-occurrence contributes to shaping the selective pressure acting upon animal cognition, yet leaves open the question of the underlying ecological mechanisms at play.
+In any case, the evolutionary success of primate species was unrelated to the relative sizes of brain areas but was affected by sympatry.
+Overall, this comparative study suggests that species sympatry, which likely convolutes the environment, contributes to shaping the selective pressure acting upon primate cognition and diversification.
 
@@
 
-\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Diversification - Intelligence evolution - Primates - Species co-occurrence
-
-<!-- TC:ignore -->
-\faInfoCircle  \hspace{0.01in} **Word Count (main text only):** `r words$num_words` \newline
+\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Intelligence evolution - Primates - Sympatry
+
+\faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline
 <!-- Character Count: `r words$num_char` -->
-<!-- TC:endignore -->
 
@@
 
+<!-- TC:endignore -->
+
 # Introduction
 
-On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
+<!-- On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
 Overall, the evolution of the brain is the consequence of constraints (e.g.
 energetic limitations, @navarrete2011energetics), but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
-Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
-Their cognition can result from interactions of individuals with conspecifics within the social unit (*Social Intelligence Hypothesis*, @byrne1994machiavellian; @dunbar2017there), among generations (*Cultural Intelligence Hypothesis*, @whiten2007evolution; @reader2002social, also known as the *Vygotskian Intelligence Hypothesis* in humans, @herrmann2007humans; @tomasello2009cultural; @wilson1991molecular; @van2011social), between social units (*Napoleonic Intelligence Hypothesis*, @ashton2020interactions), or with the rest of their environment (*Ecological Intelligence Hypothesis*; @clutton1980primates; @milton1981distribution; @rosati2017foraging).
-
-|   A particular emphasis was given to the role of intra-species conspecifics in shaping animals cognitive abilities.
-Yet, space is a place shared between a plethora of species that can interact directly or indirectly, in particular if sharing some ecological traits, especially diet [@drury2018contrasting].
-To settle to new coral reefs, fishes use pops and clicks of other fishes as an honest signal for resourcefulness there [@gordon2019acoustic], mangabeys follow calls from hornbills to locate fruiting trees [@olupot1998fruit], and interactions even happen across kingdoms, with migratory birds interpreting phenological cues as synonymous of insect availability [@mcgrath2009flower].
+-->
+<!-- Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
+-->
+
+\initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
+Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
 
@@
 Although generally considered as a singular entity, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
-For instance, the Striatum is stimulated during social interaction [@baez2013role].
-Therefore, its size is expected to be positively influenced when contacts with other species increase, for instance in species performing mixed-species groups (e.g.
-in callhitrichine primates, @heymann2015unlike).
-Conversely, the evolution of the Main Olfactory Bulb (MOB), allowing processing olfactory cues, or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], should be linked to environmental complexity faced by a species, in particular when foraging.
-This environmental complexity can increase if space is shared with species with similar dietary habits because it contributes to impoverishing the environment and increasing its unpredictability, thus looping on selective pressure towards cognitive abilities [@grove2013evolution: @robirainreview].
-Given high energetic costs of the brain [@raichle2006brain], it is thus expected that sympatry should induce positive selection on the size of brain areas involved in foraging-related information processing, unless the induced environmental complexity starts being too high for cognitive foraging to be adaptive.
-Given that the Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating], the same scenario might apply as well to the Striatum of species that do not live in mixed-groups, which actually constitute the majority of the primate lineage.
+For instance, the Striatum is stimulated during social interactions [@baez2013role].
+Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, a rare  fact in primates nonetheless (e.g.
+in callitrichine primates, @heymann2015unlike).
+The Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
+Foraging-related areas, as are also the Main Olfactory Bulb (MOB) or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], are expected to be influenced by the ecological environment.
+Fruits being the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany], this might be particularly relevant for frugivorous primates.
+The changes induced by other species with similar dietary habits can contribute to increasing its unpredictability, thus changing the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
+Due to the cost of maintaining the brain functional [@raichle2006brain], it expected that the increase in environmental unpredictable only stimulates cognition up to a certain threshold (i;e.
+positive selection for bigger brain), before it is such high that smaller brain sizes are more adaptive.
 In between, more generalist areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
 
-|    Recent tools have been developed to infer the effect of species interactions on trait evolution, either by modelling trait divergence in co-occurring species from a same guild (e.g.
-dietary guild; Matching Competition: MC models) or considering that the evolutionary rate depends on the number of co-occurring lineages within the guild (density dependence; linear: DD$_{lin}$ or exponential: DD$_{exp}$; @drury2016estimating).
-After reconstructing primate biogeography history (N$_{species}$ = `r minRange`, @matzke2013probabilistic; @matzke2016stochastic) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); @kamilar2009environmental) and diet evolution (N$_species$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; @bollback2006simmap), we calculated the likelihoods of models considering the role of species interactions (including competitive scenarios) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy, N$_{species}$ = `r minEQ` to `r maxEQ`), or the relative size of specific brain areas associated with foraging-related information perception, processing or retention (Figure.
-\@ref(fig:figbrain); N$_{species}$ = `r minAllAreas` to `r max(maxNeocortex,maxHippocampus,maxCerebellum,maxStriatum,maxMOB)`).
-The use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in @deaner2000comparative).
-We also estimated the likelihoods of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
+|    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primate as study example.
+To infer the effect of species interactions on brain size evolution within the frugivorous primates, we evaluated the support for competitive or non-competitive evolutionary scenarios in the context of sympatry and investigated the directionality of the selection upon brain size evolution in the context of sympatry.
+Finally, we tested for correlative pattern of the evolutionary success in primates with brain size and current sympatry context.
+
+# Results
+
+```{r calculationValueForFirstResults}
+#Import data
+summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
+
+summaryDataForPlot <- summaryDataForPlot[!is.na(summaryDataForPlot$geographicCode),]
+# summaryDataForPlot <- summaryDataForPlot[summaryDataForPlot$DietaryGuild=="Fruit",]
+
+summaryDataForPlot$Family <- Data_powell2$MSW05_Family[match(summaryDataForPlot$Species_abbrv,Data_powell2$Species_abbrv)]#summaryData$Family[match(summaryDataForPlot$Species_abbrv, summaryData$Species_abbrv)]
+
+summaryDataForPlot[is.na(summaryDataForPlot$Family ),c(1,2,3)]
+#summaryDataForPlot$SpeciesForPhylogeny[which(is.na(summaryDataForPlot$Family))]
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Galagoides_demi"]<-"Galagonidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Macaca_munz"]<-"Cercopithecidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Microcebus_mitt"]<-"Cheirogaleidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Mirza_zaza"]<-"Lorisidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Nycticebus_java"]<-"Galagonidae"
+summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Tarsius_lari"]<-"Tarsiidae"
+
+lemuriformes.v <- 
+c(  
+"Daubentoniidae",
+"Lemuridae",
+"Indriidae",
+"Cheirogaleidae",
+"Lepilemuridae"
+)
+
+platyrrhini.v <- c(
+"Atelidae",   
+"Aotidae",
+"Pitheciidae",
+"Cebidae"
+)
+
+meanseMOBlemu <- round(c(
+  mean(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v &
+                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseMOBother <- round(c(
+  mean(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v &
+                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseStriatumplaty <- round(c(
+  mean(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v &
+                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+meanseStriatumother <- round(c(
+  mean(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v], 
+    na.rm=TRUE), 
+  sd(
+    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v],
+    na.rm=TRUE)/
+    sqrt(
+      length(
+        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v &
+                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
+), digit=2)
+
+# summaryDataForPlot[order(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+# summaryDataForPlot[order(summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+# summaryDataForPlot[order(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass, decreasing = TRUE),]
+
+```
+
+We gathered a large database on the whole brain size, the size of the Cerebellum and the Neocortex, involved in daily information processing and retention, and the Main Olfactory Bulb (MOB), the Striatum, and the Hippocampus, those three latter being related to social and foraging-related tasks, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
+It evidenced ample variations in brain size.
+For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (i.e.
+pondered by whole-body mass) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
+Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+
+|   We first reconstructed primate biogeography history (N$_{species}$ = `r minRange`, @matzke2013probabilistic; @matzke2016stochastic) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); @kamilar2009environmental) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; @bollback2006simmap).
+We then calculated the likelihoods of models considering the role of species interactions (matching competition MC models, @nuismer2015predicting; models of linear or exponential density dependence, DD$_{lin}$and  DD$_{exp}$, of the evolutionary rate on the number of sympatric lineages; @drury2016estimating see [Models of trait evolution: does interspecific interactions shape brain size evolution?]) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
+\@ref(fig:figbrain)) and compared their likelihood to those of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
 stabilizing selection; see @blomberg2020beyond for a review) or the Early-Burst model (EB, @blomberg2003testing), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
@@
 
-# Results
-
-|   Non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
-By contrast, competitive models were most supported in areas involved in short-term working memory and long-term spatio-temporal information retention (Hippocampus, @burgess2002human) and in planning, reward assessment, and information processing during social interaction (Striatum, @baez2013role; @johnson2007integrating), while they tended to be so for one involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+|   We found that non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
+The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size and illustrates the trade-offs between costs and benefices of brain development [@isler2009expensive].
+By contrast, competitive models were most supported in areas involved in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, @burgess2002human) or planning abilities and reward assessment (Striatum, @baez2013role; @johnson2007integrating), while they tended to be so for one involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
 When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and the Striatum, but a slowdown for the MOB.
@@
 
-|   Next, to understand the directionality of the selection gradient shaped by co-occurrence (i.e.
-selection for “bigger” or “smaller” brain if the more species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
+|   Next, to understand the directionality of the selection gradient shaped by sympatry (i.e.
+selection for “bigger” or “smaller” brain the more species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
 For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates.
+We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates based on IUCN date [@IUCN].
 On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
 That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
-In term of distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
+In terms of distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
 The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas for which the evolutionary history was better described with competitive models: The Hippocampus, the MOB and the Striatum (Hippocampus: $t$`r testGradientHippocampus`;  MOB: $t$`r testGradientMOB`; Striatum: $t$`r testGradientStriatum`).
-The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`;  MOB: `r estimateGradientMOB`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogeny variability (Table \@ref(tab:tabledfsensitivity)).
-Thus, it suggests that sympatric species are either subject to a positive selection for smaller brain, or to a less stringent selection on advanced cognitive abilities.
+Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with competitive models: The Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
+The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
+Thus, it suggests that sympatric species are either subject to a positive selection towards smaller brain, or to a less intense selection for advanced cognitive abilities compared with isolated species.
 
@@
 
-|   Finally, we investigated the evolutionary consequences of brain evolution by evaluating whether brain sizes correlated with species diversification rates (i.e.
+|   In addition, we investigated the evolutionary consequences of brain evolution by evaluating whether brain sizes correlated with species diversification rates (i.e.
 speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
 Overall, species diversification, estimated based on molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
-When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification); see robustness in Table \@ref(tab:tabledfsensitivity2)).
+When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
+Given the context dependence of the direction of selection (towards bigger sizes in the absence of other species, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by inter-species sympatry.
+Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to inter-species sympatry too.
+This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
+The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetic signals (Figure \@ref(fig:figRegressionDiversification)).
+In fact, a sudden encephalisation in primates is clearly associated to a limited number of close-related species [@decasien2017primate; @melchionna2020macroevolutionary].
+This clearly limits the statistical power of our phylogenetically corrected analyses as we cannot decipher whether the connivance between brain size and evolutionary success results from a true biological link or appeared by chance.
+A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
+This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in @melchionna2020macroevolutionary remains a likely possibility.
+Finally, despite diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
+In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
+In other words, the higher the number of sympatric species, the lower the diversification, an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
 
 # Discussion
-
-```{r calculationValueDiscussion}
-#Import data
-summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
-
-summaryDataForPlot <- summaryDataForPlot[!is.na(summaryDataForPlot$geographicCode),]
-# summaryDataForPlot <- summaryDataForPlot[summaryDataForPlot$DietaryGuild=="Fruit",]
-
-summaryDataForPlot$Family <- Data_powell2$MSW05_Family[match(summaryDataForPlot$Species_abbrv,Data_powell2$Species_abbrv)]#summaryData$Family[match(summaryDataForPlot$Species_abbrv, summaryData$Species_abbrv)]
-
-summaryDataForPlot[is.na(summaryDataForPlot$Family ),c(1,2,3)]
-#summaryDataForPlot$SpeciesForPhylogeny[which(is.na(summaryDataForPlot$Family))]
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Galagoides_demi"]<-"Galagonidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Macaca_munz"]<-"Cercopithecidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Microcebus_mitt"]<-"Cheirogaleidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Mirza_zaza"]<-"Lorisidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Nycticebus_java"]<-"Galagonidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Tarsius_lari"]<-"Tarsiidae"
-
-lemuriformes.v <- 
-c(  
-"Daubentoniidae",
-"Lemuridae",
-"Indriidae",
-"Cheirogaleidae",
-"Lepilemuridae"
-)
-
-platyrrhini.v <- c(
-"Atelidae",   
-"Aotidae",
-"Pitheciidae",
-"Cebidae"
-)
-
-meanseMOBlemu <- round(c(
-  mean(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v &
-                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseMOBother <- round(c(
-  mean(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v &
-                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseStriatumplaty <- round(c(
-  mean(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v &
-                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseStriatumother <- round(c(
-  mean(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v &
-                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-# summaryDataForPlot[order(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-# summaryDataForPlot[order(summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-# summaryDataForPlot[order(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-
-```
 
@@
 This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ) were best described by the Orstein-Uhlenbeck process, what might suggest a stabilisation towards an optimal size as a result of an equilibrium between costs and benefices.
-As the brain area is regionally specialised [@barton2000mosaic], it was also expected that brain regions could be under different selective pressures.
-For instance, the Lemuriformes, that are known to prioritize smell compared to other primate species, indeed have the largest relative MOB size (i.e.
-pondered by body size) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-Similarly, Platyrrhini, and Callitrichine in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
-Here, we show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species co-occurrence, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB.
-These areas imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates.
-This supports the general discussion on the importance of social *vs* ecological factors to explain primate cognition evolution and diversity [@decasien2017primate; @powell2017re].
-
-|   The relative size of these brain areas were negatively associated with one index of sympatry intensity, the average overlap of a species distribution range with that of other species.
-Because the ratio of the other brain areas is insensitive to sympatry intensity, it is unlikely that this results from a by-product of a selection on body mass and might thus be a consequence of species direct or indirect interactions.
+As the brain area is regionally specialised [@barton2000mosaic], brain regions could be under different selective pressures as suggested by the differences we highlighted in some brain areas (e.g.
+MOB or Striatum) across different primate genus.
+Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB.
+These areas imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
+Overall, the relative size of foraging-related brain areas were negatively associated with one index of sympatry intensity (the range overlap with other species) and might thus be a consequence of species direct or indirect interactions.
 In general, competition is the first-thought mechanism to describe community structures [e.g.
@@
 That would explain a relaxed positive selection for advance cognitive abilities, and conversely, given the cost of brain maintenance [@raichle2006brain], would induce a negative selection towards areas involved in foraging related activities like the Hippocampus, the MOB and the Striatum.
-
-|   Given the context dependence of the direction of selection (towards bigger sizes in the absence of other species, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by inter-species sympatry.
-Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to inter-species sympatry too.
-This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
-The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetical signals (Figure \@ref(fig:figRegressionDiversification)).
-In fact, a sudden encephalisation in primates is clearly associated to a limited number of close-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically corrected analyses and might thus explain why we did not observe evidence of connivance between brain size and evolutionary success.
-A positive association between brain size and bigger brain was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
-This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in @melchionna2020macroevolutionary remains a likely possibility.
-
-# Conclusion
-
-In conclusion, the use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond).
+Not only was brain evolution affected by sympatry, but sympatry (the maximum number of co-occurring species only) induced a slowdown in diversification, which contrasts with the picture offered by passerine birds at finer resolution [@kennedy2017historical].
+Density-dependence within clade is a known factor to affect negatively diversification rate [@moen2014does].
+In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
+Given the large resolution and low overlap threshold to consider sympatry considered here (i.e.
+overlap of `r geographicThresholdVector[1]*100`% of the distribution area), this competitive view fits the observed influence of sympatry on frugivorous primate diversification.
+
+|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond).
 The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
@@
 To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
+As such, the use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in @deaner2000comparative).
 Percentage of frugivory and/or folivory was obtained based on freely available dataset from @decasien2017primate and @powell2017re for the frugivory and folivory rate, or @willems2013collective for the folivory rate.
@@
 
-## Primate species co-occurrence
+## Primate species sympatry
 
@@
 
-We focused on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic models of EQ - or relative size of a specific brain area – evolution with and without species competitions.
+We focused only on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic models of EQ - or relative size of a specific brain area – evolution with and without species competitions.
 Models were fitted on different sample sizes due to non-availability of some data for some traits.
@@
 EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species co-occurrence]) and of diet (see [Dietary guild]), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These competitive models notably account for interaction matrices that are built on the evolutionary history of species co-occurrence and diet.
+Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+These competitive models notably account for interaction matrices that are built on the evolutionary history of species sympatry and diet.
 These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see @drury2016estimating).
@@
 
-$f_{lin}(\lambda)=\lambda_{0}(1 + r)$
+$f_{lin}(\lambda)=\lambda_{0} + rl$
 
@@
 Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
-In addition, this study is based on several arbitrary thresholds, namely (i) to assess species co-occurrence (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
+In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
 To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
-equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory and geographic co-occurrence, and (3) various biogeography and dietary evolutionary history reconstructions.
+equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory and geographic sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
 
 |   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
-We stopped computations when the calculation of the likelihood was excessively long.
+We stopped computations when the calculation of the likelihood was excessively long (> 1 week).
 The final sample size thus was of `r min(totModelsWorked[-2])*10` models.
@@
 constant ratio between extinction and speciation rates).
-This Bayesian approach considers speciation rate heterogeneity by modeling small shifts in this rate at speciation events.
+This Bayesian approach considers speciation rate heterogeneity by modeling small shifts in the rate at speciation events.
 In other words, the daughter lineage is assumed to inherit new speciation rates that is sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the parental speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
@@
 |   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
-@estrada2017impending estimated that, given current knowledge, the primate lineage should be composed of 504 species.
+@estrada2017impending estimated that, given current knowledge, the primate clade should be composed of 504 species.
 This means that the current sampling fraction is around 73%.
@@
 
-To determine the nature of the relationship between species co-occurrence and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
+To determine the nature of the relationship between species sympatry and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
 a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients but its diagonal multiplied by lambda) for each brain region individually and for frugivorous species only.
@@
 
-|    The response variable was the relative size of areas shown as better described by competitive phylogenetic scenario (see above).
-Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see Model Robustness).
+|    The response variable was the relative size of brain areas shown as better described by competitive phylogenetic scenario (see above).
+Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability and assumption]).
 In this model, the covariates (i.e.
-continuous predictors) were the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species (both were square rooted, to reach symmetrical distribution).
+continuous predictors) were the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square rooted, to reach symmetrical distribution).
 For a given species A, sympatry with another species B was considered when species B range overlapped on more than 10% of the range of species A.
@@
 
-(b)	Diversification analysis
+(b)	Diversification and brain size
 
@@
 
-(c)	Model implementation
+(c) Diversification and sympatry
+
+To determine whether sympatry was associated to specific diversification pattern (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
+
+\hfill
+
+(d)	Model implementation
 
@@
 Other function parameters were set to default.
-Prior fitting, the covariates were square-rooted to reach more symmetrical distribution.
+Prior fitting, covariates were symmetrized if necessary.
 Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
@@
 
-(ii)	Diversification analysis
+(ii)	Diversification and brain size
 
@@
 
-We could not compute phylogenetic regressions to link diversification and brain traits using a frequentist approach because it led to violation of homoscedasticity.
+We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist approach because it led to violation of homoscedasticity.
 Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
@@
 $P(\beta<0|\hat{\beta}>0)$).
+
+\hfill
+
+(iii) Diversification and sympatry
+
+We fitted phylogenetic regression as explained in (i).
+In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability and assumption]).
 
@@
 
-<!-- TC:endignore -->
-
 \newpage
@@
 rownames(results.df_diversification) <- NULL
-knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the diversification pattern | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between diversification and brain size | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
 samp.=Effective sample (adjusted for autocorrelation).
@@
   #kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\newpage
+
+```{r tableRegDiversificationAndSympatry, include=TRUE}
+knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,
+             caption = "Model estimates and significance of phylogenetic regressions to assess the correlation between diversification and sympatry | Est.=Estimate, CI2.5%=Lower border of the CI95%, CI97.5%=Upper border of the CI95%, Sd= Standard deviation, t= Statitsitics t-vale.
+The brain area (as well as the associated sample size)
+             are indicate prior each list of estimates. the transformation (logarithm or square-root) if indicated in parenthese by the abbreviation (log or sqrt).") %>%
+  kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down")
+
 ```
@@
 
-```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Current frugivorous primate co-occurrence pattern and phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
+```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Current frugivorous primate sympatry pattern and phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
 The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
@@
 
-```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="AICc weights of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
+```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="Relative support of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
 The points represent the average AICc weight obtained (when considering the six models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does interspecific interactions shape brain size evolution?])."}
@@
 \newpage
-
-```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
-The grey background depicts the standard deviation.
-The two breakpoints, depicted by the plain dots and the vertical dotted bars, were thus estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
-The three fitted regressions are displayed by the dashed lines.
-The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the the Bayesian Information Criterion.
-The identified breakpoints coin with identified sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
-
-##Plot diversification in function of time
-xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
-xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
-ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
-ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
-
-plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
-     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
-     las=1, type="n", tcl=-0.25, bty="n",
-     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
-     xpd=TRUE)
-
-#Add grid
-addGrid(
-  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
-  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
-  axisPlot=TRUE, round=TRUE, digit=c(2,2))
-axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
-
-#Add background se
-polygon(
-  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
-  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
-  col=grey(level=0.5, alpha=0.15),
-  border=NA
-)
-
-#Add mean
-lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
-
-library(strucchange)
-## confidence interval
-colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
-
-yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
-ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
-
-# Rupture points and (CI too reduced to be plotted)
-points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
-# errorBars(location=c(yFirst), 
-#          meanPt=c(-dateFirstRupt[2]),
-#          barValue=c(0,0), refUnit=1, 
-#          minValue=-80, maxValue=80, 
-#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
-#          col="black", lty=1, 
-#          horiz=TRUE, symmetrical=FALSE)
-
-#Vertical bars
-segments(
-  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  y0=c(0,0),
-  y1=c(yFirst, ySecond),
-  lty=3
-)
-mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
-
-#three fitted regressions
-fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
-
-reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
-reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
-reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
-
-lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
-```
-
-<!-- TC:ignore -->
 
@@
 
+### Primate diversification rate over time
+
+\vspace{-2in}
+
+```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
+The grey background depicts the standard deviation.
+The two breakpoints, depicted by the plain dots and the vertical dotted bars, were thus estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
+The three fitted regressions are displayed by the dashed lines.
+The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the the Bayesian Information Criterion.
+The identified breakpoints coin with identified sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
+
+##Plot diversification in function of time
+xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
+xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
+ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
+ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
+
+plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
+     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
+     las=1, type="n", tcl=-0.25, bty="n",
+     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
+     xpd=TRUE)
+
+#Add grid
+addGrid(
+  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
+  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
+  axisPlot=TRUE, round=TRUE, digit=c(2,2))
+axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
+
+#Add background se
+polygon(
+  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
+  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
+  col=grey(level=0.5, alpha=0.15),
+  border=NA
+)
+
+#Add mean
+lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
+
+library(strucchange)
+## confidence interval
+colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
+
+yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
+ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
+
+# Rupture points and (CI too reduced to be plotted)
+points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
+# errorBars(location=c(yFirst), 
+#          meanPt=c(-dateFirstRupt[2]),
+#          barValue=c(0,0), refUnit=1, 
+#          minValue=-80, maxValue=80, 
+#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
+#          col="black", lty=1, 
+#          horiz=TRUE, symmetrical=FALSE)
+
+#Vertical bars
+segments(
+  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
+  y0=c(0,0),
+  y1=c(yFirst, ySecond),
+  lty=3
+)
+mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
+
+#three fitted regressions
+fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
+
+reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
+reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
+reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
+
+lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
+lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
+```
+
+\newpage
+
 ## Phylogenetic regressions: results, stability and assumption
@@
 
-(b) Phylogenetic regressions: diversification
+(b) Phylogenetic regressions: diversification and brain size
 
@@
 \end{figure}
+```
+
+(b) Phylogenetic regressions: diversification and sympatry
+
+```{=latex}
+\begin{figure}
+\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf}
+\caption{\scriptsize{Phylogenetic regressions of diversification rate in function of sympatry intensity indices | Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the distribution range overlapped by sympatric species is averaged, while the right graphics do the opposite.
+Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent gray background.}}\label{fig:figRegressionDiversificationSympatry}
+\end{figure}
+```
+\newpage
+
+(d) Forest plot of estimates
+
+```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap="Forest plot of the phylogenetic regressions | CI: Confindence interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible as reduced).
+Plain dots depict negative effects, open dots depict positive effect.
+"}
+
+source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
+par(mar=c(8, 8, 0.5, 2), mgp=c(2.5, 0.5, 0), xpd=TRUE)
+
+emptyPlot(xlim=c(-3,3), ylim=c(-3,3), asp=1)
+#Grid
+addGrid(
+  cexAxisX=1.15, cexAxisY=1.15,
+  xmin=-3, xmax=3, xintsmall=0.1, xintbig=0.5,
+  ymin=-3, ymax=3, yintsmall=0.1, yintbig=0.5,
+  axisPlot=FALSE, round=TRUE, digit=c(2,2), contour=TRUE)
+
+#0 line
+segments(x0=0, x1=0, y0=-3, y1=3, lty=2)
+
+#Xaxis
+axis(side=1, at=seq(-3, 3, 0.5), pos=-3, labels=seq(-3, 3, 0.5), las=1, tcl=-0.25)
+mtext(side=1, at=0, line=1, text="Model estimate (point) and 95% CI/HDP (segment)")
+
+#yAxis
+axis(side=2, at=c(2, 0, -2), pos=-3, labels=c("Overlap (%)", "N sympatric\nspecies", "Relative\nbrain size"), las=1, tcl=-0.25)
+mtext(side=2, at=0, line=6, text="PARAMETER", font=2)
+
+#Add the different values
+
+#Analysis of brain size and sympatry
+traitName_rdc=c("EQ (log)", #"Brain (/bodymass, log)",
+                "Striatum (/bodymass, log)",
+                "MOB (/bodymass, log)",
+                "Hippocampus (/bodymass, log)",
+                "Neocortex (/bodymass, log)", 
+                "Cerebellum (/bodymass, log)",
+                "DiversificationAndSympatry"
+)
+
+traitName_legend <- c("EQ", "Striatum", "MOB", "Hippocampus", "Neocortex", "Cerebellum", "Diversification")
+library(RColorBrewer)
+colourModelsReg <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5], "black")
+
+for(a in 1:length(traitName_rdc)){
+
+  if(a!=length(traitName_rdc)){
+    model <- get(paste("modelBrain", traitName_rdc[a], sep="_"))
+  }else{
+    model <- get(paste("modelBrain", traitName_rdc[a], sep=""))
+  }
+
+  #Overlap
+  errorBars(location=2.5-(a-1)*1/length(traitName_rdc), 
+            meanPt=cbind(model$bootmean, t(model$bootconfint95))[2,1], 
+            barValue=1, 
+            refUnit=0.75, 
+            minValue=-3, 
+            maxValue=3, 
+            upperBarValue=cbind(model$bootmean, t(model$bootconfint95))[2,2], 
+            lowerBarValue=cbind(model$bootmean, t(model$bootconfint95))[2,3], 
+            col=colourModelsReg[a], 
+            lty=1, 
+            horiz=TRUE, 
+            symmetrical=FALSE)
+  points(x=cbind(model$bootmean, t(model$bootconfint95))[2,1], y=2.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[2,1]>0,21,19), bg="white", col=colourModelsReg[a])
+  if(a!=length(traitName_rdc)){
+    text(x=cbind(model$bootmean, t(model$bootconfint95))[2,3], y=2.5-(a-1)*1/length(traitName_rdc),
+       pos=4, col=colourModelsReg[a],
+       labels=pvalueToText(as.numcharac(results.df_gradient[5*(a-1)+3,7])), cex=0.75)
+  }else{
+    text(x=cbind(model$bootmean, t(model$bootconfint95))[2,3], y=2.5-(a-1)*1/length(traitName_rdc),
+         pos=4, col=colourModelsReg[a],
+         labels=pvalueToText(as.numcharac(results.df_diversificationAndSympatry[3,7])), cex=0.75)
+  }
+
+  #N species
+  errorBars(location=0.5-(a-1)*1/length(traitName_rdc), 
+            meanPt=cbind(model$bootmean, t(model$bootconfint95))[3,1], 
+            barValue=1, 
+            refUnit=0.75, 
+            minValue=-3, 
+            maxValue=3, 
+            upperBarValue=cbind(model$bootmean, t(model$bootconfint95))[3,2], 
+            lowerBarValue=cbind(model$bootmean, t(model$bootconfint95))[3,3], 
+            col=colourModelsReg[a], 
+            lty=1, 
+            horiz=TRUE, 
+            symmetrical=FALSE)
+  points(x=cbind(model$bootmean, t(model$bootconfint95))[3,1], y=0.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[3,1]>0,21,19), , bg="white", col=colourModelsReg[a])
+  if(a!=length(traitName_rdc)){
+    text(x=cbind(model$bootmean, t(model$bootconfint95))[3,3], y=0.5-(a-1)*1/length(traitName_rdc),
+       pos=4, col=colourModelsReg[a],
+       labels=pvalueToText(as.numcharac(results.df_gradient[5*(a-1)+4,7])), cex=0.75)
+  }else{
+    text(x=cbind(model$bootmean, t(model$bootconfint95))[3,3], y=0.5-(a-1)*1/length(traitName_rdc),
+         pos=4, col=colourModelsReg[a],
+         labels=pvalueToText(as.numcharac(results.df_diversificationAndSympatry[4,7])), cex=0.75)
+  }
+
+  #Analysis of diversification and brain size
+  if(a!=length(traitName_rdc)){
+    model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
+
+    errorBars(location=-1.5-(a-1)*1/(length(traitName_rdc)-1), 
+              meanPt=as.data.frame(summary(model)$solutions[,1:3])[2,1], 
+              barValue=1, 
+              refUnit=0.75, 
+              minValue=-3, 
+              maxValue=3, 
+              upperBarValue=as.data.frame(summary(model)$solutions[,1:3])[2,2], 
+              lowerBarValue=as.data.frame(summary(model)$solutions[,1:3])[2,3], 
+              col=colourModelsReg[a], 
+              lty=1, 
+              horiz=TRUE, 
+              symmetrical=FALSE)
+    points(x=as.data.frame(summary(model)$solutions[,1:3])[2,1], y=-1.5-(a-1)*1/(length(traitName_rdc)-1), pch=ifelse(as.data.frame(summary(model)$solutions[,1:3])[2,1]>0,21,19), , bg="white", col=colourModelsReg[a])
+    text(x=as.data.frame(summary(model)$solutions[,1:3])[2,3], y=-1.5-(a-1)*1/(length(traitName_rdc)-1),
+         pos=4, col=colourModelsReg[a],
+         labels=pvalueToText(as.numcharac(results.df_diversification[4*(a-1)+3,5])), cex=0.75)
+
+  }
+}
+
+legend(x=3, y=0.5, 
+       pch=c(19,21), 
+       bg=c("white", "white"),
+       col=c("black", "black"),
+       legend=c("> 0", "< 0"),
+       #title="Output:",
+       bty="n", 
+       xjust=1,
+       xpd=TRUE)
+
+legend(x=-3.25, y=-4, 
+       pch=rep(19, times=length(traitName_rdc)), 
+       col=c(colourModelsReg),
+       legend=traitName_legend,
+       #title="Output:",
+       ncol=3,
+       bty="n", 
+       xpd=TRUE)
+
 ```
@@
 knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between speies co-occurrence and relative brain sizes | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between speies sympatry and relative brain sizes | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 
+(b) Phylogenetic regressions: diversification and sympatry
+
+```{r tabledfsensitivity3, include=TRUE}
+knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the selection diversificationAndSympatry direction | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data)") %>%
+  kableExtra::kable_styling(latex_options = "striped") %>%
+  kableExtra::kable_styling(latex_options="scale_down") %>%
+  kableExtra::add_header_above(c("Model:" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction"))
+
+```
+
+\newpage
 ### Model assumptions
@@
 
-```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
+```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Brain size and sympatry' | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
 for(a in 1:length(traitName)){
@@
 
-(b) Phylogenetic regressions: diversification
-
-```{r modelAssumption2a, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Trace and density of posteriors"}
+(b) Phylogenetic regressions: diversification and brain size
+
+```{r modelAssumption2a, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Diversity and brain size' | Trace and density of posteriors"}
 for(a in 1:length(traitName)){
@@
 
-```{r modelAssumption2b, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=10, fig.cap="Q-Q plot of the posterior distribution and the expected Gaussian distribution"}
+```{r modelAssumption2b, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=10, fig.cap="Model assumption check 'Diversity and brain size' | Q-Q plot of the posterior distribution and the expected Gaussian distribution"}
 
@@
 
+(b) Phylogenetic regressions: diversification and sympatry
+
+```{r modelAssumption3, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Diversity and sympatry'| Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
+    model <- get(paste("modelBrainDiversificationAndSympatry", sep="_"))
+
+    diagnostics.plot(model)
+
+```
+
 <!-- TC:endignore -->

### 2021-08-19 Scripts/Analysis2_competitiondirection/PGLSdirectionSelection.R

@@ -397,6 +397,9 @@ dataRangePrimate$Bodymass <- summaryData$Bodymass[match(dataRangePrimate$Species
 dataRangePrimate$Bodymass.log <- log(dataRangePrimate$Bodymass)
 
 dataRangePrimate_rdc <- dataRangePrimate[!is.na(dataRangePrimate[,2])&!is.na(dataRangePrimate[,3])&!is.na(dataRangePrimate[,4]),]
+#keep only frugivorous
+dataRangePrimate_rdc$Diet <- summaryData$DietaryGuild[match(dataRangePrimate_rdc$Species,summaryData$SpeciesForPhylogeny)]
+dataRangePrimate_rdc <- dataRangePrimate_rdc[dataRangePrimate_rdc$Diet=="Fruit",]
 
 #Readjust phylo tree
 phyloConsensus <- drop.tip(phylo,
@@ -437,8 +440,8 @@ rownames(dataRangePrimate_rdc) <- dataRangePrimate_rdc$Species
 
 # plot(dataRangePrimate_rdc$Number_species_cooccurrence.sqrt, dataRangePrimate_rdc$Overlap_average.sqrt)
      
-modelBrain <- phylolm(formula = Trait ~ Overlap_average.sqrt + Number_species_cooccurrence.sqrt, 
-                       data=dataRangePrimate_rdc ,phy=phyloConsensus,model="lambda",measurement_error=FALSE,boot=repetitionBootstrap)
+modelBrain <- phylolm(formula = Trait ~ Overlap_average + Number_species_cooccurrence.sqrt, 
+                       data=dataRangePrimate_rdc ,phy=phyloConsensus,model="lambda", measurement_error=FALSE,boot=repetitionBootstrap)
 
 # modelBrain <- gls(Trait ~ Overlap_average.sqrt  correlation = corPagel(1, phyloConsensus, form = ~Species),
 #                   data = dataRangePrimate_rdc, method = "ML")
@@ -470,7 +473,7 @@ assign(paste("modelBrain", traitName[a], sep="_"), modelBrain)
 #assign(paste(modelBrainPgls, traitName[a], sep="_"), modelBrainPgls)
 
 #since only two variables
-cortest <- cor.test(dataRangePrimate_rdc$Number_species_cooccurrence.sqrt, dataRangePrimate_rdc$Overlap_average.sqrt)
[…]

### 2021-08-19 Scripts/Analysis3_diversification/PGLSdiversification_bayesian.R

@@ -392,6 +392,10 @@ for(a in 1:length(traitToStudy)){
   dataRangePrimate$Bodymass <-  summaryData$Bodymass[match(dataRangePrimate$Species,summaryData$SpeciesForPhylogeny)]
   dataRangePrimate_rdc <- dataRangePrimate[!is.na(dataRangePrimate[,4])&!is.na(dataRangePrimate[,5]),]
   
+  #keep only frugivorous
+  dataRangePrimate_rdc$Diet <- summaryData$DietaryGuild[match(dataRangePrimate_rdc$Species,summaryData$SpeciesForPhylogeny)]
+  dataRangePrimate_rdc <- dataRangePrimate_rdc[dataRangePrimate_rdc$Diet=="Fruit",]
+  
   #Readjust phylo tree
   phyloConsensus <- drop.tip(phylo,
                              phylo$tip.label[
@@ -421,7 +425,7 @@ for(a in 1:length(traitToStudy)){
   phyloConsensus <- force.ultrametric(tree=phyloConsensus, method="extend")#method="nnls")
   
   ##MCMC glmm
-  set.seed(a)
+  set.seed(a+100)
   
   library(MCMCglmm)
   
@@ -491,7 +495,7 @@ results.df[2:ncol(results.df)] <- replaceNAtable(results.df[2:ncol(results.df)],
 results.df <- results.df[, -6] #delete column that was created for frequentist and is useless
 results.df_diversification <- results.df
 
-save.image("REnvironments/PGLSdiversification.RData")
+save.image("REnvironments/PGLSdiversification1.RData")
 
 ##############
 ## PLOTTING RESULTS
@@ -519,6 +523,10 @@ for(i in 1:length(traitToStudy)){
     dataRangePrimate$Diversification_rate <-  summaryData$Diversification_rate[match(dataRangePrimate$Species,summaryData$SpeciesForPhylogeny)]
     dataRangePrimate_rdc <- dataRangePrimate[!is.na(dataRangePrimate[,4])&!is.na(dataRangePrimate[,5]),]
     
+    #keep only frugivorous
+    dataRangePrimate_rdc$Diet <- summaryData$DietaryGuild[match(dataRangePrimate_rdc$Species,summaryData$SpeciesForPhylogeny)]
+    dataRangePrimate_rdc <- dataRangePrimate_rdc[dataRangePrimate_rdc$Diet=="Fruit",]
+    
     #Readjust phylo tree
[…]

### 2021-09-23 Article/Article.Rmd
Update manuscript

@@
 
+# output: 
+#  #      - '--lua-filter=scholarly-metadata.lua'
+#  #      - '--lua-filter=author-info-blocks.lua'
+#  bookdown::pdf_book:
+#  #bookdown::word_document2:
+#    number_sections: false
+#    toc: false
+#    #citation_package: natbib
+#    latex_engine: pdflatex
+#    fig_caption: true
+#    pandoc_args:
+#      - '--lua-filter=scholarly-metadata.lua'
+#      - '--lua-filter=author-info-blocks.lua'
+# 
+# bibliography: bibliographyarticlepackage.bib
+# csl: nature.csl
+# #biblio-style: apa
+# always_allow_html: true
+# link-citations: yes
+
 output: 
@@
    toc: false
-   #citation_package: natbib
+   citation_package: biblatex
    latex_engine: pdflatex
@@
      - '--lua-filter=author-info-blocks.lua'
+always_allow_html: true
 
 bibliography: bibliographyarticlepackage.bib
-csl: nature.csl
-#biblio-style: apa
-always_allow_html: true
-link-citations: yes
+biblio-style: nature
+biblatexoptions: [natbib=true]
 
 urlcolor: blue
+filecolor: blue
+linkcolor: blue
 fontsize: 12pt
@@
 citeR(
-bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticle.bib",
+bibliographyArticle="T:/Saved_PhD/Library_general/libraryMdf.bib",
 bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticlepackage.bib",
@@
 
-**Abstract |** Hypotheses related to animal intelligence evolution highlight the role of intra-species conspecifics.
+**Abstract |** Hypotheses related to animal intelligence evolution highlight the role of conspecifics.
 Yet, one species rarely occupies an area alone: Space is a place often occupied by many species, sometimes belonging to the same ecological guild.
-These species can act as competitors to outperform or cooperators to decode and maneuver, thereby stimulating cognition.
-They can also contribute to modifying and depleting the environment such as it overly increases depletion intensity and makes it poorly predictable, thereby alleviating the benefice of cognition.
+These sympatric heterospecifics can act as competitors or (direct or indirect) cooperators, thereby stimulating cognition.
+They can also contribute to modifying and depleting the environment such as it makes it poorly predictable, thereby alleviating the benefice of cognition.
 Considering brain size as a proxy for cognition, we used primates as a study example to test for the intertwine between species sympatry and cognition.
@@
 We found that competitive evolutionary scenarios best predicted the evolution of brain areas related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
-The whole brain size, as well as the size of areas used in more general contexts were not related to the sympatry rate.
-In any case, the evolutionary success of primate species was unrelated to the relative sizes of brain areas but was affected by sympatry.
+The whole brain size, as well as the size of areas used in more general contexts were not related to the sympatry level.
+In any case, the evolutionary success of primate species was unrelated to the relative sizes of brain areas but was negatively affected by sympatry.
 Overall, this comparative study suggests that species sympatry, which likely convolutes the environment, contributes to shaping the selective pressure acting upon primate cognition and diversification.
@@
 For instance, the Striatum is stimulated during social interactions [@baez2013role].
-Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, a rare  fact in primates nonetheless (e.g.
-in callitrichine primates, @heymann2015unlike).
+Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is rather infrequent in primates nonetheless (but see callitrichine primates in particular, @heymann2015unlike).
 The Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
 Foraging-related areas, as are also the Main Olfactory Bulb (MOB) or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], are expected to be influenced by the ecological environment.
-Fruits being the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany], this might be particularly relevant for frugivorous primates.
+Such areas are tought to be particularly key for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany].
 The changes induced by other species with similar dietary habits can contribute to increasing its unpredictability, thus changing the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
-Due to the cost of maintaining the brain functional [@raichle2006brain], it expected that the increase in environmental unpredictable only stimulates cognition up to a certain threshold (i;e.
-positive selection for bigger brain), before it is such high that smaller brain sizes are more adaptive.
-In between, more generalist areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
+Due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
+positive selection for bigger brain), before smaller brain sizes become more adaptive.
+Conversely, more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
 
@@
 To infer the effect of species interactions on brain size evolution within the frugivorous primates, we evaluated the support for competitive or non-competitive evolutionary scenarios in the context of sympatry and investigated the directionality of the selection upon brain size evolution in the context of sympatry.
-Finally, we tested for correlative pattern of the evolutionary success in primates with brain size and current sympatry context.
+Finally, we tested for correlative pattern of the evolutionary success (species diversification) in primates with brain size or current sympatry context.
 
@@
 
-|   We found that non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
+|   We found that non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
 The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size and illustrates the trade-offs between costs and benefices of brain development [@isler2009expensive].
@@
 
-|   In addition, we investigated the evolutionary consequences of brain evolution by evaluating whether brain sizes correlated with species diversification rates (i.e.
+|   In addition, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with species diversification rates (i.e.
 speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
@@
 The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetic signals (Figure \@ref(fig:figRegressionDiversification)).
-In fact, a sudden encephalisation in primates is clearly associated to a limited number of close-related species [@decasien2017primate; @melchionna2020macroevolutionary].
+In fact, a sudden encephalisation in primates is clearly associated to a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
 This clearly limits the statistical power of our phylogenetically corrected analyses as we cannot decipher whether the connivance between brain size and evolutionary success results from a true biological link or appeared by chance.
@@
 This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in @melchionna2020macroevolutionary remains a likely possibility.
-Finally, despite diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
+Finally, although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
 In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
@@
 MOB or Striatum) across different primate genus.
-Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB.
+Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB of frugivorous primates.
 These areas imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
-Overall, the relative size of foraging-related brain areas were negatively associated with one index of sympatry intensity (the range overlap with other species) and might thus be a consequence of species direct or indirect interactions.
+Overall, the relative sizes of foraging-related brain areas were negatively associated with one index of sympatry intensity (the range overlap with other species) and might thus be a consequence of direct or indirect interspecific interactions.
 In general, competition is the first-thought mechanism to describe community structures [e.g.
@@
 In primates, it is rare to observe direct competition between species, which should translate into site exclusion.
-In fact, inter-species site exclusion in this taxa has only been observed in gibbons [@suwanvecho2012interspecific].
-For species with overlapping diet, indirect competition for resource might happen.
+In fact, inter-species site exclusion in this taxon has only been observed in gibbons [@suwanvecho2012interspecific].
+For species with overlapping diet, indirect competition for resources might happen.
 It has been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging].
@@
 Our results could thus suggest that species sympatry may trigger an important decrease in cues reliability, for instance due to higher and unforeseen depletion rate.
-That would explain a relaxed positive selection for advance cognitive abilities, and conversely, given the cost of brain maintenance [@raichle2006brain], would induce a negative selection towards areas involved in foraging related activities like the Hippocampus, the MOB and the Striatum.
+That would explain a relaxed positive selection for advance cognitive abilities, and conversely, given the cost of brain maintenance [@raichle2006brain], would induce a negative selection towards the sizes of areas involved in foraging-related activities like the Hippocampus, the MOB and the Striatum.
 Not only was brain evolution affected by sympatry, but sympatry (the maximum number of co-occurring species only) induced a slowdown in diversification, which contrasts with the picture offered by passerine birds at finer resolution [@kennedy2017historical].
-Density-dependence within clade is a known factor to affect negatively diversification rate [@moen2014does].
+Density-dependence within clade is a known factor to negatively affect diversification rate [@moen2014does].
 In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
@@
 
-# Literature cited
-
-<div id="refs"></div>
-
-\newpage
-
 ```{r tableRegGradient, include=TRUE}
@@
 
-\newpage
+\clearpage
 
@@
 layout(mat=t(c(1:nbPlot)), widths=rep(5, times=nbPlot), heights=c(5*nbPlot))
-par(mar=c(0, 0, 3, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+par(mar=c(0, 0, 3, 0.5), mgp=c(2, 0.5, 0), xpd=TRUE)
 
@@
 
-\vspace{-2in}
-
-```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, fig.cap="Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
+```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4.5, fig.height=4.5, fig.cap="\\footnotesize Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
 The grey background depicts the standard deviation.
@@
 
-\newpage
-
 ## Phylogenetic regressions: results, stability and assumption
@@
 (a) Phylogenetic regressions: selection gradient
+
+\clearpage
 
@@
 ```
-\newpage
+\clearpage
 
@@
 ```
+
+\clearpage
 
@@
 ```
-\newpage
+
+\clearpage
 
@@
 
-```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap="Forest plot of the phylogenetic regressions | CI: Confindence interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible as reduced).
-Plain dots depict negative effects, open dots depict positive effect.
+```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=6.25, fig.height=6.25, fig.cap="Forest plot of the phylogenetic regressions | CI: Confindence Interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible because reduced).
+Plain dots depict negative effects, open dots depict positive effects.
 "}
@@
        pos=4, col=colourModelsReg[a],
-       labels=pvalueToText(as.numcharac(results.df_gradient[5*(a-1)+3,7])), cex=0.75)
+       labels=pvalueToText(as.numcharac(results.df_gradient[grep(traitName_legend[a], results.df_gradient[,1]) + 2,7])), cex=0.75)
   }else{
@@
             symmetrical=FALSE)
-  points(x=cbind(model$bootmean, t(model$bootconfint95))[3,1], y=0.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[3,1]>0,21,19), , bg="white", col=colourModelsReg[a])
+  points(x=cbind(model$bootmean, t(model$bootconfint95))[3,1], y=0.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[3,1]>0,21,19), bg="white", col=colourModelsReg[a])
   if(a!=length(traitName_rdc)){
@@
        pos=4, col=colourModelsReg[a],
-       labels=pvalueToText(as.numcharac(results.df_gradient[5*(a-1)+4,7])), cex=0.75)
+       labels=pvalueToText(as.numcharac(results.df_gradient[grep(traitName_legend[a], results.df_gradient[,1]) + 3,7])), cex=0.75)
   }else{
@@
               symmetrical=FALSE)
-    points(x=as.data.frame(summary(model)$solutions[,1:3])[2,1], y=-1.5-(a-1)*1/(length(traitName_rdc)-1), pch=ifelse(as.data.frame(summary(model)$solutions[,1:3])[2,1]>0,21,19), , bg="white", col=colourModelsReg[a])
+    points(x=as.data.frame(summary(model)$solutions[,1:3])[2,1], y=-1.5-(a-1)*1/(length(traitName_rdc)-1), pch=ifelse(as.data.frame(summary(model)$solutions[,1:3])[2,1]>0,21,19), bg="white", col=colourModelsReg[a])
     text(x=as.data.frame(summary(model)$solutions[,1:3])[2,3], y=-1.5-(a-1)*1/(length(traitName_rdc)-1),
          pos=4, col=colourModelsReg[a],
-         labels=pvalueToText(as.numcharac(results.df_diversification[4*(a-1)+3,5])), cex=0.75)
+         labels=pvalueToText(as.numcharac(results.df_diversification[grep(traitName_legend[a], results.df_diversification[,1]) + 2,5])), cex=0.75)
 
@@
 
-legend(x=-3.25, y=-4, 
+legend(x=-2.5, y=-4, 
        pch=rep(19, times=length(traitName_rdc)), 

### 2021-10-03 Article/Article.Rmd
Latest modif main art + cover letter

@@
 ---
-title: \Huge \textbf{Species sympatry shapes brain size evolution in Primates}
+title: "Species sympatry shapes brain size evolution in Primates"
 # date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 author: 
-  - name: \textit{Benjamin Robira}
+  - name: Benjamin Robira
     email: benjamin.robira@normalesup.org
@@
     correspondence: true
-  - name: \textit{Benoit Perez-Lamarque}
+  - name: Benoît Perez-Lamarque
     email: benoit.perez@ens.psl.eu
@@
     } 
+  - \usepackage{titling}
+  - \pretitle{
+    \begin{flushleft}
+    \rule[-0.15in]{0.25\linewidth}{0.8ex}
+    \vspace{-0.8ex}
+    \hrule
+    \vspace{0.3in}
+    \begin{LARGE}
+    \noindent
+    \textbf
+    }
+  - \posttitle{
+    \end{LARGE}\newline
+    \rule[-0.15in]{0.25\linewidth}{0.8ex}
+    \hrule
+    \end{flushleft}
+    \vspace{0.2in}}
 ---
@@
 
-**Abstract |** Hypotheses related to animal intelligence evolution highlight the role of conspecifics.
-Yet, one species rarely occupies an area alone: Space is a place often occupied by many species, sometimes belonging to the same ecological guild.
-These sympatric heterospecifics can act as competitors or (direct or indirect) cooperators, thereby stimulating cognition.
-They can also contribute to modifying and depleting the environment such as it makes it poorly predictable, thereby alleviating the benefice of cognition.
-Considering brain size as a proxy for cognition, we used primates as a study example to test for the intertwine between species sympatry and cognition.
-We retraced the evolutionary history of several brain areas considering competitive or non-competitive evolutionary scenarios.
-We found that competitive evolutionary scenarios best predicted the evolution of brain areas related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
-The whole brain size, as well as the size of areas used in more general contexts were not related to the sympatry level.
-In any case, the evolutionary success of primate species was unrelated to the relative sizes of brain areas but was negatively affected by sympatry.
+**Abstract |** Main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
+Yet, space is a place often occupied by many species, sometimes belonging to the same ecological guild.
+These sympatric heterospecifics can act as competitors or cooperators, thereby stimulating cognition.
+They can also contribute to modifying and depleting the environment, making it poorly predictable and thereby alleviating the benefit of cognition.
+Considering brain size as a proxy for cognition, we used primates to test for the intertwine between species sympatry and cognition, and retraced the evolutionary history of several brain areas considering competitive or non-competitive evolutionary scenarios.
+We found that competitive evolutionary scenarios best predicted the evolution of brain areas related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate, but not of the whole brain or brain areas used in immediate information processing.
+Moreover, sympatry negatively affected primate diversification which was unrelated to the size of brain areas.
 Overall, this comparative study suggests that species sympatry, which likely convolutes the environment, contributes to shaping the selective pressure acting upon primate cognition and diversification.
@@
 Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
+However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are likely to strongly shape the evolution of cognition.
 
@@
 Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond).
-Although generally considered as a singular entity, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
+Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic] and these areas are likely to be differently affected by species sympatry.
 For instance, the Striatum is stimulated during social interactions [@baez2013role].
-Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is rather infrequent in primates nonetheless (but see callitrichine primates in particular, @heymann2015unlike).
+Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike).
 The Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
-Foraging-related areas, as are also the Main Olfactory Bulb (MOB) or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], are expected to be influenced by the ecological environment.
-Such areas are tought to be particularly key for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany].
-The changes induced by other species with similar dietary habits can contribute to increasing its unpredictability, thus changing the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
-Due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
-positive selection for bigger brain), before smaller brain sizes become more adaptive.
-Conversely, more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
-
-|    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primate as study example.
-To infer the effect of species interactions on brain size evolution within the frugivorous primates, we evaluated the support for competitive or non-competitive evolutionary scenarios in the context of sympatry and investigated the directionality of the selection upon brain size evolution in the context of sympatry.
-Finally, we tested for correlative pattern of the evolutionary success (species diversification) in primates with brain size or current sympatry context.
+Other foraging-related areas, as the Main Olfactory Bulb (MOB) or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], are also expected to be influenced by the ecological environment.
+Such areas are thought to be particularly important for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany], and larger areas, taken as equivalent to more advanced cognitive abilities, might be more advantageous.
+Similarly, more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
+To sum up, a first possibility is that sympatric heterospecifics could altogether stimulate cognition and promote larger sizes of the brain areas related to interacting with the social or ecological environment.
+
+|   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
+Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
+positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory).
+Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g.
+phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social].
+In this case, the size of brain areas involved in immediate information processing should be less large in sympatric than in non-sympatric conditions.
+To sum up, a second possibility is that sympatric heterospecifics could hamper the benefits of cognition on foraging, and thus slowdown brain size increase.
+In an extreme case, it could even induce positive selection for smaller brain size.
+
+|    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
+To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
+Finally, we tested for correlative patterns between the evolutionary success (species diversification) in primates with brain size or current sympatry context.
 
@@
 The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size and illustrates the trade-offs between costs and benefices of brain development [@isler2009expensive].
-By contrast, competitive models were most supported in areas involved in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, @burgess2002human) or planning abilities and reward assessment (Striatum, @baez2013role; @johnson2007integrating), while they tended to be so for one involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+By contrast, competitive models were most supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, @burgess2002human) or planning abilities and reward assessment (Striatum, @baez2013role; @johnson2007integrating), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
 When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and the Striatum, but a slowdown for the MOB.
@@
 The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with competitive models: The Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
+Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with competitive models: the Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
 The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
@@
 This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
-The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetic signals (Figure \@ref(fig:figRegressionDiversification)).
+The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetic non-independence (Figure \@ref(fig:figRegressionDiversification)).
 In fact, a sudden encephalisation in primates is clearly associated to a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
@@
 In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification, an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
+In other words, the higher the number of sympatric species, the lower the diversification, a trend that is frequently suggested in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
 
@@
 As the brain area is regionally specialised [@barton2000mosaic], brain regions could be under different selective pressures as suggested by the differences we highlighted in some brain areas (e.g.
-MOB or Striatum) across different primate genus.
-Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: Although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB of frugivorous primates.
-These areas imply individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
+MOB or Striatum) across different primate genera.
+Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB of frugivorous primates.
+These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
 Overall, the relative sizes of foraging-related brain areas were negatively associated with one index of sympatry intensity (the range overlap with other species) and might thus be a consequence of direct or indirect interspecific interactions.
@@
 Not only was brain evolution affected by sympatry, but sympatry (the maximum number of co-occurring species only) induced a slowdown in diversification, which contrasts with the picture offered by passerine birds at finer resolution [@kennedy2017historical].
-Density-dependence within clade is a known factor to negatively affect diversification rate [@moen2014does].
+Density-dependence within clade is often thought to lower diversification rate [@moen2014does].
 In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
@@
 In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species.
-Here, we showed that species sympatry can influence the evolutionary scenario that applies to animals' brain, but the proximate mechanisms at play remain to be elucidated.
-Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: Polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
+Here, we showed that species sympatry is an important factor shaping the evolutionary history of animals' brain, but the proximate mechanisms at play remain to be elucidated.
+Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
 As Alice said “It's a great huge game of chess that's being played—all over the world” (@Carroll, Chapter II) and all individuals are just pieces to play with or against, no matter the species.

### 2021-10-03 Article/Coverletter.Rmd
Latest modif main art + cover letter

---
output: pdf_document
#word_document

header-includes:
  - \usepackage{fontawesome5}
  - \pagenumbering{gobble} #for no page numbering
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include=FALSE, warning = FALSE)
```
```{r}
journal <- "Nature Ecology \\& Evolution"
editor <- "Dr. Vera Domingues"
title <- "Species sympatry shapes brain size evolution in Primates"
listOfAuthors <- paste("Benjamin Robira,", "and Benoît Perez-Lamarque", collapse=" ")
```

\begin{flushleft}
\rule[-0.15in]{0.25\linewidth}{0.8ex}
\vspace{-0.8ex}
\hrule
\vspace{0.1in}
To the Editorial Board of \textit{`r journal`}
\end{flushleft}

\begin{flushright}
On the `r Sys.Date()`
\end{flushright}

\hfill

\begin{center}
Dear `r editor`,
\end{center}

\hfill

We hereby submit our manuscript entitled **"`r title`"**, by `r listOfAuthors`, for consideration as a Research Article to *`r journal`*.

|   The road to understanding the evolutionary history and significance of cognition is still little paved. Currently formulated theories generally oppose social to ecological drivers of cognition and are oten framed within a foraging-related context. These theories, nonetheless, give a priority to the challenges an individual faces with regards to its ecological environment, or its conspecifics from a same group and/or species. Yet, space is also shared with other species that might also shape the environment and be competitors or cooperators. Thus, it is likely that cognate species, with which dietary overlap occurs, are likely to affect the social and ecological environment a species evolves in. This should loop onto the selective pressures that apply to cognition. This facet remained unexplored.

|   To help filling this gap, we provide a meta-analysis to investigate the role of sympatry in shaping animals' the size of different brain areas, and animals' evolutionary success. In particular, we focus on frugivorous primates because the consumption of fruits is highly tightened to advanced cognitive skills. Using recently developed evolutionary phylogenetic models accounting for competition or not with sympatric species, we retrace the evolution of the size of brain areas related to foraging or note. We also correlate brain size, diversification rate (a proxy for evolutionary success), and sympatry intensity.

|  We show that the evolutionary history of brain areas associated to foraging tasks is more accurately summarised when using competitive models. In particular, sympatry negatively affects their relative size. We additionally show that, despite these brain sizes are not related to diversification rate, this latter is reduced when sympatry rates increases. Altogether, these findings suggest that sympatry is associated to a relaxed selection for bigger brain, or even a positive selection for smaller brain. We speculate that this is due to an overcomplexification of the environment.

|  This study enlarges our understanding on the effect of space use and distribution in animal cognition, and show unprecedent evidence of direct and/or inderect effect of competition on cognition evolution, questioning proximate mechanisms at play. We strongly believe that this stands as an important complementary piece of meta-analyses that were already published in your journal that will be of interest to empiricists and theoreticians from ecological and evolutionary fields. On behalf of all authors, I certify that this is a completely novel contribution that has not been submitted elsewhere, and that all authors approved the manuscript and its submission to *`r journal`*.

\hfill

\begin{flushright}
Benjamin Robira, on behalf of all authors.\\
\faEnvelope \hspace{0.01in} \href{mailto:benjamin.robira@normalesup.org}{benjamin.robira@normalesup.org}\\
\vspace{0.1in}
\includegraphics[width=0.55\textwidth]{T:/Saved_PhD/CV/signature.png}\\
\end{flushright}

### 2021-12-02 Article/Article.Rmd
Revision intro + figures + discussion + citation (all in exponent)

@@
 
-**Abstract |** Main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
+**Abstract |** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
 Yet, space is a place often occupied by many species, sometimes belonging to the same ecological guild.
-These sympatric heterospecifics can act as competitors or cooperators, thereby stimulating cognition.
-They can also contribute to modifying and depleting the environment, making it poorly predictable and thereby alleviating the benefit of cognition.
-Considering brain size as a proxy for cognition, we used primates to test for the intertwine between species sympatry and cognition, and retraced the evolutionary history of several brain areas considering competitive or non-competitive evolutionary scenarios.
-We found that competitive evolutionary scenarios best predicted the evolution of brain areas related to interacting with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate, but not of the whole brain or brain areas used in immediate information processing.
-Moreover, sympatry negatively affected primate diversification which was unrelated to the size of brain areas.
-Overall, this comparative study suggests that species sympatry, which likely convolutes the environment, contributes to shaping the selective pressure acting upon primate cognition and diversification.
+These sympatric heterospecifics can act as competitors or cooperators, thereby shaping cognition.
+They can provide new cues to infer food presence, or impoverish the environment, stimulating the need of cognition.
+They can also make the environment poorly predictable, thereby alleviating the benefit of cognition.
+Considering brain size as a proxy for cognition, we used primates to test for the intertwine between species sympatry and cognition.
+We retraced the evolutionary history of several brain areas with evolutionary scenarios considering or discarding sympatry.
+We found that evolutionary scenarios considering sympatry best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
+By contrast, the whole brain or brain areas used in immediate information processing were best described by evolutionary models not considering sympatry.
+Moreover, sympatry negatively affected primate diversification which was unrelated to the size of the studied brain areas.
+Overall, this comparative study suggests that species sympatry contributes to shaping the selective pressure acting upon primate cognition and diversification.
+We speculate that this is due to an over-complexification of resource spatio-temporal pattern.
 
@@
 
-\initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
+<!-- \initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
 Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
-However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are likely to strongly shape the evolution of cognition.
-
-|   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
+However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition.
+-->
+
+<!-- |   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
 Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond).
 Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic] and these areas are likely to be differently affected by species sympatry.
-For instance, the Striatum is stimulated during social interactions [@baez2013role].
-Its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike).
-The Striatum also underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
-Other foraging-related areas, as the Main Olfactory Bulb (MOB) or the Hippocampus, home of a spatio-temporal memory [@burgess2002human], are also expected to be influenced by the ecological environment.
-Such areas are thought to be particularly important for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany], and larger areas, taken as equivalent to more advanced cognitive abilities, might be more advantageous.
-Similarly, more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
+For instance, the Main Olfactory Bulb (MOB) or the Hippocampus , home of a spatio-temporal memory [@burgess2002human], are largely involved in efficient foraging, especially for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany]: we therefore expect that primate species with larger MOB or Hippocampus areas, taken as equivalent to more advanced perceptive and cognitive abilities for efficient foraging, might be more fit than their sympatric species with smaller areas.
+Similarly, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
+-->
+<!-- are expected to be influenced by the ecological environment.
+The Striatum is also stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike).
+Finally, besides foraging-related areas (Striatum, MOB or Hippocampus), more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
 To sum up, a first possibility is that sympatric heterospecifics could altogether stimulate cognition and promote larger sizes of the brain areas related to interacting with the social or ecological environment.
-
-|   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
+-->
+
+<!-- |   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
 Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
@@
 In an extreme case, it could even induce positive selection for smaller brain size.
+-->
+
+<!-- |    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
+To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
+Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in primates.
+-->
+
+\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
+Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
+However, space is a place often occupied by many species belonging to the same ecological guild.
+We can predict that interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition.
+Heterospecifics can act as indirect competitors for food (Hypothesis 1) and might also be indirect cooperators, providing cues on food location and availability (Hypothesis 2, e.g.
+[@olupot1998fruit]).
+
+|   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
+Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities, with larger size considered equivalent to larger cognitive abilities (but see discussion in @logan2018beyond).
+Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
+These areas are likely to be under different selective pressures, and thus, to be differently affected by species sympatry.
+Brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected under the competitive hypothesis (Hypothesis 1).
+Brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] should be particularly affected under the cooperative hypothesis (Hypothesis 2).
+
+|   Under both of the two (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
+On the one hand, species co-occurrence could contribute to increasing food depletion and reducing food predictability because of unforeseen depletion by heterospecifics, two facts that might imply the use cognitive abilities for inferring food location and availability [@grove2013evolution; @robirainreview].
+Thus, under hypothesis 1, because of reasonable environmental complexification due to heterospecifics, the size of the area such as the Hippocampus should eventually be larger (Prediction 1.1).
+Heterospecifics might also leave traces of presence or passage that can lead to available food.
+These cues might add to environmentally used ones.
+This should thus stimulate areas involved in general and immediate information processing.
+Thus, under hypothesis 2, due to an additive effect of heterospecifics cues over environmental cues, the size of areas such as the MOB, the Cerebellum or the Neocortex should be larger (Prediction 2.1).
+
+|   On the other hand, if changes induced by sympatric species increase environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution; @robirainreview].
+Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
+positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory).
+Thus, under hypothesis 1, in case of an over-complexification of the environment, the Hippocampus size should be smaller (Prediction 1.2).
+Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g.
+phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social].
+It has indeed been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging], favouring social cues in particular when environmental cues are too noisy.
+Thus, under hypothesis 2 and an exclusion effect of heterospecifics cues over environmental cues, the size of the MOB, the Cerebellum or the Neocortex should be smaller (Prediction 2.2).
+
+|   While cognition can be intensively shaped under the rationale centred around resource harvesting [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
+The Striatum is stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]) and should not be affected under indirect competition or cooperation with heterospecifics.
+It can thus serve as as a null comparative area.
+Considering the Striatum as only social-related is however reductive, as the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
+Thus, very important evolutionary pressure on energetic optimisation might also shape the Striatum size equivalently to the Hippocampus.
 
 |   Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
-To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between the evolutionary success (species diversification) in primates with brain size or current sympatry context.
+Frugivorous primates are an interesting group for such a question because fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio], for which cognition thus considerably shapes the foraging strategy [@trapanese2019and].
+To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for evolutionary scenarios accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
+Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in all primates.
 
@@
 
-We gathered a large database on the whole brain size, the size of the Cerebellum and the Neocortex, involved in daily information processing and retention, and the Main Olfactory Bulb (MOB), the Striatum, and the Hippocampus, those three latter being related to social and foraging-related tasks, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
+We gathered a large database on the whole brain size, the size of the MOB, Cerebellum and the Neocortex, involved in daily information processing, and the Striatum and the Hippocampus, related to either social and foraging-related tasks, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
 It evidenced ample variations in brain size.
@@
 pondered by whole-body mass) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
-
-|   We first reconstructed primate biogeography history (N$_{species}$ = `r minRange`, @matzke2013probabilistic; @matzke2016stochastic) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); @kamilar2009environmental) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; @bollback2006simmap).
-We then calculated the likelihoods of models considering the role of species interactions (matching competition MC models, @nuismer2015predicting; models of linear or exponential density dependence, DD$_{lin}$and  DD$_{exp}$, of the evolutionary rate on the number of sympatric lineages; @drury2016estimating see [Models of trait evolution: does interspecific interactions shape brain size evolution?]) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
+Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (a brain area related to social interactions, Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+
+|   In order to get the evolutionary history of sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`, [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
+We then calculated the likelihoods of models considering the role of species interactions (matching competition MC models, [@nuismer2015predicting]; models of linear or exponential density dependence, DD$_{lin}$ and DD$_{exp}$, of the evolutionary rate on the number of sympatric lineages; [@drury2016estimating] see [Models of trait evolution: does interspecific interactions shape brain size evolution?]) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
 \@ref(fig:figbrain)) and compared their likelihood to those of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
-stabilizing selection; see @blomberg2020beyond for a review) or the Early-Burst model (EB, @blomberg2003testing), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
+stabilizing selection; see [@blomberg2020beyond] for a review) or the Early-Burst model (EB, [@blomberg2003testing]), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
 Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criterions corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does interspecific interactions shape brain size evolution?]).
 
-|   We found that non-competitive models were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
-The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size and illustrates the trade-offs between costs and benefices of brain development [@isler2009expensive].
-By contrast, competitive models were most supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, @burgess2002human) or planning abilities and reward assessment (Striatum, @baez2013role; @johnson2007integrating), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased lineage diversity for the Hippocampus and the Striatum, but a slowdown for the MOB.
+|   We found that models discarding species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
+The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefices of brain development [@isler2009expensive].
+By contrast, models considering sympatry were most supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, [@burgess2002human]) or planning abilities and reward assessment (Striatum, [@baez2013role; @johnson2007integrating]), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased diversity of sympatric lineages for the Hippocampus and the Striatum, but a slowdown for the MOB.
 
@@
 For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates based on IUCN date [@IUCN].
+We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates based on IUCN data [@IUCN].
 On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
@@
 The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with competitive models: the Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
+Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with models considering sympatry: the Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
 The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
-Thus, it suggests that sympatric species are either subject to a positive selection towards smaller brain, or to a less intense selection for advanced cognitive abilities compared with isolated species.
+Given the acceleration of the evolutionary tempo, it suggests that sympatric species are subject to a positive selection towards smaller brain, and not to a less intense selection for advanced cognitive abilities compared with isolated species.
 
@@
 speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
-Overall, species diversification, estimated based on molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
+Overall, species diversification rates, estimated based on molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
 When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
@@
 In fact, a sudden encephalisation in primates is clearly associated to a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically corrected analyses as we cannot decipher whether the connivance between brain size and evolutionary success results from a true biological link or appeared by chance.
+This clearly limits the statistical power of our phylogenetically-corrected analyses as we cannot decipher whether the connivence between brain size and evolutionary success results from a true biological link or appeared by chance.
 A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
-This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in @melchionna2020macroevolutionary remains a likely possibility.
+This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
 Finally, although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
 In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification, a trend that is frequently suggested in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
+In other words, the higher the number of sympatric species, the lower the diversification, a density-dependendence trend that is frequently suggested in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
 
@@
 MOB or Striatum) across different primate genera.
-Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus, and the Striatum, and potentially in the MOB of frugivorous primates.
+Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
 These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
-Overall, the relative sizes of foraging-related brain areas were negatively associated with one index of sympatry intensity (the range overlap with other species) and might thus be a consequence of direct or indirect interspecific interactions.
-In general, competition is the first-thought mechanism to describe community structures [e.g.
+The fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
+By contrast, potential indirect cooperation between species (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in general information processing (e.g.
+Cerebellum or Neocortex).
+
+|   In general, competition is the first-thought mechanism to describe community structures [e.g.
 @rocha2015role].
-In primates, it is rare to observe direct competition between species, which should translate into site exclusion.
+In primates, it is rare to observe direct competition between species (but see recently @southern2021lethal), which should translate into site exclusion.
 In fact, inter-species site exclusion in this taxon has only been observed in gibbons [@suwanvecho2012interspecific].
 For species with overlapping diet, indirect competition for resources might happen.
-It has been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging].
-The utilization of these cues should promote cognition until reaching a certain range of environmental complexity [@grove2013evolution; @robirainreview].
-Our results could thus suggest that species sympatry may trigger an important decrease in cues reliability, for instance due to higher and unforeseen depletion rate.
-That would explain a relaxed positive selection for advance cognitive abilities, and conversely, given the cost of brain maintenance [@raichle2006brain], would induce a negative selection towards the sizes of areas involved in foraging-related activities like the Hippocampus, the MOB and the Striatum.
-Not only was brain evolution affected by sympatry, but sympatry (the maximum number of co-occurring species only) induced a slowdown in diversification, which contrasts with the picture offered by passerine birds at finer resolution [@kennedy2017historical].
-Density-dependence within clade is often thought to lower diversification rate [@moen2014does].
+We show that higher sympatry rate is actually associated with smaller size of the Hippocampus or Striatum (negative effect of the intensity of overlap with co-occurring species on the specific area size, in accordance with Prediction 1.2).
+This suggests that indirect competition might contribute to convoluting the environment such as cognitive foraging might no longer be beneficial.
+In particular, the acceleration of the evolutionary tempo (i.e.
+the effect size associated to density dependence terms is positive) suggests that it is not limited to a relax of positive selection for bigger brains, but to a positive selection for smaller brains.
+
+|   Not only was brain evolution affected by sympatry, but sympatry (here the maximum number of co-occurring species only) induced a slowdown in diversification.
+Density-dependence within clade is indeed generally associated to lower diversification rate [@moen2014does].
 In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
-Given the large resolution and low overlap threshold to consider sympatry considered here (i.e.
-overlap of `r geographicThresholdVector[1]*100`% of the distribution area), this competitive view fits the observed influence of sympatry on frugivorous primate diversification.
-
-|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond).
+These observations thus strengthen our view on indirect species interaction by scramble competition which might cascade both on population dynamics and species cognition.
+
+|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from [@deaner2000comparative; @healy2007critique; @logan2018beyond]).
 The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
-in primates: @milham2018open), or with standardized behaviourally explicit comparisons (e.g.
+in primates: [@milham2018open]), or with standardized behaviourally explicit comparisons (e.g.
 on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time to generate large-enough datasets.
@@
 Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
-As Alice said “It's a great huge game of chess that's being played—all over the world” (@Carroll, Chapter II) and all individuals are just pieces to play with or against, no matter the species.
+As Alice said “It's a great huge game of chess that's being played—all over the world” ([@Carroll], Chapter II) and all individuals are just pieces to play with or against, no matter the species.
 
@@
 
-Brain data were obtained from @decasien2019primate for whole brain and all mentioned other parts (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size.
+Brain data were obtained from [@decasien2019primate] for whole brain and all mentioned other parts (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
 They were freely available in the main manuscript or supplementary materials.
@@
 EQ indicates whether the brain size ranges above (> 1) or below (< 1) expected given the body mass.
-Body mass was obtained from @decasien2017primate, @powell2017re, @grueter2015home and @pearce2013space.
-The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, @wiltgen2004new; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, @burgess2002human).
+Body mass was obtained from [@decasien2017primate; @powell2017re; @grueter2015home; @pearce2013space].
+The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, [@wiltgen2004new]; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, [@koziol2014consensus; @sokolov2017cerebellum]), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, [@burgess2002human]).
 The Striatum (N$_{Striatum,max}$ = `r maxStriatum`) supports information processing during social interaction, reward assessment, planning or goal-oriented behaviours [@baez2013role; @johnson2007integrating].
 To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
-As such, the use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in @deaner2000comparative).
-Percentage of frugivory and/or folivory was obtained based on freely available dataset from @decasien2017primate and @powell2017re for the frugivory and folivory rate, or @willems2013collective for the folivory rate.
+As such, the use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in [@deaner2000comparative]).
+Percentage of frugivory and/or folivory was obtained based on freely available dataset from [@decasien2017primate; @powell2017re] for the frugivory and folivory rate, or [@willems2013collective] for the folivory rate.
 
@@
 Based on the structure (i.e.
-number of species and their phylogenetic relationship) of primate communities at different field sites, @kamilar2009environmental determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
+number of species and their phylogenetic relationship) of primate communities at different field sites, [@kamilar2009environmental] determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
 We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
@@
 Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
-evidenced on the North American fauna in @pineda2021mammal).
+evidenced on the North American fauna in [@pineda2021mammal]).
 
 |   We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
-We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
+We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see [@matzke2013probabilistic] for further details on these events).
 To reconstruct the evolution of species range, we fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas.
@@
 If this was not the case, or frugivory rate was unavailable, a species could be classified as folivorous if the folivory rate was at least above `r folivoryThresholdVector[1]` (low threshold) or `r folivoryThresholdVector[2]`% (high threshold).
-Otherwise, @decasien2017primate gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria.
+Otherwise, [@decasien2017primate] gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria.
 Whenever the rate was not available, we referred to this classification.
@@
 First, such static rate does not reflect potential seasonality in fruit eating (e.g.
-@masi2009western), which is generally shorter, hence a lower overall frugivory rate.
+[@masi2009western]), which is generally shorter, hence a lower overall frugivory rate.
 Second, frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
@@
 within brain area), the sample was strictly identical, allowing within set comparison.
-Prior fitting, trait parameters were log-transformed to reach more symmetrical distributions.
+Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
 Models without competition, Brownian Motion (i.e.
@@
 EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted competitive models using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These competitive models notably account for interaction matrices that are built on the evolutionary history of species sympatry and diet.
-These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see @drury2016estimating).
-We fitted three different competitive models.
+Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted models considering sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+These models notably account for interaction matrices that are built on the evolutionary history of species sympatry and diet.
+These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see [@drury2016estimating]).
+We fitted three different models including sympatry.
 The matching competition model (MC) may consider divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
@@
 Three independent chains were run until their respective convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
-The analysis relied on the use of a consensus tree of primate phylogeny from @dos2018using.
+The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
 This latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
@@
 |   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
-@estrada2017impending estimated that, given current knowledge, the primate clade should be composed of 504 species.
+[@estrada2017impending] estimated that, given current knowledge, the primate clade should be composed of 504 species.
 This means that the current sampling fraction is around 73%.
@@
 
-(a)	Determining the direction of the selection gradient shaped by interspecific competition
+(a)	Determining the direction of the selection gradient shaped by interspecific interactions
 
@@
 a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients but its diagonal multiplied by lambda) for each brain region individually and for frugivorous species only.
-We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we it included brain areas for which the evolutionary history was best described by competitive models.
+We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we it included brain areas for which the evolutionary history was best described by models considering sympatry.
 Here specifically, we considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
@@
 
-|    The response variable was the relative size of brain areas shown as better described by competitive phylogenetic scenario (see above).
+|    The response variable was the relative size of brain areas.
 Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability and assumption]).
@@
 Other function parameters were set to default.
-Prior fitting, covariates were symmetrized if necessary.
+Prior to fitting, covariates were symmetrized if necessary.
 Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
-We did not observe correlation issue among predictors either (VIF$_{max}$ < 2, @mundry2014statistical).
+We did not observe correlation issue among predictors either (VIF$_{max}$ < 2, [@mundry2014statistical]).
 
@@
 results.df_gradient <- results.df_gradient[-(6:10),]
+results.df_gradient[1] <- gsub("frugivorous", "frugivores", results.df_gradient[,1])
+results.df_gradient[1] <- gsub("home range", "range", results.df_gradient[,1])
+
 rownames(results.df_gradient) <- NULL
-knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the selection gradient direction | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
-The brain area (as well as the associated sample size) are indicated prior each list of estimates.
+knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+The brain area (as well as the associated sample size) are indicated prior to each list of estimates.
 The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
@@
 rownames(results.df_diversification) <- NULL
-knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between diversification and brain size | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between species diversification and relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
 samp.=Effective sample (adjusted for autocorrelation).
-The brain area (as well as the associated sample size) are indicated prior each list of estimates.
+The brain area (as well as the associated sample size) are indicated prior to each list of estimates.
 The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
@@
 ```{r tableRegDiversificationAndSympatry, include=TRUE}
+results.df_diversificationAndSympatry[1] <- gsub("frugivorous", "frugivores", results.df_diversificationAndSympatry[,1])
+results.df_diversificationAndSympatry[1] <- gsub("home range", "range", results.df_diversificationAndSympatry[,1])
+
 knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,
@@
 The brain area (as well as the associated sample size)
-             are indicate prior each list of estimates. the transformation (logarithm or square-root) if indicated in parenthese by the abbreviation (log or sqrt).") %>%
+             are indicate prior to each list of estimates. the transformation (logarithm or square-root) if indicated in parenthese by the abbreviation (log or sqrt).") %>%
   kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
@@
 warnings()
-```
-
-```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction represented on the Natural Earth projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
-Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-Hence, *Macaca Sylvanus* is not considered in this study.", sep="")}
-
-#abbreviation name are available in https://proj.org/operations/projections/index.html
-#help for graticule: https://rpsychologist.com/working-with-shapefiles-projections-and-world-maps-in-ggplot
-
-proj.map <- "+proj=natearth +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
-
-centroid <- as.data.frame(centroid)
-colnames(centroid) <- c("long", "lat")
-centroid$nudge_y <- 0
-centroid$nudge_y[5] <- -5
-
-library(tidyverse)
-library(ggspatial)
-
-library(rnaturalearth)
-world <- ne_countries(scale = "medium", returnclass = "sf")
-
-# graticule (Robin)
-grat <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_graticules_15")
-grat_df <- fortify(grat)
-
-bbox <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_wgs84_bounding_box")
-bbox_df<- fortify(bbox)
-
-bbox.sf <- sfheaders::sf_polygon(  obj = bbox_df 
-                                         , x = "long"
-                                         , y = "lat"
-                                         , polygon_id = "group"
-)
-sf::st_crs(bbox.sf) <- st_crs(world)
-
-grat_df <- grat_df[,c(1,2,6)]
-colnames(grat_df) <- c("x", "y", "linestring_id")
-grat_df.sf <- sfheaders::sf_line(obj = grat_df)
-
-sf::st_crs(grat_df.sf) <- st_crs(world)
-
-#Main map
-map <- ggplot() +
-  geom_sf(data = bbox.sf, fill=adjustcolor("white", alpha.f=0.45), col="white") +
-  geom_sf(data = grat_df.sf, col="darkgrey", lty=2) +
-  geom_sf(data = world, fill = "black", col = "white") +
-  theme(panel.background=element_rect(fill="white"),
-        panel.grid = element_blank(),
-        axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
-        axis.ticks.y=element_blank()
-  )
-
-#Plot polygons areas
-mergedArea <- c()
+
+# Create legend
 areaNameCorrected <- c(
@@
   "Asian islands")
+colourArea <- c(
+"white",
+"darkseagreen2",
+"darkseagreen",
+"darkseagreen4",
+"black",
+"orange1", 
+"darkorange2",
+"darkorange4",
+"lightgoldenrod1",
+"lightgoldenrod2",
+"lightgoldenrod3",
+"lightgoldenrod4"
+)
+
+par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+emptyPlot()
+legend(x=0, y=0.9, col=c("black", colourArea[2:5]), legend=areaNameCorrected[1:5], pch=c(1, rep(19, times=length(2:5))), pt.cex=1.5, xjust=0, yjust=1, bty="n",
+      y.intersp=2.75,
+      title=expression(bold("Africa")))
+legend(x=0.5, y=0.9, col=c(colourArea[6:8]), legend=areaNameCorrected[6:8], pch=19, bty="n", pt.cex=1.5, xjust=0.5, yjust=1,
+       y.intersp=2.75,
+       title=expression(bold("America")))
+legend(x=1, y=0.9, col=c(colourArea[9:12]), legend=areaNameCorrected[9:12], pch=19, bty="n", pt.cex=1.5, xjust=1, yjust=1,
+       y.intersp=2.75,
+       title=expression(bold("Asia")))
+my_legend <- recordPlot()     
+```
+
+```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Natural Earth projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
+Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
+Hence, *Macaca Sylvanus* is not considered in this study.", sep="")}
+
+#abbreviation name are available in https://proj.org/operations/projections/index.html
+#help for graticule: https://rpsychologist.com/working-with-shapefiles-projections-and-world-maps-in-ggplot
+
+proj.map <- "+proj=natearth +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
+
+centroid <- as.data.frame(centroid)
+colnames(centroid) <- c("long", "lat")
+centroid$nudge_y <- 0
+centroid$nudge_y[5] <- -10
+
+library(tidyverse)
+library(ggspatial)
+
+library(rnaturalearth)
+world <- ne_countries(scale = "medium", returnclass = "sf")
+
+# graticule (Robin)
+grat <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_graticules_15")
+grat_df <- fortify(grat)
+
+bbox <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_wgs84_bounding_box")
+bbox_df<- fortify(bbox)
+
+###----
+### OLD WAY: when using sf package
+###----
+# bbox.sf <- sfheaders::sf_polygon(  obj = bbox_df 
+#                                          , x = "long"
+#                                          , y = "lat"
+#                                          , polygon_id = "group"
+# )
+# sf::st_crs(bbox.sf) <- st_crs(world)
+# 
+# grat_df <- grat_df[,c(1,2,6)]
+# colnames(grat_df) <- c("x", "y", "linestring_id")
+# grat_df.sf <- sfheaders::sf_line(obj = grat_df)
+# 
+# sf::st_crs(grat_df.sf) <- st_crs(world)
+
+#Main map
+# map <- ggplot() +
+#   geom_sf(data = bbox.sf, fill=adjustcolor("white", alpha.f=0.45), col="white") +
+#   geom_sf(data = grat_df.sf, col="darkgrey", lty=2) +
+#   geom_sf(data = world, fill = "black", col = "white") +
+#   theme(panel.background=element_rect(fill="white"),
+#         panel.grid = element_blank(),
+#         axis.title.x=element_blank(),
+#         axis.text.x=element_blank(),
+#         axis.ticks.x=element_blank(),
+#         axis.title.y=element_blank(),
+#         axis.text.y=element_blank(),
+#         axis.ticks.y=element_blank()
+#   )
+
+#Plot polygons areas
+mergedArea <- c()
 
@@
 
-centroid.sf <- st_as_sf(centroid, coords=c("long", "lat"), crs=st_crs(world))
-library(sfheaders)
-mergedArea.sf <- sfheaders::sf_polygon(  obj = mergedArea
-                                         , x = "long"
-                                         , y = "lat"
-                                         , polygon_id = "group"
-)
-sf::st_crs(mergedArea.sf) <- st_crs(world)
-
-#Readd colour
-mergedArea.sf$colour <- unique(mergedArea[,c(7,8)])[,2]
-
+###----
+### OLD WAY: when using sf package
+###----
+
+# centroid.sf <- st_as_sf(centroid, coords=c("long", "lat"), crs=st_crs(world))
+# library(sfheaders)
+# mergedArea.sf <- sfheaders::sf_polygon(  obj = mergedArea
+#                                          , x = "long"
+#                                          , y = "lat"
+#                                          , polygon_id = "group"
+# )
+# sf::st_crs(mergedArea.sf) <- st_crs(world)
+# 
+# #Readd colour
+# mergedArea.sf$colour <- unique(mergedArea[,c(7,8)])[,2]
 #   mergedArea, coords=c("long", "lat"), crs=st_crs(world))
 # st_cast(mergedArea.sf, to="POLYGON")
-
-map <- map +
-  geom_sf(data = mergedArea.sf, aes(fill = colour)) +
-  geom_sf_label(data = centroid.sf, aes(label = 1:nrow(centroid)),
-             fill = c(colourArea[11], colourArea[12], rep("white", times=10)),
-             col = c("black", "white", rep("black", times=10)),#colourArea[3:12]),
-             nudge_y=centroid$nudge_y,
+#
+
+library(ggmap)
+library(scales)
+
+#Getting the stammen background map and adding the graticule
+mapStammen <- get_stamenmap( bbox = c(left = -180, bottom = -66, right = 180, top = 66), zoom = 4, maptype = "watercolor")#maptype = "terrain-background")
+# plot(mergedArea.sf, add=TRUE)
+mapPlot <- ggmap(mapStammen) #+
+  # theme_void() +
+  # theme(
+  #   panel.border = element_rect(colour = "white", fill=NA, size=2)
+  # )
+for(k in 0:max(as.numcharac(grat_df$id))){
+mapPlot <- mapPlot +
+  geom_path(data = grat_df %>% filter(as.numcharac(id)==k), aes(x=long, y=lat), colour="white", linetype="dashed")
+}
+
+#Adding the coloured cropped polygons of areas
+for(i in 1:length(areaName)){
+  polygonToAdd <- get(paste("area", i, sep="_"))
+
+  for(j in 1:length(polygonToAdd@polygons[[1]]@Polygons)){#Some problem with fortified when multiple polygons. Trying using one sub-polygon at a time.
+    toPlot <- sp::Polygons(list(polygonToAdd@polygons[[1]]@Polygons[[j]]), ID = "A")
+    toPlot <- sp::SpatialPolygons(list(toPlot))
+      fortifiedArea <- fortify(toPlot)
+      mapPlot <- mapPlot + geom_polygon(data = fortifiedArea, aes(x = long, y= lat), fill=colourArea[i], col=colourArea[i], lwd=0.5) +
+          geom_label(data = centroid[i,], aes(x=long, y=lat), label=(1:length(colourArea))[i],
+             fill = ifelse(i != 1 & i != 2, "white", colourArea[i]),
+             col = "black",
+             nudge_y=centroid$nudge_y[i],
              label.r = unit(0.4, "lines"),
-             size = 2) +
-  coord_sf(crs = proj.map, expand = F) +
-  scale_fill_manual(values = colourArea, labels=c("Central Africa", "South/East Africa", "West Africa", "Central America", "North of South America", "South of South America", "Central/East Asia", "Asian islands", "South Asia", "West Asia", "East Madagascar", "West Madagascar")) +
-  labs(fill = "")  +
+             size = 2) 
+  }
+}
+mapPlot <- mapPlot +
+  # scale_color_manual(name='',
+  # breaks=c(
+  # "East Madagascar",
+  # "West Madagascar",
+  # "West Africa",
+  # "Central Africa",
+  # "East/South Africa",
+  # "Central America",
+  # "Northern South America",
+  # "Southern South America",
+  # "West Asia",
+  # "Central/East Asia",
+  # "South Asia",
+  # "Asian islands"),
+  # values=c(
+  # "East Madagascar"=colourArea[1],
+  # "West Madagascar"=colourArea[1],
+  # "West Africa"=colourArea[1],
+  # "Central Africa"=colourArea[1],
+  # "East/South Africa"=colourArea[1],
+  # "Central America"=colourArea[1],
+  # "Northern South America"=colourArea[1],
+  # "Southern South America"=colourArea[1],
+  # "West Asia"=colourArea[1],
+  # "Central/East Asia"=colourArea[1],
+  # "South Asia"=colourArea[1],
+  # "Asian islands"=colourArea[1])
+  # )+
     theme(
@@
         legend.key.size = unit(1, 'lines'),
-        legend.position="bottom")
-map
-
+        legend.position="bottom",
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=15,face="bold")
+        ) +
+  xlab("Longitude") +
+  ylab("Latitude") +
+  scale_x_continuous(breaks = c(seq(from=-165, to=-15, by=30), 0, seq(from=15, to=165, by=30)), expand = c(0, 0))# +
+  #scale_y_continuous(breaks = pretty(-66:66, n = 10))
+
+library(cowplot)
+# Create grid of plots
+plot_grid(mapPlot, 
+          my_legend,
+          ncol = 1,
+          rel_heights = c(2.25,1))
+
+##--------
+###OLD WAY
+##-------
+
+# map <- map +
+#   geom_sf(data = mergedArea.sf, aes(fill = colour)) +
+#   geom_sf_label(data = centroid.sf, aes(label = 1:nrow(centroid)),
+#              fill = c(colourArea[11], colourArea[12], rep("white", times=10)),
+#              col = c("black", "white", rep("black", times=10)),#colourArea[3:12]),
+#              nudge_y=centroid$nudge_y,
+#              label.r = unit(0.4, "lines"),
+#              size = 2) +
+#   coord_sf(crs = proj.map, expand = F) +
+#   scale_fill_manual(values = colourArea, labels=c("Central Africa", "South/East Africa", "West Africa", "Central America", "North of South America", "South of South America", "Central/East Asia", "Asian islands", "South Asia", "West Asia", "East Madagascar", "West Madagascar")) +
+#   labs(fill = "")  +
+#   theme(
+#         text = element_text(size = 10),
+#         legend.key = element_rect(size = 4),
+#         legend.key.size = unit(1, 'lines'),
+#         legend.position="bottom")
+# map
 # # #Just to see the difference as pinpointed by the warning
@@
 
-```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Current frugivorous primate sympatry pattern and phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
+```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels of sympatry significantly vary across the primate phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
 The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
@@
 
-```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("(Left) EQ or relative brain size value among frugivorous primates (Right) Studied brain areas | (Left) The circular rows are indicated by the colours which match a specific brain area.
+<!-- A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]). The arrows indicate the sagital and frontal axes.  -->
+<!-- , although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere -->
+```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) The circular rows are indicated by the colours which match a specific brain area.
 The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.
@@
 The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%.
-(Right) A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]).
-The arrows indicate the sagital and frontal axes.
-Studied brain area are coloured, although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere.
+(Right) The different studied brain areas.
 In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation processes [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
@@
 library(RColorBrewer)
+
+colourEQ <- "gray"
+colourEQbis <- "lightgray"
+colourEQdark <- "black"
+
+colourHippocampus <- rgb(0,128,0,maxColorValue = 255)
+colourHippocampusbis <- rgb(95,211,95,maxColorValue = 255)#pastellize(colourHippocampus)
+colourHippocampusdark <- rgb(0,208,0,maxColorValue = 255)
+
+colourStriatum <- rgb(255,204,0,maxColorValue = 255)
+colourStriatumbis <- rgb(255,230,128,maxColorValue = 255)#pastellize(colourStriatum)
+colourStriatumdark <- "darkgoldenrod2"
+
+colourNeocortex <- rgb(255,213,213,maxColorValue = 255)
+colourNeocortexbis <- "white"#rgb(255,213,213,maxColorValue = 255)#pastellize(colourNeocortex)
+colourNeocortexdark <- rgb(255,175,175,maxColorValue = 255)
+
+colourCerebellum <- rgb(255,128,128,maxColorValue = 255)
+colourCerebellumbis <- rgb(255,170,170,maxColorValue = 255)#pastellize(colourCerebellum)
+colourCerebellumdark <- rgb(255,64,64,maxColorValue = 255)
+
+colourMOB <- rgb(255,0,0,maxColorValue = 255)
+colourMOBbis <- rgb(255,95,95,maxColorValue = 255)#pastellize(colourMOB)
+colourMOBdark <- "darkred"
+
 colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
 colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
-colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
+colour.circle.points <- c("black", "darkred", "darkblue", "purple4", "darkgreen", "orange4")
 
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
+circos.track(ylim = c(0, 1), bg.border = colourEQ, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourEQ, border=colourEQ)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
+circos.track(ylim = c(0, 1), bg.border = colourEQbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourEQbis, border=colourEQbis)
 }, track.height = 1/15)
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
+circos.track(ylim = c(0, 1), bg.border = colourStriatum, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourStriatum, border=colourStriatum)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
+circos.track(ylim = c(0, 1), bg.border = colourStriatumbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourStriatumbis, border=colourStriatumbis)
 }, track.height = 1/15)
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
+circos.track(ylim = c(0, 1), bg.border = colourHippocampus, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourHippocampus, border=colourHippocampus)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
+circos.track(ylim = c(0, 1), bg.border = colourHippocampusbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourHippocampusbis, border=colourHippocampusbis)
 }, track.height = 1/15)
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
+circos.track(ylim = c(0, 1), bg.border = colourMOB, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourMOB, border=colourMOB)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
+circos.track(ylim = c(0, 1), bg.border = colourMOBbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourMOBbis, border=colourMOBbis)
 }, track.height = 1/15)
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
+circos.track(ylim = c(0, 1), bg.border = colourCerebellum, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourCerebellum, border=colourCerebellum)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
+circos.track(ylim = c(0, 1), bg.border = colourCerebellumbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourCerebellumbis, border=colourCerebellumbis)
 }, track.height = 1/15)
@@
 #Background
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
+circos.track(ylim = c(0, 1), bg.border = colourNeocortex, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourNeocortex, border=colourNeocortex)
 }, track.height = 1/15)
 
-circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
+circos.track(ylim = c(0, 1), bg.border = colourNeocortexbis, panel.fun = function(x, y) {
+  circos.rect(0, 0, 1, 1, col=colourNeocortexbis, border=colourNeocortexbis)
 }, track.height = 1/15)
@@
     if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+      #circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colourEQdark, cex=0.7)
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
     }
     else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
+      #circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colourEQdark, bg="white", cex=0.7)
+      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
     }
@@
     if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colourEQdark, cex=0.7)
     }
     else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colourEQdark, bg="white", cex=0.7)
     }
@@
     if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colourStriatumdark, cex=0.65)
     }
     else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colourStriatumdark, bg="white", cex=0.65)
     }
@@
     if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colourStriatumdark, cex=0.65)
     }
     else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colourStriatumdark, bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Hippocampus
+absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueHippocampus[i])){}  else{
+    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colourHippocampusdark, cex=0.55)
+    }
+    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colourHippocampusdark, bg="white", cex=0.55)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueHippocampus[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colourHippocampusdark, cex=0.55)
+    }
+    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colourHippocampusdark, bg="white", cex=0.55)
     }
@@
 absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
   i=CELL_META$sector.numeric.index
@@
     if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colourMOBdark, cex=0.65)
     }
     else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colourMOBdark, bg="white", cex=0.65)
     }
@@
 
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
   i=CELL_META$sector.numeric.index
@@
     if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colour.circle.points[3], cex=0.65)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colourMOBdark, cex=0.65)
     }
     else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colour.circle.points[3], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colour.circle.points[3], bg="white", cex=0.65)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colourMOBdark, bg="white", cex=0.65)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+#Cerebellum
+absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
+  if(is.na(relativeValueCerebellum[i])){}  else{
+    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colourCerebellumdark, cex=0.5)
+    }
+    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colourCerebellumdark, bg="white", cex=0.5)
+    }
+    else{}
+  }
+}, track.height = 0.1)
+
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
+  i=CELL_META$sector.numeric.index
+  if(is.na(relativeValueCerebellum[i])){}  else{
+    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
+    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colourCerebellumdark, cex=0.5)
+    }
+    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colourCerebellumdark, bg="white", cex=0.5)
     }
@@
 absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
   i=CELL_META$sector.numeric.index
@@
     if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colourNeocortexdark, cex=0.6)
     }
     else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
+      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
+      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colourNeocortexdark, bg="white", cex=0.6)
     }
@@
 
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
+circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
   i=CELL_META$sector.numeric.index
@@
     if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colour.circle.points[4], cex=0.6)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colourNeocortexdark, cex=0.6)
     }
     else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colour.circle.points[4], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colour.circle.points[4], bg="white", cex=0.6)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Hippocampus
-absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colour.circle.points[5], cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colour.circle.points[5], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colour.circle.points[5], bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Cerebellum
-absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colour.circle.points[6], cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colour.circle.points[6], lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colour.circle.points[6], bg="white", cex=0.5)
+      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
+      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colourNeocortexdark, bg="white", cex=0.6)
     }
@@
 par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
-     xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
-
-# #Add brain
+emptyPlot()
+# plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
+#      xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
+# 
+#Add brain
  library(png)
-brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/3dplot.png")
-addImg(brainIMG, x = 0.425, y = 0.65, width = 1.3)
-
-#Add circle contour
-draw.circle(x=0.45,y=0.55,0.435, col=NA, border="lightgray", lwd=2)
-draw.circle(x=0.45,y=0.55,0.405, col=NA, border="lightgray", lwd=2)
+brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/brain_draw.png")
+addImg(brainIMG, x = 0.425, y = 0.5, width = 0.7)
+
+# brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/3dplot.png")
+# addImg(brainIMG, x = 0.425, y = 0.65, width = 1.3)
+# 
+# #Add circle contour
+# draw.circle(x=0.45,y=0.55,0.435, col=NA, border="lightgray", lwd=2)
+# draw.circle(x=0.45,y=0.55,0.405, col=NA, border="lightgray", lwd=2)
+# 
+# par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+# plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
+#      xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
+# colourHip=colourHippocampus
+# colourCereb=colourCerebellum
+# colourOlf=colourMOB
+# colourStri=colourStriatum
 
 par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
-     xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
-
-colourHip=colourVector[5]
-colourCereb=colourVector[6]
-colourOlf=colourVector[3]
-colourStri=colourVector[2]
-
-legend(x=0.1, y=0.8, legend = c("EQ", "Striatum", "MOB",  "Hippocampus", "Neocortex", "Cerebellum", "Frugivorous species", "Folivorous species"), cex = 1, fill = c(colourVector, NA, NA), pch=c(NA, NA, NA, NA, NA, NA, 19, 1), border=c("black", "black", "black", "black", "black", "black", "white", "white"), col=c(NA, NA, NA, NA, NA, NA, "black", "black"), bty="n", seg.len=0.75)
+emptyPlot()
+legend(x=0.1, y=1, yjust=1, legend = c("EQ", "Striatum", "Hippocampus", "MOB", "Cerebellum", "Neocortex", "Frugivorous species", "Folivorous species"), cex = 1, fill = c(colourEQ, colourStriatum, colourHippocampus, colourMOB, colourCerebellum, colourNeocortex, NA, NA), pch=c(NA, NA, NA, NA, NA, NA, 19, 1), border=c("black", "black", "black", "black", "black", "black", "white", "white"), col=c(NA, NA, NA, NA, NA, NA, "black", "black"), bty="n", seg.len=0.75)
 
@@
 
-```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="Relative support of fitted models of trait evolution for each brain part | Plotted is the AICc weight, a measure of relative support for a given model, for non-competitive (BM, OU, EB) and competitive (MC, DD$_{lin}$, DD$_{exp}$) models.
+```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the size of foraging-related brain areas is best fitted by models considering sympatry of trait evolution in frugivorous primates | Plotted is the AICc weight, a measure of relative support for a given model, for models discarding sympatry (BM, OU, EB) and considering sympatry (MC, DD$_{lin}$, DD$_{exp}$).
 The points represent the average AICc weight obtained (when considering the six models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does interspecific interactions shape brain size evolution?])."}
 
-layout(mat=rbind(c(1,2,3), c(4,5,6)), widths=c(5,5,5), heights=c(5,5))
+layout(mat=rbind(c(1,2,3), c(4,5,6), c(7,7,7)), widths=c(5,5,5), heights=c(5,5,1))
 par(mar=c(3.5, 3, 2, 0.5), mgp=c(2, 0.5, 0), xpd=TRUE)
@@
 plot(
-  x=0, y=0, xlab="", ylab="AICc weight", cex.sub=1.6,
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
   xlim=c(0,7), ylim=c(0,1.2),
@@
 
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
 addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
 axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+mtext(side=2, line=2, at=0.5, text="AICc weight", cex=1)
+
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
 
@@
   errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
 
@@
        round(mean(as.numcharac(summaryEQFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
-
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[1], border=NA)
-text(x=0.3, y=1.1, labels="1", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="EQ", xpd=TRUE, col="black", font=2, cex=1.5)
+     ), cex=0.85, xpd=TRUE)
+
+draw.circle(x=0.3,y=1.1,0.35, col=colourEQ, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="1", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="EQ", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
 
@@
 
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
 addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
 #axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[2])
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8, xpd=TRUE)
+#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourStriatum)
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.75, xpd=TRUE)
 for(i in 1:6){
@@
   errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[2], border=NA)
-text(x=0.3, y=1.1, labels="2", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="Striatum", xpd=TRUE, col="black", font=2, cex=1.5)
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.35, col=colourStriatum, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="2", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="Striatum", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
 
@@
        round(mean(as.numcharac(summaryStriatumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
+     ), cex=0.85, xpd=TRUE)
 
@@
 
-##-------------
-#MOB
+##------------
+
+#Hippocampus
 
@@
 
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
 addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[3])
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
+# axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryHippocampusFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.35, col=colourHippocampus, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="4", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="Hippocampus", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryHippocampusFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryHippocampusFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.85, xpd=TRUE)
+##------------
+
+##-------------
+#MOB
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+mtext(side=2, line=2, at=0.5, text="AICc weight", cex=1)
+#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourMOB)
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
 for(i in 1:6){
@@
   errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[3], border=NA)
-text(x=0.3, y=1.1, labels="3", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="MOB", xpd=TRUE, col="black", font=2, cex=1.5)
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.35, col=colourMOB, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="3", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="MOB", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
 
@@
        round(mean(as.numcharac(summaryMOBFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
+     ), cex=0.85, xpd=TRUE)
 ##------------
 
-##------------
-
-#Hippocampus
-
-plot(
-  x=0, y=0, xlab="", ylab="AICc weight", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryHippocampusFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[4], border=NA)
-text(x=0.3, y=1.1, labels="6", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="Hippocampus", xpd=TRUE, col="black", font=2, cex=1.5)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryHippocampusFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryHippocampusFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
-##------------
-
 ##-------------
-#Neocortex
+#Cerebellum
 
@@
 
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
 addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
 #axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[5])
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8, xpd=TRUE)
+#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourCerebellum)
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
+for(i in 1:6){
+
+  meanPt <- mean(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
+  sd <- sd(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
+  #sd <- sd/nrow(summaryCerebellumFrugivory) #error not sd
+  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.35, col=colourCerebellum, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="6", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="Cerebellum", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
+
+#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#add their values below:
+
+text(x=c(4,5,6), y=c(-0.2, -0.2),
+     labels=c(
+       "r ~",
+       round(mean(as.numcharac(summaryCerebellumFrugivory$DDlingeo.b)), digit=3),
+       round(mean(as.numcharac(summaryCerebellumFrugivory$DDexpgeo.r)), digit=3)
+     ), cex=0.85, xpd=TRUE)
+###----------------------
+
+##-------------
+#Neocortex
+
+plot(
+  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
+  xlim=c(0,7), ylim=c(0,1.2),
+  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
+  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
+
+rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
+rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
+
+addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
+#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
+#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourNeocortex)
+segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
+text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.75, xpd=TRUE)
 for(i in 1:6){
@@
   errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[5], border=NA)
-text(x=0.3, y=1.1, labels="5", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="Neocortex", xpd=TRUE, col="black", font=2, cex=1.5)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
+
+}
+draw.circle(x=0.3,y=1.1,0.35, col=colourNeocortex, border=NA)
+#text(x=0.3, y=1.1, cex=1.15, labels="5", xpd=TRUE, col="white", font=2)
+text(x=0.75, y=1.1, labels="Neocortex", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
+
+#b and r are the rate for density dependence (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
 #add their values below:
@@
        round(mean(as.numcharac(summaryNeocortexFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
+     ), cex=0.85, xpd=TRUE)
 
@@
 
-##-------------
-#Cerebellum
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colNum[6])
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.8,  xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryCerebellumFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col=colourModels[i], xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.25, col=colNum[6], border=NA)
-text(x=0.3, y=1.1, labels="7", xpd=TRUE, col="white", font=2)
-text(x=3.5, y=1.1, labels="Cerebellum", xpd=TRUE, col="black", font=2, cex=1.5)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryCerebellumFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryCerebellumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.75, xpd=TRUE)
-###----------------------
+par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
+emptyPlot()
+legend(x=0.25, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("NO species interaction", "Species interaction"), bty="n", cex=1.35)
 ```
@@
 
-```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Supplementary Figure.
-Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
+```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
 indicates the frugivory rate and Fol.
@@
 (C) Repeatability: Repeatability was assessed for traits that were included in at least three datasets.
-Prior calculation, traits were pondered *within* species by the *within* species max value.
+Before calculation, traits were pondered *within* species by the *within* species max value.
 The point represents the mean repeatability $r$ calculated as $\\sigma^{2}_{between}/(\\sigma^{2}_{between}+\\sigma^{2}_{within})$, with the $\\sigma^{2}_{between}$ and $\\sigma^{2}_{within}$ corresponding the variance *between* or *within* species.
@@
 
-colourWhatCompared <-  c("gray", brewer.pal(n = 9, name = "Pastel1")[c(1:5)], "black", brewer.pal(n = 9, name = "Pastel1")[7])#c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
+colourWhatCompared <-  c("gray", colourHippocampusbis, colourNeocortexbis, colourCerebellumbis, colourStriatumbis, "orange", "black", "lightgray")#c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
 
@@
 summarySensitivityGradient <- summarySensitivityGradient[-(1:4),]
+summarySensitivityGradient[,1] <- gsub("Overlap", "\\% of overlappend range", summarySensitivityGradient[,1])
+summarySensitivityGradient[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivityGradient[,1])
+
 rownames(summarySensitivityGradient) <- NULL
 knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between speies sympatry and relative brain sizes | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the relationship between species diversifition and relative brain sizes| Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 ```{r tabledfsensitivity3, include=TRUE}
+summarySensitivitydiversificationAndSympatry[,1] <- gsub("Overlap", "\\% of overlappend range", summarySensitivitydiversificationAndSympatry[,1])
+summarySensitivitydiversificationAndSympatry[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivitydiversificationAndSympatry[,1])
+
 knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the selection diversificationAndSympatry direction | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data)") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data)") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%

### 2021-12-02 Article/Coverletter.Rmd
Revision intro + figures + discussion + citation (all in exponent)

@@
 #word_document
+geometry: "left=3cm,right=3cm,top=1cm,bottom=2cm"
 
@@
 \begin{flushright}
-On the `r Sys.Date()`
+\faEnvelope \hspace{0.01in} \href{mailto:benjamin.robira@normalesup.org}{benjamin.robira@normalesup.org}\\
+\faHome \hspace{0.01in} Université de Montpellier/CEFE/CNRS\\
+\faMapPin \hspace{0.01in} 1919, route de Mende, 34293 Montpellier cedex 5\\
+
+\hfill
+
+On the `r Sys.Date()`,\\
+
 \end{flushright}
@@
 
-|   The road to understanding the evolutionary history and significance of cognition is still little paved.
-Currently formulated theories generally oppose social to ecological drivers of cognition and are oten framed within a foraging-related context.
-These theories, nonetheless, give a priority to the challenges an individual faces with regards to its ecological environment, or its conspecifics from a same group and/or species.
-Yet, space is also shared with other species that might also shape the environment and be competitors or cooperators.
-Thus, it is likely that cognate species, with which dietary overlap occurs, are likely to affect the social and ecological environment a species evolves in.
-This should loop onto the selective pressures that apply to cognition.
+|   The road to understanding the evolutionary history of cognition is still little paved.
+Currently formulated theories generally oppose social and ecological drivers of cognition and are often framed within a foraging-related context.
+These theories, nonetheless, primarily focus on the challenges an individual faces with regards to its food spatio-temporal distribution, or to its conspecifics from a same group and/or species.
+Space is also shared with other species with similar ecological niche that might also shape the environment and be competitors or cooperators.
+Thus, it is likely that cognate species that share diet are likely to affect the social and ecological environment a species evolves in.
+This should therefore loop onto the selective pressures that apply to cognition.
 This facet remained unexplored.
 
-|   To help filling this gap, we provide a meta-analysis to investigate the role of sympatry in shaping animals' the size of different brain areas, and animals' evolutionary success.
+|   To help filling this gap, we perform a global-scale analysis to investigate the role of sympatry in shaping the size of different brain areas in animals, and shaping their evolutionary success.
 In particular, we focus on frugivorous primates because the consumption of fruits is highly tightened to advanced cognitive skills.
-Using recently developed evolutionary phylogenetic models accounting for competition or not with sympatric species, we retrace the evolution of the size of brain areas related to foraging or note.
+Using recently developed phylogenetic models accounting for competition or not with sympatric species, we retrace the evolution of the size of brain areas related to foraging or not.
 We also correlate brain size, diversification rate (a proxy for evolutionary success), and sympatry intensity.
 
-|  We show that the evolutionary history of brain areas associated to foraging tasks is more accurately summarised when using competitive models.
+|  We show that the evolutionary history of brain areas associated to foraging tasks is more accurately described by competitive models.
 In particular, sympatry negatively affects their relative size.
-We additionally show that, despite these brain sizes are not related to diversification rate, this latter is reduced when sympatry rates increases.
+We additionally show that, even if these brain sizes are not related to diversification rate, this latter is reduced when sympatry rates increases.
 Altogether, these findings suggest that sympatry is associated to a relaxed selection for bigger brain, or even a positive selection for smaller brain.
-We speculate that this is due to an overcomplexification of the environment.
+We speculate that this is due to an over-complexification of the environment, which makes cognition not advantageous anymore.
 
-|  This study enlarges our understanding on the effect of space use and distribution in animal cognition, and show unprecedent evidence of direct and/or inderect effect of competition on cognition evolution, questioning proximate mechanisms at play.
-We strongly believe that this stands as an important complementary piece of meta-analyses that were already published in your journal that will be of interest to empiricists and theoreticians from ecological and evolutionary fields.
+|  This study enlarges our understanding on the effect of space use and species distribution in animal cognition.
+It shows unprecedent evidence of direct and/or indirect effect of competition on cognition evolution, questioning proximate mechanisms at play.
+We strongly think that this stands as an important complementary piece of global analyses that were already published in your journal that will be of interest to empiricists and theoreticians from ecological and evolutionary fields.
 On behalf of all authors, I certify that this is a completely novel contribution that has not been submitted elsewhere, and that all authors approved the manuscript and its submission to *`r journal`*.
@@
 Benjamin Robira, on behalf of all authors.\\
-\faEnvelope \hspace{0.01in} \href{mailto:benjamin.robira@normalesup.org}{benjamin.robira@normalesup.org}\\
+
 \vspace{0.1in}

### 2021-12-02 Article/Article.Rmd
Revision intro + figures + discussion + citation (all in exponent)

@@
 
-```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Natural Earth projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
+```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Mercator projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
 Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].

### 2021-12-03 Article/Article.Rmd
Changes in the intro abstract and discussion

@@
 **Abstract |** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
-Yet, space is a place often occupied by many species, sometimes belonging to the same ecological guild.
-These sympatric heterospecifics can act as competitors or cooperators, thereby shaping cognition.
-They can provide new cues to infer food presence, or impoverish the environment, stimulating the need of cognition.
-They can also make the environment poorly predictable, thereby alleviating the benefit of cognition.
+Yet, space is a place often simultaneously occupied by species sharing the same ecological guild.
+These sympatric heterospecifics can compete for food, thereby stimulating or hampering cognition.
 Considering brain size as a proxy for cognition, we used primates to test for the intertwine between species sympatry and cognition.
-We retraced the evolutionary history of several brain areas with evolutionary scenarios considering or discarding sympatry.
-We found that evolutionary scenarios considering sympatry best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their relative size the higher the sympatry rate.
+We retraced the evolutionary history of several brain areas with evolutionary scenarios considering or not sympatry.
+Sympatry-related evolutionary scenarios best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
 By contrast, the whole brain or brain areas used in immediate information processing were best described by evolutionary models not considering sympatry.
-Moreover, sympatry negatively affected primate diversification which was unrelated to the size of the studied brain areas.
-Overall, this comparative study suggests that species sympatry contributes to shaping the selective pressure acting upon primate cognition and diversification.
+Moreover, sympatry negatively affected primate diversification.
+Overall, this comparative study suggests that species sympatry contributes to shaping primate cognition and diversification.
 We speculate that this is due to an over-complexification of resource spatio-temporal pattern.
@@
 
-\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Intelligence evolution - Primates - Sympatry
+\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
 
@@
 
-\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
+\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics].
 Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
 However, space is a place often occupied by many species belonging to the same ecological guild.
-We can predict that interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition.
-Heterospecifics can act as indirect competitors for food (Hypothesis 1) and might also be indirect cooperators, providing cues on food location and availability (Hypothesis 2, e.g.
+Because of indirect competition for food, we can predict that interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, either because they affect the resource landscape (Hypothesis 1), or the landscape of usable cues to locate available food (Hypothesis 2; e.g.
 [@olupot1998fruit]).
@@
 These areas are likely to be under different selective pressures, and thus, to be differently affected by species sympatry.
-Brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected under the competitive hypothesis (Hypothesis 1).
-Brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] should be particularly affected under the cooperative hypothesis (Hypothesis 2).
+Brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape greatly varies with sympatry (Hypothesis 1).
+Brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2).
 
 |   Under both of the two (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
-On the one hand, species co-occurrence could contribute to increasing food depletion and reducing food predictability because of unforeseen depletion by heterospecifics, two facts that might imply the use cognitive abilities for inferring food location and availability [@grove2013evolution; @robirainreview].
-Thus, under hypothesis 1, because of reasonable environmental complexification due to heterospecifics, the size of the area such as the Hippocampus should eventually be larger (Prediction 1.1).
-Heterospecifics might also leave traces of presence or passage that can lead to available food.
-These cues might add to environmentally used ones.
-This should thus stimulate areas involved in general and immediate information processing.
-Thus, under hypothesis 2, due to an additive effect of heterospecifics cues over environmental cues, the size of areas such as the MOB, the Cerebellum or the Neocortex should be larger (Prediction 2.1).
-
-|   On the other hand, if changes induced by sympatric species increase environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution; @robirainreview].
-Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
-positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory).
-Thus, under hypothesis 1, in case of an over-complexification of the environment, the Hippocampus size should be smaller (Prediction 1.2).
-Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g.
-phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social].
-It has indeed been shown that individuals tend to use social or environmental cues depending on their reliability [@rafacz2003environmental; @dunlap2016foraging], favouring social cues in particular when environmental cues are too noisy.
-Thus, under hypothesis 2 and an exclusion effect of heterospecifics cues over environmental cues, the size of the MOB, the Cerebellum or the Neocortex should be smaller (Prediction 2.2).
-
-|   While cognition can be intensively shaped under the rationale centred around resource harvesting [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
-The Striatum is stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]) and should not be affected under indirect competition or cooperation with heterospecifics.
-It can thus serve as as a null comparative area.
-Considering the Striatum as only social-related is however reductive, as the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
-Thus, very important evolutionary pressure on energetic optimisation might also shape the Striatum size equivalently to the Hippocampus.
-
-|   Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
+Reasonable food depletion should promote cognition which stands as a valuable tool to infer food availability and location when food is rare and ephemeral but predictable [@grove2013evolution; @robirainreview].
+In this case, the size of the Hippocampus should be larger (Prediction 1.1).
+On the other hand, maintaining the brain functional has important energetic consequences [@raichle2006brain].
+Thus, if changes induced by sympatric species increase environmental unpredictability too much, rendering cognitive foraging less efficient [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller (Prediction 1.2).
+
+|   "Social" cues left out by heterospecifics might add to environmental ones.
+This supplementary load of cues could stimulate areas involved in general and immediate information processing.
+We should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex (Prediction 2.1).
+Yet, social and environmental cues might not necessarily add, and foragers might choose one or the other.
+In particular, it has been shown that foragers tend to use social information over environmental (i.e.
+personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
+Thus, the presence of heterospecific competitors might simplify the track and processing of immediate cues to locate food.
+From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should be smaller (Prediction 2.2).
+
+|   While cognition can be intensively shaped under the rationale centered around resource harvesting [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
+The Striatum is stimulated during social interactions [@baez2013role]: its size is expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups.
+yet, mixed-group species is rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]).
+This social area should thus be little affected by heterospecifics.
+It can eventually serve as a null comparative area.
+
+|   Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as a study example.
 Frugivorous primates are an interesting group for such a question because fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio], for which cognition thus considerably shapes the foraging strategy [@trapanese2019and].
@@
 
-|   In order to get the evolutionary history of sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`, [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
+|   In order to get the evolutionary history of sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
 We then calculated the likelihoods of models considering the role of species interactions (matching competition MC models, [@nuismer2015predicting]; models of linear or exponential density dependence, DD$_{lin}$ and DD$_{exp}$, of the evolutionary rate on the number of sympatric lineages; [@drury2016estimating] see [Models of trait evolution: does interspecific interactions shape brain size evolution?]) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
-\@ref(fig:figbrain)) and compared their likelihood to those of simpler models assuming no effect of species interactions, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
+\@ref(fig:figbrain)).
+We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
 stabilizing selection; see [@blomberg2020beyond] for a review) or the Early-Burst model (EB, [@blomberg2003testing]), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
@@
 The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefices of brain development [@isler2009expensive].
-By contrast, models considering sympatry were most supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, [@burgess2002human]) or planning abilities and reward assessment (Striatum, [@baez2013role; @johnson2007integrating]), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
+By contrast, models considering sympatry were best supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, [@burgess2002human]) or planning abilities and reward assessment (Striatum, [@baez2013role; @johnson2007integrating]), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
 When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased diversity of sympatric lineages for the Hippocampus and the Striatum, but a slowdown for the MOB.
@@
 In fact, a sudden encephalisation in primates is clearly associated to a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically-corrected analyses as we cannot decipher whether the connivence between brain size and evolutionary success results from a true biological link or appeared by chance.
+This clearly limits the statistical power of our phylogenetically-corrected analyses as we cannot decipher whether the connivance between brain size and evolutionary success results from a true biological link or appeared by chance.
 A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
@@
 In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification, a density-dependendence trend that is frequently suggested in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
+In other words, the higher the number of sympatric species, the lower the diversification, a density-dependence trend that is frequently observed in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
 
@@
 
-The bigger is not necessarily the better.
+Bigger brains are not necessarily better.
 The size of the brain is subject to a compromise between the energy it incurs, and the increase of fitness it allows.
@@
 These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
-The fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
-By contrast, potential indirect cooperation between species (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in general information processing (e.g.
+The influence of sympatry on the Striatum is surprising, because mixed-species groups are rather infrequent in primates.
+Yet, when interacting with conspecifics, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating], a key thing within group and in a Machiavellian perspective [@byrne1994machiavellian].
+It is thus possible that actions underpinned by the Striatum (e.g.
+planning/anticipating heterospecifics move) might be key, and up to now overlooked, when foraging in a multi-species context too.
+Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
+By contrast, potential indirect facilitation between species (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in general and immediate information processing (e.g.
 Cerebellum or Neocortex).
@@
 In particular, the acceleration of the evolutionary tempo (i.e.
-the effect size associated to density dependence terms is positive) suggests that it is not limited to a relax of positive selection for bigger brains, but to a positive selection for smaller brains.
+the slope associated to density dependence terms is positive) suggests that it is not limited to a relax of positive selection for bigger brains, but to a positive selection for smaller brains.
 
@@
 In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
-These observations thus strengthen our view on indirect species interaction by scramble competition which might cascade both on population dynamics and species cognition.
+These observations thus strengthen the idea of scramble competition between species that cascades both on population dynamics and species cognition.
 
@@
 Data processing, analyses, and plots were computed with R software [`r extractRversion()`, @Rsoftware].
-Used codes and data are freely available at [https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency](https://github.com/benjaminrobira/Temporal_memory_and_foraging_efficiency).
+Used codes and data are freely available at [https://github.com/benjaminrobira/Meta_analysis_cognition_primates](https://github.com/benjaminrobira/Meta_analysis_cognition_primates).
 Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*, this latter being too geographically isolated.
@@
 axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-mtext(side=2, line=2, at=0.5, text="AICc weight", cex=1)
+mtext(side=2, line=2, at=0.5, text="AICc weight", cex=0.85)
 
@@
        round(mean(as.numcharac(summaryEQFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 
@@
        round(mean(as.numcharac(summaryStriatumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 
@@
        round(mean(as.numcharac(summaryHippocampusFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 ##------------
@@
 axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-mtext(side=2, line=2, at=0.5, text="AICc weight", cex=1)
+mtext(side=2, line=2, at=0.5, text="AICc weight", cex=0.85)
 #segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourMOB)
@@
        round(mean(as.numcharac(summaryMOBFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 ##------------
@@
        round(mean(as.numcharac(summaryCerebellumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 ###----------------------
@@
        round(mean(as.numcharac(summaryNeocortexFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.85, xpd=TRUE)
+     ), cex=0.8, xpd=TRUE)
 

### 2021-12-08 Article/Article.Rmd
Update main text

@@
 
-<!-- TO CREATE GRAY BOX -->
+<!-- TO CREATE grey BOX -->
 
@@
 **Abstract |** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
-Yet, space is a place often simultaneously occupied by species sharing the same ecological guild.
+Yet, space is often simultaneously occupied by species sharing the same ecological guild.
 These sympatric heterospecifics can compete for food, thereby stimulating or hampering cognition.
-Considering brain size as a proxy for cognition, we used primates to test for the intertwine between species sympatry and cognition.
-We retraced the evolutionary history of several brain areas with evolutionary scenarios considering or not sympatry.
-Sympatry-related evolutionary scenarios best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
-By contrast, the whole brain or brain areas used in immediate information processing were best described by evolutionary models not considering sympatry.
+Considering brain size as a proxy for cognition, we used primates to test for the intertwining between species sympatry and cognition.
+We retraced the evolutionary history of several brain areas with evolutionary models considering or not sympatry.
+Sympatry-related models best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
+By contrast, the whole brain or brain areas used in immediate information processing were best described by models not considering sympatry.
 Moreover, sympatry negatively affected primate diversification.
 Overall, this comparative study suggests that species sympatry contributes to shaping primate cognition and diversification.
-We speculate that this is due to an over-complexification of resource spatio-temporal pattern.
+We speculate that this is due to an over-complexification of resource spatio-temporality.
 
@@
 Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
-However, space is a place often occupied by many species belonging to the same ecological guild.
-Because of indirect competition for food, we can predict that interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, either because they affect the resource landscape (Hypothesis 1), or the landscape of usable cues to locate available food (Hypothesis 2; e.g.
-[@olupot1998fruit]).
+However, space is often occupied by many species belonging to the same ecological guild.
+Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food (Hypothesis 2).
+For instance, wild grey-cheeked mangabeys (*Lophocebus albigena*) increase targeting towards fruit trees from which black-and-white-casqued hornbill (*Bycanistes subcylindricus*) calls can be heard  [@olupot1998fruit].
 
@@
 These areas are likely to be under different selective pressures, and thus, to be differently affected by species sympatry.
-Brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape greatly varies with sympatry (Hypothesis 1).
-Brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2).
-
-|   Under both of the two (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
+First, brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape is complexified by sympatric species foraging on the same resource (Hypothesis 1).
+Second, brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2).
+
+|   Under these two (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
 Reasonable food depletion should promote cognition which stands as a valuable tool to infer food availability and location when food is rare and ephemeral but predictable [@grove2013evolution; @robirainreview].
-In this case, the size of the Hippocampus should be larger (Prediction 1.1).
-On the other hand, maintaining the brain functional has important energetic consequences [@raichle2006brain].
-Thus, if changes induced by sympatric species increase environmental unpredictability too much, rendering cognitive foraging less efficient [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller (Prediction 1.2).
-
-|   "Social" cues left out by heterospecifics might add to environmental ones.
-This supplementary load of cues could stimulate areas involved in general and immediate information processing.
-We should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex (Prediction 2.1).
+In this case, the size of the Hippocampus should be larger the higher the sympatry (Prediction 1.1).
+On the other hand, maintaining the brain functional is energetically costly [@raichle2006brain], and if changes induced by sympatric species increase environmental unpredictability too much, which would make cognitive foraging less efficient [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller the higher the sympatry (Prediction 1.2).
+
+|   "Social" cues left out by heterospecifics might also add to environmental ones.
+If species sympatry increases the load of usable cues to locate available food, we should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex (Prediction 2.1).
 Yet, social and environmental cues might not necessarily add, and foragers might choose one or the other.
@@
 personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
-Thus, the presence of heterospecific competitors might simplify the track and processing of immediate cues to locate food.
+Thus, the “social” cues provided by heterospecifics might replace, and be simpler to cognitively process, than environmental ones.
 From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should be smaller (Prediction 2.2).
 
-|   While cognition can be intensively shaped under the rationale centered around resource harvesting [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
+|   While cognition can be intensively shaped when foragers are individually in quest for food [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by direct interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
 The Striatum is stimulated during social interactions [@baez2013role]: its size is expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups.
-yet, mixed-group species is rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]).
+Yet, mixed-group species is rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]).
 This social area should thus be little affected by heterospecifics.
-It can eventually serve as a null comparative area.
-
-|   Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as a study example.
+
+|   Here, we investigated the intertwining between species sympatry and cognition using frugivorous primates as a study example.
 Frugivorous primates are an interesting group for such a question because fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio], for which cognition thus considerably shapes the foraging strategy [@trapanese2019and].
-To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for evolutionary scenarios accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in all primates.
+To infer the effect of species sympatry on brain size evolution within frugivorous primates, we evaluated the support for evolutionary models accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
+Finally, we tested for correlative patterns between brain size or current sympatry and the evolutionary consequences (assumed to be reflected by species diversification) in all primates.
 
@@
 We gathered a large database on the whole brain size, the size of the MOB, Cerebellum and the Neocortex, involved in daily information processing, and the Striatum and the Hippocampus, related to either social and foraging-related tasks, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
-It evidenced ample variations in brain size.
+It evidenced ample variations in brain sizes.
 For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (i.e.
@@
 |   In order to get the evolutionary history of sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
-We then calculated the likelihoods of models considering the role of species interactions (matching competition MC models, [@nuismer2015predicting]; models of linear or exponential density dependence, DD$_{lin}$ and DD$_{exp}$, of the evolutionary rate on the number of sympatric lineages; [@drury2016estimating] see [Models of trait evolution: does interspecific interactions shape brain size evolution?]) in the evolution of either the whole brain (using the encephalic quotient, EQ, as a proxy), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
+We then calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
 \@ref(fig:figbrain)).
+We specifically considered the matching competition (MC) model [@nuismer2015predicting] and models of linear or exponential density dependence (DD$_{lin}$ and DD$_{exp}$) of the evolutionary rate of the brain sizes on the number of sympatric lineages ([@drury2016estimating] see [Models of trait evolution: does species sympatry shape brain size evolution?]).
 We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
-stabilizing selection; see [@blomberg2020beyond] for a review) or the Early-Burst model (EB, [@blomberg2003testing]), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density effect is not an artefact due to time-dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criterions corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does interspecific interactions shape brain size evolution?]).
-
-|   We found that models discarding species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in movement and/or general information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum] but also in memory consolidation for the Neocortex [@wiltgen2004new].
-The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefices of brain development [@isler2009expensive].
-By contrast, models considering sympatry were best supported in foraging-related and social areas, either specialised in spatio-temporal memory (Hippocampus, [@burgess2002human]) or planning abilities and reward assessment (Striatum, [@baez2013role; @johnson2007integrating]), and tended to be so for one brain area involved in sensory abilities (the main olfactory bulb, MOB; Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-When density-dependent models were the best fit, the rate (*r*, Figure \@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo together with increased diversity of sympatric lineages for the Hippocampus and the Striatum, but a slowdown for the MOB.
+stabilizing selection; see [@blomberg2020beyond] for a review) or the Early-Burst model (EB, [@blomberg2003testing]), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density dependence is not an artefact due to time dependence.
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criterions corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does species sympatry shape brain size evolution?]).
+
+|   We found that models not considering  species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in general and immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
+The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefits of brain development [@isler2009expensive].
+By contrast, density-dependence models considering sympatry were best supported in the foraging-related and social areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions (Striatum, [@baez2013role]).
+The fact that we inferred positive rates *r* of density-dependence (Figure \@ref(fig:figresultsevolution)), suggested an acceleration of the evolutionary tempo of trait evolution together with increased diversity of sympatric lineages for the Hippocampus and the Striatum.
+The main olfactory bulb (MOB), the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole: yet, individually,Brownian-Motion was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)) .
 
@@
 
-|   Next, to understand the directionality of the selection gradient shaped by sympatry (i.e.
+|   Next, to understand the effect of sympatry on brain sizes (i.e.
 selection for “bigger” or “smaller” brain the more species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
@@
 
-|   In addition, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with species diversification rates (i.e.
-speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
-Overall, species diversification rates, estimated based on molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
+|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with species diversification rates (defined  as speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
+Overall, species diversification rates, estimated based on the primate molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
 When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
-Given the context dependence of the direction of selection (towards bigger sizes in the absence of other species, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by inter-species sympatry.
-Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to inter-species sympatry too.
+Given the context dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by species sympatry.
+Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to species sympatry too.
 This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
@@
 In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification, a density-dependence trend that is frequently observed in many tetrapod clades [@condamine2019assessing], but which stands as an inverted pattern compared to what is found in New World passerines [@kennedy2017historical].
+In other words, the higher the number of sympatric species, the lower the diversification rate, a density-dependence trend that is frequently observed in many tetrapod clades [@condamine2019assessing].
 
@@
 The size of the brain is subject to a compromise between the energy it incurs, and the increase of fitness it allows.
-This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ) were best described by the Orstein-Uhlenbeck process, what might suggest a stabilisation towards an optimal size as a result of an equilibrium between costs and benefices.
+This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ) were best described by the Ornstein-Uhlenbeck process, what might suggest a stabilisation towards an optimal size as a result of an equilibrium between costs and benefits.
 As the brain area is regionally specialised [@barton2000mosaic], brain regions could be under different selective pressures as suggested by the differences we highlighted in some brain areas (e.g.
@@
 Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
-These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
+These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under strong selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
 The influence of sympatry on the Striatum is surprising, because mixed-species groups are rather infrequent in primates.
-Yet, when interacting with conspecifics, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating], a key thing within group and in a Machiavellian perspective [@byrne1994machiavellian].
+Yet, when interacting with conspecifics, the Striatum underpins reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating], a key thing within group and in a Machiavellian perspective [@byrne1994machiavellian].
 It is thus possible that actions underpinned by the Striatum (e.g.
-planning/anticipating heterospecifics move) might be key, and up to now overlooked, when foraging in a multi-species context too.
+planning/anticipating heterospecifics moves) might be key, and up to now overlooked, when foraging in a multi-species context too.
 Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
@@
 
-|   In general, competition is the first-thought mechanism to describe community structures [e.g.
-@rocha2015role].
-In primates, it is rare to observe direct competition between species (but see recently @southern2021lethal), which should translate into site exclusion.
-In fact, inter-species site exclusion in this taxon has only been observed in gibbons [@suwanvecho2012interspecific].
-For species with overlapping diet, indirect competition for resources might happen.
-We show that higher sympatry rate is actually associated with smaller size of the Hippocampus or Striatum (negative effect of the intensity of overlap with co-occurring species on the specific area size, in accordance with Prediction 1.2).
-This suggests that indirect competition might contribute to convoluting the environment such as cognitive foraging might no longer be beneficial.
-In particular, the acceleration of the evolutionary tempo (i.e.
-the slope associated to density dependence terms is positive) suggests that it is not limited to a relax of positive selection for bigger brains, but to a positive selection for smaller brains.
-
-|   Not only was brain evolution affected by sympatry, but sympatry (here the maximum number of co-occurring species only) induced a slowdown in diversification.
+|   Competition is generally the first-thought mechanism to describe community structures [e.g.
+@rocha2015role] because it might affect the environment, and associate selective pressure, in which species evolve.
+We show that higher sympatry is actually associated with smaller size of the Hippocampus or Striatum (in accordance with Prediction 1.2).
+This suggests that indirect competition for food might contribute to convoluting the environment such as cognitive foraging might no longer be beneficial.
+In particular, the increase in the evolutionary tempo of brain size changes when in sympatry (i.e.
+the positive density dependence) suggests that species sympatry does not relax the positive selection for bigger brains, but generates a positive selection for smaller brains.
+
+|   Not only was brain evolution affected by sympatry, but sympatry induced a slowdown in diversification.
 Density-dependence within clade is indeed generally associated to lower diversification rate [@moen2014does].
@@
 
-Brain data were obtained from [@decasien2019primate] for whole brain and all mentioned other parts (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
+Brain data were obtained from [@decasien2019primate] for whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
 They were freely available in the main manuscript or supplementary materials.
@@
 
-|   We retraced the history of the lineage ranges based on current observations of species range using the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+|   We retraced the history of the lineage ranges based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
 We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see [@matzke2013probabilistic] for further details on these events).
@@
 Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
+Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
 
@@
 
-|   Frugivory rate was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
+|   Frugivory was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
 Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
@@
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits [Phylogenetic models] to account for uncertainty of these ancestral diet estimations (see [Phylogenetic models, Models of trait evolution: does interspecific interactions shape brain size evolution?] (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
 
@@
 
-### Models of trait evolution: does interspecific interactions shape brain size evolution?
+### Models of trait evolution: does species sympatry shape brain size evolution?
 
@@
 Models without competition, Brownian Motion (i.e.
-BM), Orstein-Uhlenbeck process (i.e.
+BM), Ornstein-Uhlenbeck process (i.e.
 OU, model with stabilizing selection), or Early-Burst model (i.e.
 EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted models considering sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
 These models notably account for interaction matrices that are built on the evolutionary history of species sympatry and diet.
@@
 We fitted three different models including sympatry.
-The matching competition model (MC) may consider divergence of traits of co-occurring lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
-Here, that would mean that co-occurring species would tend to have either lower or higher EQ or relative brain size.
+The matching competition model (MC) may consider divergence of traits of sympatric lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
+Here, that would mean that sympatric species would tend to have either lower or higher EQ or relative brain size.
 Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
-Density-dependence means that the evolutionary rate $\lambda$ varies either positively or negatively as a function $f$ of the number of co-occurring lineages sharing the same diet such as
+Density-dependence means that the evolutionary rate $\lambda$ of trait changes varies either positively or negatively as a function $f$ of the number of sympatric lineages sharing the same diet such as
 
@@
 where $\lambda_{0}$ corresponds to the value of the initial ancestor, $l$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
-All these models were repeated `r numberSimulations` times, using `r randomSampling` different combination of the evolutionary history of ranging and diet.
+All these models were repeated `r numberSimulations` times, using `r randomSampling` different combinations of the evolutionary histories of primate ranges and diets.
 They were then compared within an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
@@
 
-(b) Dealing with data uncertainty and parameter sensitivity
+(b) Dealing with data uncertainty and parameterisation sensitivity
 
@@
 In this analysis, uncertainty can stem from two sources.
-First, the true phylogeny is never known with certainty, and is estimated through Bayesian inference, thus we used the consensus tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
-
-|   Similarly, the estimated evolutionary history of the diet and ranging might vary as well.
-Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
-Particularly, although correlations seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)), while, in order to increase the overall number of species, trait values were not mandatorily from a single dataset.
+First, the evolutionary history (phylogeny, diet, and ranging) were reconstructed based on Bayesian inference.
+They are susceptible to be uncertain at some points.
+Thus, we used a consensus phylogenetic tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
+In addition, we repeated these history reconstructions `r numberSimulations` times.
+
+|   Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
+Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)).
 In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
 To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
-equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory and geographic sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
-
-|   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolution) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
-We stopped computations when the calculation of the likelihood was excessively long (> 1 week).
+equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory, and species sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
+
+|   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolutionary reconstructions) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold defining sympatry) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
+We stopped computations when the optimization of the likelihood was excessively long (> 1 week).
 The final sample size thus was of `r min(totModelsWorked[-2])*10` models.
@@
 constant ratio between extinction and speciation rates).
-This Bayesian approach considers speciation rate heterogeneity by modeling small shifts in the rate at speciation events.
-In other words, the daughter lineage is assumed to inherit new speciation rates that is sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the parental speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
+This Bayesian approach considers speciation rate heterogeneity by modelling small shifts in the rate at speciation events.
+In other words, the two new lineages are assumed to inherit new speciation rates that are sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the initial speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
 Three independent chains were run until their respective convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
@@
 
-(a)	Determining the direction of the selection gradient shaped by interspecific interactions
+(a)	Determining the effect of sympatry on brain sizes
 
@@
 
-In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the diversification rate (i.e.
+In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the diversification rates (i.e.
 accounting for both, speciation and extinction) estimated for each species by the *ClaDS* algorithm.
@@
 
-(c) Diversification and sympatry
-
-To determine whether sympatry was associated to specific diversification pattern (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
+(c) Diversification and species sympatry
+
+To determine whether sympatry was associated to specific diversification patterns (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
 
@@
 
-(i)	Direction of the selection gradient shaped by interspecific competition
+(i)	Effect of sympatry on brain sizes
 
@@
 Other function parameters were set to default.
-Prior to fitting, covariates were symmetrized if necessary.
+Prior to fitting, covariates were transformed so as to reach more symmetrical distribution when adequate.
 Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
-We did not observe correlation issue among predictors either (VIF$_{max}$ < 2, [@mundry2014statistical]).
+We did not observe correlation issue among predictors neither (VIF$_{max}$ < 2, [@mundry2014statistical]).
 
@@
 Prior on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
-We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=2)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
+We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=4)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
 In Appendix [Model assumptions], we present trace and distributions of posterior estimates.
@@
 
-|   The results of these assessment (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes weak sensitivity of the results.
+|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes weak sensitivity of the results.
 
@@
 
-We considerably value the help provided by Jonathan Drury in making some scripts available, but mostly for helping us in solving issues encountered with the use of functions of his own in the *RPANDA* package in *R*, and that of Marie-Claude Quidoz for assistance for using the CEFE cluster.
-We thank Simon Benhamou and Manon Clairbaux for discussion and advices on spatial projections, and M.
+We considerably value the help provided by J.
+Drury in making some scripts available, but mostly for helping us in solving issues encountered with the use of his functions in the *RPANDA* package in *R*, and that of M-C.
+Quidoz for assistance for using the CEFE cluster.
+We thank S.
+Benhamou and M.
+Clairbaux for discussion and advices on spatial projections, and M.
 Quéroué, V.
@@
 Teplistky for feedback on Bayesian computations too.
-Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and Alexandra R.
-DeCasien and collaborators, Lauren E.
-Powell and collaborators, Orlin S.
-Todorov and collaborators, Erik P.
-Willems and collaborators, Fiona Pearce and collaborators, Navarrete and collaborators, and Cyril C.
+Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and A.
+R.
+DeCasien and collaborators, L.
+E.
+Powell and collaborators, O.
+S.
+Todorov and collaborators, E.
+P.
+Willems and collaborators, F.
+Pearce and collaborators, Navarrete and collaborators, and C.
+C.
 Grueter who provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J.
@@
 
-BR conceived the study, collected, cleaned and analyzed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
+BR conceived the study, collected, cleaned and analysed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
 BP-L implemented the ClaDS algorithm for our data, helped with running other analyses, and revised the manuscript multiple times.
@@
 rownames(results.df_gradient) <- NULL
-knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
-The brain area (as well as the associated sample size) are indicated prior to each list of estimates.
+knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
 The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
@@
 samp.=Effective sample (adjusted for autocorrelation).
-The brain area (as well as the associated sample size) are indicated prior to each list of estimates.
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
 The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
@@
 
-knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,
-             caption = "Model estimates and significance of phylogenetic regressions to assess the correlation between diversification and sympatry | Est.=Estimate, CI2.5%=Lower border of the CI95%, CI97.5%=Upper border of the CI95%, Sd= Standard deviation, t= Statitsitics t-vale.
-The brain area (as well as the associated sample size)
-             are indicate prior to each list of estimates. the transformation (logarithm or square-root) if indicated in parenthese by the abbreviation (log or sqrt).") %>%
+knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
+The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
   kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
@@
 Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-Hence, *Macaca Sylvanus* is not considered in this study.", sep="")}
+Hence, *Macaca sylvanus* is not considered in this study.", sep="")}
 
@@
 
-```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels of sympatry significantly vary across the primate phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
+```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels of sympatry vary across the primate phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
 The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
-Co-occurring frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by lightgray lines.
-The geographic area occupied by a species is depicted by the coloured rectangles.
-Presence was assed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1]*100, "%.", sep="")}
+Sympatric frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by light grey lines.
+The geographic areas occupied by a species are depicted by the coloured rectangles.
+Presence was assessed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1]*100, "%.", sep="")}
 
@@
 <!-- , although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere -->
-```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) The circular rows are indicated by the colours which match a specific brain area.
+```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) Circular plot of relative size of the different brain areas.
+Colours indicates the rows for the different brain areas.
 The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.
-The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain parts, when available, is depicted by a plain circle for frugivorous species.
+The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain regions, when available, is depicted by a plain circle for frugivorous species.
 The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%.
-(Right) The different studied brain areas.
-In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation processes [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
+(Right) The different studied brain areas (human brain as illustration).
+In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation of general and immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
 The Striatum is involved in social information processing [@baez2013role].", sep="")}
@@
 
-```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the size of foraging-related brain areas is best fitted by models considering sympatry of trait evolution in frugivorous primates | Plotted is the AICc weight, a measure of relative support for a given model, for models discarding sympatry (BM, OU, EB) and considering sympatry (MC, DD$_{lin}$, DD$_{exp}$).
+```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the Hippocampus and Striatum are best fitted by models considering sympatry of trait evolution in frugivorous primates | Plotted is the AICc weight, a measure of relative support for a given model, for models not considering  sympatry (BM, OU, EB) and considering sympatry (MC, DD$_{lin}$, DD$_{exp}$).
 The points represent the average AICc weight obtained (when considering the six models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does interspecific interactions shape brain size evolution?])."}
@@
 emptyPlot()
-legend(x=0.25, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("NO species interaction", "Species interaction"), bty="n", cex=1.35)
+legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)
 ```
@@
 
+par(mar=c(4, 3, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
 plot(
-  x=0, y=0, xlab="Overlap threshold", ylab="Variation percent (relative to 15%)", 
+  x=0, y=0, xlab="Overlap threshold", ylab="Percent of species with different biogeographic areas\ncompared to when a 15% overlap is used", 
   xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
@@
 
-```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
+```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10.5, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
 indicates the frugivory rate and Fol.
@@
 plot(
-  x=0, y=0, xlab="", ylab="Coefficient of correlation", 
+  x=0, y=0, xlab="", ylab="Coefficient of correlation", cex.lab=1.5, 
   xlim=c(0,length(meanCoeff)+1), ylim=c(0.6,1),
@@
 addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0.6, ymax=1, yintsmall=0.025, yintbig=0.1, axisPlot=FALSE)
-axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25)
+axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
 addLabel(x=0.05, y=0.075, label="A", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
@@
 plot(
-  x=0, y=0, xlab="", ylab="Variability", 
+  x=0, y=0, xlab="", ylab="Variability", cex.lab=1.5,
   xlim=c(0,length(meanCoeff)+1), ylim=c(0,ymax),
@@
 addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25)
+axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
 addLabel(x=0.05, y=0.075, label="B", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
@@
 plot(
-  x=0, y=0, xlab="", ylab="Repeatability", 
+  x=0, y=0, xlab="", ylab="Repeatability", cex.lab=1.5,
   xlim=c(0,length(colRep)+1), ylim=c(0,ymax),
@@
 addGrid(xmin=0, xmax=length(colRep), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25)
+axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
 addLabel(x=0.05*2, y=0.075, label="C", radius=0.75*length(colRep)/length(meanCoeff)*2, circle=TRUE, circle.bg="black", font.col="white")
@@
 The grey background depicts the standard deviation.
-The two breakpoints, depicted by the plain dots and the vertical dotted bars, were thus estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
+The two breakpoints, depicted by the plain dots and the vertical dotted bars, were estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
 The three fitted regressions are displayed by the dashed lines.
-The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the the Bayesian Information Criterion.
+The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the Bayesian Information Criterion.
 The identified breakpoints coin with identified sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
@@
 
-(a) Phylogenetic regressions: selection gradient
+(a) Phylogenetic regressions: effect of sympatry on brain sizes
 
@@
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent gray background.}}\label{fig:figRegressionGradient}
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionGradient}
 \end{figure}
@@
 \caption{\scriptsize{Phylogenetic regressions of the diversification rate in function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent gray background.}}\label{fig:figRegressionDiversification}
+The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent grey background.}}\label{fig:figRegressionDiversification}
 \end{figure}
@@
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent gray background.}}\label{fig:figRegressionDiversificationSympatry}
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionDiversificationSympatry}
 \end{figure}
@@
 
-```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=6.25, fig.height=6.25, fig.cap="Forest plot of the phylogenetic regressions | CI: Confindence Interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible because reduced).
+```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=6.25, fig.height=6.25, fig.cap="Forest plot of the phylogenetic regressions | CI: 95\\% Confidence Interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible because reduced).
 Plain dots depict negative effects, open dots depict positive effects.
@@
 summarySensitivityGradient <- summarySensitivityGradient[-(1:4),]
-summarySensitivityGradient[,1] <- gsub("Overlap", "\\% of overlappend range", summarySensitivityGradient[,1])
-summarySensitivityGradient[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivityGradient[,1])
+summarySensitivityGradient[,2] <- gsub("Overlap", "\\% of overlapping range", summarySensitivityGradient[,2])
+summarySensitivityGradient[,2] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivityGradient[,2])
 
@@
 knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to detect the assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 ```{r tabledfsensitivity3, include=TRUE}
-summarySensitivitydiversificationAndSympatry[,1] <- gsub("Overlap", "\\% of overlappend range", summarySensitivitydiversificationAndSympatry[,1])
+summarySensitivitydiversificationAndSympatry[,1] <- gsub("Overlap", "\\% of overlapping range", summarySensitivitydiversificationAndSympatry[,1])
 summarySensitivitydiversificationAndSympatry[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivitydiversificationAndSympatry[,1])

### 2021-12-14 Scripts/Analysis2_competitiondirection/SpatialProcessingSympatry.R
Update article + update readme + reorganise files

@@ -342,7 +342,7 @@ for(i in 1:nrow(speciesLabels)){#for all species for which phylogeny is known
                   if(!is.null(intersectingArea)){
                     intersectingArea <- spTransform(intersectingArea, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
                     speciesRangeTransitory <- spTransform(speciesRangeTransitory, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))#the initially correct proj
-                    overlapPair[j] <- geosphere::areaPolygon(intersectingArea)/geosphere::areaPolygon(speciesRangeTransitory)#counSpecies
+                    overlapPair[j] <- geosphere::areaPolygon(intersectingArea)/geosphere::areaPolygon(speciesRangeTransitory)#count Species
                   }
                 }
               }

### 2021-12-14 Article/Article.Rmd
Update article + update readme + reorganise files

@@
   # - \usepackage[nolists, nomarkers,tablesfirst]{endfloat} # For figures and tables at end
-  #- \usepackage{lineno} # For line numbering
-  #- \linenumbers # For line numbering
-  #- \usepackage{setspace}\doublespacing
+  - \usepackage{lineno} # For line numbering
+  - \linenumbers # For line numbering
+  - \usepackage{setspace}\doublespacing
   - \usepackage{fontawesome} #for fa symbols
@@
 However, space is often occupied by many species belonging to the same ecological guild.
-Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food (Hypothesis 2).
-For instance, wild grey-cheeked mangabeys (*Lophocebus albigena*) increase targeting towards fruit trees from which black-and-white-casqued hornbill (*Bycanistes subcylindricus*) calls can be heard  [@olupot1998fruit].
+Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food ([@Avargues-Weber2013]; Hypothesis 2).
+In addition, direct interactions with heterospecifics, as much as with conspecifics [@dunbar2017there], might also affect cognition (Hypothesis 3).
 
 |   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
-Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities, with larger size considered equivalent to larger cognitive abilities (but see discussion in @logan2018beyond).
+Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities, with larger size considered equivalent to more advanced cognitive abilities [@Benson-Amram2016].
 Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
-These areas are likely to be under different selective pressures, and thus, to be differently affected by species sympatry.
-First, brain areas involved in processing and storing spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape is complexified by sympatric species foraging on the same resource (Hypothesis 1).
-Second, brain areas involved in processing more general and immediate information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2).
-
-|   Under these two (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
-Reasonable food depletion should promote cognition which stands as a valuable tool to infer food availability and location when food is rare and ephemeral but predictable [@grove2013evolution; @robirainreview].
+These areas are likely to be under different selective pressures, and thus, to follow different evolutionary paths.
+In particular, they might be differently affected by species sympatry.
+First, brain areas involved in the storing of spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape is complexified by sympatric species foraging on the same resource (Hypothesis 1: memory is affected).
+Second, brain areas involved in processing more immediate sensory information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2: cue processing is affected).
+Besides individual foraging, cognition can also be triggered by direct "social" interactions with other individuals [@byrne1994machiavellian; @dunbar2017there].
+The Striatum is a brain area stimulated during social interactions [@baez2013role], and should, therefore, be affected by direct social interactions with heterospecifics (Hypothesis 3).
+
+|   Under these (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
+Reasonable food depletion should promote memory, which stands as a valuable tool to infer food availability and location when food is rare and ephemeral but predictable [@milton1981distribution; @rosati2017foraging].
 In this case, the size of the Hippocampus should be larger the higher the sympatry (Prediction 1.1).
-On the other hand, maintaining the brain functional is energetically costly [@raichle2006brain], and if changes induced by sympatric species increase environmental unpredictability too much, which would make cognitive foraging less efficient [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller the higher the sympatry (Prediction 1.2).
-
-|   "Social" cues left out by heterospecifics might also add to environmental ones.
-If species sympatry increases the load of usable cues to locate available food, we should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex (Prediction 2.1).
-Yet, social and environmental cues might not necessarily add, and foragers might choose one or the other.
-In particular, it has been shown that foragers tend to use social information over environmental (i.e.
-personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
-Thus, the “social” cues provided by heterospecifics might replace, and be simpler to cognitively process, than environmental ones.
-From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should be smaller (Prediction 2.2).
-
-|   While cognition can be intensively shaped when foragers are individually in quest for food [@milton1981distribution; @rosati2017foraging], cognition can also be triggered by direct interactions with conspecifics [@byrne1994machiavellian; @dunbar2017there].
-The Striatum is stimulated during social interactions [@baez2013role]: its size is expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups.
-Yet, mixed-group species is rather infrequent in primates (but see callitrichine primates in particular [@heymann2015unlike]).
-This social area should thus be little affected by heterospecifics.
+On the other hand, maintaining a functional brain is energetically costly [@raichle2006brain], and if changes induced by sympatric species increase environmental unpredictability too much, which would make cognitive foraging not advantageous anymore [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller the higher the sympatry (Prediction 1.2).
+In the meanwhile, "social" cues  left out by heterospecifics might also add to environmental ones.
+If species sympatry increases the load of usable cues to locate available food, we should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex.
+Interactions between species can also occur directly, with the formation of mixed-group species [@Goodale2010].
+This, in particular, should promote larger Striatum size in sympatry.
 
@@
 
-We gathered a large database on the whole brain size, the size of the MOB, Cerebellum and the Neocortex, involved in daily information processing, and the Striatum and the Hippocampus, related to either social and foraging-related tasks, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
-It evidenced ample variations in brain sizes.
-For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (i.e.
-pondered by whole-body mass) in our data (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural] and indeed show the highest relative size of the Striatum in our data (a brain area related to social interactions, Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
-
-|   In order to get the evolutionary history of sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
+We gathered a large database on the whole brain size, the size of the MOB, Cerebellum, and the Neocortex, involved in immediate sensory information processing, and the Striatum and the Hippocampus, related to either social and foraging-related memory, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
+After pondering by whole-body mass, we observed ample variations in brain area relative sizes.
+For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
+Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural].
+The latter show the highest relative size of the Striatum (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+
+|   To get the evolutionary history of species sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
 We then calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
 \@ref(fig:figbrain)).
-We specifically considered the matching competition (MC) model [@nuismer2015predicting] and models of linear or exponential density dependence (DD$_{lin}$ and DD$_{exp}$) of the evolutionary rate of the brain sizes on the number of sympatric lineages ([@drury2016estimating] see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around on optimal value (e.g.
-stabilizing selection; see [@blomberg2020beyond] for a review) or the Early-Burst model (EB, [@blomberg2003testing]), this latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density dependence is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criterions corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-
-|   We found that models not considering  species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in general and immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
+We specifically considered the matching competition (MC) model [@nuismer2015predicting] and density dependence models (DD$_{lin}$ and DD$_{exp}$), which assume a linear or exponential dependence of the brain sizes evolutionary rates on the number of sympatric lineages ([@drury2016estimating] see [Models of trait evolution: does species sympatry shape brain size evolution?]).
+We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around an optimal value (e.g.
+stabilizing selection; see [@blomberg2020beyond] for a review), or the Early-Burst model (EB, [@blomberg2003testing]), the latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density dependence is not an artefact due to time dependence.
+Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criteria corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does species sympatry shape brain size evolution?]).
+
+|   We found that models not considering species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
 The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefits of brain development [@isler2009expensive].
-By contrast, density-dependence models considering sympatry were best supported in the foraging-related and social areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions (Striatum, [@baez2013role]).
+By contrast, density-dependence models considering sympatry were best supported in the foraging-related and social-related areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions [@baez2013role].
 The fact that we inferred positive rates *r* of density-dependence (Figure \@ref(fig:figresultsevolution)), suggested an acceleration of the evolutionary tempo of trait evolution together with increased diversity of sympatric lineages for the Hippocampus and the Striatum.
-The main olfactory bulb (MOB), the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole: yet, individually,Brownian-Motion was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)) .
+The Main Olfactory Bulb (MOB), the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole: yet, Brownian-Motion was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
 
@@
 |   Next, to understand the effect of sympatry on brain sizes (i.e.
-selection for “bigger” or “smaller” brain the more species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
+toward “bigger” or “smaller” brains the more sympatric species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
 For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered the average surface of the frugivorous species range that was overlapped by other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range as covariates based on IUCN data [@IUCN].
+We considered as covariates the average percentage of overlapping range with other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range based on IUCN data [@IUCN].
 On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
 That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
-In terms of distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species (*`r whichSpeciesMinNCoocc`*), to `r maxNspeciesCoocc` species (*`r whichSpeciesMaxNCoocc`*).
+In terms of the distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species to `r maxNspeciesCoocc`.
 The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the percentage of range shared with other species correlated with the relative size of areas that were better fit with models considering sympatry: the Hippocampus, and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
-The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher species overlap associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
-Given the acceleration of the evolutionary tempo, it suggests that sympatric species are subject to a positive selection towards smaller brain, and not to a less intense selection for advanced cognitive abilities compared with isolated species.
+Conversely, we found that the average percentage of overlapping range correlated with the relative size of areas that were better fit with models considering sympatry: the Hippocampus and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
+The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher range overlap between frugivorous species associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
+Given the acceleration of the evolutionary tempo with species sympatry ($r>0$ in the density-dependence models), it suggests that compared with isolated species, sympatric species are subject to a positive selection towards smaller brains, and not to a less intense selection for advanced cognitive abilities.
 
@@
 
-|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with species diversification rates (defined  as speciation minus extinction rates), by using lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
-Overall, species diversification rates, estimated based on the primate molecular phylogeny increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around `r dateFirstRupt[2]` (CI95% = `r paste("[",dateFirstRupt[3],",",dateFirstRupt[1],"]", sep="")`) and `r dateSecondRupt[2]` (CI95% = `r paste("[",dateSecondRupt[3],",",dateSecondRupt[1],"]", sep="")`) Myr ago (Figure \@ref(fig:figdiversificationTime)).
-When accounting for phylogenetic dependence, no significant relationship between diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
-Given the context dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between evolutionary success (approximated by diversification rate) and the three studied areas affected by species sympatry.
-Surprisingly however, we found no positive association between the EQ and the diversification rate, nor of that latter with the relative size of the Cerebellum or the Neocortex, two areas insensitive to species sympatry too.
+|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with the net species diversification rates (defined as speciation minus extinction rates).
+To do so, we used lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
+Overall, species diversification rates, estimated based on the primate molecular phylogeny, increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around 25 and 11 Myr ago (Figure \@ref(fig:figdiversificationTime)).
+When accounting for phylogenetic dependence, no significant relationship between the net diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
+Given the context-dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between the diversification rate and the three brain areas affected by species sympatry.
+Surprisingly however, we found no positive association between the net diversification rate and the EQ, nor with the relative sizes of the Cerebellum or the Neocortex, two areas insensitive to species sympatry too.
 This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
-The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex if discarding phylogenetic non-independence (Figure \@ref(fig:figRegressionDiversification)).
-In fact, a sudden encephalisation in primates is clearly associated to a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically-corrected analyses as we cannot decipher whether the connivance between brain size and evolutionary success results from a true biological link or appeared by chance.
-A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenge, thus boosting individuals' fitness [@sol2007big].
-This means that, despite what we found here, the positive association between brain size and evolutionary success evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
+The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex, if discarding phylogenetic non-independence (Figure \@ref(fig:figRegressionDiversification)).
+Indeed, sudden encephalisation in primates is clearly associated with a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
+This clearly limits the statistical power of our phylogenetically-corrected analyses, as we cannot decipher whether the connivance between brain size and species diversification results from a true biological link or appeared by chance.
+A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenges [@sol2007big].
+This means that, despite what we found here, a positive association between brain size and species diversification evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
 Finally, although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
@@
 The size of the brain is subject to a compromise between the energy it incurs, and the increase of fitness it allows.
-This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ) were best described by the Ornstein-Uhlenbeck process, what might suggest a stabilisation towards an optimal size as a result of an equilibrium between costs and benefits.
-As the brain area is regionally specialised [@barton2000mosaic], brain regions could be under different selective pressures as suggested by the differences we highlighted in some brain areas (e.g.
-MOB or Striatum) across different primate genera.
-Here, we further show that sympatry is one factor that affects the selective regime under which each brain region evolves: although the brain as a whole was insensitive to species sympatry, this latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
+This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ), were best described by the Ornstein-Uhlenbeck process.
+This evidence might suggest a stabilisation towards an optimal size resulting from an equilibrium between costs and benefits.
+As the brain is regionally specialised [@barton2000mosaic], different brain areas could be under different selective pressures.
+This is evidenced, here, by the differences of relative sizes across lineages in the MOB or Striatum in particular.
+We further show that sympatry is one factor that affects the selective regime under which some brain region evolves: although the brain as a whole was insensitive to species sympatry, the latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
 These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under strong selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
-The influence of sympatry on the Striatum is surprising, because mixed-species groups are rather infrequent in primates.
-Yet, when interacting with conspecifics, the Striatum underpins reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating], a key thing within group and in a Machiavellian perspective [@byrne1994machiavellian].
+
+|   The negative influence of sympatry on the Striatum might be quite surprising.
+Direct interactions with heterospecifics should stimulate this area (Hypothesis 3).
+We observed that this area was relatively larger in callitrichines, particularly known to perform mixed-species groups [@heymann2015unlike].
+When interacting with conspecifics, the Striatum underpins reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating].
+These skills are key within group, following a Machiavellian perspective [@byrne1994machiavellian].
+Yet, these skills might also be relevant in a foraging context.
 It is thus possible that actions underpinned by the Striatum (e.g.
-planning/anticipating heterospecifics moves) might be key, and up to now overlooked, when foraging in a multi-species context too.
-Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
-By contrast, potential indirect facilitation between species (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in general and immediate information processing (e.g.
+planning/anticipating heterospecifics moves), might be key and up to now overlooked, when foraging in a multi-species context too.
+
+|   Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
+Competition is generally the first-thought mechanism to describe community structures [@rocha2015role] because it might affect the environment, and associate selective pressure, in which species evolve.
+We show that higher levels of sympatry is actually associated with smaller sizes of the Hippocampus or Striatum (in accordance with Prediction 1.2).
+This suggests that indirect competition for food might contribute to convoluting the environment which might generate a positive selection for smaller brains.
+Not only was brain evolution affected by sympatry, but sympatry induced a slowdown in diversification.
+Density-dependence within a clade is indeed generally associated with lower diversification rates [@moen2014does].
+In particular, species competing for resources are thought to contribute to limiting their ranges [@price2009evolutionarily], hence constraining population size and their subsequent diversification [@pigot2013species].
+These observations thus strengthen the idea of scramble competition between species that cascades both on species population dynamics and species cognition.
+
+|   By contrast, potential indirect facilitation between species due to “social” cues (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in immediate sensory information processing (e.g.
 Cerebellum or Neocortex).
-
-|   Competition is generally the first-thought mechanism to describe community structures [e.g.
-@rocha2015role] because it might affect the environment, and associate selective pressure, in which species evolve.
-We show that higher sympatry is actually associated with smaller size of the Hippocampus or Striatum (in accordance with Prediction 1.2).
-This suggests that indirect competition for food might contribute to convoluting the environment such as cognitive foraging might no longer be beneficial.
-In particular, the increase in the evolutionary tempo of brain size changes when in sympatry (i.e.
-the positive density dependence) suggests that species sympatry does not relax the positive selection for bigger brains, but generates a positive selection for smaller brains.
-
-|   Not only was brain evolution affected by sympatry, but sympatry induced a slowdown in diversification.
-Density-dependence within clade is indeed generally associated to lower diversification rate [@moen2014does].
-In particular, species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
-These observations thus strengthen the idea of scramble competition between species that cascades both on population dynamics and species cognition.
-
-|   The use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from [@deaner2000comparative; @healy2007critique; @logan2018beyond]).
+This absence of effect can stem from two possibilities.
+Either sympatry, indeed, does not affect the landscape of cues for foragers.
+Otherwise, it has been shown that foragers tend to use social information over environmental (i.e.
+personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
+Thus, if environmental complexity increases too much, “social” cues provided by heterospecifics might replace environmental ones.
+From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should, at the very least, remain unaffected by sympatry.
+This nonetheless deserves further attention.
+
+|   To conclude, the use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from [@deaner2000comparative; @healy2007critique; @logan2018beyond]).
 The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
@@
 In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species.
-Here, we showed that species sympatry is an important factor shaping the evolutionary history of animals' brain, but the proximate mechanisms at play remain to be elucidated.
-Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: polyspecific social associations do exist [@porter2001benefits], as well as inter-species territory defense [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
+Here, we showed that species sympatry is an important factor shaping the evolutionary history of animals' brains, but the proximate mechanisms at play remain to be elucidated.
+Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: foraging facilitation between species does exist [@olupot1998fruit; @Havmoller2021], and so do polyspecific social associations [@porter2001benefits], as well as inter-species territory defence [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
+Similarly, prey-predator races could shape selection on cognitive abilities [@shultz2006chimpanzee].
 As Alice said “It's a great huge game of chess that's being played—all over the world” ([@Carroll], Chapter II) and all individuals are just pieces to play with or against, no matter the species.
@@
 
-Data processing, analyses, and plots were computed with R software [`r extractRversion()`, @Rsoftware].
+Data processing, analyses, and plots were computed with R software (`r extractRversion()`, @Rsoftware).
 Used codes and data are freely available at [https://github.com/benjaminrobira/Meta_analysis_cognition_primates](https://github.com/benjaminrobira/Meta_analysis_cognition_primates).
-Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*, this latter being too geographically isolated.
+Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*.
+The latter was discarded in the analyses because of geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
 A summary of available data per species is presented in Appendix Figure \@ref(fig:figmap).
@@
 
-We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
+We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on May 2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
 The trees contain `r length(phylo_init$tip.label)` primate species.
@@
 
-Brain data were obtained from [@decasien2019primate] for whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
+Brain data were obtained from [@decasien2019primate] for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for the whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
 They were freely available in the main manuscript or supplementary materials.
-When a species was represented multiple times within dataset, we obtained a unique attribute by averaging it.
+When a species was represented multiple times within the dataset, we obtained a unique attribute by averaging it.
 From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
@@
 
-$\mathrm{EQ}=1.036 \times \mathrm{Brainvolume}/ (0.085 \times \mathrm{Body mass}^{0.775})$
+$\mathrm{EQ}=1.036 \times \mathrm{Brain\,volume}/ (0.085 \times \mathrm{Body\,mass}^{0.775})$
 
@@
 To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
-As such, the use of specific region size relatively to the body mass and not raw size depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in [@deaner2000comparative]).
-Percentage of frugivory and/or folivory was obtained based on freely available dataset from [@decasien2017primate; @powell2017re] for the frugivory and folivory rate, or [@willems2013collective] for the folivory rate.
+As such, the use of specific region sizes relative to the body mass and not raw sizes depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in [@deaner2000comparative]).
+Percentage of frugivory and/or folivory was obtained based on a freely available dataset from [@decasien2017primate; @powell2017re; willems2013collective].
 
@@
 
-One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Figure \@ref(fig:figmap)).
-Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlap contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
-Based on the structure (i.e.
-number of species and their phylogenetic relationship) of primate communities at different field sites, [@kamilar2009environmental] determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
+For primate biogeography, based on the structure (i.e.
+number of species and their phylogenetic relationships) of primate communities at different field sites, Kamilar et al.
+[@kamilar2009environmental] determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
 We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
-These geographic areas are represented in Figure \@ref(fig:figmap) and correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia and the Asian Islands.
-The chosen scale for the areas is large because (i) retracing history of a large number of areas necessitates considerable computational means.
-In addition, this drastically increases computational time of phylogenetic model of brain trait evolution too.
-Furthermore (ii), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with reduction of ranging areas at an unprecedented speed rate.
+These geographic areas are represented in Figure \@ref(fig:figmap) and correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia, and the Asian Islands.
+The chosen scale for the areas is large because (i) retracing the history of a large number of areas necessitates considerable computational means.
+In addition, this drastically increases the computational time for fitting the phylogenetic models of brain trait evolution too.
+Furthermore (ii), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with a reduction of ranging areas at an unprecedented speed rate.
 Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
 evidenced on the North American fauna in [@pineda2021mammal]).
-
-|   We retraced the history of the lineage ranges based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in the surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Figure \@ref(fig:figmap)).
+Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlapping contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
+
+|   We retraced the biogeographic history of the lineage ranges based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
 We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see [@matzke2013probabilistic] for further details on these events).
-To reconstruct the evolution of species range, we fixed the maximum numbers of areas that could be occupied by a lineage at one time to three areas.
+To reconstruct the evolution of species range, we fixed the maximum number of areas that could be occupied by a lineage at one time to three areas.
 A too high number of areas that can be occupied simultaneously drastically increases computational time.
 Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
-
-## Dietary guild
-
-We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate, prioritizing fruvigory over folivory.
+Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for the uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
+
+## Dietary guilds
+
+We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate , prioritizing frugivory over folivory.
 First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold).
@@
 In any other cases, the species was discarded.
+To illustrate, if a species reached 30% of frugivory, and 65% of folivory (the rest being due, for instance, to insectivory), then, it would be categorized as, “frugivorous” if low thresholds are considered, or as “folivorous” in case high thresholds are considered.
+If we suppose now another species with 30% of frugivory and 50% of folivory, but considered by [@decasien2017primate] as frugivorous, then, the species would be “frugivorous” for low threshold, and still “frugivorous” with high thresholds.
 
@@
 Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
-First, such static rate does not reflect potential seasonality in fruit eating (e.g.
+First, such a static rate does not reflect potential seasonality in fruit-eating (e.g.
 [@masi2009western]), which is generally shorter, hence a lower overall frugivory rate.
-Second, frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
+Second, the frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
 Finally, the methodology to obtain this rate could additionally vary (e.g.
@@
 |   Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
-at the root) but with no prior on the transition matrix.
+at the root), but with no prior on the transition matrix.
 Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits (see [Phylogenetic models]), to account for the uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
 
@@
 
-We focused only on frugivorous primates, because sample size was otherwise insufficient, and fitted phylogenetic models of EQ - or relative size of a specific brain area – evolution with and without species competitions.
-Models were fitted on different sample sizes due to non-availability of some data for some traits.
+We focused only on frugivorous primates, because the sample size was otherwise insufficient, and fitted phylogenetic models of the evolution of the EQ or the relative size of a specific brain area considering or not species sympatry.
+Models were fitted on different sample sizes due to the non-availability of some data for some traits.
 Specifically, models using EQ included `r minEQ` to `r maxEQ` frugivorous species.
@@
 Nonetheless, for a given set of models (i.e.
-within brain area), the sample was strictly identical, allowing within set comparison.
+within brain area), the sample was strictly identical, allowing within-set comparisons.
 Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
-Models without competition, Brownian Motion (i.e.
-BM), Ornstein-Uhlenbeck process (i.e.
-OU, model with stabilizing selection), or Early-Burst model (i.e.
-EB, for assessing a time-dependence of the evolutionary rate) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guild]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These models notably account for interaction matrices that are built on the evolutionary history of species sympatry and diet.
+Models without species sympatry, Brownian Motion (BM), Ornstein-Uhlenbeck process (OU, model with stabilizing selection), or Early-Burst model (EB, for assessing a time-dependence of the evolutionary rate), were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
+Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guilds]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet.
 These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see [@drury2016estimating]).
-We fitted three different models including sympatry.
-The matching competition model (MC) may consider divergence of traits of sympatric lineages from a same dietary guild due to repulsion of traits (character displacement) [@drury2016estimating].
-Here, that would mean that sympatric species would tend to have either lower or higher EQ or relative brain size.
+We fitted three different models considering species sympatry.
+The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating].
+Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size.
 Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
-Density-dependence means that the evolutionary rate $\lambda$ of trait changes varies either positively or negatively as a function $f$ of the number of sympatric lineages sharing the same diet such as
+Density-dependence means that the evolutionary rate, $\lambda$, of trait changes, varies either positively or negatively as a function $f$ of the number of sympatric lineages sharing the same diet, such as
 
@@
 All these models were repeated `r numberSimulations` times, using `r randomSampling` different combinations of the evolutionary histories of primate ranges and diets.
-They were then compared within an information-theoretic framework [@burnham2002model] based on the weight of Akaike Information Criterion corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
-The model weight then depicts the probability that it best describes the observed evolutionary pattern among the tested models.
+They were then compared within an information-theoretic framework [@burnham2002model] based on the weights of Akaike Information Criteria corrected for small samples (AICc), when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
+The model weight depicts how well the model fits the observed evolutionary pattern compared with the other tested models.
 
@@
 In this analysis, uncertainty can stem from two sources.
-First, the evolutionary history (phylogeny, diet, and ranging) were reconstructed based on Bayesian inference.
+First, the evolutionary history (phylogeny, diet, and ranging) was reconstructed based on Bayesian inference.
 They are susceptible to be uncertain at some points.
 Thus, we used a consensus phylogenetic tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
-In addition, we repeated these history reconstructions `r numberSimulations` times.
+In addition, we repeated diet and ranging history reconstructions `r numberSimulations` times.
 
 |   Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
-Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurement (Appendix Figure \@ref(fig:figvariabilitydata)).
+Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Appendix Figure \@ref(fig:figvariabilitydata)).
 In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
-To account for these three sources of variability we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
+To account for these three sources of variability, we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
 equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory, and species sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
@@
 We stopped computations when the optimization of the likelihood was excessively long (> 1 week).
-The final sample size thus was of `r min(totModelsWorked[-2])*10` models.
+The final sample size thus was of `r min(totModelsWorked[-2])*10` models that covered all the ranges of tested parameters.
 
@@
 In other words, the two new lineages are assumed to inherit new speciation rates that are sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the initial speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
-Three independent chains were run until their respective convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
+Three independent chains were run until their convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
 The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
-This latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
+The latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
 
 |   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
+Estrada et al.
 [@estrada2017impending] estimated that, given current knowledge, the primate clade should be composed of 504 species.
 This means that the current sampling fraction is around 73%.
-We thus parameterized the *ClaDS* algorithm with this value for the estimate sampling fraction.
+We thus parameterized the *ClaDS* algorithm with this value for the estimated sampling fraction.
 Yet, given that the extant number of primate species is subject to controversy, and because the estimated sampling fraction may affect diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
@@
 To determine the nature of the relationship between species sympatry and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
-a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients but its diagonal multiplied by lambda) for each brain region individually and for frugivorous species only.
-We used the Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we it included brain areas for which the evolutionary history was best described by models considering sympatry.
-Here specifically, we considered the least stringent frugivory assessment, with frugivory threshold fixed to `r frugivoryThresholdVector[1]`%, folivory threshold fixed to `r folivoryThresholdVector[1]`%.
+a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients, but its diagonal ones, multiplied by lambda) for each brain region individually and for frugivorous species only.
+We used Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we included brain areas for which the evolutionary history was best described by models considering sympatry.
+Here specifically, we considered the least stringent frugivory assessment, with the frugivory threshold fixed to `r frugivoryThresholdVector[1]`% and the folivory threshold fixed to `r folivoryThresholdVector[1]`%.
 If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
@@
 |    The response variable was the relative size of brain areas.
-Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability and assumption]).
+Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability, and assumption]).
 In this model, the covariates (i.e.
-continuous predictors) were the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square rooted, to reach symmetrical distribution).
-For a given species A, sympatry with another species B was considered when species B range overlapped on more than 10% of the range of species A.
-This was done to reduce noise induced by coarse identification of species range.
+continuous predictors) were the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square-rooted, to reach symmetrical distribution).
+For a given species A, sympatry with another species B was considered when species B range overlapped on more than `r geographicThresholdVector[1]*100`% of the range of species A.
+This was done to reduce the noise induced by coarse identification of species range.
 
@@
 
-In the same way than explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the diversification rates (i.e.
-accounting for both, speciation and extinction) estimated for each species by the *ClaDS* algorithm.
-Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values in this case.
+In the same way as explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the net diversification rates (i.e.
+the difference between speciation and extinction rates), estimated for each extant species by the *ClaDS* algorithm.
+Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values.
 
@@
 
-To determine whether sympatry was associated to specific diversification patterns (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percent of the range surface overlapping with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
-
 \hfill
 
+To determine whether species sympatry was associated with specific diversification patterns (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
+
+\hfill
+
 (d)	Model implementation
@@
 \hfill
-                                                                                                                                                                           Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (i.e.
-indicating whether the trait is subject to selection, or corresponds to Brownian Motion, if $\lambda$ tends towards 1) estimated by maximum-likelihood (argument “model” set to “lambda”).
-Bootstrapping over `r repetitionBootstrap` independent replicates was done so as to obtain confidence intervals.
+                                                                                                                                                                           Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (with $\lambda$ indicating the strength of the phylogenetic signal, where $\lambda$=1  corresponds to Brownian Motion, i.e.
+the maximal influence of the phylogenetic history on the trait evolution) estimated by maximum-likelihood (argument “model” set to “lambda”).
+Bootstrapping over `r repetitionBootstrap` independent replicates was done to obtain confidence intervals.
 Other function parameters were set to default.
-Prior to fitting, covariates were transformed so as to reach more symmetrical distribution when adequate.
+Prior to fitting, covariates were transformed so as to reach more symmetrical distributions when adequate.
 Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
@@
 
-We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist approach because it led to violation of homoscedasticity.
+We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist approach because it led to a violation of homoscedasticity.
 Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
@@
 Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
-Prior on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
+Priors on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at a limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
 We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=4)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
-In Appendix [Model assumptions], we present trace and distributions of posterior estimates.
+In Appendix [Model assumptions], we present traces and distributions of posterior estimates.
 We further checked the quality of the posterior by visually assessing the Q-Q plot of the posterior with that of a Gaussian distribution of mean 0 and sd 1 (see Appendix [Model assumptions]).
@@
 
+\hfill
+
 We fitted phylogenetic regression as explained in (i).
-In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability and assumption]).
+In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability, and assumption]).
 
@@
 
-To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree.
+To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree .
 
@@
 if body mass was provided by different datasets etc.).
-For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before) using the "standard" dataset and the consensus tree.
-
-|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes weak sensitivity of the results.
+For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before), using the "standard" dataset and the consensus tree.
+
+|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes the weak sensitivity of the results.
 
@@
 We considerably value the help provided by J.
-Drury in making some scripts available, but mostly for helping us in solving issues encountered with the use of his functions in the *RPANDA* package in *R*, and that of M-C.
-Quidoz for assistance for using the CEFE cluster.
+Drury in making some scripts available functions in the *RPANDA* package in *R* and helping us in running them, and that of M-C.
+Quidoz for assistance in using the CEFE cluster.
 We thank S.
 Benhamou and M.
-Clairbaux for discussion and advices on spatial projections, and M.
+Clairbaux for discussions on spatial projections, and M.
 Quéroué, V.
 Lauret, A.
-Caizergues and C.
+Caizergues, and C.
 Teplistky for feedback on Bayesian computations too.
@@
 Willems and collaborators, F.
-Pearce and collaborators, Navarrete and collaborators, and C.
+Pearce and collaborators, A.
+F.
+Navarrete and collaborators, and C.
 C.
@@
 rownames(results.df_gradient) <- NULL
-knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
 The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
@@
 rownames(results.df_diversification) <- NULL
-knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between species diversification and relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
 samp.=Effective sample (adjusted for autocorrelation).
@@
 
-knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
+knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
 The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
@@
 
-```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Mercator projection of the world | Areas were defined as a combination of geographic and environmental criteria relatively to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
-Note that the north part of Africa and the south of Europe were discarded despite the presence of one primate species (*Macaca sylvanus*), because of its geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-Hence, *Macaca sylvanus* is not considered in this study.", sep="")}
+```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Mercator projection of the world | Areas were defined as a combination of geographic and environmental criteria relative to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
+Note that the north part of Africa and the south of Europe were discarded because *Macaca sylvanus* was not considered.
+", sep="")}
 
@@
 
-```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels of sympatry vary across the primate phylogeny | Primate phylogeny from a consensus tree of 1000 possible trees from the 10kTrees project is depicted in the centre, together with abbreviated species name.
+```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels  of species sympatry vary across the primate phylogeny | Primate phylogeny from the consensus tree of the 10kTrees project is depicted in the center, together with abbreviated species names.
 The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
-Sympatric frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory of ", folivoryThresholdVector[1], "%) species are linked by light grey lines.
-The geographic areas occupied by a species are depicted by the coloured rectangles.
+Sympatric frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory threshold of ", folivoryThresholdVector[1], "%) species are linked by light grey lines.
+The geographic areas occupied by a species are depicted by coloured rectangles.
 Presence was assessed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1]*100, "%.", sep="")}
@@
 <!-- , although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere -->
-```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) Circular plot of relative size of the different brain areas.
+```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) Circular plot of the relative sizes of the different brain areas.
 Colours indicates the rows for the different brain areas.
@@
 The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain regions, when available, is depicted by a plain circle for frugivorous species.
-The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and folivory to ", folivoryThresholdVector[1], "%.
-(Right) The different studied brain areas (human brain as illustration).
-In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support a working memory and memory consolidation of general and immediate information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
+The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and the folivory threshold to ", folivoryThresholdVector[1], "%.
+(Right) The different studied brain areas (human brain as an illustration).
+In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support working memory and memory consolidation of immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
 The Striatum is involved in social information processing [@baez2013role].", sep="")}
@@
 
-```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the Hippocampus and Striatum are best fitted by models considering sympatry of trait evolution in frugivorous primates | Plotted is the AICc weight, a measure of relative support for a given model, for models not considering  sympatry (BM, OU, EB) and considering sympatry (MC, DD$_{lin}$, DD$_{exp}$).
-The points represent the average AICc weight obtained (when considering the six models from a same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does interspecific interactions shape brain size evolution?])."}
+```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the Hippocampus and Striatum in frugivorous primates are best fitted by models of trait evolution considering species sympatry | Plotted is the AICc weight, a measure of relative support for a given model, for models not considering species sympatry (BM, OU, EB) or considering species sympatry (MC, DD$_{lin}$, DD$_{exp}$).
+The points represent the average AICc weight obtained (when considering the six models from the same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does species sympatry shape brain size evolution?])."}
 
@@
 
-```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4, fig.height=4, fig.cap=paste("Percent of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
+```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4, fig.height=4, fig.cap=paste("Percentage of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
 ", geographicThresholdVector[2]/2*100, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2]*100, "%.
@@
 
-par(mar=c(4, 3, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
+par(mar=c(3, 5, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
 plot(
-  x=0, y=0, xlab="Overlap threshold", ylab="Percent of species with different biogeographic areas\ncompared to when a 15% overlap is used", 
+  x=0, y=0, xlab="Overlap threshold", ylab="Percentage of species with different biogeographic areas\ncompared to when a 15% overlap is used", 
   xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
@@
 
-```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10.5, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated to a specific trait: Brain, Hippocampus, Neocortex and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
+```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10.5, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated with a specific trait: Brain, Hippocampus, Neocortex, and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
 indicates the frugivory rate and Fol.
@@
 
-```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4.5, fig.height=4.5, fig.cap="\\footnotesize Diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 90% (at a step of 10%) is depicted by the plain line.
+```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4.5, fig.height=4.5, fig.cap="\\footnotesize Net diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 95% (at a step of 10%; then 5% from 90%) is depicted by the plain line.
 The grey background depicts the standard deviation.
@@
 The three fitted regressions are displayed by the dashed lines.
-The choice of two breakpoints was priorily assessed by choosing the number of breakpoints minimizing the Bayesian Information Criterion.
-The identified breakpoints coin with identified sharp decrease in extinction rate [@arbour2017major; @springer2012macroevolutionary] due to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
+The choice of two breakpoints was first assessed by choosing the number of breakpoints minimizing the Bayesian Information Criterion.
+The identified breakpoints, coining with previous studies [@arbour2017major; @springer2012macroevolutionary], correspond to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
 
@@
 
-## Phylogenetic regressions: results, stability and assumption
+## Phylogenetic regressions: results, stability, and assumption
 
@@
 \centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of relative brain size in function of sympatry intensity indices | Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the distribution range overlapped by sympatric species is averaged, while the right graphics do the opposite.
+\caption{\scriptsize{Phylogenetic regressions of relative brain size as a function of sympatry level indices | Left graphics show the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species  is averaged, while the right graphics do the opposite.
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
@@
 \centering\includegraphics[width=0.7\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of the diversification rate in function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
 The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent grey background.}}\label{fig:figRegressionDiversification}
@@
 
-(b) Phylogenetic regressions: diversification and sympatry
+(c) Phylogenetic regressions: diversification and sympatry
 
@@
 \centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of diversification rate in function of sympatry intensity indices | Left graphics depict the effect of the number of sympatric species on the brain size, when the effect of the percentage of the distribution range overlapped by sympatric species is averaged, while the right graphics do the opposite.
+\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of sympatry level indices | The left graphic depicts the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species is averaged, while the right graphic does the opposite.
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
@@
 re-sampling among possible values given all datasets) or when using different parameterisation (i.e.
-"sampling fraction" of known species for diversification analysis).
+"sampling fraction" of known species for diversification analyses).
 

### 2021-12-14 Article/Coverletter.Rmd
Update article + update readme + reorganise files

@@
 |   The road to understanding the evolutionary history of cognition is still little paved.
-Currently formulated theories generally oppose social and ecological drivers of cognition and are often framed within a foraging-related context.
-These theories, nonetheless, primarily focus on the challenges an individual faces with regards to its food spatio-temporal distribution, or to its conspecifics from a same group and/or species.
-Space is also shared with other species with similar ecological niche that might also shape the environment and be competitors or cooperators.
-Thus, it is likely that cognate species that share diet are likely to affect the social and ecological environment a species evolves in.
+Currently formulated theories generally oppose social and ecological drivers of cognition, and prioritise direct or indirect interactions with conspecifics.
+Yet, space is also shared with other species with similar ecological niches.
+Thus, it is likely that cognate species that compete for food are likely to affect the social and ecological environment a species evolves in too.
 This should therefore loop onto the selective pressures that apply to cognition.
@@
 
-|   To help filling this gap, we perform a global-scale analysis to investigate the role of sympatry in shaping the size of different brain areas in animals, and shaping their evolutionary success.
+|   To help fill this gap, we perform a global-scale analysis to investigate the role of sympatry in shaping the size of different brain areas, and shaping their evolutionary success.
 In particular, we focus on frugivorous primates because the consumption of fruits is highly tightened to advanced cognitive skills.
-Using recently developed phylogenetic models accounting for competition or not with sympatric species, we retrace the evolution of the size of brain areas related to foraging or not.
-We also correlate brain size, diversification rate (a proxy for evolutionary success), and sympatry intensity.
+Using recently developed phylogenetic models accounting for species sympatry or not, we retrace the evolution of the size of brain areas related to foraging or not.
+We also correlate brain sizes, species diversification rates, and levels of sympatry.
 
-|  We show that the evolutionary history of brain areas associated to foraging tasks is more accurately described by competitive models.
+|  We show that the evolutionary history of brain areas associated with foraging tasks is more accurately described by models considering  sympatry.
 In particular, sympatry negatively affects their relative size.
-We additionally show that, even if these brain sizes are not related to diversification rate, this latter is reduced when sympatry rates increases.
-Altogether, these findings suggest that sympatry is associated to a relaxed selection for bigger brain, or even a positive selection for smaller brain.
-We speculate that this is due to an over-complexification of the environment, which makes cognition not advantageous anymore.
+We additionally show that, even if these brain sizes do not directly impact primate diversification, this latter slowdowns when sympatry increases.
+Altogether, these findings suggest that sympatry is associated with a positive selection for smaller brains.
+We speculate that this is due to an over-complexification of the environment, which makes cognition not advantageous anymore for sympatric species.
 
-|  This study enlarges our understanding on the effect of space use and species distribution in animal cognition.
-It shows unprecedent evidence of direct and/or indirect effect of competition on cognition evolution, questioning proximate mechanisms at play.
-We strongly think that this stands as an important complementary piece of global analyses that were already published in your journal that will be of interest to empiricists and theoreticians from ecological and evolutionary fields.
+|  This study enlarges our understanding of the effect of space use and species distribution in animal cognition.
+It shows unprecedented evidence of the direct and/or indirect effects of interspecific competition on cognition evolution, questioning proximate mechanisms at play.
+We strongly think that this stands as an important complementary piece of global analyses that were already published in your journal.
+We believe it will be of interest to empiricists and theoreticians from ecological and evolutionary fields.
 On behalf of all authors, I certify that this is a completely novel contribution that has not been submitted elsewhere, and that all authors approved the manuscript and its submission to *`r journal`*.

### 2022-01-28 Article/Article_forsubmission.Rmd
Update for submission - Separation Sup mat and Main text - Add Rmd word compilation

--- 2021-12-14 Article/Article.Rmd
@@
 author:
-  - name: Benjamin Robira
-    email: benjamin.robira@normalesup.org
-    institute: [CEFE, MH]
-    correspondence: true
-  - name: Benoît Perez-Lamarque
-    email: benoit.perez@ens.psl.eu
-    institute: [ENS, MNHN]
-institute:
-  - CEFE: Centre d’Écologie Fonctionnelle et Évolutive, Université de Montpellier & CNRS, Montpellier, France.
-  - MH: Anthropologie et Ethnobiologie, Centre National de la Recherche Scientifique/Muséum National d'Histoire Naturelle, University Paris Diderot, Sorbonne Paris Cité, Musée de l'Homme, Paris, France.
-  - ENS: Institut de Biologie de l’École Normale Supérieure (IBENS), École Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France.
-  - MNHN: Institut de Systématique, Évolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France.
+#   - name: Benjamin Robira
+#     email: benjamin.robira@normalesup.org
+#     institute: [CEFE, MH]
+#     correspondence: true
+#   - name: Benoît Perez-Lamarque
+#     email: benoit.perez@ens.psl.eu
+#     institute: [ENS, MNHN]
+# institute:
+#   - CEFE: Centre d’Écologie Fonctionnelle et Évolutive, Université de Montpellier & CNRS, Montpellier, France.
+#   - MH: Eco-anthropologie (EA), Muséum National d'Histoire Naturelle, CNRS, Université de Paris, Musée de l'Homme, Paris, France.
+#   - ENS: Institut de Biologie de l’École Normale Supérieure (IBENS), École Normale Supérieure, CNRS, INSERM, Université PSL, Paris, France.
+#   - MNHN: Institut de Systématique, Évolution, Biodiversité (ISYEB), Muséum National d’Histoire Naturelle, CNRS, Sorbonne Université, EPHE, Université des Antilles, Paris, France.
 
@@
    fig_caption: true
-   pandoc_args:
-     - '--lua-filter=scholarly-metadata.lua'
-     - '--lua-filter=author-info-blocks.lua'
+   #pandoc_args:
+     #- '--lua-filter=scholarly-metadata.lua'
+     #- '--lua-filter=author-info-blocks.lua'
+ keep_tex: true
 always_allow_html: true
@@
 bibliography: bibliographyarticlepackage.bib
-biblio-style: nature
+biblio-style: apa
 biblatexoptions: [natbib=true]
@@
   - \usepackage{tcolorbox}
-  - \pagenumbering{gobble} #for no page numbering
+  #- \pagenumbering{gobble} #for no page numbering
+  - \pagenumbering{arabic} #for no page numbering
   - \setlength{\parskip}{0em} #to remove line gaps
@@
 knitr::opts_chunk$set(include=FALSE, echo=FALSE, message=FALSE)
-knitr::opts_chunk$set(dpi=300) # Figure resolution and size out.width = '100%', 
+knitr::opts_chunk$set(dpi=300) # Fig. resolution and size out.width = '100%', 
 knitr::opts_chunk$set(fig.pos = 'p'#, fig.align = 'center'
                       ) # Places figures on pages separate from text, centered
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R figure caption
+knitr::opts_chunk$set(fig.env="figure") # Latex Fig. environment
+knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R Fig. caption
 ```
@@
 ```{r wordCount}
-words <- RmdWords("Article.Rmd")
+words <- RmdWords("Article_forsubmission.Rmd")
 ```
@@
 
-**Abstract |** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
+**Abstract |**  
+**Aim** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
 Yet, space is often simultaneously occupied by species sharing the same ecological guild.
 These sympatric heterospecifics can compete for food, thereby stimulating or hampering cognition.
-Considering brain size as a proxy for cognition, we used primates to test for the intertwining between species sympatry and cognition.
-We retraced the evolutionary history of several brain areas with evolutionary models considering or not sympatry.
-Sympatry-related models best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
+Considering brain size as a proxy for cognition, we tested for the intertwining between species sympatry and cognition in primates.
+**Location** Central/South America, Africa, South/East Asia  
+**Time period** From ~ 74 My ago to present  
+**Major taxa studied** Primates  
+**Methods** We compiled the size of several brain areas, diet and range data, and the phylogeny of more than 300 primate species based on published literature.
+We first retraced the evolutionary history of primate diet and biogeography.
+We then focused on frugivorous primates, and retraced the evolutionary history of the size of brain areas with evolutionary models considering or not sympatry.
+**Results** Models considering sympatry best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
 By contrast, the whole brain or brain areas used in immediate information processing were best described by models not considering sympatry.
 Moreover, sympatry negatively affected primate diversification.
-Overall, this comparative study suggests that species sympatry contributes to shaping primate cognition and diversification.
-We speculate that this is due to an over-complexification of resource spatio-temporality.
+**Main conclusions** This comparative study suggests that species sympatry contributes to shaping primate cognition and diversification.
+We speculate that this is due to an over-complexification of resource spatio-temporality in sympatry that counteracts the benefits of high cognitive abilities.
 
@@
 <!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
-
+**Running title:** Species sympatry shapes primates' brain size  
 \faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
-
-\faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline
+<!-- \faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline -->
 <!-- Character Count: `r words$num_char` -->
@@
 
+<!-- TC:ignore -->
+
 <!-- On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
@@
 
+<!-- TC:endignore -->
+
 \initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics].
@@
 However, space is often occupied by many species belonging to the same ecological guild.
-Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food ([@Avargues-Weber2013]; Hypothesis 2).
+Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food [@Avargues-Weber2013, Hypothesis 2].
 In addition, direct interactions with heterospecifics, as much as with conspecifics [@dunbar2017there], might also affect cognition (Hypothesis 3).
@@
 Besides individual foraging, cognition can also be triggered by direct "social" interactions with other individuals [@byrne1994machiavellian; @dunbar2017there].
-The Striatum is a brain area stimulated during social interactions [@baez2013role], and should, therefore, be affected by direct social interactions with heterospecifics (Hypothesis 3).
+The Striatum is a brain area stimulated during social interactions [@baez2013role] and should, therefore, be affected by direct social interactions with heterospecifics (Hypothesis 3).
 
@@
 To infer the effect of species sympatry on brain size evolution within frugivorous primates, we evaluated the support for evolutionary models accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between brain size or current sympatry and the evolutionary consequences (assumed to be reflected by species diversification) in all primates.
+Finally, we investigated the evolutionary  of the intertwining between brain size and sympatry, by testing for correlative patterns between brain size or current sympatry and the species diversification in all primates.
+
+# Methods
+
+Data processing, analyses, and plots were computed with R software [`r extractRversion()`, @Rsoftware].
+
+### Phylogeny
+
+We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on May 2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
+The trees contain `r length(phylo_init$tip.label)` primate species (Fig.
+\@ref(fig:phylogeny)).
+Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*.
+The latter was discarded because of geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
+A summary of available data per species is presented in Appendix Fig.
+S3.
+
+### Trait data
+
+Data were pooled from previous literature surveys (see Appendix [Data availability]).
+Brain data were obtained from @decasien2019primate for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for the whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size.
+They were freely available in the main manuscript or supplementary materials.
+Percentage of frugivory and/or folivory was obtained based on a freely available dataset from @decasien2017primate, @powell2017re, and @willems2013collective.
+Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Fig.
+S3.
+From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
+
+\hfill
+
+\begin{center}
+
+$\mathrm{EQ}=1.036 \times \mathrm{Brain\,volume}/ (0.085 \times \mathrm{Body\,mass}^{0.775})$
+
+\end{center}
+
+\hfill
+
+with the brain volume in cm$^{3}$, 1.036 g/cm$^{3}$ being the assumed homogeneous brain density, and the body mass in g.
+EQ indicates whether the brain size ranges above (> 1) or below (< 1) expected given the body mass.
+Body mass was obtained from @decasien2017primate, @powell2017re, @grueter2015home, @pearce2013space.
+The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention [Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, @wiltgen2004new; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, @koziol2014consensus; @sokolov2017cerebellum], short-term working memory and long-term spatio-temporal memory [Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, @burgess2002human].
+The Striatum (N$_{Striatum,max}$ = `r maxStriatum`) supports information processing during social interaction, reward assessment, planning or goal-oriented behaviours [@baez2013role; @johnson2007integrating].
+To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
+As such, the use of specific region sizes relative to the body mass and not raw sizes depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se [but see discussion in @deaner2000comparative].
+
+### Ranging Data
+
+Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list [@IUCN].
+Ranging data were available for `r nrow(matrixRangingSensitivity[!is.na(matrixRangingSensitivity[,1]),])` species among the `r length(phylo_init$tip.label)` represented in the 10kTrees primate phylogeny.
+
+## Primate species sympatry
+
+For primate biogeography, @kamilar2009environmental determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
+We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
+These geographic areas are represented in Fig.
+\@ref(fig:figmap).
+One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in the surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Fig.
+\@ref(fig:figmap)).
+Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlapping contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
+
+|   We retraced the biogeographic history of the lineages based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
+We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see @matzke2013probabilistic for further details on these events).
+We fixed to three areas the maximum number of areas that a lineage can simultaneously occupy  since it offers the possibility to occupy a complete mainland continent while keeping computational time reasonable..
+Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for the uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
+
+## Dietary guilds
+
+We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate , prioritizing frugivory over folivory.
+First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold).
+If this was not the case, or frugivory rate was unavailable, a species could be classified as folivorous if the folivory rate was at least above `r folivoryThresholdVector[1]` (low threshold) or `r folivoryThresholdVector[2]`% (high threshold).
+Otherwise, @decasien2017primate gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria.
+Whenever the rate was not available, we referred to this classification.
+In any other cases, the species was discarded.
+
+```{r transitionMatrix}
+
+transitionMatrix <- matrix(NA, nrow=repetition, ncol=2)
+
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        start=which(is.na(transitionMatrix[,1]))[1]
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_simmap_transition",a,"_",b,"_",c,"_",d, ".txt", sep=""))
+          transitionMatrix[start,1] <- toAdd[1,1]
+          transitionMatrix[start,2] <- toAdd[2,1]
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+minProba.v <- apply(abs(transitionMatrix), 2, min)
+maxProba.v <- apply(abs(transitionMatrix), 2, max)
+
+```
+
+|   Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait, but with no prior on the transition matrix.
+Again, the obtained character history is in no case certain.
+Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits, to account for the uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
+
+## Phylogenetic models
+
+### Models of trait evolution: does species sympatry shape brain size evolution?
+
+\hfill
+
+(a)	Fitting models of trait evolution
+
+\hfill
+
+We focused only on frugivorous primates and fitted phylogenetic models of the evolution of the size of the different brain areas.
+The models were based on different sample sizes depending on the brain areas and the frugivory thresholds considered: EQ: `r minEQ` to `r maxEQ`, Striatum: `r minStriatum` to `r maxStriatum`, MOB: `r minMOB` to `r maxMOB`, Neocortex: `r minNeocortex` to `r maxNeocortex`, Hippocampus: `r minHippocampus` to `r maxHippocampus`, Cerebellum: `r minCerebellum` to `r maxCerebellum` frugivorous species.
+For each set of models in a given brain area, the sample was strictly identical, allowing within-set comparisons.
+Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
+We calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure \@ref(fig:figbrain)).
+We specifically considered three different models considering species sympatry: the matching competition (MC) model [@nuismer2015predicting] and density-dependent models [DD$_{lin}$ and DD$_{exp}$, @drury2016estimating].
+These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet.
+These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas [see @drury2016estimating].
+The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating].
+Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size.
+Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
+Density-dependence means that the evolutionary rate, $\lambda$, of trait change, varies either positively or negatively as a function $f$ of the number of frugivorous sympatric lineages, such as
+
+\begin{center}
+
+\hfill
+
+$f_{lin}(\lambda)=\lambda_{0} + rl$
+
+$f_{exp}(\lambda)=\lambda_{0}\exp(rl)$
+
+\hfill
+
+\end{center}
+
+where $\lambda_{0}$ corresponds to the value of the initial ancestor, $l$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
+Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guilds]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
+|	We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry: the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU, a model with an optimum value, see @blomberg2020beyond for a review), or the Early-Burst model (EB), for assessing a time-dependence of the evolutionary rate @blomberg2003testing.
+These models without species sympatry, (BM, OU, EB) were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
+All these models were repeated `r numberSimulations` times, using `r randomSampling` different combinations of the evolutionary histories of primate ranges and diets.
+They were then compared within an information-theoretic framework [@burnham2002model], based on the weights of Akaike Information Criteria corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
+The model weight depicts how well the model fits the observed evolutionary pattern compared with the other tested models.
+
+\hfill
+
+```{r prepfigevolution}
+
+###Set working directory
+setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
+
+summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
+
+counter=0
+start=counter
+end=counter
+numberSimulations=10
+totModelsWorked=c(0,0,0,0,0,0,0)
+for(a in 1:2){
+  for(b in 1:2){
+    for(c in 1:2){
+      for(d in 1:10){
+        counter=end+1
+        start=counter
+        end=counter + numberSimulations - 1
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
+        totModelsWorked[1]=totModelsWorked[1]+1
+        }, error=function(e){
+          #Do nothing
+          }
+        )
+
+        tryCatch(
+        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryEQFrugivory[start:end,] <- toAdd
+        totModelsWorked[2]=totModelsWorked[2]+1
+        }, error=function(e){
+          #Do nothing
+        }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryNeocortexFrugivory[start:end,] <- toAdd
+        totModelsWorked[3]=totModelsWorked[3]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryHippocampusFrugivory[start:end,] <- toAdd
+        totModelsWorked[4]=totModelsWorked[4]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryCerebellumFrugivory[start:end,] <- toAdd
+        totModelsWorked[5]=totModelsWorked[5]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryStriatumFrugivory[start:end,] <- toAdd
+        totModelsWorked[6]=totModelsWorked[6]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+
+        tryCatch(
+          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
+        summaryMOBFrugivory[start:end,] <- toAdd
+        totModelsWorked[7]=totModelsWorked[7]+1
+          }, error=function(e){
+            #Do nothing
+          }
+        )
+      }
+    }
+  }
+}
+
+summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
+summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
+summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
+summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
+summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
+summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
+summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
+
+colnames(summaryBrainFrugivory) <- colnames(toAdd)
+colnames(summaryEQFrugivory) <- colnames(toAdd)
+colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
+colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
+colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
+colnames(summaryStriatumFrugivory) <- colnames(toAdd)
+colnames(summaryMOBFrugivory) <- colnames(toAdd)
+
+##----
+
+colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
+
+models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
+colourModels <- brewer.pal(n = 6, name = "Set1")
+
+```
+
+### Models of species diversification
+
+We investigated how primates diversified over time and across lineages.
+Lineage-specific net diversification rates (defined as speciation minus extinction rates) were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
+Particularly, we used *ClaDS2*, the model with constant turnover (i.e.
+constant ratio between extinction and speciation rates; see Appendix [Primate diversification rate over time] for further explanations).
+We extracted the mean diversification rates through time and the lineage-specific diversification rate of each extent species.
+
+### Phylogenetic regressions
+
+\hfill
+
+(a)	Determining the effect of sympatry on brain sizes
+
+\hfill
+
+To determine the nature of the relationship between species sympatry and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions for each brain region individually and for frugivorous species only.
+This model is a derivative of the Brownian Motion model, where the phylogenetic variance-covariance matrix has all coefficients, but its diagonal ones, multiplied by lambda: it thus relaxes the hypothesis of Brownian Motion since we included brain areas for which the evolutionary history was best described by models considering sympatry (see [Results]).
+To fit these models, we used a frequentist-based approach with the “phylolm” function from the *phylolm* package [@phylolm].
+We considered the least stringent frugivory assessment, with the frugivory threshold fixed to `r frugivoryThresholdVector[1]`% and the folivory threshold fixed to `r folivoryThresholdVector[1]`%.
+If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
+could be either of the two), it was considered as frugivorous nonetheless.
+
+|   The response variable was the relative size of brain areas.
+Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability, and assumption]).
+In this model, the covariates (i.e.
+continuous predictors) were the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square-rooted, to reach symmetrical distribution).
+For a given species A, sympatry with another species B was considered when species B range overlapped on more than `r geographicThresholdVector[1]*100`% of the range of species A.
+This was done to reduce the noise induced by coarse identification of species range.
+
+\hfill
+
+(b)	Diversification and brain size
+
+\hfill
+
+We also fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the net diversification rates (i.e.
+the difference between speciation and extinction rates), estimated for each extant species by the *ClaDS* algorithm.
+Because of troubles of the frequentist-based approach, we used a Bayesian-based approach.
+We used the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
+Each chain was based on a burnin period of `r burnin` iterations, among a total of `r nitt` iterations, and was sampled every `r thin` iterations.
+We used the least informative priors.
+Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
+Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values.
+
+\hfill
+
+(c) Diversification and species sympatry
+
+\hfill
+
+To determine whether species sympatry was associated with specific diversification patterns, we fitted frequentist-based Gaussian Pagel's lambda phylogenetic regressions with the lineage-specific diversification rate as output variable, and used the two metrics for describing sympatry (the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as in (a).
+
+Details on the implementation, stability, and uncertainty of phylogenetic regressions are provided in appendix (see [Phylogenetic regressions: results, stability, and assumption]).
 
 # Results
+
+<!-- TC:ignore -->
 
@@
 
-We gathered a large database on the whole brain size, the size of the MOB, Cerebellum, and the Neocortex, involved in immediate sensory information processing, and the Striatum and the Hippocampus, related to either social and foraging-related memory, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
-After pondering by whole-body mass, we observed ample variations in brain area relative sizes.
-For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural].
-The latter show the highest relative size of the Striatum (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
-
-|   To get the evolutionary history of species sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
-We then calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
-\@ref(fig:figbrain)).
-We specifically considered the matching competition (MC) model [@nuismer2015predicting] and density dependence models (DD$_{lin}$ and DD$_{exp}$), which assume a linear or exponential dependence of the brain sizes evolutionary rates on the number of sympatric lineages ([@drury2016estimating] see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around an optimal value (e.g.
-stabilizing selection; see [@blomberg2020beyond] for a review), or the Early-Burst model (EB, [@blomberg2003testing]), the latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density dependence is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criteria corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-
-|   We found that models not considering species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
-The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefits of brain development [@isler2009expensive].
-By contrast, density-dependence models considering sympatry were best supported in the foraging-related and social-related areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions [@baez2013role].
-The fact that we inferred positive rates *r* of density-dependence (Figure \@ref(fig:figresultsevolution)), suggested an acceleration of the evolutionary tempo of trait evolution together with increased diversity of sympatric lineages for the Hippocampus and the Striatum.
-The Main Olfactory Bulb (MOB), the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole: yet, Brownian-Motion was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-
 ```{r samplecooccurrence}
@@
 
+<!-- TC:endignore -->
+
+The database we gathered contained between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
+After pondering by whole-body mass, we observed ample variations in brain area relative sizes.
+For instance, the lemuriformes, which are known to prioritize smell compared to other primate species, have the largest relative MOB size (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
+Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural].
+The latter show the highest relative size of the Striatum (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
+In terms of measure of sympatry, we observed that on average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
+That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
+In terms of the distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species to `r maxNspeciesCoocc`.
+
+|   To get the evolutionary history of species sympatry between frugivorous lineages, we first reconstructed primate biogeography history when considering `r length(areaName)` biogeographic areas [Fig.
+\@ref(fig:figmap), @kamilar2009environmental] and their diet evolution.
+We then modelled the evolution of the size of the whole brain (EQ), or regionalized areas (Neocortex, Cerebellum, MOB, Hippocampus and Striatum) when considering the history of sympatry or not.
+We found that models not considering species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Fig.
+\@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
+The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-off between costs and benefits of brain development [@isler2009expensive].
+By contrast, density-dependent models considering sympatry were best supported in the foraging-related and social-related areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions [@baez2013role].
+The fact that we inferred positive rates *r* of density-dependence (Fig.
+\@ref(fig:figresultsevolution)) suggested an acceleration of the evolutionary tempo of trait evolution together with increased diversity of sympatric lineages for the Hippocampus and the Striatum.
+The MOB, the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole.
+Yet, BM was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Fig.
+\@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), especially since this coincided with the most reduced sample size we had (N$_{species}$ = `r minMOB` to `r maxMOB`).
+
+<!-- TC:ignore -->
+
 ```{r estimateRegGradient, error=TRUE, include=TRUE}
@@
 
+<!-- TC:endignore -->
+
 |   Next, to understand the effect of sympatry on brain sizes (i.e.
-toward “bigger” or “smaller” brains the more sympatric species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
-For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered as covariates the average percentage of overlapping range with other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range based on IUCN data [@IUCN].
-On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
-That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
-In terms of the distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species to `r maxNspeciesCoocc`.
-The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the average percentage of overlapping range correlated with the relative size of areas that were better fit with models considering sympatry: the Hippocampus and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
-The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher range overlap between frugivorous species associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
-Given the acceleration of the evolutionary tempo with species sympatry ($r>0$ in the density-dependence models), it suggests that compared with isolated species, sympatric species are subject to a positive selection towards smaller brains, and not to a less intense selection for advanced cognitive abilities.
+toward “bigger” or “smaller” brains the more sympatric species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)) between the relative brain size values of the different areas and the average percentage of overlapping range with other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range based on IUCN data [@IUCN].
+The number of sympatric species never influenced significantly the relative brain sizes (Table \@ref(tab:tableRegGradient)).
+Conversely, we found that the average percentage of overlapping range correlated with the relative size of brain areas that were better fit with models considering sympatry: the Hippocampus and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
+The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher range overlap between frugivorous species associates with lower relative size, insensitive to data and phylogenetic uncertainty (Appendix Table S1, Appendix Fig.
+S8, Appendix Table S1).
+Given the acceleration of the evolutionary tempo with species sympatry ($r>0$ in the density-dependent models), it suggests that compared with isolated species, sympatric species are subject to a positive selection towards smaller brains, and not to a less intense selection for advanced cognitive abilities.
+
+<!-- TC:ignore -->
 
@@
 
-|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with the net species diversification rates (defined as speciation minus extinction rates).
-To do so, we used lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
-Overall, species diversification rates, estimated based on the primate molecular phylogeny, increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around 25 and 11 Myr ago (Figure \@ref(fig:figdiversificationTime)).
-When accounting for phylogenetic dependence, no significant relationship between the net diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
-Given the context-dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between the diversification rate and the three brain areas affected by species sympatry.
-Surprisingly however, we found no positive association between the net diversification rate and the EQ, nor with the relative sizes of the Cerebellum or the Neocortex, two areas insensitive to species sympatry too.
-This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
-The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex, if discarding phylogenetic non-independence (Figure \@ref(fig:figRegressionDiversification)).
-Indeed, sudden encephalisation in primates is clearly associated with a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically-corrected analyses, as we cannot decipher whether the connivance between brain size and species diversification results from a true biological link or appeared by chance.
-A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenges [@sol2007big].
-This means that, despite what we found here, a positive association between brain size and species diversification evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
-Finally, although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
-In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification rate, a density-dependence trend that is frequently observed in many tetrapod clades [@condamine2019assessing].
+<!-- TC:endignore -->
+
+|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with the lineage-specific net diversification rates (defined as speciation minus extinction rates).
+Overall, species diversification rates, estimated based on the primate molecular phylogeny, increased over time (Appendix Fig.
+S4), particularly in the early and late Miocene, around 25 and 11 Myr ago (Appendix Fig.
+S4).
+When accounting for phylogenetic dependence, no significant relationship between the net diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Appendix Fig.
+S8; see robustness in Appendix Table S2).
+Although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
+In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Appendix Fig.
+S8, Appendix Table S3).
+In other words, the higher the number of sympatric species, the lower the diversification rate.
 
@@
 This evidence might suggest a stabilisation towards an optimal size resulting from an equilibrium between costs and benefits.
-As the brain is regionally specialised [@barton2000mosaic], different brain areas could be under different selective pressures.
-This is evidenced, here, by the differences of relative sizes across lineages in the MOB or Striatum in particular.
-We further show that sympatry is one factor that affects the selective regime under which some brain region evolves: although the brain as a whole was insensitive to species sympatry, the latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
+As the brain is regionally specialised [@barton2000mosaic], different brain areas can nonetheless be under different selective pressures, and thus can evolve rather independently to each other, despite responding similarly to allometric/developmental constraints or when in close spatial proximity [@Gomez-Robles2014].
+This is evidenced by the differences of relative sizes across lineages in the MOB or Striatum in particular, and by the difference in the evolutionary models that best fitted the data for each brain area.
+We indeed show that sympatry is one factor that affects the selective regime under which only some brain region evolves: although the brain as a whole was insensitive to species sympatry, the latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
 These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under strong selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
 
-|   The negative influence of sympatry on the Striatum might be quite surprising.
-Direct interactions with heterospecifics should stimulate this area (Hypothesis 3).
-We observed that this area was relatively larger in callitrichines, particularly known to perform mixed-species groups [@heymann2015unlike].
-When interacting with conspecifics, the Striatum underpins reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating].
-These skills are key within group, following a Machiavellian perspective [@byrne1994machiavellian].
-Yet, these skills might also be relevant in a foraging context.
-It is thus possible that actions underpinned by the Striatum (e.g.
-planning/anticipating heterospecifics moves), might be key and up to now overlooked, when foraging in a multi-species context too.
-
-|   Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
+|   As expected (Hypothesis 3), the Striatum size was relatively larger in callitrichines, particularly known to perform mixed-species groups [@heymann2015unlike].
+Yet, overall, the Striatum size was negatively affected by sympatry.
+This puzzle might take root in secondary, but key, functions supported by the Striatum, namely reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating].
+These three functions might as well be advantageous when foraging.
+As for the Hippocampus, then, the increase in environment unpredictability could diminish the benefits of these future-oriented skills.
+
+|   Overall, the fact that only the Hippocampus and the Striatum, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of sympatric species on resource spatio-temporality (Hypothesis 1).
 Competition is generally the first-thought mechanism to describe community structures [@rocha2015role] because it might affect the environment, and associate selective pressure, in which species evolve.
 We show that higher levels of sympatry is actually associated with smaller sizes of the Hippocampus or Striatum (in accordance with Prediction 1.2).
-This suggests that indirect competition for food might contribute to convoluting the environment which might generate a positive selection for smaller brains.
-Not only was brain evolution affected by sympatry, but sympatry induced a slowdown in diversification.
-Density-dependence within a clade is indeed generally associated with lower diversification rates [@moen2014does].
-In particular, species competing for resources are thought to contribute to limiting their ranges [@price2009evolutionarily], hence constraining population size and their subsequent diversification [@pigot2013species].
-These observations thus strengthen the idea of scramble competition between species that cascades both on species population dynamics and species cognition.
+This suggests that indirect competition for food might contribute to convoluting the environment, which might generate a positive selection for smaller brains.
 
@@
 This absence of effect can stem from two possibilities.
-Either sympatry, indeed, does not affect the landscape of cues for foragers.
+Either foragers do not exploit cues left out by sympatric heterospecifics.
 Otherwise, it has been shown that foragers tend to use social information over environmental (i.e.
 personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
-Thus, if environmental complexity increases too much, “social” cues provided by heterospecifics might replace environmental ones.
-From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should, at the very least, remain unaffected by sympatry.
-This nonetheless deserves further attention.
-
-|   To conclude, the use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from [@deaner2000comparative; @healy2007critique; @logan2018beyond]).
+Thus, if environmental complexity increases too much, “social” cues provided by heterospecifics might replace environmental ones, which should not be visible through an analysis of the size of the MOB, the Cerebellum, or the Neocortex..
+This thus deserves further attention.
+
+|  Given the context-dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between the diversification rate and the three brain areas affected by species sympatry.
+Surprisingly however, we found no positive association between the net diversification rate and the EQ, the Cerebellum or the Neocortex, which were insensitive to species sympatry.
+This contradicts a recent study [@melchionna2020macroevolutionary], while a positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenges [@sol2007big].
+Visual inspection of the regressions however clearly evidenced a positive trend if discarding phylogeny (EQ and Neocortex, Fig.
+S6).
+Sudden encephalisation in primates is clearly associated with a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
+Thus, this clearly limits the statistical power of our phylogenetically-corrected analyses, as we cannot decipher whether larger brain size and faster species diversification results from a true biological link or appeared simultaneously but independently.
+This means that, despite what we found here, a positive association between brain size and species diversification evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
+Sympatry, however, induced a slowdown in diversification, a density-dependence trend frequently observed in many tetrapod clades [@condamine2019assessing].
+This frames coherently with a competitive scenario.
+Species competing for resource are thought to contribute to limiting competitors' range [@price2009evolutionarily], hence to constrain population size and diversification rate [@pigot2013species].
+
+# Conclusion
+
+The use of brain size as a proxy for cognition is a central debate with no optimal solution [see grounded criticism from @deaner2000comparative; @healy2007critique; @logan2018beyond].
 The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
-in primates: [@milham2018open]), or with standardized behaviourally explicit comparisons (e.g.
+in primates: @milham2018open), or with standardized behaviourally explicit comparisons (e.g.
 on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time to generate large-enough datasets.
@@
 Similarly, prey-predator races could shape selection on cognitive abilities [@shultz2006chimpanzee].
-As Alice said “It's a great huge game of chess that's being played—all over the world” ([@Carroll], Chapter II) and all individuals are just pieces to play with or against, no matter the species.
+As Alice said “It's a great huge game of chess that's being played—all over the world” [@Carroll, Chapter II] and all individuals are just pieces to play with or against, no matter the species.
 
@@
 \newpage
-
-# Methods
-
-Data processing, analyses, and plots were computed with R software (`r extractRversion()`, @Rsoftware).
-Used codes and data are freely available at [https://github.com/benjaminrobira/Meta_analysis_cognition_primates](https://github.com/benjaminrobira/Meta_analysis_cognition_primates).
-Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*.
-The latter was discarded in the analyses because of geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-A summary of available data per species is presented in Appendix Figure \@ref(fig:figmap).
-
-## Data Collection
-
-### Phylogeny
-
-We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on May 2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
-The trees contain `r length(phylo_init$tip.label)` primate species.
-
-### Trait data
-
-Brain data were obtained from [@decasien2019primate] for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for the whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
-They were freely available in the main manuscript or supplementary materials.
-When a species was represented multiple times within the dataset, we obtained a unique attribute by averaging it.
-From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
-
-\hfill
-
-\begin{center}
-
-$\mathrm{EQ}=1.036 \times \mathrm{Brain\,volume}/ (0.085 \times \mathrm{Body\,mass}^{0.775})$
-
-\end{center}
-
-\hfill
-
-with the brain volume in cm$^{3}$, 1.036 g/cm$^{3}$ being the assumed homogeneous brain density, and the body mass in g.
-EQ indicates whether the brain size ranges above (> 1) or below (< 1) expected given the body mass.
-Body mass was obtained from [@decasien2017primate; @powell2017re; @grueter2015home; @pearce2013space].
-The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, [@wiltgen2004new]; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, [@koziol2014consensus; @sokolov2017cerebellum]), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, [@burgess2002human]).
-The Striatum (N$_{Striatum,max}$ = `r maxStriatum`) supports information processing during social interaction, reward assessment, planning or goal-oriented behaviours [@baez2013role; @johnson2007integrating].
-To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
-As such, the use of specific region sizes relative to the body mass and not raw sizes depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in [@deaner2000comparative]).
-Percentage of frugivory and/or folivory was obtained based on a freely available dataset from [@decasien2017primate; @powell2017re; willems2013collective].
-
-### Ranging Data
-
-Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list [@IUCN].
-Ranging data were available for `r nrow(matrixRangingSensitivity[!is.na(matrixRangingSensitivity[,1]),])` species among the `r length(phylo_init$tip.label)` represented in the 10kTrees primate phylogeny.
-
-## Primate species sympatry
-
-For primate biogeography, based on the structure (i.e.
-number of species and their phylogenetic relationships) of primate communities at different field sites, Kamilar et al.
-[@kamilar2009environmental] determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
-We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
-These geographic areas are represented in Figure \@ref(fig:figmap) and correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia, and the Asian Islands.
-The chosen scale for the areas is large because (i) retracing the history of a large number of areas necessitates considerable computational means.
-In addition, this drastically increases the computational time for fitting the phylogenetic models of brain trait evolution too.
-Furthermore (ii), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with a reduction of ranging areas at an unprecedented speed rate.
-Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
-evidenced on the North American fauna in [@pineda2021mammal]).
-One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in the surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Figure \@ref(fig:figmap)).
-Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlapping contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
-
-|   We retraced the biogeographic history of the lineage ranges based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
-We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see [@matzke2013probabilistic] for further details on these events).
-To reconstruct the evolution of species range, we fixed the maximum number of areas that could be occupied by a lineage at one time to three areas.
-A too high number of areas that can be occupied simultaneously drastically increases computational time.
-Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for the uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
-
-## Dietary guilds
-
-We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate , prioritizing frugivory over folivory.
-First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold).
-If this was not the case, or frugivory rate was unavailable, a species could be classified as folivorous if the folivory rate was at least above `r folivoryThresholdVector[1]` (low threshold) or `r folivoryThresholdVector[2]`% (high threshold).
-Otherwise, [@decasien2017primate] gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria.
-Whenever the rate was not available, we referred to this classification.
-In any other cases, the species was discarded.
-To illustrate, if a species reached 30% of frugivory, and 65% of folivory (the rest being due, for instance, to insectivory), then, it would be categorized as, “frugivorous” if low thresholds are considered, or as “folivorous” in case high thresholds are considered.
-If we suppose now another species with 30% of frugivory and 50% of folivory, but considered by [@decasien2017primate] as frugivorous, then, the species would be “frugivorous” for low threshold, and still “frugivorous” with high thresholds.
-
-```{r transitionMatrix}
-
-transitionMatrix <- matrix(NA, nrow=repetition, ncol=2)
-
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        start=which(is.na(transitionMatrix[,1]))[1]
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_simmap_transition",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-          transitionMatrix[start,1] <- toAdd[1,1]
-          transitionMatrix[start,2] <- toAdd[2,1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-minProba.v <- apply(abs(transitionMatrix), 2, min)
-maxProba.v <- apply(abs(transitionMatrix), 2, max)
-
-```
-
-|   Frugivory was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
-Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
-First, such a static rate does not reflect potential seasonality in fruit-eating (e.g.
-[@masi2009western]), which is generally shorter, hence a lower overall frugivory rate.
-Second, the frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
-Finally, the methodology to obtain this rate could additionally vary (e.g.
-in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves).
-For all these reasons, we used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
-
-|   Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
-at the root), but with no prior on the transition matrix.
-Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits (see [Phylogenetic models]), to account for the uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
-
-## Phylogenetic models
-
-### Models of trait evolution: does species sympatry shape brain size evolution?
-
-\hfill
-
-(a)	Fitting models of trait evolution
-
-\hfill
-
-We focused only on frugivorous primates, because the sample size was otherwise insufficient, and fitted phylogenetic models of the evolution of the EQ or the relative size of a specific brain area considering or not species sympatry.
-Models were fitted on different sample sizes due to the non-availability of some data for some traits.
-Specifically, models using EQ included `r minEQ` to `r maxEQ` frugivorous species.
-Other models included more reduced sample sizes (in species number): Striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), Neocortex (`r minNeocortex` to `r maxNeocortex`), Hippocampus (`r minHippocampus` to `r maxHippocampus`), Cerebellum (`r minCerebellum` to `r maxCerebellum`).
-Nonetheless, for a given set of models (i.e.
-within brain area), the sample was strictly identical, allowing within-set comparisons.
-Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
-Models without species sympatry, Brownian Motion (BM), Ornstein-Uhlenbeck process (OU, model with stabilizing selection), or Early-Burst model (EB, for assessing a time-dependence of the evolutionary rate), were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guilds]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet.
-These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see [@drury2016estimating]).
-We fitted three different models considering species sympatry.
-The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating].
-Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size.
-Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
-Density-dependence means that the evolutionary rate, $\lambda$, of trait changes, varies either positively or negatively as a function $f$ of the number of sympatric lineages sharing the same diet, such as
-
-\begin{center}
-
-\hfill
-
-$f_{lin}(\lambda)=\lambda_{0} + rl$
-
-$f_{exp}(\lambda)=\lambda_{0}\exp(rl)$
-
-\hfill
-
-\end{center}
-
-where $\lambda_{0}$ corresponds to the value of the initial ancestor, $l$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
-All these models were repeated `r numberSimulations` times, using `r randomSampling` different combinations of the evolutionary histories of primate ranges and diets.
-They were then compared within an information-theoretic framework [@burnham2002model] based on the weights of Akaike Information Criteria corrected for small samples (AICc), when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
-The model weight depicts how well the model fits the observed evolutionary pattern compared with the other tested models.
-
-\hfill
-
-```{r prepfigevolution}
-
-###Set working directory
-setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
-
-summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-
-counter=0
-start=counter
-end=counter
-numberSimulations=10
-totModelsWorked=c(0,0,0,0,0,0,0)
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        counter=end+1
-        start=counter
-        end=counter + numberSimulations - 1
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
-        totModelsWorked[1]=totModelsWorked[1]+1
-        }, error=function(e){
-          #Do nothing
-          }
-        )
-
-        tryCatch(
-        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryEQFrugivory[start:end,] <- toAdd
-        totModelsWorked[2]=totModelsWorked[2]+1
-        }, error=function(e){
-          #Do nothing
-        }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryNeocortexFrugivory[start:end,] <- toAdd
-        totModelsWorked[3]=totModelsWorked[3]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryHippocampusFrugivory[start:end,] <- toAdd
-        totModelsWorked[4]=totModelsWorked[4]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryCerebellumFrugivory[start:end,] <- toAdd
-        totModelsWorked[5]=totModelsWorked[5]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryStriatumFrugivory[start:end,] <- toAdd
-        totModelsWorked[6]=totModelsWorked[6]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryMOBFrugivory[start:end,] <- toAdd
-        totModelsWorked[7]=totModelsWorked[7]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
-summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
-summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
-summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
-summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
-summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
-summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
-
-colnames(summaryBrainFrugivory) <- colnames(toAdd)
-colnames(summaryEQFrugivory) <- colnames(toAdd)
-colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
-colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
-colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
-colnames(summaryStriatumFrugivory) <- colnames(toAdd)
-colnames(summaryMOBFrugivory) <- colnames(toAdd)
-
-##----
-
-colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-
-models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
-colourModels <- brewer.pal(n = 6, name = "Set1")
-
-```
-
-(b) Dealing with data uncertainty and parameterisation sensitivity
-
-\hfill
-
-In this analysis, uncertainty can stem from two sources.
-First, the evolutionary history (phylogeny, diet, and ranging) was reconstructed based on Bayesian inference.
-They are susceptible to be uncertain at some points.
-Thus, we used a consensus phylogenetic tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
-In addition, we repeated diet and ranging history reconstructions `r numberSimulations` times.
-
-|   Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
-Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Appendix Figure \@ref(fig:figvariabilitydata)).
-In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
-To account for these three sources of variability, we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
-equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory, and species sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
-
-|   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolutionary reconstructions) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold defining sympatry) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
-We stopped computations when the optimization of the likelihood was excessively long (> 1 week).
-The final sample size thus was of `r min(totModelsWorked[-2])*10` models that covered all the ranges of tested parameters.
-
-### Models of species diversification
-
-We investigated how primates diversified over time.
-Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
-Particularly, we used *ClaDS2*, the model with constant turnover (i.e.
-constant ratio between extinction and speciation rates).
-This Bayesian approach considers speciation rate heterogeneity by modelling small shifts in the rate at speciation events.
-In other words, the two new lineages are assumed to inherit new speciation rates that are sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the initial speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
-Three independent chains were run until their convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
-The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
-The latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
-
-|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
-Estrada et al.
-[@estrada2017impending] estimated that, given current knowledge, the primate clade should be composed of 504 species.
-This means that the current sampling fraction is around 73%.
-We thus parameterized the *ClaDS* algorithm with this value for the estimated sampling fraction.
-Yet, given that the extant number of primate species is subject to controversy, and because the estimated sampling fraction may affect diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
-At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each extant primate species, as well as the mean diversification rate (given all lineages) through time.
-
-### Phylogenetic regressions
-
-\hfill
-
-(a)	Determining the effect of sympatry on brain sizes
-
-\hfill
-
-To determine the nature of the relationship between species sympatry and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
-a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients, but its diagonal ones, multiplied by lambda) for each brain region individually and for frugivorous species only.
-We used Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we included brain areas for which the evolutionary history was best described by models considering sympatry.
-Here specifically, we considered the least stringent frugivory assessment, with the frugivory threshold fixed to `r frugivoryThresholdVector[1]`% and the folivory threshold fixed to `r folivoryThresholdVector[1]`%.
-If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
-could be either of the two), it was considered as frugivorous nonetheless.
-
-|    The response variable was the relative size of brain areas.
-Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability, and assumption]).
-In this model, the covariates (i.e.
-continuous predictors) were the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square-rooted, to reach symmetrical distribution).
-For a given species A, sympatry with another species B was considered when species B range overlapped on more than `r geographicThresholdVector[1]*100`% of the range of species A.
-This was done to reduce the noise induced by coarse identification of species range.
-
-\hfill
-
-(b)	Diversification and brain size
-
-\hfill
-
-In the same way as explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the net diversification rates (i.e.
-the difference between speciation and extinction rates), estimated for each extant species by the *ClaDS* algorithm.
-Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values.
-
-\hfill
-
-(c) Diversification and species sympatry
-
-\hfill
-
-To determine whether species sympatry was associated with specific diversification patterns (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
-
-\hfill
-
-(d)	Model implementation
-
-\hfill
-
-(i)	Effect of sympatry on brain sizes
-
-\hfill
-                                                                                                                                                                           Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (with $\lambda$ indicating the strength of the phylogenetic signal, where $\lambda$=1  corresponds to Brownian Motion, i.e.
-the maximal influence of the phylogenetic history on the trait evolution) estimated by maximum-likelihood (argument “model” set to “lambda”).
-Bootstrapping over `r repetitionBootstrap` independent replicates was done to obtain confidence intervals.
-Other function parameters were set to default.
-Prior to fitting, covariates were transformed so as to reach more symmetrical distributions when adequate.
-Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
-We did not observe correlation issue among predictors neither (VIF$_{max}$ < 2, [@mundry2014statistical]).
-
-\hfill
-
-(ii)	Diversification and brain size
-
-\hfill
-
-We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist approach because it led to a violation of homoscedasticity.
-Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
-Each chain was based on a burnin period of `r burnin` iterations, among a total of `r nitt` iterations, and was sampled every `r thin` iterations.
-We used the least informative priors.
-Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
-Priors on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at a limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
-We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=4)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
-In Appendix [Model assumptions], we present traces and distributions of posterior estimates.
-We further checked the quality of the posterior by visually assessing the Q-Q plot of the posterior with that of a Gaussian distribution of mean 0 and sd 1 (see Appendix [Model assumptions]).
-We present the estimate together with the 95% credibility interval centered on the mode (Highest Density Posterior, HDP), together with a MCMC p-value (pMCMC) that corresponds to the probability that the estimate ($\beta$) is positive if the mean estimate ($\hat{\beta}$) is negative (i.e.
-$P(\beta>0|\hat{\beta}<0)$), or if the mean estimate is positive, the probability that the estimate is negative (i.e.
-$P(\beta<0|\hat{\beta}>0)$).
-
-\hfill
-
-(iii) Diversification and sympatry
-
-\hfill
-
-We fitted phylogenetic regression as explained in (i).
-In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability, and assumption]).
-
-\hfill
-
-(d)	Model robustness
-
-\hfill
-
-To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree .
-
-|   To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10000 possible trees from the 10kTrees project.
-For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple values (e.g.
-if body mass was provided by different datasets etc.).
-For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before), using the "standard" dataset and the consensus tree.
-
-|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes the weak sensitivity of the results.
-
-# Acknowledgements
-
-We considerably value the help provided by J.
-Drury in making some scripts available functions in the *RPANDA* package in *R* and helping us in running them, and that of M-C.
-Quidoz for assistance in using the CEFE cluster.
-We thank S.
-Benhamou and M.
-Clairbaux for discussions on spatial projections, and M.
-Quéroué, V.
-Lauret, A.
-Caizergues, and C.
-Teplistky for feedback on Bayesian computations too.
-Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and A.
-R.
-DeCasien and collaborators, L.
-E.
-Powell and collaborators, O.
-S.
-Todorov and collaborators, E.
-P.
-Willems and collaborators, F.
-Pearce and collaborators, A.
-F.
-Navarrete and collaborators, and C.
-C.
-Grueter who provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J.
-Matzke for available algorithm scripts allowing us to implement and better understand the methods.
-Their indirect input is therefore tremendous.
-Both authors were supported by a doctoral grant from the *École Normale Supérieure*, Paris.
-
-# Authors' contribution
-
-BR conceived the study, collected, cleaned and analysed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
-BP-L implemented the ClaDS algorithm for our data, helped with running other analyses, and revised the manuscript multiple times.
-The authors declare having no conflict of interest.
-All authors gave final approval for publication and agree to be held accountable for the work performed therein.
 
@@
   #kableExtra::kable_styling(latex_options = "HOLD_position")
+
+# as_huxtable(results.df_gradient) %>%
+#   set_caption("Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
+The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
+# 
+#   
+# #Bold row with p-value < 0.05
+# set_bold(row = which(toPlotBold[-(6:10)]), col = 2:ncol(results.df_gradient)) %>%
+# 
+# #Main layout
+# set_bottom_border(row = 1, col = everywhere) %>% 
+# set_bold(row = 1, col = everywhere) %>% 
+# set_background_color(evens, everywhere, "grey95") %>%
+# as_flextable() %>%
+
 ```
@@
 ```{r prepareMap}
+
+library(rgdal)
+library(cleangeo)
 #Reimport areas with cropping
@@
 # #
-# # Add figure interaction here if needed
+# # Add Fig. interaction here if needed
 # ####
@@
 ```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels  of species sympatry vary across the primate phylogeny | Primate phylogeny from the consensus tree of the 10kTrees project is depicted in the center, together with abbreviated species names.
-The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
+The corresponding non-abbreviated names can be found using Appendix Fig.
+S3.
 Sympatric frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory threshold of ", folivoryThresholdVector[1], "%) species are linked by light grey lines.
@@
 The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.
-The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain regions, when available, is depicted by a plain circle for frugivorous species.
+The mean value (after scaling and based on one random sampling among possible values, but see Appendix Fig.
+S2 for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain regions, when available, is depicted by a plain circle for frugivorous species.
 The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and the folivory threshold to ", folivoryThresholdVector[1], "%.
@@
 
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
+#b and r are the rate for density dependence (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
 #add their values below:
@@
 legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)
+
+save.image("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/RDataforAppendix.RData")
 ```
@@
 \newpage
-
-\beginsupplement
-
-\clearpage
-
-# Appendix
-
-## Data availability
-
-Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Figure \@ref(fig:figdata).
-
-## Data variability
-
-We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to distribution ranges, or anatomical/behavioural traits.
-
-### Sensitivity to variation in distribution range
-
-```{r figcomparison, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4, fig.height=4, fig.cap=paste("Percentage of species with differently identified biogeographic areas in function of the overlap threshold (reference is an overlap threshold of ", geographicThresholdVector[2]/2*100,"%) | For a given species, a biogeographic area difference means that at least one biogeographic area considers absence/presence of the species while this was not the case with the ", geographicThresholdVector[2]/2*100, "% threshold.
-", geographicThresholdVector[2]/2*100, "% was chosen as the reference since halfway to the chosen maximum of ", geographicThresholdVector[2]*100, "%.
-", geographicThresholdVector[2]*100, "% was chosen as the maximum because based on current observations, a species occupied at best three different biogeographic areas.", sep="")}
-
-par(mar=c(3, 5, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
-plot(
-  x=0, y=0, xlab="Overlap threshold", ylab="Percentage of species with different biogeographic areas\ncompared to when a 15% overlap is used", 
-  xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=5/100, xmax=30/100, xintsmall=2.5/200, xintbig=5/100, ymin=0, ymax=0.4, yintsmall=0.01, yintbig=0.1, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=1, tcl=-0.25)
-axis(side=1, at=thresholdPresenceRange, labels=thresholdPresenceRange, las=1, tcl=-0.25)
-
-points(x=thresholdPresenceRange, y=howManyDifferent, pch=19, xpd=TRUE)
-lines(x=thresholdPresenceRange, y=howManyDifferent)
-
-```
-
-\clearpage
-
-### Sensitivity to variation in trait value
-
-```{r figvariabilitydata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=10.5, fig.height=4, fig.cap="Variation in trait values among reference datasets | Colours are associated with a specific trait: Brain, Hippocampus, Neocortex, and Cerebellum refers to the volume of the area (in mm$^{3}$), Body refers to the body mass (in g), Frug.
-indicates the frugivory rate and Fol.
-indicates the folivory rate.
-(A) Correlation: The points depict the coefficient of correlation while the bar depicts the 95% confidence interval (CI).
-(B) Variability: The points depict the average of the mean ratio $m$ of the absolute of differences with paired values; If we reduce the equation, we have $m=|(v_{1}^{2}-v_{2}^{2})|/(2v_{1}v_{2})$, where $v_{1}$ and $v_{2}$ are the two paired values from two different datasets and are different from 0.
-If $v_{1}$ and $v_{2}$ equal 0, then $m=0$.
-If $v_{1}$ or $v_{2}$ equals 0 (case for the diet rates constrained between [0,1]), then we fixed the null value to 0.01.
-The bar depicts the standard error.
-(C) Repeatability: Repeatability was assessed for traits that were included in at least three datasets.
-Before calculation, traits were pondered *within* species by the *within* species max value.
-The point represents the mean repeatability $r$ calculated as $\\sigma^{2}_{between}/(\\sigma^{2}_{between}+\\sigma^{2}_{within})$, with the $\\sigma^{2}_{between}$ and $\\sigma^{2}_{within}$ corresponding the variance *between* or *within* species.
-The bar depicts the standard error.
-For all graphics, sample sizes are indicated above the upper value of the CI/error interval."}
-
-layout(mat=t(c(1,2,3)), widths=c(5,5,3), heights=c(5))
-par(mar=c(4, 3, 2, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-cexText <-  c(
-  rep(0.8, times=10),
-  rep(0.4, times=3),
-  rep(0.8, times=6),
-  rep(0.4, times=3),
-  rep(1, times=1),
-  rep(0.8, times=6),
-  rep(1, times=1),
-  rep(1, times=1)
-)
-
-addToY <- c(
-  rep(0, times=10),
-  rep(0, times=3),
-  rep(0, times=6),
-  rep(0, times=3),
-  rep(0, times=1),
-  rep(0, times=6),
-  rep(-0.05, times=1),
-  rep(0, times=1)
-)
-
-colourWhatCompared <-  c("gray", colourHippocampusbis, colourNeocortexbis, colourCerebellumbis, colourStriatumbis, "orange", "black", "lightgray")#c(brewer.pal(n = length(unique(whatCompared)) - 1, name = "Pastel1"), "darkgrey")
-
-###------
-### CORRELATION
-
-#Vectors to save results
-barLower <- rep(NA, times=length(colNumTest))
-barUpper <- rep(NA, times=length(colNumTest))
-meanCoeff <- rep(NA, times=length(colNumTest))
-N <- rep(NA, times=length(colNumTest))
-
-for (i in 1:length(colNumTest)){
-  test <- #abs(as.numeric(as.character(summaryData[,colNumTest[i]])) - as.numeric(as.character(summaryData[,colNumToCompare[i]])))
-    cor.test(as.numeric(as.character(summaryData[,colNumTest[i]])), 
-             as.numeric(as.character( summaryData[,colNumToCompare[i]])), method="pearson")
-  barLower[i] <- test$conf.int[1]
-  barUpper[i] <- test$conf.int[2]
-  meanCoeff[i] <- test$estimate[1]
-  N[i] <- nrow(summaryData[!is.na(summaryData[,colNumTest[i]])&!is.na(summaryData[,colNumToCompare[i]]),])
-}
-
-plot(
-  x=0, y=0, xlab="", ylab="Coefficient of correlation", cex.lab=1.5, 
-  xlim=c(0,length(meanCoeff)+1), ylim=c(0.6,1),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0.6, ymax=1, yintsmall=0.025, yintbig=0.1, axisPlot=FALSE)
-axis(side=2, at=seq(from=0.6, to=1, by=0.2), labels=seq(from=0.6, to=1, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
-addLabel(x=0.05, y=0.075, label="A", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
-
-#Comparison
-whatCompared <- c(
-  rep("Brain", times=10),
-  "Hippocampus",
-  "Hippocampus",
-  "Hippocampus",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Cerebellum",
-  "Cerebellum",
-  "Cerebellum",
-  "Striatum",
-  rep("Body", times=6),
-  "Frug.",
-  "Fol."
-)
-
-#Plot legend of what is compared in coloured rectangles
-whereToPlot <- as.data.frame(table(whatCompared))
-whereToPlot$loc <- whereToPlot$Freq/2
-
-#Colour rectangle to indicate what is compared
-refLoc=0
-for (i in 1:length(whatCompared)){
-  rect(xleft=i-1,
-       xright=i,
-       ybottom=0.6-0.05*0.4,#-0.05,
-       ytop=0.6,#0,
-       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       xpd=TRUE
-  )
-  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
-  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-         xpd=TRUE)
-  text(x=i-0.5, y=barUpper[i]+0.015, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.8,xpd=TRUE)
-
-  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
-    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
-      segments(x0=refLoc, x1=refLoc, y0=0.6-0.025*0.4,#-0.025,
-               y1=0.6-0.075*0.4 + addToY[i]*0.4,#-0.075,
-               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
-      text(x=refLoc, y=0.6-0.1*0.4 + addToY[i]*0.4,#-0.1, 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=cexText[i], xpd=TRUE)
-    }
-    else{
-      text(x=refLoc, y=0.6-0.025*0.4,#-0.025, 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=cexText[i], xpd=TRUE)
-    }
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
-  }
-}
-
-###------
-### VARIABILITY
-
-#cbind(colnames(summaryData[colNumTest]), colnames(summaryData[colNumToCompare]))
-#Vectors to save results
-barLower <- rep(NA, times=length(colNumTest))
-barUpper <- rep(NA, times=length(colNumTest))
-meanCoeff <- rep(NA, times=length(colNumTest))
-N <- rep(NA, times=length(colNumTest))
-
-for (i in 1:length(colNumTest)){
-  transitoryinit <- as.data.frame(cbind(as.numeric(as.character(summaryData[,colNumTest[i]])),as.numeric(as.character(summaryData[,colNumToCompare[i]]))))
-  transitoryinit <- transitoryinit[!is.na(transitoryinit[,1])&!is.na(transitoryinit[,2]),]
-
-  # transitoryinit <- transitoryinit/max(apply(transitoryinit, 2, max))
-
-  transitory <- apply(transitoryinit, 1, function(v){abs(v[1]**2 - v[2]**2)/2/v[1]/v[2]}) #note= (abs((v1-v2))/v1 + abs((v2-v1))/v2)/2
-
-  #When rate is 0 for both, gives NA, so to transform to 0
-  transitory[is.na(transitory)] <- 0
-
-  transitory[!is.finite(transitory)] <- apply(transitoryinit[!is.finite(transitory),], 1, function(x) abs(max(x)**2 - 1**2)/2/max(x)/1)
-
-  barLower[i] <- mean(transitory) - sd(transitory)/sqrt(length(transitory))#min(transitory)
-  barUpper[i] <- mean(transitory) + sd(transitory)/sqrt(length(transitory))#max(transitory)
-  meanCoeff[i] <- mean(transitory)
-  N[i] <- length(transitory)
-
-}
-
-ymax <- 1#round((barUpper)/10)*10
-
-plot(
-  x=0, y=0, xlab="", ylab="Variability", cex.lab=1.5,
-  xlim=c(0,length(meanCoeff)+1), ylim=c(0,ymax),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=length(meanCoeff), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
-addLabel(x=0.05, y=0.075, label="B", radius=0.75, circle=TRUE, circle.bg="black", font.col="white")
-
-#Comparison
-whatCompared <- c(
-  rep("Brain", times=10),
-  "Hippocampus",
-  "Hippocampus",
-  "Hippocampus",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Neocortex",
-  "Cerebellum",
-  "Cerebellum",
-  "Cerebellum",
-  "Striatum",
-  rep("Body", times=6),
-  "Frug.",
-  "Fol."
-)
-
-#Plot legend of what is compared in coloured rectangles
-whereToPlot <- as.data.frame(table(whatCompared))
-whereToPlot$loc <- whereToPlot$Freq/2
-
-#Colour rectangle to indicate what is compared
-refLoc=0
-
-for (i in 1:length(whatCompared)){
-  rect(xleft=i-1,
-       xright=i,
-       ybottom=-0.05,
-       ytop=0,
-       border=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-       xpd=TRUE
-  )
-  errorBars(location=i-0.5, meanPt=meanCoeff[i], refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=barUpper[i], lowerBarValue=barLower[i], horiz=FALSE, symmetrical=FALSE)
-  points(x=i-0.5, y=meanCoeff[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])],
-         xpd=TRUE)
-  text(x=i-0.5, y=barUpper[i]+0.05, labels=N[i], pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=0.8,xpd=TRUE)
-
-  if(i==length(whatCompared)|whatCompared[i]!=whatCompared[i+1]){
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]
-    if(whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]<=1){
-      segments(x0=refLoc, x1=refLoc, y0=-0.025,
-               y1=-0.075 + addToY[i],
-               col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], xpd=TRUE)
-      text(x=refLoc, y=-0.1  + addToY[i], 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col=colourWhatCompared[which(unique(whatCompared)==whatCompared[i])], cex=cexText[i], xpd=TRUE)
-    }
-    else{
-      text(x=refLoc, y=-0.025, 
-           labels=whereToPlot[whereToPlot[,1]==whatCompared[i],1], col="black", cex=cexText[i], xpd=TRUE)
-    }
-    refLoc=refLoc+whereToPlot$loc[whereToPlot[,1]==whatCompared[i]]#add second time for having complete rectangle
-  }
-}
-
-##----
-## Repeatability of measure
-
-colRep <- list(c(4, 14, 17, 22, 23),
-               c(5, 15, 18),
-               c(6, 12, 16, 19),
-               c(7, 13, 20),
-               #c(8, 21),
-               c(24, 25, 26, 27)#,
-               #c(29, 33),
-               #c(30, 34)
-)
-
-ymax <- 1
-
-plot(
-  x=0, y=0, xlab="", ylab="Repeatability", cex.lab=1.5,
-  xlim=c(0,length(colRep)+1), ylim=c(0,ymax),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-addGrid(xmin=0, xmax=length(colRep), xintsmall=0.5, xintbig=1, ymin=0, ymax=ymax, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=ymax, by=0.2), labels=seq(from=0, to=ymax, by=0.2), las=2, tcl=-0.25, cex.axis=1.25)
-addLabel(x=0.05*2, y=0.075, label="C", radius=0.75*length(colRep)/length(meanCoeff)*2, circle=TRUE, circle.bg="black", font.col="white")
-
-#Comparison
-whatCompared2 <- c(
-  "Brain",
-  "Hippocampus",
-  "Neocortex",
-  "Cerebellum",
-  #"Striatum",
-  "Body"#,
-  #"Fol.",
-  #"Frug."
-)
-
-for(i in 1:length(colRep)){
-  dataRdc <- summaryData[, colRep[[i]]]
-
-  #Normalise by max for all species (i.e. by row)
-  maxVector <- apply(dataRdc, 1, function(x)max(x, na.rm=TRUE))
-  maxVector[!is.finite(maxVector)] <- NA
-  dataRdc <- apply(dataRdc, 2, function(x) x/maxVector) 
-  dataRdc <- as.data.frame(dataRdc)
-
-  #Create common ID
-  dataRdc$id <- 1:nrow(dataRdc)
-
-  #Switch to 1 row=1value
-  dataRdc <- pivot_longer(dataRdc, col=1:(ncol(dataRdc)-1), names_to="Dataset", values_to="Value")
-
-  #Remove NAs
-  dataRdc <- dataRdc[!is.na(dataRdc$Value),]
-
-  #Keep thos with multiple obs
-  whichKeep <- dataRdc %>% count(id)
-  whichKeep <- whichKeep$id[whichKeep$n > 2]
-
-  dataRdc <- dataRdc[dataRdc$id %in% whichKeep,]
-  dataRdc <- pivot_wider(dataRdc, names_from="Dataset", values_from="Value")
-
-  withinVariance <- apply(dataRdc[,2:ncol(dataRdc)], 1, function(x) var(x, na.rm=TRUE))
-  betweenVariance <- var(apply(dataRdc[,2:ncol(dataRdc)], 1, function(x) mean(x, na.rm=TRUE)), na.rm=TRUE)
-
-  repeatability <- betweenVariance/(betweenVariance + withinVariance)
-
-  #Plot mean +/- SE
-  errorBars(location=i-0.5, meanPt=mean(repeatability),
-            refUnit=1, col="black", minValue=0, maxValue=1, upperBarValue=mean(repeatability)+sd(repeatability)/sqrt(length(repeatability)),
-            lowerBarValue=mean(repeatability)-sd(repeatability)/sqrt(length(repeatability)), horiz=FALSE, symmetrical=FALSE)
-
-  points(x=i-0.5, y=mean(repeatability), pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared2[i])],
-         xpd=TRUE)
-  text(x=i-0.5, y=mean(repeatability)+sd(repeatability)/sqrt(length(repeatability))+0.05, labels=length(repeatability), pch=19, col=colourWhatCompared[which(unique(whatCompared)==whatCompared2[i])], cex=0.8, xpd=TRUE)
-
-  # library(rptR)
-  # repeatabilityTest <- rpt(Value ~ (1 | id), grname = "id", data = dataRdc, datatype = "Proportion", 
-  #   nboot = 10, npermut = 0)
-  # Too few data to do that way
-
-}
-
-```
-
-```{r figdata, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=20, fig.height=25, fig.cap="Data availability | Black boxes indicate data availability while grey boxes indicate absence of data."}
-# 
-# plot(
-#   x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-#   xlim=c(-10,ncol(dataForSample)-1), ylim=c(0,nrow(dataForSample)),
-#   las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-#   xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-# 
-# text(x=rep(-2, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$SpeciesForPhylo, xpd=TRUE, cex=0.4)
-# text(x=rep(-0, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$Species, xpd=TRUE, cex=0.4)
-# text(x=3:ncol(dataForSample)-1.5, y=rep(nrow(dataForSample)+3, times=length(3:ncol(dataForSample))), labels=colnames(dataForSample)[3:ncol(dataForSample)], xpd=TRUE, cex=0.4, srt=45)
-# 
-# for(i in 1:nrow(dataForSample)){
-#   for(j in 3:ncol(dataForSample)){
-#     if(!is.na(dataForSample[i,j])&dataForSample[i,j]==1){
-#       rect(
-#         xleft=j-2,
-#         xright=j-1,
-#         ybottom=i-1,
-#         ytop=i,
-#         border="black",
-#         col="black"
-#       )
-#     } else{
-#       rect(
-#         xleft=j-2,
-#         xright=j-1,
-#         ybottom=i-1,
-#         ytop=i,
-#         border="lightgrey",
-#         col="lightgrey"
-#       )
-#     }
-#   }
-# }
-# 
-# addGrid(xmin=1, xmax=ncol(dataForSample), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
-# 
-# 
-# 
-# plot(
-#   x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-#   xlim=c(-10,ncol(dataForSample)-1), ylim=c(0,nrow(dataForSample)),
-#   las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-#   xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-# 
-# text(x=rep(-2, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$SpeciesForPhylo, xpd=TRUE, cex=0.4)
-# text(x=rep(-0, times=nrow(dataForSample)), y=1:nrow(dataForSample)-0.5, labels=dataForSample$Species, xpd=TRUE, cex=0.4)
-# text(x=3:ncol(dataForSample)-1.5, y=rep(nrow(dataForSample)+3, times=length(3:ncol(dataForSample))), labels=colnames(dataForSample)[3:ncol(dataForSample)], xpd=TRUE, cex=0.4, srt=45)
-# 
-# for(i in 1:nrow(dataForSample)){
-#   for(j in 3:ncol(dataForSample)){
-#     if(!is.na(dataForSample[i,j])&dataForSample[i,j]==1){
-#       rect(
-#         xleft=j-2,
-#         xright=j-1,
-#         ybottom=i-1,
-#         ytop=i,
-#         border="black",
-#         col="black"
-#       )
-#     } else{
-#       rect(
-#         xleft=j-2,
-#         xright=j-1,
-#         ybottom=i-1,
-#         ytop=i,
-#         border="lightgrey",
-#         col="lightgrey"
-#       )
-#     }
-#   }
-# }
-# 
-# addGrid(xmin=1, xmax=ncol(dataForSample), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
-
-dataForSample <- dataForSample[dataForSample$SpeciesForPhylo != "Homo_sapiens",]
-dataForSample <- dataForSample[order(dataForSample$SpeciesForPhylo),]
-
-nbPlot=4
-
-layout(mat=t(c(1:nbPlot)), widths=rep(5, times=nbPlot), heights=c(5*nbPlot))
-par(mar=c(0, 0, 3, 0.5), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-for(p in 1:nbPlot){
-  dataForSample_rdcplot <- dataForSample[(1+(p-1)*nrow(dataForSample)/nbPlot):(1+(p)*nrow(dataForSample)/nbPlot),]
-  plot(
-    x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-    xlim=c(-10,ncol(dataForSample_rdcplot)-1), ylim=c(0,nrow(dataForSample_rdcplot)+3),
-    las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-    xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-  text(x=rep(-5, times=nrow(dataForSample_rdcplot)), y=1:nrow(dataForSample_rdcplot)-0.5, labels=dataForSample_rdcplot$SpeciesForPhylo, xpd=TRUE, cex=1.1)
-  text(x=rep(-0.5, times=nrow(dataForSample_rdcplot)), y=1:nrow(dataForSample_rdcplot)-0.5, labels=dataForSample_rdcplot$Species, xpd=TRUE, cex=1.1)
-  text(x=3:ncol(dataForSample_rdcplot)-1.5, y=rep(nrow(dataForSample_rdcplot)+2, times=length(3:ncol(dataForSample_rdcplot))), labels=colnames(dataForSample_rdcplot)[3:ncol(dataForSample_rdcplot)], xpd=TRUE, cex=1.1, srt=45)
-
-  for(i in 1:nrow(dataForSample_rdcplot)){
-    for(j in 3:ncol(dataForSample_rdcplot)){
-      if(!is.na(dataForSample_rdcplot[i,j])&dataForSample_rdcplot[i,j]==1){
-        rect(
-          xleft=j-2,
-          xright=j-1,
-          ybottom=i-1,
-          ytop=i,
-          border="black",
-          col="black"
-        )
-      } else{
-        rect(
-          xleft=j-2,
-          xright=j-1,
-          ybottom=i-1,
-          ytop=i,
-          border="lightgrey",
-          col="lightgrey"
-        )
-      }
-    }
-  }
-
-  addGrid(xmin=1, xmax=ncol(dataForSample_rdcplot), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample_rdcplot), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
-  #if(p==2){cat('\r\n\r\n')} #Allows to consider plot as a new figure at each step of the loop
-}
-
-```
-
-\clearpage
-
-### Primate diversification rate over time
-
-```{r figdiversificationTime, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=4.5, fig.height=4.5, fig.cap="\\footnotesize Net diversification rate over time in the Primate taxon | The average diversification rate estimated based on an assumed sampling fraction of primate species ranging from 60 to 95% (at a step of 10%; then 5% from 90%) is depicted by the plain line.
-The grey background depicts the standard deviation.
-The two breakpoints, depicted by the plain dots and the vertical dotted bars, were estimated based on a three-linear regression segmentation using the *strucchange* package [@strucchange1; @strucchange2; @strucchange3; see the vignette package for statistical details].
-The three fitted regressions are displayed by the dashed lines.
-The choice of two breakpoints was first assessed by choosing the number of breakpoints minimizing the Bayesian Information Criterion.
-The identified breakpoints, coining with previous studies [@arbour2017major; @springer2012macroevolutionary], correspond to the emergence of more favourable environmental conditions stemming from a progressive warming after harsh temperature cooling that started earlier in the Oligocene until reaching a mid-Miocene Climatic Optimum [@fleagle2006biogeography]."}
-
-##Plot diversification in function of time
-xmin=floor(min(aggregatedSpeciationTime.mean[,1]/10))*10
-xmax=ceiling(max(aggregatedSpeciationTime.mean[,1]/10))*10
-ymin=floor(min(aggregatedSpeciationTime.mean[,2]*10))/10
-ymax=ceiling(max(aggregatedSpeciationTime.mean[,2]*10))/10
-
-plot(0, 0, xlab="Time before present (Myr)", ylab="Diversification rate",
-     xlim=c(xmin, xmax), ylim=c(ymin, ymax),
-     las=1, type="n", tcl=-0.25, bty="n",
-     xaxt="n",xaxs="i",yaxs="i", yaxt="n",
-     xpd=TRUE)
-
-#Add grid
-addGrid(
-  xmin=xmin, xmax=xmax, xintsmall=(xmax-xmin)/20, xintbig=(xmax-xmin)/5,
-  ymin=ymin, ymax=ymax, yintsmall=(ymax-ymin)/20, yintbig=(ymax-ymin)/5,
-  axisPlot=TRUE, round=TRUE, digit=c(2,2))
-axis(side=1, at=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), labels=round(seq(from=xmin, to=xmax, by=(xmax-xmin)/5), digit=1), las=1, tcl=-0.25)
-
-#Add background se
-polygon(
-  x=c(aggregatedSpeciationTime.mean[,1], rev(aggregatedSpeciationTime.mean[,1])),
-  y=c(aggregatedSpeciationTime.mean[,2]-aggregatedSpeciationTime.sd[,2], rev(aggregatedSpeciationTime.mean[,2]+aggregatedSpeciationTime.sd[,2])),
-  col=grey(level=0.5, alpha=0.15),
-  border=NA
-)
-
-#Add mean
-lines(aggregatedSpeciationTime.mean[,1], aggregatedSpeciationTime.mean[,2])
-
-library(strucchange)
-## confidence interval
-colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
-
-yFirst <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateFirstRupt[2])))]
-ySecond <- aggregatedSpeciationTime.mean$Diversification[which((abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2]))==min(abs(aggregatedSpeciationTime.mean$Time+dateSecondRupt[2])))]
-
-# Rupture points and (CI too reduced to be plotted)
-points(c(-dateFirstRupt[2], -dateSecondRupt[2]), c(yFirst, ySecond), pch=19)
-# errorBars(location=c(yFirst), 
-#          meanPt=c(-dateFirstRupt[2]),
-#          barValue=c(0,0), refUnit=1, 
-#          minValue=-80, maxValue=80, 
-#          upperBarValue=c(-dateFirstRupt[1]), lowerBarValue=c(-dateFirstRupt[3]), 
-#          col="black", lty=1, 
-#          horiz=TRUE, symmetrical=FALSE)
-
-#Vertical bars
-segments(
-  x0=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  x1=c(-dateFirstRupt[2], -dateSecondRupt[2]),
-  y0=c(0,0),
-  y1=c(yFirst, ySecond),
-  lty=3
-)
-mtext(side=1, at=c(-dateFirstRupt[2], -dateSecondRupt[2]), line=0, text=c(-dateFirstRupt[2], -dateSecondRupt[2]), cex=0.8)
-
-#three fitted regressions
-fm1 <- lm(Diversification ~ breakfactor(bp.resp, breaks = 2)*Time, data=aggregatedSpeciationTime.mean)
-
-reg1 <- summary(fm1)$coefficients[1,1] + aggregatedSpeciationTime.mean$Time*summary(fm1)$coefficients[4,1]
-reg2 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[2,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[5,1])
-reg3 <- summary(fm1)$coefficients[1,1] + summary(fm1)$coefficients[3,1] + aggregatedSpeciationTime.mean$Time*(summary(fm1)$coefficients[4,1] + summary(fm1)$coefficients[6,1])
-
-lines(aggregatedSpeciationTime.mean$Time, reg1, lty = 2)
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -40], reg2[aggregatedSpeciationTime.mean$Time > -40], lty = 2)#truncaturate for readability
-lines(aggregatedSpeciationTime.mean$Time[aggregatedSpeciationTime.mean$Time > -16], reg3[aggregatedSpeciationTime.mean$Time > -16], lty = 2)#truncaturate for readability
-```
-
-## Phylogenetic regressions: results, stability, and assumption
-
-### Model results
-
-<!-- We present below the visual fit of phylogenetic regressions. -->
-
-(a) Phylogenetic regressions: effect of sympatry on brain sizes
-
-\clearpage
-
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of relative brain size as a function of sympatry level indices | Left graphics show the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species  is averaged, while the right graphics do the opposite.
-Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionGradient}
-\end{figure}
-```
-\clearpage
-
-(b) Phylogenetic regressions: diversification and brain size
-
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.7\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent grey background.}}\label{fig:figRegressionDiversification}
-\end{figure}
-```
-
-\clearpage
-
-(c) Phylogenetic regressions: diversification and sympatry
-
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of sympatry level indices | The left graphic depicts the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species is averaged, while the right graphic does the opposite.
-Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionDiversificationSympatry}
-\end{figure}
-```
-
-\clearpage
-
-(d) Forest plot of estimates
-
-```{r forestPlot, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=6.25, fig.height=6.25, fig.cap="Forest plot of the phylogenetic regressions | CI: 95\\% Confidence Interval, HDP: Highest Posterior Density (when brain size is the predictor, they are barely visible because reduced).
-Plain dots depict negative effects, open dots depict positive effects.
-"}
-
-source("T:/Saved_PhD/Empirical_analysis/Scripts&Functions/Functions/toolbox.R")
-par(mar=c(8, 8, 0.5, 2), mgp=c(2.5, 0.5, 0), xpd=TRUE)
-
-emptyPlot(xlim=c(-3,3), ylim=c(-3,3), asp=1)
-#Grid
-addGrid(
-  cexAxisX=1.15, cexAxisY=1.15,
-  xmin=-3, xmax=3, xintsmall=0.1, xintbig=0.5,
-  ymin=-3, ymax=3, yintsmall=0.1, yintbig=0.5,
-  axisPlot=FALSE, round=TRUE, digit=c(2,2), contour=TRUE)
-
-#0 line
-segments(x0=0, x1=0, y0=-3, y1=3, lty=2)
-
-#Xaxis
-axis(side=1, at=seq(-3, 3, 0.5), pos=-3, labels=seq(-3, 3, 0.5), las=1, tcl=-0.25)
-mtext(side=1, at=0, line=1, text="Model estimate (point) and 95% CI/HDP (segment)")
-
-#yAxis
-axis(side=2, at=c(2, 0, -2), pos=-3, labels=c("Overlap (%)", "N sympatric\nspecies", "Relative\nbrain size"), las=1, tcl=-0.25)
-mtext(side=2, at=0, line=6, text="PARAMETER", font=2)
-
-#Add the different values
-
-#Analysis of brain size and sympatry
-traitName_rdc=c("EQ (log)", #"Brain (/bodymass, log)",
-                "Striatum (/bodymass, log)",
-                "MOB (/bodymass, log)",
-                "Hippocampus (/bodymass, log)",
-                "Neocortex (/bodymass, log)", 
-                "Cerebellum (/bodymass, log)",
-                "DiversificationAndSympatry"
-)
-
-traitName_legend <- c("EQ", "Striatum", "MOB", "Hippocampus", "Neocortex", "Cerebellum", "Diversification")
-library(RColorBrewer)
-colourModelsReg <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5], "black")
-
-for(a in 1:length(traitName_rdc)){
-
-  if(a!=length(traitName_rdc)){
-    model <- get(paste("modelBrain", traitName_rdc[a], sep="_"))
-  }else{
-    model <- get(paste("modelBrain", traitName_rdc[a], sep=""))
-  }
-
-  #Overlap
-  errorBars(location=2.5-(a-1)*1/length(traitName_rdc), 
-            meanPt=cbind(model$bootmean, t(model$bootconfint95))[2,1], 
-            barValue=1, 
-            refUnit=0.75, 
-            minValue=-3, 
-            maxValue=3, 
-            upperBarValue=cbind(model$bootmean, t(model$bootconfint95))[2,2], 
-            lowerBarValue=cbind(model$bootmean, t(model$bootconfint95))[2,3], 
-            col=colourModelsReg[a], 
-            lty=1, 
-            horiz=TRUE, 
-            symmetrical=FALSE)
-  points(x=cbind(model$bootmean, t(model$bootconfint95))[2,1], y=2.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[2,1]>0,21,19), bg="white", col=colourModelsReg[a])
-  if(a!=length(traitName_rdc)){
-    text(x=cbind(model$bootmean, t(model$bootconfint95))[2,3], y=2.5-(a-1)*1/length(traitName_rdc),
-       pos=4, col=colourModelsReg[a],
-       labels=pvalueToText(as.numcharac(results.df_gradient[grep(traitName_legend[a], results.df_gradient[,1]) + 2,7])), cex=0.75)
-  }else{
-    text(x=cbind(model$bootmean, t(model$bootconfint95))[2,3], y=2.5-(a-1)*1/length(traitName_rdc),
-         pos=4, col=colourModelsReg[a],
-         labels=pvalueToText(as.numcharac(results.df_diversificationAndSympatry[3,7])), cex=0.75)
-  }
-
-  #N species
-  errorBars(location=0.5-(a-1)*1/length(traitName_rdc), 
-            meanPt=cbind(model$bootmean, t(model$bootconfint95))[3,1], 
-            barValue=1, 
-            refUnit=0.75, 
-            minValue=-3, 
-            maxValue=3, 
-            upperBarValue=cbind(model$bootmean, t(model$bootconfint95))[3,2], 
-            lowerBarValue=cbind(model$bootmean, t(model$bootconfint95))[3,3], 
-            col=colourModelsReg[a], 
-            lty=1, 
-            horiz=TRUE, 
-            symmetrical=FALSE)
-  points(x=cbind(model$bootmean, t(model$bootconfint95))[3,1], y=0.5-(a-1)*1/length(traitName_rdc), pch=ifelse(cbind(model$bootmean, t(model$bootconfint95))[3,1]>0,21,19), bg="white", col=colourModelsReg[a])
-  if(a!=length(traitName_rdc)){
-    text(x=cbind(model$bootmean, t(model$bootconfint95))[3,3], y=0.5-(a-1)*1/length(traitName_rdc),
-       pos=4, col=colourModelsReg[a],
-       labels=pvalueToText(as.numcharac(results.df_gradient[grep(traitName_legend[a], results.df_gradient[,1]) + 3,7])), cex=0.75)
-  }else{
-    text(x=cbind(model$bootmean, t(model$bootconfint95))[3,3], y=0.5-(a-1)*1/length(traitName_rdc),
-         pos=4, col=colourModelsReg[a],
-         labels=pvalueToText(as.numcharac(results.df_diversificationAndSympatry[4,7])), cex=0.75)
-  }
-
-  #Analysis of diversification and brain size
-  if(a!=length(traitName_rdc)){
-    model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
-
-    errorBars(location=-1.5-(a-1)*1/(length(traitName_rdc)-1), 
-              meanPt=as.data.frame(summary(model)$solutions[,1:3])[2,1], 
-              barValue=1, 
-              refUnit=0.75, 
-              minValue=-3, 
-              maxValue=3, 
-              upperBarValue=as.data.frame(summary(model)$solutions[,1:3])[2,2], 
-              lowerBarValue=as.data.frame(summary(model)$solutions[,1:3])[2,3], 
-              col=colourModelsReg[a], 
-              lty=1, 
-              horiz=TRUE, 
-              symmetrical=FALSE)
-    points(x=as.data.frame(summary(model)$solutions[,1:3])[2,1], y=-1.5-(a-1)*1/(length(traitName_rdc)-1), pch=ifelse(as.data.frame(summary(model)$solutions[,1:3])[2,1]>0,21,19), bg="white", col=colourModelsReg[a])
-    text(x=as.data.frame(summary(model)$solutions[,1:3])[2,3], y=-1.5-(a-1)*1/(length(traitName_rdc)-1),
-         pos=4, col=colourModelsReg[a],
-         labels=pvalueToText(as.numcharac(results.df_diversification[grep(traitName_legend[a], results.df_diversification[,1]) + 2,5])), cex=0.75)
-
-  }
-}
-
-legend(x=3, y=0.5, 
-       pch=c(19,21), 
-       bg=c("white", "white"),
-       col=c("black", "black"),
-       legend=c("> 0", "< 0"),
-       #title="Output:",
-       bty="n", 
-       xjust=1,
-       xpd=TRUE)
-
-legend(x=-2.5, y=-4, 
-       pch=rep(19, times=length(traitName_rdc)), 
-       col=c(colourModelsReg),
-       legend=traitName_legend,
-       #title="Output:",
-       ncol=3,
-       bty="n", 
-       xpd=TRUE)
-
-```
-
-\clearpage
-
-### Model stability
-
-We present below statistical indicators related to changes in estimates when re-fitting the model considering sub-samples (i.e.
-DfBetas and Cook's distance), as well as when accounting for data variability (i.e.
-re-sampling among possible values given all datasets) or when using different parameterisation (i.e.
-"sampling fraction" of known species for diversification analyses).
-
-```{r correctSensitivityTable}
-#Include true estimator in the min-max range
-
-#1)Change min-max interval
-summarySensitivityGradient[,1:3+2] <- t(apply(summarySensitivityGradient[,1:3+2], 1, function(x){
-  x <- as.numeric(x)
-  if(x[1] > x[2]){
-   x[1] <- x[2] 
-  } else if (x[2] > x[3]){
-    x[3] <- x[2]
-  }else{}
-  return(x)
-}
-)
-)
-
-summarySensitivityGradient[,4:6+2] <- t(apply(summarySensitivityGradient[,4:6+2], 1, function(x){
-  x <- as.numeric(x)
-  if(x[1] > x[2]){
-   x[1] <- x[2] 
-  } else if (x[2] > x[3]){
-    x[3] <- x[2]
-  }else{}
-  return(x)
-}
-)
-)
-
-#2) Re-round intelligent with scientific writing
-summarySensitivityGradient[, 1:6+2] <- t(apply(summarySensitivityGradient[, 1:6+2], 1, function(x)
-roundIntelligent(as.numcharac(x))))
-
-#1)Change min-max interval
-summarySensitivityDiversification[,1:3+2] <- t(apply(summarySensitivityDiversification[,1:3+2], 1, function(x){
-  x <- as.numeric(x)
-  if(x[1] > x[2]){
-   x[1] <- x[2] 
-  } else if (x[2] > x[3]){
-    x[3] <- x[2]
-  }else{}
-  return(x)
-}
-)
-)
-summarySensitivityDiversification[,4:6+2] <- t(apply(summarySensitivityDiversification[,4:6+2], 1, function(x){
-  x <- as.numeric(x)
-  if(x[1] > x[2]){
-   x[1] <- x[2] 
-  } else if (x[2] > x[3]){
-    x[3] <- x[2]
-  }else{}
-  return(x)
-}
-)
-)
-summarySensitivityDiversification[,7:9+2] <- t(apply(summarySensitivityDiversification[,7:9+2], 1, function(x){
-  x <- as.numeric(x)
-  if(x[1] > x[2]){
-   x[1] <- x[2] 
-  } else if (x[2] > x[3]){
-    x[3] <- x[2]
-  }else{}
-  return(x)
-}
-)  
-)
-
-#2) Re-round intelligent with scientific writing
-summarySensitivityDiversification[,-c(1,2)] <- t(apply(summarySensitivityDiversification[,-c(1,2)], 1, function(x) roundIntelligent(as.numcharac(x)))) 
-```
-
-\hfill
-
-(a) Phylogenetic regressions: effect of sympatry on brain sizes
-
-```{r tabledfsensitivity, include=TRUE}
-summarySensitivityGradient <- summarySensitivityGradient[-(1:4),]
-summarySensitivityGradient[,2] <- gsub("Overlap", "\\% of overlapping range", summarySensitivityGradient[,2])
-summarySensitivityGradient[,2] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivityGradient[,2])
-
-rownames(summarySensitivityGradient) <- NULL
-knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
-  kableExtra::add_header_above(c("Regression" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3))
-```
-
-\newpage
-
-(b) Phylogenetic regressions: diversification and brain size
-
-```{r tabledfsensitivity2, include=TRUE}
-summarySensitivityDiversification <- summarySensitivityDiversification[-(1:3),]
-rownames(summarySensitivityDiversification) <- NULL
-knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
-  kableExtra::add_header_above(c("Regression" = 2, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
-```
-
-\newpage
-
-(b) Phylogenetic regressions: diversification and sympatry
-
-```{r tabledfsensitivity3, include=TRUE}
-summarySensitivitydiversificationAndSympatry[,1] <- gsub("Overlap", "\\% of overlapping range", summarySensitivitydiversificationAndSympatry[,1])
-summarySensitivitydiversificationAndSympatry[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivitydiversificationAndSympatry[,1])
-
-knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data)") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::add_header_above(c("Model:" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction"))
-
-```
-
-\newpage
-### Model assumptions
-
-We present below the visual assessment of linear modelling assumptions (histogram of residuals, Q-Q plot, and scatterplot of fitted values vs residuals).
-
-(a) Phylogenetic regressions: effect of sympatry on brain sizes
-
-```{r modelAssumption, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Brain size and sympatry' | Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
-for(a in 1:length(traitName)){
-  if(a!=2){#Remove brain
-    model <- get(paste("modelBrain", traitName[a], sep="_"))
-
-    diagnostics.plot(model)
-    text(x=0.85, y=0.15, paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
-
-    if(a/2==floor(a/2)){
-      cat('\n') #Break page for new figure
-    }
-  }
-}
-```
-
-\newpage
-
-(b) Phylogenetic regressions: diversification and brain size
-
-```{r modelAssumption2a, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Diversity and brain size' | Trace and density of posteriors"}
-for(a in 1:length(traitName)){
-  if(a!=2){#Remove brain
-    model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
-
-    plot(model1$Sol)
-    mtext(paste("Fixed effects: ", traitName[a], sep=""), side = 3, line = -1, outer = TRUE, xpd=TRUE)
-    #cat('\n') #Break page for new figure
-
-    plot(model1$VCV)
-    mtext(paste("Random/residuals: ", traitName[a], sep=""), side = 3, line = -1, outer = TRUE, xpd=TRUE)
-    #text(x=max(fitted(model)) + abs(min(fitted(model))), y=mean(residuals(model)), paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
-    if(a/2==floor(a/2)){
-      cat('\n') #Break page for new figure
-    }
-  }
-}
-```
-
-```{r modelAssumption2b, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=10, fig.cap="Model assumption check 'Diversity and brain size' | Q-Q plot of the posterior distribution and the expected Gaussian distribution"}
-
-layout(mat=matrix(1:(2*ceiling(length(traitName)/2)), ncol=2), widths=c(5,5), heights=rep(5, times=2*ceiling(length(traitName)/2)))
-par(mar=c(3, 3, 3, 1), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-for(a in 1:length(traitName)){
-  if(a!=2){#Remove brain
-    model <- get(paste("modelBrainDiversification", traitName[a], sep="_"))
-
-    posterior <- as.data.frame(model$Sol)
-    qqnorm(posterior$Trait, main=paste("Normal Q-Q Plot of the posterior distribution;\nModel:", traitName[a], sep=" "))
-    qqline(posterior$Trait)
-    #text(x=max(fitted(model)) + abs(min(fitted(model))), y=mean(residuals(model)), paste("Model:\n",traitName[a], sep=""), xpd=TRUE)
-
-    #cat('\n') #Break page for new figure
-  }
-}
-```
-
-\newpage
-
-(b) Phylogenetic regressions: diversification and sympatry
-
-```{r modelAssumption3, include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=4.5, fig.cap="Model assumption check 'Diversity and sympatry'| Depicted are the histogram of residuals, the Q-Q plot, and the scatter plot of the fitted values *vs* the residuals."}
-    model <- get(paste("modelBrainDiversificationAndSympatry", sep="_"))
-
-    diagnostics.plot(model)
-
-```
-
-<!-- TC:endignore -->

### 2022-01-28 Article/Article_forsubmission_wordworking.Rmd
Update for submission - Separation Sup mat and Main text - Add Rmd word compilation

--- 2022-01-28 Article/Article_forsubmission.Rmd
@@
      #- '--lua-filter=author-info-blocks.lua'
- keep_tex: true
 always_allow_html: true
@@
 
+#Tables
+library(huxtable)
+
 #Plot
@@
 library(circlize)
+library(magick)
+library(knitr)
+library(png)
 
@@
 **Running title:** Species sympatry shapes primates' brain size  
-\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
+**Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
 <!-- \faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline -->
@@
 
-<!-- TC:ignore -->
-
-<!-- On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
-Overall, the evolution of the brain is the consequence of constraints (e.g.
-energetic limitations, @navarrete2011energetics), but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
--->
-<!-- Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
--->
-
-<!-- \initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
-Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
-However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition.
--->
-
-<!-- |   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
-Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond).
-Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic] and these areas are likely to be differently affected by species sympatry.
-For instance, the Main Olfactory Bulb (MOB) or the Hippocampus , home of a spatio-temporal memory [@burgess2002human], are largely involved in efficient foraging, especially for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany]: we therefore expect that primate species with larger MOB or Hippocampus areas, taken as equivalent to more advanced perceptive and cognitive abilities for efficient foraging, might be more fit than their sympatric species with smaller areas.
-Similarly, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
--->
-<!-- are expected to be influenced by the ecological environment.
-The Striatum is also stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike).
-Finally, besides foraging-related areas (Striatum, MOB or Hippocampus), more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
-To sum up, a first possibility is that sympatric heterospecifics could altogether stimulate cognition and promote larger sizes of the brain areas related to interacting with the social or ecological environment.
--->
-
-<!-- |   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
-Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
-positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory).
-Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g.
-phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social].
-In this case, the size of brain areas involved in immediate information processing should be less large in sympatric than in non-sympatric conditions.
-To sum up, a second possibility is that sympatric heterospecifics could hamper the benefits of cognition on foraging, and thus slowdown brain size increase.
-In an extreme case, it could even induce positive selection for smaller brain size.
--->
-
-<!-- |    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
-To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in primates.
--->
-
-<!-- TC:endignore -->
-
-\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics].
+  Cognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics].
 Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
@@
 Data were pooled from previous literature surveys (see Appendix [Data availability]).
+Data were pooled from previous literature surveys (see Appendix [Data availability]).
 Brain data were obtained from @decasien2019primate for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for the whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size.
@@
 
-\begin{center}
+<!-- \begin{center} -->
 
@@
 
-\end{center}
+  <!-- \end{center} -->
 
@@
 The models were based on different sample sizes depending on the brain areas and the frugivory thresholds considered: EQ: `r minEQ` to `r maxEQ`, Striatum: `r minStriatum` to `r maxStriatum`, MOB: `r minMOB` to `r maxMOB`, Neocortex: `r minNeocortex` to `r maxNeocortex`, Hippocampus: `r minHippocampus` to `r maxHippocampus`, Cerebellum: `r minCerebellum` to `r maxCerebellum` frugivorous species.
-For each set of models in a given brain area, the sample was strictly identical, allowing within-set comparisons.
+For a given set of models (i.e.
+within brain area), the sample was strictly identical, allowing within-set comparisons.
 Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
-We calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure \@ref(fig:figbrain)).
+We calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Fig.
+\@ref(fig:figbrain)).
 We specifically considered three different models considering species sympatry: the matching competition (MC) model [@nuismer2015predicting] and density-dependent models [DD$_{lin}$ and DD$_{exp}$, @drury2016estimating].
@@
 
-\end{center}
+<!-- \end{center} -->
 
@@
 rownames(results.df_gradient) <- NULL
-knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+# knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
 The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
 The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") #%>%
-  #kableExtra::kable_styling(latex_options = "HOLD_position")
-
-# as_huxtable(results.df_gradient) %>%
-#   set_caption("Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
+#   kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down") #%>%
+#   #kableExtra::kable_styling(latex_options = "HOLD_position")
+
+as_huxtable(results.df_gradient) %>%
+  set_caption("Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
 The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
 The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
-# 
-#   
-# #Bold row with p-value < 0.05
-# set_bold(row = which(toPlotBold[-(6:10)]), col = 2:ncol(results.df_gradient)) %>%
-# 
-# #Main layout
-# set_bottom_border(row = 1, col = everywhere) %>% 
-# set_bold(row = 1, col = everywhere) %>% 
-# set_background_color(evens, everywhere, "grey95") %>%
-# as_flextable() %>%
+
+#Bold row with p-value < 0.05
+set_bold(row = which(toPlotBold[-(6:10)])+1, col = 2:ncol(results.df_gradient)) %>%
+
+#Main layout
+set_bottom_border(row = 1, col = everywhere) %>%
+set_bold(row = 1, col = everywhere) %>%
+set_background_color(evens, everywhere, "grey95") %>%
+as_flextable()
 
@@
 rownames(results.df_diversification) <- NULL
-knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+# knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
 samp.=Effective sample (adjusted for autocorrelation).
@@
 The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") #%>%
-  #kableExtra::kable_styling(latex_options = "HOLD_position")
+#   kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down") #%>%
+#   #kableExtra::kable_styling(latex_options = "HOLD_position")
+#
+
+as_huxtable(results.df_diversification) %>%
+  set_caption("The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
+samp.=Effective sample (adjusted for autocorrelation).
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
+The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
+
+#Bold row with p-value < 0.05
+set_bold(row = which(toPlotBoldDiversification[-(5:8)])+1, col = 2:ncol(results.df_diversification)) %>%
+
+#Main layout
+set_bottom_border(row = 1, col = everywhere) %>%
+set_bold(row = 1, col = everywhere) %>%
+set_background_color(evens, everywhere, "grey95") %>%
+as_flextable()
 ```
@@
 
-knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
+# knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
 The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
 The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
-  kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down")
+#   kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down")
+
+as_huxtable(results.df_diversificationAndSympatry) %>%
+  set_caption("Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
+The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
+The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
+
+#Bold row with p-value < 0.05
+set_bold(row = which(toPlotBoldSympatry)+1, col = 2:ncol(results.df_diversificationAndSympatry)) %>%
+
+#Main layout
+set_bottom_border(row = 1, col = everywhere) %>%
+set_bold(row = 1, col = everywhere) %>%
+set_background_color(evens, everywhere, "grey95") %>%
+as_flextable()
 
@@
 legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)
-
-save.image("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/RDataforAppendix.RData")
 ```

### 2022-01-28 Article/Supplementary_material_forsubmission.Rmd
Update for submission - Separation Sup mat and Main text - Add Rmd word compilation

--- 2021-12-14 Article/Article.Rmd
@@
 ---
-title: "Species sympatry shapes brain size evolution in Primates"
+title: "Supporting Information to: Species sympatry shapes brain size evolution in Primates"
 # date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 knitr::opts_chunk$set(include=FALSE, echo=FALSE, message=FALSE)
-knitr::opts_chunk$set(dpi=300) # Figure resolution and size out.width = '100%', 
+knitr::opts_chunk$set(dpi=300) # Fig. resolution and size out.width = '100%', 
 knitr::opts_chunk$set(fig.pos = 'p'#, fig.align = 'center'
                       ) # Places figures on pages separate from text, centered
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R figure caption
-```
-
-<!-- TC:ignore -->
+knitr::opts_chunk$set(fig.env="figure") # Latex Fig. environment
+knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R Fig. caption
+```
 
@@
 
+library(tidyverse)
 #Import own function
@@
 load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/PGLSdiversificationAndSympatry.RData")
-```
-
-\captionsetup{list=no}
-\newpage
-
-```{r wordCount}
-words <- RmdWords("Article.Rmd")
-```
-
-:::: {.graybox data-latex=""}
-
-**Abstract |** The main hypotheses related to animal intelligence evolution highlight the role of conspecifics.
-Yet, space is often simultaneously occupied by species sharing the same ecological guild.
-These sympatric heterospecifics can compete for food, thereby stimulating or hampering cognition.
-Considering brain size as a proxy for cognition, we used primates to test for the intertwining between species sympatry and cognition.
-We retraced the evolutionary history of several brain areas with evolutionary models considering or not sympatry.
-Sympatry-related models best predicted the evolution of brain areas related to long-term memory of interactions with the social or ecological environment, with a decrease of their size the higher the sympatry.
-By contrast, the whole brain or brain areas used in immediate information processing were best described by models not considering sympatry.
-Moreover, sympatry negatively affected primate diversification.
-Overall, this comparative study suggests that species sympatry contributes to shaping primate cognition and diversification.
-We speculate that this is due to an over-complexification of resource spatio-temporality.
-
-\hfill
-
-<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
-
-\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
-
-\faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline
-<!-- Character Count: `r words$num_char` -->
-
-::::
-
-\newpage
-
-```{r sampleCalculation,  warning = FALSE, message = FALSE}
-###Set working directory
-setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
-
-repetition=2*2*2*10#length(frugivoryThresholdVector)*length(folivoryThresholdVector)*length(geographicThresholdVector)*randomSampling
-
-checkSampleFruit <- rep(NA, times=repetition)
-checkSampleLeaf <- rep(NA, times=repetition)
-checkSampleRange <- rep(NA, times=repetition)
-checkSampleBrain <-  rep(NA, times=repetition)
-checkSampleEQ <-  rep(NA, times=repetition)
-checkSampleNeocortex <-  rep(NA, times=repetition)
-checkSampleHippocampus <- rep(NA, times=repetition)
-checkSampleCerebellum <- rep(NA, times=repetition)
-checkSampleStriatum <- rep(NA, times=repetition)
-checkSampleMOB <- rep(NA, times=repetition)
-checkSampleRange <- rep(NA, times=repetition)
-
-counter=0
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        counter=counter+1
-        tryCatch(
-        {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleFruit",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-         checkSampleFruit[counter] <- toAdd[1]
-        }, error=function(e){
-          #Do nothing
-        }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleLeaf",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleLeaf[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleRange",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleRange[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleBrain",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleBrain[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleEQ",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleEQ[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleNeocortex",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleNeocortex[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleHippocampus",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleHippocampus[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleCerebellum",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleCerebellum[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleStriatum",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleStriatum[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/Sample_size/checkSampleMOB",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-           checkSampleMOB[counter] <- toAdd[1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-checkSampleFruit <- unlist(checkSampleFruit)
-checkSampleLeaf <- unlist(checkSampleLeaf)
-checkSampleRange <- unlist(checkSampleRange)
-checkSampleBrain <-  unlist(checkSampleBrain)
-checkSampleEQ <-  unlist(checkSampleEQ)
-checkSampleNeocortex <-  unlist(checkSampleNeocortex)
-checkSampleHippocampus <- unlist(checkSampleHippocampus)
-checkSampleCerebellum <- unlist(checkSampleCerebellum)
-checkSampleStriatum <- unlist(checkSampleStriatum)
-checkSampleMOB <- unlist(checkSampleMOB)
-
-#Min values
-minFruit <- min(checkSampleFruit)
-minLeaf <- min(checkSampleLeaf)
-minRange <- min(checkSampleRange)
-minBrain <- min(checkSampleBrain)
-minEQ <- min(checkSampleEQ)
-minNeocortex <- min(checkSampleNeocortex)
-minHippocampus <- min(checkSampleHippocampus)
-minCerebellum <- min(checkSampleCerebellum)
-minStriatum <- min(checkSampleStriatum)
-minMOB <- min(checkSampleMOB)
-
-minAllAreas <- min(
-minEQ,
-minNeocortex,
-minHippocampus,
-minCerebellum,
-minStriatum,
-minMOB
-)
-
-#Max values
-maxFruit <- max(checkSampleFruit)
-maxLeaf <- max(checkSampleLeaf)
-maxRange <- max(checkSampleRange)
-maxBrain <- max(checkSampleBrain)
-maxEQ <- max(checkSampleEQ)
-maxNeocortex <- max(checkSampleNeocortex)
-maxHippocampus <- max(checkSampleHippocampus)
-maxCerebellum <- max(checkSampleCerebellum)
-maxStriatum <- max(checkSampleStriatum)
-maxMOB <- max(checkSampleMOB)
-
-maxAllAreas <- max(
-maxEQ,
-maxNeocortex,
-maxHippocampus,
-maxCerebellum,
-maxStriatum,
-maxMOB
-)
-
-```
-
-<!-- TC:endignore -->
-
-# Introduction
-
-<!-- On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there].
-Overall, the evolution of the brain is the consequence of constraints (e.g.
-energetic limitations, @navarrete2011energetics), but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].
--->
-<!-- Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].
--->
-
-<!-- \initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics].
-Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
-However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition.
--->
-
-<!-- |   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
-Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond).
-Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic] and these areas are likely to be differently affected by species sympatry.
-For instance, the Main Olfactory Bulb (MOB) or the Hippocampus , home of a spatio-temporal memory [@burgess2002human], are largely involved in efficient foraging, especially for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany]: we therefore expect that primate species with larger MOB or Hippocampus areas, taken as equivalent to more advanced perceptive and cognitive abilities for efficient foraging, might be more fit than their sympatric species with smaller areas.
-Similarly, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging.
--->
-<!-- are expected to be influenced by the ecological environment.
-The Striatum is also stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike).
-Finally, besides foraging-related areas (Striatum, MOB or Hippocampus), more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode.
-To sum up, a first possibility is that sympatric heterospecifics could altogether stimulate cognition and promote larger sizes of the brain areas related to interacting with the social or ecological environment.
--->
-
-<!-- |   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview].
-Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e.
-positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory).
-Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g.
-phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social].
-In this case, the size of brain areas involved in immediate information processing should be less large in sympatric than in non-sympatric conditions.
-To sum up, a second possibility is that sympatric heterospecifics could hamper the benefits of cognition on foraging, and thus slowdown brain size increase.
-In an extreme case, it could even induce positive selection for smaller brain size.
--->
-
-<!-- |    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example.
-To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in primates.
--->
-
-\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics].
-Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging].
-However, space is often occupied by many species belonging to the same ecological guild.
-Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food ([@Avargues-Weber2013]; Hypothesis 2).
-In addition, direct interactions with heterospecifics, as much as with conspecifics [@dunbar2017there], might also affect cognition (Hypothesis 3).
-
-|   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species.
-Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities, with larger size considered equivalent to more advanced cognitive abilities [@Benson-Amram2016].
-Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic].
-These areas are likely to be under different selective pressures, and thus, to follow different evolutionary paths.
-In particular, they might be differently affected by species sympatry.
-First, brain areas involved in the storing of spatio-temporal information, such as the Hippocampus, home of an associative memory used for spatio-temporal navigation [@burgess2002human], should in particular be affected if the resource landscape is complexified by sympatric species foraging on the same resource (Hypothesis 1: memory is affected).
-Second, brain areas involved in processing more immediate sensory information, such as the Main Olfactory Bulb (MOB), Cerebellum [@koziol2014consensus; @sokolov2017cerebellum], and the Neocortex [@wiltgen2004new] should be particularly affected if the landscape of cues varies with sympatry (Hypothesis 2: cue processing is affected).
-Besides individual foraging, cognition can also be triggered by direct "social" interactions with other individuals [@byrne1994machiavellian; @dunbar2017there].
-The Striatum is a brain area stimulated during social interactions [@baez2013role], and should, therefore, be affected by direct social interactions with heterospecifics (Hypothesis 3).
-
-|   Under these (non-exclusive) hypotheses, sympatry could stimulate or hamper cognition evolution.
-Reasonable food depletion should promote memory, which stands as a valuable tool to infer food availability and location when food is rare and ephemeral but predictable [@milton1981distribution; @rosati2017foraging].
-In this case, the size of the Hippocampus should be larger the higher the sympatry (Prediction 1.1).
-On the other hand, maintaining a functional brain is energetically costly [@raichle2006brain], and if changes induced by sympatric species increase environmental unpredictability too much, which would make cognitive foraging not advantageous anymore [@grove2013evolution; @robirainreview], the Hippocampus size should be smaller the higher the sympatry (Prediction 1.2).
-In the meanwhile, "social" cues  left out by heterospecifics might also add to environmental ones.
-If species sympatry increases the load of usable cues to locate available food, we should then expect larger sizes of the MOB, the Cerebellum, or the Neocortex.
-Interactions between species can also occur directly, with the formation of mixed-group species [@Goodale2010].
-This, in particular, should promote larger Striatum size in sympatry.
-
-|   Here, we investigated the intertwining between species sympatry and cognition using frugivorous primates as a study example.
-Frugivorous primates are an interesting group for such a question because fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio], for which cognition thus considerably shapes the foraging strategy [@trapanese2019and].
-To infer the effect of species sympatry on brain size evolution within frugivorous primates, we evaluated the support for evolutionary models accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution.
-Finally, we tested for correlative patterns between brain size or current sympatry and the evolutionary consequences (assumed to be reflected by species diversification) in all primates.
-
-# Results
-
-```{r calculationValueForFirstResults}
-#Import data
-summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
-
-summaryDataForPlot <- summaryDataForPlot[!is.na(summaryDataForPlot$geographicCode),]
-# summaryDataForPlot <- summaryDataForPlot[summaryDataForPlot$DietaryGuild=="Fruit",]
-
-summaryDataForPlot$Family <- Data_powell2$MSW05_Family[match(summaryDataForPlot$Species_abbrv,Data_powell2$Species_abbrv)]#summaryData$Family[match(summaryDataForPlot$Species_abbrv, summaryData$Species_abbrv)]
-
-summaryDataForPlot[is.na(summaryDataForPlot$Family ),c(1,2,3)]
-#summaryDataForPlot$SpeciesForPhylogeny[which(is.na(summaryDataForPlot$Family))]
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Galagoides_demi"]<-"Galagonidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Macaca_munz"]<-"Cercopithecidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Microcebus_mitt"]<-"Cheirogaleidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Mirza_zaza"]<-"Lorisidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Nycticebus_java"]<-"Galagonidae"
-summaryDataForPlot$Family[summaryDataForPlot$Species_abbrv=="Tarsius_lari"]<-"Tarsiidae"
-
-lemuriformes.v <- 
-c(  
-"Daubentoniidae",
-"Lemuridae",
-"Indriidae",
-"Cheirogaleidae",
-"Lepilemuridae"
-)
-
-platyrrhini.v <- c(
-"Atelidae",   
-"Aotidae",
-"Pitheciidae",
-"Cebidae"
-)
-
-meanseMOBlemu <- round(c(
-  mean(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% lemuriformes.v &
-                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseMOBother <- round(c(
-  mean(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% lemuriformes.v &
-                                                               !is.na(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseStriatumplaty <- round(c(
-  mean(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %in% platyrrhini.v &
-                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-meanseStriatumother <- round(c(
-  mean(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v], 
-    na.rm=TRUE), 
-  sd(
-    (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v],
-    na.rm=TRUE)/
-    sqrt(
-      length(
-        (summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)[summaryDataForPlot$Family %nin% platyrrhini.v &
-                                                               !is.na(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass)]))
-), digit=2)
-
-# summaryDataForPlot[order(summaryDataForPlot$MOB/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-# summaryDataForPlot[order(summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-# summaryDataForPlot[order(summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass, decreasing = TRUE),]
-
-```
-
-We gathered a large database on the whole brain size, the size of the MOB, Cerebellum, and the Neocortex, involved in immediate sensory information processing, and the Striatum and the Hippocampus, related to either social and foraging-related memory, containing between `r minAllAreas` to `r maxEQ` frugivorous primate species (depending on the brain area considered).
-After pondering by whole-body mass, we observed ample variations in brain area relative sizes.
-For instance, the lemuriformes, that are known to prioritize smell compared to other primate species, have the largest relative MOB size (Lemuriformes: mean $\pm$ SE = `r meanseMOBlemu[1]` $\pm$ `r meanseMOBlemu[2]`, other: `r meanseMOBother[1]` $\pm$ `r meanseMOBother[2]`, \@ref(fig:figbrain)).
-Similarly, platyrrhini, and callitrichine primates in particular, are known to form poly-specific associations [@heymann2000behavioural].
-The latter show the highest relative size of the Striatum (Platyrrhini: mean $\pm$ SE = `r meanseStriatumplaty[1]` $\pm$ `r meanseStriatumplaty[2]`, other: `r meanseStriatumother[1]` $\pm$ `r meanseStriatumother[2]`, \@ref(fig:figbrain)).
-
-|   To get the evolutionary history of species sympatry between frugivorous lineages, we first reconstructed primate biogeography history (N$_{species}$ = `r minRange`; [@matzke2013probabilistic; @matzke2016stochastic]) when considering `r length(areaName)` biogeographic areas (Figure \@ref(fig:figmap); [@kamilar2009environmental]) and their diet evolution (N$_{species}$ = `r minFruit + minLeaf` to `r maxFruit + maxLeaf`; [@bollback2006simmap]).
-We then calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure.
-\@ref(fig:figbrain)).
-We specifically considered the matching competition (MC) model [@nuismer2015predicting] and density dependence models (DD$_{lin}$ and DD$_{exp}$), which assume a linear or exponential dependence of the brain sizes evolutionary rates on the number of sympatric lineages ([@drury2016estimating] see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-We compared the support of models considering species sympatry to the support of simpler models assuming no effect of species sympatry, like the Brownian Motion (BM), the Ornstein-Uhlenbeck process (OU) considering that traits are constrained around an optimal value (e.g.
-stabilizing selection; see [@blomberg2020beyond] for a review), or the Early-Burst model (EB, [@blomberg2003testing]), the latter allowing to check for a time-dependence of the evolutionary rate, hence emphasizing that, if any, the density dependence is not an artefact due to time dependence.
-Support for each model was evaluated using an information-theoretic framework [@burnham2002model] based on the weights of the Akaike Information Criteria corrected for small samples (AICc) when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB, see [Models of trait evolution: does species sympatry shape brain size evolution?]).
-
-|   We found that models not considering species sympatry were the most likely in describing the evolutionary history of the EQ, the Neocortex, and the Cerebellum (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)), two areas specifically involved in immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and also in memory consolidation for the Neocortex [@wiltgen2004new].
-The fact that these biggest areas are best described by the Ornstein-Uhlenbeck process suggests a stabilization towards an optimal size, which may illustrate the trade-offs between costs and benefits of brain development [@isler2009expensive].
-By contrast, density-dependence models considering sympatry were best supported in the foraging-related and social-related areas respectively: the Hippocampus, specialised in spatio-temporal memory [@burgess2002human] and the Striatum, involved in social interactions [@baez2013role].
-The fact that we inferred positive rates *r* of density-dependence (Figure \@ref(fig:figresultsevolution)), suggested an acceleration of the evolutionary tempo of trait evolution together with increased diversity of sympatric lineages for the Hippocampus and the Striatum.
-The Main Olfactory Bulb (MOB), the area involved in sensory abilities, also tended to be best fitted by models considering sympatry as a whole: yet, Brownian-Motion was as likely as density-dependent or MC models, preventing firm conclusions on whether sympatry affected or not MOB size evolution (Figure \@ref(fig:figbrain) and \@ref(fig:figresultsevolution)).
-
-```{r samplecooccurrence}
-
-minNspeciesCoocc <- round(min(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
-maxNspeciesCoocc <- round(max(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
-meanNspeciesCoocc <- round(mean(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE), digit=2)
-seNspeciesCoocc <- round(sd(dataRangePrimate$Number_species_cooccurrence, na.rm=TRUE)/sqrt(length(dataRangePrimate$Number_species_cooccurrence[!is.na(dataRangePrimate$Number_species_cooccurrence)])), digit=2)
-
-whichSpeciesMinNCoocc <- paste(sort(dataRangePrimate$Species[which(round(dataRangePrimate$Number_species_cooccurrence, digit=2)==minNspeciesCoocc)]), collapse=", ")
-whichSpeciesMaxNCoocc <- paste(sort(dataRangePrimate$Species[which(round(dataRangePrimate$Number_species_cooccurrence, digit=2)==maxNspeciesCoocc)]), collapse=", ")
-whichSpeciesMinNCoocc <- gsub("_", " ", whichSpeciesMinNCoocc)
-whichSpeciesMaxNCoocc <- gsub("_", " ", whichSpeciesMaxNCoocc)
-
-minOverlapSpecies <- round(min(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
-maxOverlapSpecies <- round(max(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
-meanOverlap <- round(mean(dataRangePrimate$Overlap_average, na.rm=TRUE), digit=2)
-seOverlap <- round(sd(dataRangePrimate$Overlap_average, na.rm=TRUE)/sqrt(length(dataRangePrimate$Overlap_average[!is.na(dataRangePrimate$Overlap_average)])), digit=2)
-
-whichSpeciesMinOverlap <- paste(dataRangePrimate$Species[which(round(dataRangePrimate$Overlap_average, digit=2)==minOverlapSpecies)], collapse=", ")
-whichSpeciesMaxOverlap <- paste(dataRangePrimate$Species[which(round(dataRangePrimate$Overlap_average, digit=2)==maxOverlapSpecies)], collapse=", ")
-whichSpeciesMinOverlap <- gsub("_", " ", whichSpeciesMinOverlap)
-whichSpeciesMaxOverlap <- gsub("_", " ", whichSpeciesMaxOverlap)
-
-```
-
-```{r estimateRegGradient, error=TRUE, include=TRUE}
-
-#Hippocampus
-model <- get(paste("modelBrain", traitName[3], sep="_"))
-
-estimateGradientHippocampus <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-testGradientHippocampus <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-
-#Striatum
-model <- get(paste("modelBrain", traitName[6], sep="_"))
-
-estimateGradientStriatum <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-testGradientStriatum <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-
-#MOB
-model <- get(paste("modelBrain", traitName[7], sep="_"))
-
-estimateGradientMOB <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-testGradientMOB <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-```
-
-|   Next, to understand the effect of sympatry on brain sizes (i.e.
-toward “bigger” or “smaller” brains the more sympatric species), we fitted phylogenetic regressions (see [Phylogenetic regressions] a)).
-For these linear regressions, the predicted variable was the relative brain size values of the different areas.
-We considered as covariates the average percentage of overlapping range with other sympatric frugivorous species, as well as the number of such sympatric frugivorous species across their entire distribution range based on IUCN data [@IUCN].
-On average ($\pm$ SE), the considered primate species had `r meanOverlap*100`% of their range overlapping with other species ($\pm$ `r seOverlap*100`).
-That ranged from `r minOverlapSpecies*100`% of overlap (*`r whichSpeciesMinOverlap`*), to `r maxOverlapSpecies*100`% of overlap (*`r whichSpeciesMaxOverlap`*).
-In terms of the distribution range, the considered primate species co-occurred on average with `r meanNspeciesCoocc` other primate species ($\pm$ `r seNspeciesCoocc`), ranging from `r minNspeciesCoocc` other species to `r maxNspeciesCoocc`.
-The number of sympatric species never influenced significantly the relative size of the brain or other specific areas (Table \@ref(tab:tableRegGradient)).
-Conversely, we found that the average percentage of overlapping range correlated with the relative size of areas that were better fit with models considering sympatry: the Hippocampus and the Striatum (Hippocampus: $t$`r testGradientHippocampus`; Striatum: $t$`r testGradientStriatum`).
-The correlations were all negative (Hippocampus: `r estimateGradientHippocampus`; Striatum: `r estimateGradientStriatum`), which means that higher range overlap between frugivorous species associates with lower relative size, insensitive to data and phylogenetic uncertainty (Table \@ref(tab:tabledfsensitivity), Figure \@ref(fig:forestPlot)).
-Given the acceleration of the evolutionary tempo with species sympatry ($r>0$ in the density-dependence models), it suggests that compared with isolated species, sympatric species are subject to a positive selection towards smaller brains, and not to a less intense selection for advanced cognitive abilities.
-
-```{r estimateRegDiversification, error=TRUE, include=TRUE}
-
-#print(traitName)
-# increaseHippocampus <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
-# averageDivRateHippocampus <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
-# estimateHippocampus <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-# testHippocampus <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-# 
-# #Neocortex
-# model <- get(paste("modelBrainDiversification", traitName[4], sep="_"))
-# 
-# increaseNeocortex <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
-# averageDivRateNeocortex <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
-# estimateNeocortex <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-# testNeocortex <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-#   
-# #Striatum
-# model <- get(paste("modelBrainDiversification", traitName[6], sep="_"))
-# 
-# increaseStriatum <- round(exp(summary(model)$coefficients[2,c(1)]), digit=2)
-# averageDivRateStriatum <- round(exp(summary(model)$coefficients[1,c(1)]), digit=2)
-# estimateStriatum <- textEstOneVar(summary(model)$coefficients[2,c(1,4,5)])
-# testStriatum <- textTestOneVar(summary(model)$coefficients[2,c(3,6)], statistics="")
-
-#print(c(increaseStriatum, averageDivRateStriatum, estimateStriatum, testStriatum))
-
-```
-
-```{r determineBoomTime}
-###-----
-## Diversification evolution over time
-fraction.v <- c(60, 70, 80, 90, 95)
-table_MAPS_rates_time <- c()
-for (f in fraction.v){
-  table_MAPS_rates_time_transitory <- read.table(paste0("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Scripts/Analysis3_diversification/diversification/MAPS_speciation_rates_trought_time_ClaDS2_tree_primate_complete_f",f,".csv"),sep=";",header=T)###Hahah nice English Benoit, trought ;)
-  table_MAPS_rates_time_transitory$f <- f
-  table_MAPS_rates_time <- rbind(table_MAPS_rates_time, table_MAPS_rates_time_transitory)
-}
-
-aggregatedSpeciationTime.mean <- aggregate(table_MAPS_rates_time$speciation_rates, by = list(table_MAPS_rates_time$time), FUN = mean)
-aggregatedSpeciationTime.sd <- aggregate(table_MAPS_rates_time$speciation_rates, by = list(table_MAPS_rates_time$time), FUN = sd)
-
-colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
-colnames(aggregatedSpeciationTime.sd) <- c("Time", "Diversification")
-
-# bp.resp <- breakpoints(Diversification ~ Time, data=aggregatedSpeciationTime.mean)
-# summary(bp.resp)
-# ## the BIC 
-# plot(bp.resp)
-# breakpoints(bp.resp)
-
-#Suggest that 4 is better from stats, visually 2
-
-bp.resp <- breakpoints(Diversification ~ Time, data=aggregatedSpeciationTime.mean, breaks=2)
-ci.resp <- confint(bp.resp)
-dates <- as.data.frame(breakdates(ci.resp))
-dateFirstRupt <- as.numeric(round((1-dates[1,])*(max(aggregatedSpeciationTime.mean$Time) - min(aggregatedSpeciationTime.mean$Time)), digit=2))
-dateSecondRupt <- as.numeric(round((1-dates[2,])*(max(aggregatedSpeciationTime.mean$Time) - min(aggregatedSpeciationTime.mean$Time)), digit=2))
-
-```
-
-|   Finally, we investigated the evolutionary consequences of brain evolution and sympatry by evaluating whether brain sizes and sympatry level correlated with the net species diversification rates (defined as speciation minus extinction rates).
-To do so, we used lineage-specific birth-death models of species diversification [@maliet2019model; @maliet2020fast].
-Overall, species diversification rates, estimated based on the primate molecular phylogeny, increased over time (Figure \@ref(fig:figdiversificationTime)), particularly in the early and late Miocene, around 25 and 11 Myr ago (Figure \@ref(fig:figdiversificationTime)).
-When accounting for phylogenetic dependence, no significant relationship between the net diversification rate and the relative size of brain areas was found (Table \@ref(tab:tableRegDiversification), Figure \@ref(fig:forestPlot); see robustness in Table \@ref(tab:tabledfsensitivity2)).
-Given the context-dependence of the direction of selection (towards bigger sizes when sympatry is low, smaller sizes otherwise), there is no surprise that we do not observe a correlation between the diversification rate and the three brain areas affected by species sympatry.
-Surprisingly however, we found no positive association between the net diversification rate and the EQ, nor with the relative sizes of the Cerebellum or the Neocortex, two areas insensitive to species sympatry too.
-This is puzzling because this contradicts a recent study [@melchionna2020macroevolutionary].
-The visual inspection of the regressions however clearly evidenced a positive trend for the EQ and the Neocortex, if discarding phylogenetic non-independence (Figure \@ref(fig:figRegressionDiversification)).
-Indeed, sudden encephalisation in primates is clearly associated with a limited number of closely-related species [@decasien2017primate; @melchionna2020macroevolutionary].
-This clearly limits the statistical power of our phylogenetically-corrected analyses, as we cannot decipher whether the connivance between brain size and species diversification results from a true biological link or appeared by chance.
-A positive association between brain size and diversification was also found in birds [@sayol2019larger] given that bigger brains act as a buffer to environmental challenges [@sol2007big].
-This means that, despite what we found here, a positive association between brain size and species diversification evidenced in [@melchionna2020macroevolutionary] remains a likely possibility.
-Finally, although diversification was uncorrelated with brain size in frugivorous primates, it was influenced by the sympatry context.
-In particular, phylogenetic regressions highlighted a negative effect of the number of sympatric species on the diversification rate (`r textEstOneVar(as.numcharac(results.df_diversificationAndSympatry[4,2:4]))`, `r textTestOneVar(as.numcharac(results.df_diversificationAndSympatry[4,5:6]), statistics="t")`, Table \@ref(tab:tableRegDiversificationAndSympatry), Figure \@ref(fig:forestPlot)).
-In other words, the higher the number of sympatric species, the lower the diversification rate, a density-dependence trend that is frequently observed in many tetrapod clades [@condamine2019assessing].
-
-# Discussion
-
-Bigger brains are not necessarily better.
-The size of the brain is subject to a compromise between the energy it incurs, and the increase of fitness it allows.
-This is clearly emphasized by the fact that the biggest areas, the Cerebellum and the Neocortex, as well as the whole brain (EQ), were best described by the Ornstein-Uhlenbeck process.
-This evidence might suggest a stabilisation towards an optimal size resulting from an equilibrium between costs and benefits.
-As the brain is regionally specialised [@barton2000mosaic], different brain areas could be under different selective pressures.
-This is evidenced, here, by the differences of relative sizes across lineages in the MOB or Striatum in particular.
-We further show that sympatry is one factor that affects the selective regime under which some brain region evolves: although the brain as a whole was insensitive to species sympatry, the latter nonetheless induced a change in the relative size of the Hippocampus and the Striatum.
-These areas are involved in individual-based and social-based information processing, pinpointing that the two components might be under strong selection in primates [@decasien2017primate; @powell2017re; @gonzalez2018inference].
-
-|   The negative influence of sympatry on the Striatum might be quite surprising.
-Direct interactions with heterospecifics should stimulate this area (Hypothesis 3).
-We observed that this area was relatively larger in callitrichines, particularly known to perform mixed-species groups [@heymann2015unlike].
-When interacting with conspecifics, the Striatum underpins reward expectation, goal-directed behaviour, and planning abilities [@johnson2007integrating].
-These skills are key within group, following a Machiavellian perspective [@byrne1994machiavellian].
-Yet, these skills might also be relevant in a foraging context.
-It is thus possible that actions underpinned by the Striatum (e.g.
-planning/anticipating heterospecifics moves), might be key and up to now overlooked, when foraging in a multi-species context too.
-
-|   Overall, the fact that only these two areas, particularly relevant to process and memorise spatio-temporal information, are sensitive to sympatry, is consistent with the idea of an effect of species affecting resource spatio-temporal patterns (Hypothesis 1).
-Competition is generally the first-thought mechanism to describe community structures [@rocha2015role] because it might affect the environment, and associate selective pressure, in which species evolve.
-We show that higher levels of sympatry is actually associated with smaller sizes of the Hippocampus or Striatum (in accordance with Prediction 1.2).
-This suggests that indirect competition for food might contribute to convoluting the environment which might generate a positive selection for smaller brains.
-Not only was brain evolution affected by sympatry, but sympatry induced a slowdown in diversification.
-Density-dependence within a clade is indeed generally associated with lower diversification rates [@moen2014does].
-In particular, species competing for resources are thought to contribute to limiting their ranges [@price2009evolutionarily], hence constraining population size and their subsequent diversification [@pigot2013species].
-These observations thus strengthen the idea of scramble competition between species that cascades both on species population dynamics and species cognition.
-
-|   By contrast, potential indirect facilitation between species due to “social” cues (Hypothesis 2), is ruled out by the absence of an effect of sympatry on brain areas involved in immediate sensory information processing (e.g.
-Cerebellum or Neocortex).
-This absence of effect can stem from two possibilities.
-Either sympatry, indeed, does not affect the landscape of cues for foragers.
-Otherwise, it has been shown that foragers tend to use social information over environmental (i.e.
-personal) information, in particular in non-perfectly predictable environments [@rafacz2003environmental; @dunlap2016foraging].
-Thus, if environmental complexity increases too much, “social” cues provided by heterospecifics might replace environmental ones.
-From this point of view, the size of the MOB, the Cerebellum, or the Neocortex should, at the very least, remain unaffected by sympatry.
-This nonetheless deserves further attention.
-
-|   To conclude, the use of brain size as a proxy for cognition is a central debate with no optimal solution (see grounded criticism from [@deaner2000comparative; @healy2007critique; @logan2018beyond]).
-The current flourishment of consortia, allowing for much more detailed and standardized anatomical measurements (e.g.
-in primates: [@milham2018open]), or with standardized behaviourally explicit comparisons (e.g.
-on captive [@many2019establishing] or wild [@janmaat2021using] primates), might alleviate biases stemming from brain size analysis, but this will take time to generate large-enough datasets.
-In the meanwhile, brain size is a proxy much appreciated in practice, because of its easy accessibility for a “large” number of species.
-Here, we showed that species sympatry is an important factor shaping the evolutionary history of animals' brains, but the proximate mechanisms at play remain to be elucidated.
-Finally, it is very likely that any hypothesis on cognition evolution, generally discussed within species, could be broadened to a between-species context: foraging facilitation between species does exist [@olupot1998fruit; @Havmoller2021], and so do polyspecific social associations [@porter2001benefits], as well as inter-species territory defence [@drury2020competition; @losin2016ecological] or imitation and copying [@persson2018spontaneous; @pepperberg2002allospecific].
-Similarly, prey-predator races could shape selection on cognitive abilities [@shultz2006chimpanzee].
-As Alice said “It's a great huge game of chess that's being played—all over the world” ([@Carroll], Chapter II) and all individuals are just pieces to play with or against, no matter the species.
-
-<!-- TC:ignore -->
-
-\newpage
-
-# Methods
-
-Data processing, analyses, and plots were computed with R software (`r extractRversion()`, @Rsoftware).
-Used codes and data are freely available at [https://github.com/benjaminrobira/Meta_analysis_cognition_primates](https://github.com/benjaminrobira/Meta_analysis_cognition_primates).
-Note that in all these analyses, we discarded *Homo sapiens* and *Macaca sylvanus*.
-The latter was discarded in the analyses because of geographical complete isolation and repeated intervention of human people in population maintenance [@modolo2005phylogeography].
-A summary of available data per species is presented in Appendix Figure \@ref(fig:figmap).
-
-## Data Collection
-
-### Phylogeny
-
-We used a block of chronogram trees of the primate taxon of the 10kTrees project (downloaded on May 2021, version 3), as well as a consensus tree of 1000 trees for the subsequent phylogenetic analyses.
-The trees contain `r length(phylo_init$tip.label)` primate species.
-
-### Trait data
-
-Brain data were obtained from [@decasien2019primate] for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), [@powell2017re] and [@powell2019maternal] for the whole brain, Cerebellum and Neocortex size, [@todorov2019primate] for Hippocampus and Neocortex size, [@grueter2015home] for the whole brain size and [@navarrete2018primate] for the whole brain, Cerebellum, Hippocampus and Striatum size.
-They were freely available in the main manuscript or supplementary materials.
-When a species was represented multiple times within the dataset, we obtained a unique attribute by averaging it.
-From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]
-
-\hfill
-
-\begin{center}
-
-$\mathrm{EQ}=1.036 \times \mathrm{Brain\,volume}/ (0.085 \times \mathrm{Body\,mass}^{0.775})$
-
-\end{center}
-
-\hfill
-
-with the brain volume in cm$^{3}$, 1.036 g/cm$^{3}$ being the assumed homogeneous brain density, and the body mass in g.
-EQ indicates whether the brain size ranges above (> 1) or below (< 1) expected given the body mass.
-Body mass was obtained from [@decasien2017primate; @powell2017re; @grueter2015home; @pearce2013space].
-The sub-parts of the brain were chosen because they were involved in immediate sensory information processing (MOB, N$_{MOB,max}$ = `r maxMOB`), in movement and/or general information processing and retention (Neocortex, N$_{Neocortex,max}$ = `r maxNeocortex`, [@wiltgen2004new]; Cerebellum, N$_{Cerebellum,max}$ = `r maxCerebellum`, [@koziol2014consensus; @sokolov2017cerebellum]), short-term working memory and long-term spatio-temporal memory (Hippocampus, N$_{Hippocampus,max}$ = `r maxHippocampus`, [@burgess2002human]).
-The Striatum (N$_{Striatum,max}$ = `r maxStriatum`) supports information processing during social interaction, reward assessment, planning or goal-oriented behaviours [@baez2013role; @johnson2007integrating].
-To investigate their evolutionary history, we used the ratio between their volume and body mass, so as to maximize comparability.
-As such, the use of specific region sizes relative to the body mass and not raw sizes depicts the evolution of cognitive abilities in terms of allocation rather than abilities per se (but see discussion in [@deaner2000comparative]).
-Percentage of frugivory and/or folivory was obtained based on a freely available dataset from [@decasien2017primate; @powell2017re; willems2013collective].
-
-### Ranging Data
-
-Current geographic (maximal possible) range of each primate species was assessed using ranging maps provided by the IUCN red list [@IUCN].
-Ranging data were available for `r nrow(matrixRangingSensitivity[!is.na(matrixRangingSensitivity[,1]),])` species among the `r length(phylo_init$tip.label)` represented in the 10kTrees primate phylogeny.
-
-## Primate species sympatry
-
-For primate biogeography, based on the structure (i.e.
-number of species and their phylogenetic relationships) of primate communities at different field sites, Kamilar et al.
-[@kamilar2009environmental] determined clusters of sites with highly similar community structures that were shaped by both the environment geography and climatic correlates.
-We used this classification and manually mapped the geographic areas using Google earth professional (v7.3.3).
-These geographic areas are represented in Figure \@ref(fig:figmap) and correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia, and the Asian Islands.
+load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/RDataforAppendix.RData")
+```
+
+# Data variability
+
+We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to distribution ranges, or anatomical/behavioural traits.
+
+## Sensitivity to variation in distribution range
+
+The chosen biogeographic areas correspond to Central America, the North and the South of South America respectively, West Africa, Central Africa, and East/South Africa, East and West of Madagascar respectively, West Asia, Central/East Asia, South Asia, and the Asian Islands.
 The chosen scale for the areas is large because (i) retracing the history of a large number of areas necessitates considerable computational means.
@@
 Furthermore (ii), all species and particularly primate species suffer(ed) from recent extinction [@pavoine2019mammal], with a reduction of ranging areas at an unprecedented speed rate.
-Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution (e.g.
-evidenced on the North American fauna in [@pineda2021mammal]).
-One to multiple large-scale geographic areas were assigned to each species as soon as the species current distribution range overlapped in the surface at `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold; the maximum was chosen to `r geographicThresholdVector[2]*100`% because on present data, a species could occupy as far as three areas, Figure \@ref(fig:figmap)).
-Overlap was calculated with the “gIntersection” function from the *rgeos* package [@rgeos] applied to Mercator-projected data to get the overlapping contour, and the “area” function from the *geosphere* package [@geosphere], applied directly on unprojected longitudinal-latitudinal data for area size calculation.
-
-|   We retraced the biogeographic history of the lineage ranges based on current observations of species range with the *BioGeoBEARS* package [@matzke2013probabilistic], using the biogeographic stochastic mapping algorithm [@matzke2016stochastic].
-We fitted non-time-stratified dispersal-extinction-cladogenesis (DEC) models specifically suiting analyses of range data since it accounts for spatially explicit processes of cladogenetic and anagenetic events (see [@matzke2013probabilistic] for further details on these events).
-To reconstruct the evolution of species range, we fixed the maximum number of areas that could be occupied by a lineage at one time to three areas.
-A too high number of areas that can be occupied simultaneously drastically increases computational time.
-Here, we therefore chose that a species can at most occupy three areas since it offers the possibility to occupy a complete mainland continent.
-Finally, because these history reconstructions are likely to vary, for each run of DEC models (considering both possible overlaps to consider species presence), we obtained `r numberSimulations` stochastic maps that were all used in subsequent phylogenetic model fits (see [Phylogenetic models]) to account for the uncertainty of these ancestral range estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
-
-## Dietary guilds
-
-We classified species as either “frugivorous” or “folivorous” based on the availability of frugivorous rate and folivorous rate , prioritizing frugivory over folivory.
-First, a species would be classified as frugivorous if the frugivory rate was at least above `r frugivoryThresholdVector[1]` (low threshold) or `r frugivoryThresholdVector[2]`% (high threshold).
-If this was not the case, or frugivory rate was unavailable, a species could be classified as folivorous if the folivory rate was at least above `r folivoryThresholdVector[1]` (low threshold) or `r folivoryThresholdVector[2]`% (high threshold).
-Otherwise, [@decasien2017primate] gave a binary classification of diet, species being categorized as frugivorous or folivorous, partly based on anatomical criteria.
-Whenever the rate was not available, we referred to this classification.
-In any other cases, the species was discarded.
-To illustrate, if a species reached 30% of frugivory, and 65% of folivory (the rest being due, for instance, to insectivory), then, it would be categorized as, “frugivorous” if low thresholds are considered, or as “folivorous” in case high thresholds are considered.
-If we suppose now another species with 30% of frugivory and 50% of folivory, but considered by [@decasien2017primate] as frugivorous, then, the species would be “frugivorous” for low threshold, and still “frugivorous” with high thresholds.
-
-```{r transitionMatrix}
-
-transitionMatrix <- matrix(NA, nrow=repetition, ncol=2)
-
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        start=which(is.na(transitionMatrix[,1]))[1]
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_simmap_transition",a,"_",b,"_",c,"_",d, ".txt", sep=""))
-          transitionMatrix[start,1] <- toAdd[1,1]
-          transitionMatrix[start,2] <- toAdd[2,1]
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-minProba.v <- apply(abs(transitionMatrix), 2, min)
-maxProba.v <- apply(abs(transitionMatrix), 2, max)
-
-```
-
-|   Frugivory was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
-Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
-First, such a static rate does not reflect potential seasonality in fruit-eating (e.g.
-[@masi2009western]), which is generally shorter, hence a lower overall frugivory rate.
-Second, the frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
-Finally, the methodology to obtain this rate could additionally vary (e.g.
-in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves).
-For all these reasons, we used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
-
-|   Considering diet as a binary variable (frugivory versus folivory), we retraced the evolutionary history of such discrete traits based on a continuous Markovian process (extended Mk models) and relying on a Bayesian approach [@bollback2006simmap], using the “simmap” function of the *phytools* package [@phytools] and internally estimating the prior probability of trait (i.e.
-at the root), but with no prior on the transition matrix.
-Again, the obtained character history is in no case certain.
-Therefore, for each run, we obtained `r numberSimulations` stochastic character maps that were used in subsequent phylogenetic model fits (see [Phylogenetic models]), to account for the uncertainty of these ancestral diet estimations (see [Models of trait evolution: does species sympatry shape brain size evolution?] (b)).
-
-## Phylogenetic models
-
-### Models of trait evolution: does species sympatry shape brain size evolution?
-
-\hfill
-
-(a)	Fitting models of trait evolution
-
-\hfill
-
-We focused only on frugivorous primates, because the sample size was otherwise insufficient, and fitted phylogenetic models of the evolution of the EQ or the relative size of a specific brain area considering or not species sympatry.
-Models were fitted on different sample sizes due to the non-availability of some data for some traits.
-Specifically, models using EQ included `r minEQ` to `r maxEQ` frugivorous species.
-Other models included more reduced sample sizes (in species number): Striatum (`r minStriatum` to `r maxStriatum`), MOB (`r minMOB` to `r maxMOB`), Neocortex (`r minNeocortex` to `r maxNeocortex`), Hippocampus (`r minHippocampus` to `r maxHippocampus`), Cerebellum (`r minCerebellum` to `r maxCerebellum`).
-Nonetheless, for a given set of models (i.e.
-within brain area), the sample was strictly identical, allowing within-set comparisons.
-Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions.
-Models without species sympatry, Brownian Motion (BM), Ornstein-Uhlenbeck process (OU, model with stabilizing selection), or Early-Burst model (EB, for assessing a time-dependence of the evolutionary rate), were fitted using the “fitContinuous” function from the *geiger* package [@geiger3; @geiger5].
-Using the evolutionary history of species distribution (see [Primate species sympatry]) and of diet (see [Dietary guilds]), we fitted models considering species sympatry using the “fit_t_comp” function from the *RPANDA* package [@RPANDA].
-These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet.
-These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas (see [@drury2016estimating]).
-We fitted three different models considering species sympatry.
-The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating].
-Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size.
-Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity].
-Density-dependence means that the evolutionary rate, $\lambda$, of trait changes, varies either positively or negatively as a function $f$ of the number of sympatric lineages sharing the same diet, such as
-
-\begin{center}
-
-\hfill
-
-$f_{lin}(\lambda)=\lambda_{0} + rl$
-
-$f_{exp}(\lambda)=\lambda_{0}\exp(rl)$
-
-\hfill
-
-\end{center}
-
-where $\lambda_{0}$ corresponds to the value of the initial ancestor, $l$ indicates the number of lineages, $r$ allows for modelling the speed and direction of the dependency to lineage number ($r>0$ leads to an increase of trait changes, while $r<0$ leads to a decline of the trait changes).
-All these models were repeated `r numberSimulations` times, using `r randomSampling` different combinations of the evolutionary histories of primate ranges and diets.
-They were then compared within an information-theoretic framework [@burnham2002model] based on the weights of Akaike Information Criteria corrected for small samples (AICc), when considering all six models (MC, DD$_{lin}$, DD$_{exp}$, BM, OU, EB).
-The model weight depicts how well the model fits the observed evolutionary pattern compared with the other tested models.
-
-\hfill
-
-```{r prepfigevolution}
-
-###Set working directory
-setwd("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates")
-
-summaryBrainFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryEQFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryNeocortexFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryHippocampusFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryCerebellumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryStriatumFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-summaryMOBFrugivory <- as.data.frame(matrix(NA, nrow=10*(repetition+1), ncol=53))
-
-counter=0
-start=counter
-end=counter
-numberSimulations=10
-totModelsWorked=c(0,0,0,0,0,0,0)
-for(a in 1:2){
-  for(b in 1:2){
-    for(c in 1:2){
-      for(d in 1:10){
-        counter=end+1
-        start=counter
-        end=counter + numberSimulations - 1
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_BrainBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryBrainFrugivory[start:end,] <- as.data.frame(toAdd)
-        totModelsWorked[1]=totModelsWorked[1]+1
-        }, error=function(e){
-          #Do nothing
-          }
-        )
-
-        tryCatch(
-        {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_EQ",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryEQFrugivory[start:end,] <- toAdd
-        totModelsWorked[2]=totModelsWorked[2]+1
-        }, error=function(e){
-          #Do nothing
-        }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_NeocortexBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryNeocortexFrugivory[start:end,] <- toAdd
-        totModelsWorked[3]=totModelsWorked[3]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_HippocampusBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryHippocampusFrugivory[start:end,] <- toAdd
-        totModelsWorked[4]=totModelsWorked[4]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_CerebellumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryCerebellumFrugivory[start:end,] <- toAdd
-        totModelsWorked[5]=totModelsWorked[5]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_StriatumBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryStriatumFrugivory[start:end,] <- toAdd
-        totModelsWorked[6]=totModelsWorked[6]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-
-        tryCatch(
-          {toAdd <- read.delim(paste("Processed_data/OutputEvolModel/Output_evolutionary_history_MOBBodymassRaw",a,"_",b,"_",c,"_",d,".txt", sep=""))
-        summaryMOBFrugivory[start:end,] <- toAdd
-        totModelsWorked[7]=totModelsWorked[7]+1
-          }, error=function(e){
-            #Do nothing
-          }
-        )
-      }
-    }
-  }
-}
-
-summaryBrainFrugivory <- summaryBrainFrugivory[!is.na(summaryBrainFrugivory[,1]),]
-summaryEQFrugivory <- summaryEQFrugivory[!is.na(summaryEQFrugivory[,1]),]
-summaryNeocortexFrugivory <- summaryNeocortexFrugivory[!is.na(summaryNeocortexFrugivory[,1]),]
-summaryHippocampusFrugivory <- summaryHippocampusFrugivory[!is.na(summaryHippocampusFrugivory[,1]),]
-summaryCerebellumFrugivory <- summaryCerebellumFrugivory[!is.na(summaryCerebellumFrugivory[,1]),]
-summaryStriatumFrugivory <- summaryStriatumFrugivory[!is.na(summaryStriatumFrugivory[,1]),]
-summaryMOBFrugivory <- summaryMOBFrugivory[!is.na(summaryMOBFrugivory[,1]),]
-
-colnames(summaryBrainFrugivory) <- colnames(toAdd)
-colnames(summaryEQFrugivory) <- colnames(toAdd)
-colnames(summaryNeocortexFrugivory) <- colnames(toAdd)
-colnames(summaryHippocampusFrugivory) <- colnames(toAdd)
-colnames(summaryCerebellumFrugivory) <- colnames(toAdd)
-colnames(summaryStriatumFrugivory) <- colnames(toAdd)
-colnames(summaryMOBFrugivory) <- colnames(toAdd)
-
-##----
-
-colNum <-c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-
-models <- c("BM", "OU", "EB", "MC", expression(DD[italic(lin)]), expression(DD[italic(exp)]))
-colourModels <- brewer.pal(n = 6, name = "Set1")
-
-```
-
-(b) Dealing with data uncertainty and parameterisation sensitivity
-
-\hfill
-
-In this analysis, uncertainty can stem from two sources.
-First, the evolutionary history (phylogeny, diet, and ranging) was reconstructed based on Bayesian inference.
-They are susceptible to be uncertain at some points.
-Thus, we used a consensus phylogenetic tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
-In addition, we repeated diet and ranging history reconstructions `r numberSimulations` times.
-
-|   Second, for each species, trait estimates could vary slightly among datasets (see Appendix Figure \@ref(fig:figvariabilitydata)).
-Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Appendix Figure \@ref(fig:figvariabilitydata)).
-In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Figure \@ref(fig:figcomparison)) and (ii) to assess the species dietary guild (see Appendix Figure \@ref(fig:figvariabilitydata)) which can cause sensitivity of the results to the chosen parameters.
-To account for these three sources of variability, we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
-equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory, and species sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
-
-|   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolutionary reconstructions) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold defining sympatry) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
-We stopped computations when the optimization of the likelihood was excessively long (> 1 week).
-The final sample size thus was of `r min(totModelsWorked[-2])*10` models that covered all the ranges of tested parameters.
-
-### Models of species diversification
-
-We investigated how primates diversified over time.
-Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
-Particularly, we used *ClaDS2*, the model with constant turnover (i.e.
-constant ratio between extinction and speciation rates).
-This Bayesian approach considers speciation rate heterogeneity by modelling small shifts in the rate at speciation events.
-In other words, the two new lineages are assumed to inherit new speciation rates that are sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the initial speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
-Three independent chains were run until their convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
-The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
-The latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
-
-|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
-Estrada et al.
-[@estrada2017impending] estimated that, given current knowledge, the primate clade should be composed of 504 species.
-This means that the current sampling fraction is around 73%.
-We thus parameterized the *ClaDS* algorithm with this value for the estimated sampling fraction.
-Yet, given that the extant number of primate species is subject to controversy, and because the estimated sampling fraction may affect diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
-At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each extant primate species, as well as the mean diversification rate (given all lineages) through time.
-
-### Phylogenetic regressions
-
-\hfill
-
-(a)	Determining the effect of sympatry on brain sizes
-
-\hfill
-
-To determine the nature of the relationship between species sympatry and relative sizes of brain regions, we fitted Gaussian Pagel's lambda phylogenetic regressions (i.e.
-a derivative of the Brownian Motion model, for which the phylogenetic variance-covariance matrix has all coefficients, but its diagonal ones, multiplied by lambda) for each brain region individually and for frugivorous species only.
-We used Pagel's lambda model so as to relax the hypothesis of Brownian Motion since we included brain areas for which the evolutionary history was best described by models considering sympatry.
-Here specifically, we considered the least stringent frugivory assessment, with the frugivory threshold fixed to `r frugivoryThresholdVector[1]`% and the folivory threshold fixed to `r folivoryThresholdVector[1]`%.
-If, due to data variability, a species did not robustly fit into the categorical classification “frugivorous versus folivorous” (i.e.
-could be either of the two), it was considered as frugivorous nonetheless.
-
-|    The response variable was the relative size of brain areas.
-Due to data variability, we took the mean of the possible values given the different datasets, and assessed the sensitivity using non-averaged values (see [Phylogenetic regressions: results, stability, and assumption]).
-In this model, the covariates (i.e.
-continuous predictors) were the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species (the second was square-rooted, to reach symmetrical distribution).
-For a given species A, sympatry with another species B was considered when species B range overlapped on more than `r geographicThresholdVector[1]*100`% of the range of species A.
-This was done to reduce the noise induced by coarse identification of species range.
-
-\hfill
-
-(b)	Diversification and brain size
-
-\hfill
-
-In the same way as explained above, we fitted Gaussian Pagel's lambda phylogenetic regressions of the different relative brain sizes against the net diversification rates (i.e.
-the difference between speciation and extinction rates), estimated for each extant species by the *ClaDS* algorithm.
-Again, we took the mean of the brain trait values for the main model and assessed the sensitivity by re-running the model several times using non-averaged values.
-
-\hfill
-
-(c) Diversification and species sympatry
-
-\hfill
-
-To determine whether species sympatry was associated with specific diversification patterns (and thus if diversification rates were regionalized), we fitted Gaussian Pagel's lambda phylogenetic regressions with the diversification rate as output variable, and used the two metrics for describing sympatry (the average percentage of overlapping range with other sympatric frugivorous species, and the number of frugivorous sympatric species) as tested variables, as described in (a).
-
-\hfill
-
-(d)	Model implementation
-
-\hfill
-
-(i)	Effect of sympatry on brain sizes
-
-\hfill
-                                                                                                                                                                           Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (with $\lambda$ indicating the strength of the phylogenetic signal, where $\lambda$=1  corresponds to Brownian Motion, i.e.
-the maximal influence of the phylogenetic history on the trait evolution) estimated by maximum-likelihood (argument “model” set to “lambda”).
-Bootstrapping over `r repetitionBootstrap` independent replicates was done to obtain confidence intervals.
-Other function parameters were set to default.
-Prior to fitting, covariates were transformed so as to reach more symmetrical distributions when adequate.
-Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
-We did not observe correlation issue among predictors neither (VIF$_{max}$ < 2, [@mundry2014statistical]).
-
-\hfill
-
-(ii)	Diversification and brain size
-
-\hfill
-
-We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist approach because it led to a violation of homoscedasticity.
-Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
-Each chain was based on a burnin period of `r burnin` iterations, among a total of `r nitt` iterations, and was sampled every `r thin` iterations.
-We used the least informative priors.
-Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
-Priors on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at a limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
-We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion (max value < `r round(max(gelmanRubinValues), digit=4)`; @gelman1992inference), as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
-In Appendix [Model assumptions], we present traces and distributions of posterior estimates.
-We further checked the quality of the posterior by visually assessing the Q-Q plot of the posterior with that of a Gaussian distribution of mean 0 and sd 1 (see Appendix [Model assumptions]).
-We present the estimate together with the 95% credibility interval centered on the mode (Highest Density Posterior, HDP), together with a MCMC p-value (pMCMC) that corresponds to the probability that the estimate ($\beta$) is positive if the mean estimate ($\hat{\beta}$) is negative (i.e.
-$P(\beta>0|\hat{\beta}<0)$), or if the mean estimate is positive, the probability that the estimate is negative (i.e.
-$P(\beta<0|\hat{\beta}>0)$).
-
-\hfill
-
-(iii) Diversification and sympatry
-
-\hfill
-
-We fitted phylogenetic regression as explained in (i).
-In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability, and assumption]).
-
-\hfill
-
-(d)	Model robustness
-
-\hfill
-
-To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree .
-
-|   To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10000 possible trees from the 10kTrees project.
-For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple values (e.g.
-if body mass was provided by different datasets etc.).
-For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before), using the "standard" dataset and the consensus tree.
-
-|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes the weak sensitivity of the results.
-
-# Acknowledgements
-
-We considerably value the help provided by J.
-Drury in making some scripts available functions in the *RPANDA* package in *R* and helping us in running them, and that of M-C.
-Quidoz for assistance in using the CEFE cluster.
-We thank S.
-Benhamou and M.
-Clairbaux for discussions on spatial projections, and M.
-Quéroué, V.
-Lauret, A.
-Caizergues, and C.
-Teplistky for feedback on Bayesian computations too.
-Finally, this work could not have been possible without prior data collection from the IUCN Red List (primate ranging), the 10kTrees project (phylogenetic trees), and A.
-R.
-DeCasien and collaborators, L.
-E.
-Powell and collaborators, O.
-S.
-Todorov and collaborators, E.
-P.
-Willems and collaborators, F.
-Pearce and collaborators, A.
-F.
-Navarrete and collaborators, and C.
-C.
-Grueter who provided primate trait data we used as (supplementary) material with their articles, as well as Nicholas J.
-Matzke for available algorithm scripts allowing us to implement and better understand the methods.
-Their indirect input is therefore tremendous.
-Both authors were supported by a doctoral grant from the *École Normale Supérieure*, Paris.
-
-# Authors' contribution
-
-BR conceived the study, collected, cleaned and analysed the data, drew the figures and wrote the first version of the manuscript and subsequently revised it.
-BP-L implemented the ClaDS algorithm for our data, helped with running other analyses, and revised the manuscript multiple times.
-The authors declare having no conflict of interest.
-All authors gave final approval for publication and agree to be held accountable for the work performed therein.
-
-```{r tableRegGradient, include=TRUE}
-results.df_gradient <- results.df_gradient[-(6:10),]
-results.df_gradient[1] <- gsub("frugivorous", "frugivores", results.df_gradient[,1])
-results.df_gradient[1] <- gsub("home range", "range", results.df_gradient[,1])
-
-rownames(results.df_gradient) <- NULL
-knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value.
-The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
-The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") #%>%
-  #kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r}
-#Round numbers table
-results.df_diversification[seq(from=4, to=nrow(results.df_diversification), by=4),c(2,3,4)] <-apply(results.df_diversification[seq(from=4, to=nrow(results.df_diversification), by=4),c(2,3,4)], 2, function(x){roundIntelligent(as.numcharac(x), digit=2)})
-
-results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1] <- gsub("\\(log\\) ", "", results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1])
-results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1]  <- gsub("\\(\\/bodymass, log\\) ", "", results.df_diversification[seq(from=1, to=nrow(results.df_diversification), by=4),1])
-
-```
-
-\newpage
-
-```{r tableRegDiversification, include=TRUE}
-results.df_diversification <- results.df_diversification[-(5:8),]
-rownames(results.df_diversification) <- NULL
-knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff.
-samp.=Effective sample (adjusted for autocorrelation).
-The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
-The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
-  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") #%>%
-  #kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\newpage
-
-```{r tableRegDiversificationAndSympatry, include=TRUE}
-results.df_diversificationAndSympatry[1] <- gsub("frugivorous", "frugivores", results.df_diversificationAndSympatry[,1])
-results.df_diversificationAndSympatry[1] <- gsub("home range", "range", results.df_diversificationAndSympatry[,1])
-
-knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value.
-The brain areas (as well as the associated sample size) are indicated prior to each list of estimates.
-The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
-  kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down")
-
-```
-
-\clearpage
-
-```{r prepareMap}
-#Reimport areas with cropping
-centroid <- matrix(NA, ncol=2, nrow=length(areaName))
-for(i in 1:length(areaName)){
-  areaTransitory <- readOGR(dsn=paste("T:/IUCN_data_primate/Geographic_areas/Shapefiles/",areaName[i],".shp",sep=""))
-  areaTransitory = clgeo_Clean(areaTransitory)
-  areaTransitory <- spTransform(areaTransitory, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
-  #Have mercator for intersection
-  areaTransitory <- spTransform(areaTransitory, CRS("+proj=merc +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
-  areaTransitory <- gIntersection(areaTransitory, worldMap_mercator, byid=FALSE)
-  areaTransitory = clgeo_Clean(areaTransitory)
-  #Reunite polygon in case
-  areaTransitory <- gBuffer(areaTransitory, byid=F, width=0)
-
-  #back transform to long/lat
-  areaTransitory <- spTransform(areaTransitory, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
-  assign(paste("area", i, sep="_"), areaTransitory)
-  if(i==1){
-    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] + 5, summary(areaTransitory)$bbox[2,1])
-  }
-  else if (i==2){
-    centroid[i,] <- c(summary(areaTransitory)$bbox[1,2] - 5, summary(areaTransitory)$bbox[2,1] - 5)
-  }
-  else{
-    centroid[i,] <- geosphere::centroid(areaTransitory)
-  }
-}
-warnings()
-
-# Create legend
-areaNameCorrected <- c(
-  "East Madagascar",
-  "West Madagascar",
-  "West Africa",
-  "Central Africa",
-  "East/South Africa",
-  "Central America",
-  "Northern South America",
-  "Southern South America",
-  "West Asia",
-  "Central/East Asia",
-  "South Asia",
-  "Asian islands")
-colourArea <- c(
-"white",
-"darkseagreen2",
-"darkseagreen",
-"darkseagreen4",
-"black",
-"orange1", 
-"darkorange2",
-"darkorange4",
-"lightgoldenrod1",
-"lightgoldenrod2",
-"lightgoldenrod3",
-"lightgoldenrod4"
-)
-
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-emptyPlot()
-legend(x=0, y=0.9, col=c("black", colourArea[2:5]), legend=areaNameCorrected[1:5], pch=c(1, rep(19, times=length(2:5))), pt.cex=1.5, xjust=0, yjust=1, bty="n",
-      y.intersp=2.75,
-      title=expression(bold("Africa")))
-legend(x=0.5, y=0.9, col=c(colourArea[6:8]), legend=areaNameCorrected[6:8], pch=19, bty="n", pt.cex=1.5, xjust=0.5, yjust=1,
-       y.intersp=2.75,
-       title=expression(bold("America")))
-legend(x=1, y=0.9, col=c(colourArea[9:12]), legend=areaNameCorrected[9:12], pch=19, bty="n", pt.cex=1.5, xjust=1, yjust=1,
-       y.intersp=2.75,
-       title=expression(bold("Asia")))
-my_legend <- recordPlot()     
-```
-
-```{r figmap, include=TRUE, position='H', warning = FALSE, message = FALSE, results= 'hide', fig.width=7, fig.height=7, fig.cap=paste("Geographic areas used for ancestral range reconstruction of frugivorous primates represented on the Mercator projection of the world | Areas were defined as a combination of geographic and environmental criteria relative to the primate taxonomy following results from [@kamilar2009environmental]: (1) East Madagascar (2) West Madagascar (3) West Africa (4) Central Africa (5) East/South Africa (6) Central America (7) North South-America (8) South South-America (9) West Asia (10) Central/East Asia (11) South Asia (12) Asian peninsula and islands.
-Note that the north part of Africa and the south of Europe were discarded because *Macaca sylvanus* was not considered.
-", sep="")}
-
-#abbreviation name are available in https://proj.org/operations/projections/index.html
-#help for graticule: https://rpsychologist.com/working-with-shapefiles-projections-and-world-maps-in-ggplot
-
-proj.map <- "+proj=natearth +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
-
-centroid <- as.data.frame(centroid)
-colnames(centroid) <- c("long", "lat")
-centroid$nudge_y <- 0
-centroid$nudge_y[5] <- -10
-
-library(tidyverse)
-library(ggspatial)
-
-library(rnaturalearth)
-world <- ne_countries(scale = "medium", returnclass = "sf")
-
-# graticule (Robin)
-grat <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_graticules_15")
-grat_df <- fortify(grat)
-
-bbox <- readOGR(dsn="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Formap", layer="ne_110m_wgs84_bounding_box")
-bbox_df<- fortify(bbox)
-
-###----
-### OLD WAY: when using sf package
-###----
-# bbox.sf <- sfheaders::sf_polygon(  obj = bbox_df 
-#                                          , x = "long"
-#                                          , y = "lat"
-#                                          , polygon_id = "group"
-# )
-# sf::st_crs(bbox.sf) <- st_crs(world)
-# 
-# grat_df <- grat_df[,c(1,2,6)]
-# colnames(grat_df) <- c("x", "y", "linestring_id")
-# grat_df.sf <- sfheaders::sf_line(obj = grat_df)
-# 
-# sf::st_crs(grat_df.sf) <- st_crs(world)
-
-#Main map
-# map <- ggplot() +
-#   geom_sf(data = bbox.sf, fill=adjustcolor("white", alpha.f=0.45), col="white") +
-#   geom_sf(data = grat_df.sf, col="darkgrey", lty=2) +
-#   geom_sf(data = world, fill = "black", col = "white") +
-#   theme(panel.background=element_rect(fill="white"),
-#         panel.grid = element_blank(),
-#         axis.title.x=element_blank(),
-#         axis.text.x=element_blank(),
-#         axis.ticks.x=element_blank(),
-#         axis.title.y=element_blank(),
-#         axis.text.y=element_blank(),
-#         axis.ticks.y=element_blank()
-#   )
-
-#Plot polygons areas
-mergedArea <- c()
-
-for(i in 1:length(areaName)){
-  toFortify <- get(paste("area", i, sep="_"))
-  toFortify <- fortify(toFortify)
-
-  toFortify$group <-paste(areaName[i], toFortify$piece)
-  toFortify$colour <- gsub("_", " ", areaName[i],)#areaNameCorrected[i]#colourArea[i]
-  mergedArea <- rbind(mergedArea, toFortify)
-  #add to ggplot
-  #map <- map + geom_polygon(data = toFortify, aes(x = long, y = lat, group = group), col = colourArea[i], fill = colourArea[i])
-}
-
-###----
-### OLD WAY: when using sf package
-###----
-
-# centroid.sf <- st_as_sf(centroid, coords=c("long", "lat"), crs=st_crs(world))
-# library(sfheaders)
-# mergedArea.sf <- sfheaders::sf_polygon(  obj = mergedArea
-#                                          , x = "long"
-#                                          , y = "lat"
-#                                          , polygon_id = "group"
-# )
-# sf::st_crs(mergedArea.sf) <- st_crs(world)
-# 
-# #Readd colour
-# mergedArea.sf$colour <- unique(mergedArea[,c(7,8)])[,2]
-#   mergedArea, coords=c("long", "lat"), crs=st_crs(world))
-# st_cast(mergedArea.sf, to="POLYGON")
-#
-
-library(ggmap)
-library(scales)
-
-#Getting the stammen background map and adding the graticule
-mapStammen <- get_stamenmap( bbox = c(left = -180, bottom = -66, right = 180, top = 66), zoom = 4, maptype = "watercolor")#maptype = "terrain-background")
-# plot(mergedArea.sf, add=TRUE)
-mapPlot <- ggmap(mapStammen) #+
-  # theme_void() +
-  # theme(
-  #   panel.border = element_rect(colour = "white", fill=NA, size=2)
-  # )
-for(k in 0:max(as.numcharac(grat_df$id))){
-mapPlot <- mapPlot +
-  geom_path(data = grat_df %>% filter(as.numcharac(id)==k), aes(x=long, y=lat), colour="white", linetype="dashed")
-}
-
-#Adding the coloured cropped polygons of areas
-for(i in 1:length(areaName)){
-  polygonToAdd <- get(paste("area", i, sep="_"))
-
-  for(j in 1:length(polygonToAdd@polygons[[1]]@Polygons)){#Some problem with fortified when multiple polygons. Trying using one sub-polygon at a time.
-    toPlot <- sp::Polygons(list(polygonToAdd@polygons[[1]]@Polygons[[j]]), ID = "A")
-    toPlot <- sp::SpatialPolygons(list(toPlot))
-      fortifiedArea <- fortify(toPlot)
-      mapPlot <- mapPlot + geom_polygon(data = fortifiedArea, aes(x = long, y= lat), fill=colourArea[i], col=colourArea[i], lwd=0.5) +
-          geom_label(data = centroid[i,], aes(x=long, y=lat), label=(1:length(colourArea))[i],
-             fill = ifelse(i != 1 & i != 2, "white", colourArea[i]),
-             col = "black",
-             nudge_y=centroid$nudge_y[i],
-             label.r = unit(0.4, "lines"),
-             size = 2) 
-  }
-}
-mapPlot <- mapPlot +
-  # scale_color_manual(name='',
-  # breaks=c(
-  # "East Madagascar",
-  # "West Madagascar",
-  # "West Africa",
-  # "Central Africa",
-  # "East/South Africa",
-  # "Central America",
-  # "Northern South America",
-  # "Southern South America",
-  # "West Asia",
-  # "Central/East Asia",
-  # "South Asia",
-  # "Asian islands"),
-  # values=c(
-  # "East Madagascar"=colourArea[1],
-  # "West Madagascar"=colourArea[1],
-  # "West Africa"=colourArea[1],
-  # "Central Africa"=colourArea[1],
-  # "East/South Africa"=colourArea[1],
-  # "Central America"=colourArea[1],
-  # "Northern South America"=colourArea[1],
-  # "Southern South America"=colourArea[1],
-  # "West Asia"=colourArea[1],
-  # "Central/East Asia"=colourArea[1],
-  # "South Asia"=colourArea[1],
-  # "Asian islands"=colourArea[1])
-  # )+
-    theme(
-        text = element_text(size = 10),
-        legend.key = element_rect(size = 4),
-        legend.key.size = unit(1, 'lines'),
-        legend.position="bottom",
-        axis.text=element_text(size=10),
-        axis.title=element_text(size=15,face="bold")
-        ) +
-  xlab("Longitude") +
-  ylab("Latitude") +
-  scale_x_continuous(breaks = c(seq(from=-165, to=-15, by=30), 0, seq(from=15, to=165, by=30)), expand = c(0, 0))# +
-  #scale_y_continuous(breaks = pretty(-66:66, n = 10))
-
-library(cowplot)
-# Create grid of plots
-plot_grid(mapPlot, 
-          my_legend,
-          ncol = 1,
-          rel_heights = c(2.25,1))
-
-##--------
-###OLD WAY
-##-------
-
-# map <- map +
-#   geom_sf(data = mergedArea.sf, aes(fill = colour)) +
-#   geom_sf_label(data = centroid.sf, aes(label = 1:nrow(centroid)),
-#              fill = c(colourArea[11], colourArea[12], rep("white", times=10)),
-#              col = c("black", "white", rep("black", times=10)),#colourArea[3:12]),
-#              nudge_y=centroid$nudge_y,
-#              label.r = unit(0.4, "lines"),
-#              size = 2) +
-#   coord_sf(crs = proj.map, expand = F) +
-#   scale_fill_manual(values = colourArea, labels=c("Central Africa", "South/East Africa", "West Africa", "Central America", "North of South America", "South of South America", "Central/East Asia", "Asian islands", "South Asia", "West Asia", "East Madagascar", "West Madagascar")) +
-#   labs(fill = "")  +
-#   theme(
-#         text = element_text(size = 10),
-#         legend.key = element_rect(size = 4),
-#         legend.key.size = unit(1, 'lines'),
-#         legend.position="bottom")
-# map
-# # #Just to see the difference as pinpointed by the warning
-# # # geosphere::areaPolygon(areaTransitory)
-# # # gArea(areaTransitory)
-# # # really false
-# # # geosphere::centroid(areaTransitory)
-# # # gCentroid(areaTransitory)
-# # #ok
-# #
-# # layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
-# # par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-# #
-# # Add figure interaction here if needed
-# ####
-# ## Fig map
-# ####
-#
-# #Create the map of the geographic area
-# #Have background
-# maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA, mar = c(0, 0, 0, 0))#, ylim=c(-60, 50))
-#
-# # addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
-# #
-#
-# for(i in 1:length(areaName)){
-#   plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
-# }
-# #Have borders
-# #plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
-# # for(i in 1:length(areaName)){
-# #   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
-# # }
-# points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.3)
-# points(x=centroid[,1], y=centroid[,2], cex=1.3, col=c("white", "white", rep("black", times=10)))
-# text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.5, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))
-
-```
-
-\clearpage
-
-```{r phylogeny, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Levels  of species sympatry vary across the primate phylogeny | Primate phylogeny from the consensus tree of the 10kTrees project is depicted in the center, together with abbreviated species names.
-The corresponding non-abbreviated names can be found using Appendix Figure \\@ref(fig:figdata).
-Sympatric frugivorous (based on a frugivory threshold of ", frugivoryThresholdVector[1], "% and folivory threshold of ", folivoryThresholdVector[1], "%) species are linked by light grey lines.
-The geographic areas occupied by a species are depicted by coloured rectangles.
-Presence was assessed given an overlap between the species range and the geographic area of ", geographicThresholdVector[1]*100, "%.", sep="")}
-
-# ####
-# ## Fig interaction
-# ####
-
-#Tree
-tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
-tree <-  drop.tip(tree,
-                      tree $tip.label[
-                        which(tree$tip.label
-                              %nin% summaryDataForPlot$SpeciesForPhylogeny)])
-
-#Create geography df
-geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
-colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
-
-#Create species ID
-hc = as.hclust(tree)#bird.orders)
-labels = hc$labels  # name of birds
-
-labels.tordc <- as.data.frame(labels)
-colnames(labels.tordc) <- "Name"
-labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
-
-labels.rdc <- apply(labels.tordc, 1, function(x){
-  if(!is.na(x[3])){
-    paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
-  } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
-  }
-}
-)
-
-#Match to have right order for geography
-locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
-colLoc <- colourArea
-
-#Match to have diet
-dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
-
-#Getting species labels abbreviated
-speciesLabels <- hc$labels#Should be in the tree order
-
-#Create the circos plot linking species based on their diet and geography
-
-circos.clear()
-circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
-circos.initialize(speciesLabels, xlim = c(0, 1))
-
-# #Add family
-# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
-#              panel.fun = function(x, y) {
-#                i=CELL_META$sector.numeric.index
-#                circos.rect(CELL_META$cell.xlim[1],CELL_META$cell.ylim[1], CELL_META$cell.xlim[2],CELL_META$cell.ylim[2], col="white", border=NA)
-#                 })
-#
-# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
-#              panel.fun = function(x, y) {
-#                i=CELL_META$sector.numeric.index
-#                circos.rect(CELL_META$cell.xlim[1],CELL_META$cell.ylim[1], CELL_META$cell.xlim[2],CELL_META$cell.ylim[2], col="white", border=NA)
-#                 })
-#
-# for(i in 1:length(unique(summaryDataForPlot$Family))){
-#   speciesForPlotFamily <- speciesLabels[speciesLabels %in% summaryDataForPlot$SpeciesForPhylogeny[summaryDataForPlot$Family %in% unique(summaryDataForPlot$Family)[i]]]
-#   if(length(speciesForPlotFamily) > 0){
-#     highlight.sector(speciesForPlotFamily, track.index = 1, col = adjustcolor("black", alpha.f=0.15), padding = c(0, 0.2, 0, 0),
-#       text = unique(summaryDataForPlot$Family)[i], cex = 0.5, text.col = "white", niceFacing = TRUE)
-#   }
-# }
-
-#Species name + area it belongs to
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
-             panel.fun = function(x, y) {
-               i=CELL_META$sector.numeric.index
-               circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0),
-                           facing = "clockwise", niceFacing = TRUE,
-                           col = "black", cex = 0.75, font=3)
-
-              geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-              for(g in 1:length(geo)){
-                if(geo[g]==1){
-                  #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
-                  circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
-                }
-              }
-             })
-
-#Plot the geographic links
-for(i in 1:length(speciesLabels)){
-  #locI <- which(strsplit(locationSpecies[i], "")==1)
-  for(j in i:length(speciesLabels)){
-    #locJ <- which(strsplit(locationSpecies[j], "")==1)
-    product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
-    if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
-      #Do nothing
-    }
-    else{
-      if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
-        # colour <- as.data.frame(table(colLoc[which(product==1)]))
-        # if(is.finite(max(colour$Freq))){
-        # }else{
-        #   print(c(i,j))
-        # }
-        # colour <- colour[colour$Freq==max(colour$Freq),1][1]
-        circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col=adjustcolor("black",alpha.f=0.15))#"lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
-      }
-      else{
-        #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
-      }
-    }
-  }
-}
-circos.clear()
-
-#Plot the phylogenetic tree in a new circular plot
-n = length(labels)  # number of species
-dend = as.dendrogram(hc)
-
-par(new = TRUE) # <- magic
-circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
-circos.initialize("a", xlim = c(0, n)) # only one sector
-# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3,
-#              panel.fun = function(x, y) {
-#                for(i in seq_len(n)) {
-#                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5),
-#                              facing = "clockwise", niceFacing = TRUE,
-#                              col = "black", cex = 0.2, font=3)
-#                }
-#              })
-
-#suppressPackageStartupMessages(library(dendextend))
-#dend = color_branches(dend, k = 6, col = 1:6)
-dend_height = attr(dend, "height")
-circos.track(ylim = c(0, dend_height), bg.border = NA,
-             track.height = 0.95, panel.fun = function(x, y) {
-               circos.dendrogram(dend)
-             })
-circos.clear()
-```
-
-\clearpage
-
-<!-- A 3D brain from *Homo sapiens* is depicted (*neurobase* package [@neurobase], *misc3d* package [@misc3d]). The arrows indicate the sagital and frontal axes.  -->
-<!-- , although the neocortex was not coloured for readability since it corresponds to the external layer of the cerebral hemisphere -->
-```{r figbrain, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=7, fig.cap=paste("Variations in relative brain size areas among frugivorous primates | (Left) Circular plot of the relative sizes of the different brain areas.
-Colours indicates the rows for the different brain areas.
-The darker background emphasises when values are above average, while the lighter background emphasises when values are below average.
-The mean value (after scaling and based on one random sampling among possible values, but see \\@ref(fig:figvariabilitydata) for visualization of measure variability) for the Encephalization Quotient (EQ) or relative size of brain regions, when available, is depicted by a plain circle for frugivorous species.
-The frugivorous threshold was fixed to ", frugivoryThresholdVector[1], "% and the folivory threshold to ", folivoryThresholdVector[1], "%.
-(Right) The different studied brain areas (human brain as an illustration).
-In short, the MOB is involved in immediate olfactory information processing, the Neocortex and the Cerebellum support working memory and memory consolidation of immediate sensory information processing [@wiltgen2004new; @koziol2014consensus; @sokolov2017cerebellum], and the Hippocampus supports a working memory and a long-term spatio-temporal memory [@burgess2002human].
-The Striatum is involved in social information processing [@baez2013role].", sep="")}
-
-library(RColorBrewer)
-
-colourEQ <- "gray"
-colourEQbis <- "lightgray"
-colourEQdark <- "black"
-
-colourHippocampus <- rgb(0,128,0,maxColorValue = 255)
-colourHippocampusbis <- rgb(95,211,95,maxColorValue = 255)#pastellize(colourHippocampus)
-colourHippocampusdark <- rgb(0,208,0,maxColorValue = 255)
-
-colourStriatum <- rgb(255,204,0,maxColorValue = 255)
-colourStriatumbis <- rgb(255,230,128,maxColorValue = 255)#pastellize(colourStriatum)
-colourStriatumdark <- "darkgoldenrod2"
-
-colourNeocortex <- rgb(255,213,213,maxColorValue = 255)
-colourNeocortexbis <- "white"#rgb(255,213,213,maxColorValue = 255)#pastellize(colourNeocortex)
-colourNeocortexdark <- rgb(255,175,175,maxColorValue = 255)
-
-colourCerebellum <- rgb(255,128,128,maxColorValue = 255)
-colourCerebellumbis <- rgb(255,170,170,maxColorValue = 255)#pastellize(colourCerebellum)
-colourCerebellumdark <- rgb(255,64,64,maxColorValue = 255)
-
-colourMOB <- rgb(255,0,0,maxColorValue = 255)
-colourMOBbis <- rgb(255,95,95,maxColorValue = 255)#pastellize(colourMOB)
-colourMOBdark <- "darkred"
-
-colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
-colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
-colour.circle.points <- c("black", "darkred", "darkblue", "purple4", "darkgreen", "orange4")
-
-###
-## Fig brain values / circular
-###
-
-summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
-summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Bodymass
-summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Bodymass
-summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Bodymass
-summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Bodymass
-summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Bodymass
-
-#Brain data
-relativeValueEQ <- scale(summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])#runif(length(speciesLabels), -1, 1)
-relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
-
-layout(mat=cbind(c(1,1), c(2,3)), widths=c(35,15), heights=c(15,35))
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-
-# plot(0, 0, type="n")
-
-library(circlize)
-circos.clear()
-circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
-circos.initialize(speciesLabels, xlim = c(0, 1))
-
-#Species name
-circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
-             panel.fun = function(x, y) {
-               i=CELL_META$sector.numeric.index
-               circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
-                           facing = "clockwise", niceFacing = TRUE,
-                           col = "black", cex = 0.6, font=3)
-             })
-#
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourEQ, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourEQ, border=colourEQ)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourEQbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourEQbis, border=colourEQbis)
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourStriatum, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourStriatum, border=colourStriatum)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourStriatumbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourStriatumbis, border=colourStriatumbis)
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourHippocampus, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourHippocampus, border=colourHippocampus)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourHippocampusbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourHippocampusbis, border=colourHippocampusbis)
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourMOB, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourMOB, border=colourMOB)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourMOBbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourMOBbis, border=colourMOBbis)
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourCerebellum, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourCerebellum, border=colourCerebellum)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourCerebellumbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourCerebellumbis, border=colourCerebellumbis)
-}, track.height = 1/15)
-
-#Background
-circos.track(ylim = c(0, 1), bg.border = colourNeocortex, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourNeocortex, border=colourNeocortex)
-}, track.height = 1/15)
-
-circos.track(ylim = c(0, 1), bg.border = colourNeocortexbis, panel.fun = function(x, y) {
-  circos.rect(0, 0, 1, 1, col=colourNeocortexbis, border=colourNeocortexbis)
-}, track.height = 1/15)
-
-library(plotrix)
-#Main circle
-for(i in 1:13){
-  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
-}
-
-#increment of 0.5
-for(i in 1:26){
-  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
-}
-
-#Value
-
-#EQ
-absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueEQ[i])){}  else{
-    if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colourEQdark, cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
-    }
-    else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colourEQdark, bg="white", cex=0.7)
-      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueEQ[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colourEQdark, cex=0.7)
-    }
-    else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colourEQdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colourEQdark, bg="white", cex=0.7)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Striatum
-absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueStriatum[i])){}  else{
-    if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colourStriatumdark, cex=0.65)
-    }
-    else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colourStriatumdark, bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueStriatum[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colourStriatumdark, cex=0.65)
-    }
-    else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colourStriatumdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colourStriatumdark, bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Hippocampus
-absMax <- max(abs(relativeValueHippocampus), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=6, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=19, col=colourHippocampusdark, cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueHippocampus[i]/absMax, pch=21, col=colourHippocampusdark, bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=7,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueHippocampus[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=19, col=colourHippocampusdark, cex=0.55)
-    }
-    else if(relativeValueHippocampus[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, col=colourHippocampusdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueHippocampus[i]/absMax, pch=21, col=colourHippocampusdark, bg="white", cex=0.55)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#MOB
-absMax <- max(abs(relativeValueMOB), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=8, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueMOB[i])){}  else{
-    if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=19, col=colourMOBdark, cex=0.65)
-    }
-    else if(relativeValueMOB[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueMOB[i]/absMax, pch=21, col=colourMOBdark, bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=9,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueMOB[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=19, col=colourMOBdark, cex=0.65)
-    }
-    else if(relativeValueMOB[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, col=colourMOBdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueMOB[i]/absMax, pch=21, col=colourMOBdark, bg="white", cex=0.65)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Cerebellum
-absMax <- max(abs(relativeValueCerebellum), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=10, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=19, col=colourCerebellumdark, cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueCerebellum[i]/absMax, pch=21, col=colourCerebellumdark, bg="white", cex=0.5)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=11,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueCerebellum[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=19, col=colourCerebellumdark, cex=0.5)
-    }
-    else if(relativeValueCerebellum[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, col=colourCerebellumdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueCerebellum[i]/absMax, pch=21, col=colourCerebellumdark, bg="white", cex=0.5)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Neocortex
-absMax <- max(abs(relativeValueNeocortex), na.rm=TRUE)
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=12, panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
-  if(is.na(relativeValueNeocortex[i])){}  else{
-    if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=19, col=colourNeocortexdark, cex=0.6)
-    }
-    else if(relativeValueNeocortex[i] > 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
-      circos.points(CELL_META$xcenter, relativeValueNeocortex[i]/absMax, pch=21, col=colourNeocortexdark, bg="white", cex=0.6)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-circos.track(ylim = c(0, 1), bg.border = NA, track.index=13,  panel.fun = function(x, y) {
-  i=CELL_META$sector.numeric.index
-  if(is.na(relativeValueNeocortex[i])){}  else{
-    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
-    if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Fruit"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=19, col=colourNeocortexdark, cex=0.6)
-    }
-    else if(relativeValueNeocortex[i] <= 0 & dietSpecies[i]=="Leaf"){
-      #circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, col=colourNeocortexdark, lty=3)
-      circos.points(CELL_META$xcenter, 1 + relativeValueNeocortex[i]/absMax, pch=21, col=colourNeocortexdark, bg="white", cex=0.6)
-    }
-    else{}
-  }
-}, track.height = 0.1)
-
-#Empty plot
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-emptyPlot()
-# plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
-#      xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
-# 
-#Add brain
- library(png)
-brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/brain_draw.png")
-addImg(brainIMG, x = 0.425, y = 0.5, width = 0.7)
-
-# brainIMG <- readPNG("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/3dplot.png")
-# addImg(brainIMG, x = 0.425, y = 0.65, width = 1.3)
-# 
-# #Add circle contour
-# draw.circle(x=0.45,y=0.55,0.435, col=NA, border="lightgray", lwd=2)
-# draw.circle(x=0.45,y=0.55,0.405, col=NA, border="lightgray", lwd=2)
-# 
-# par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-# plot(0, 0, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="", las=1, type="n", tcl=-0.25, bty="n",
-#      xaxt="n",xaxs="i",yaxs="i", yaxt="n", xpd=TRUE)
-# colourHip=colourHippocampus
-# colourCereb=colourCerebellum
-# colourOlf=colourMOB
-# colourStri=colourStriatum
-
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-emptyPlot()
-legend(x=0.1, y=1, yjust=1, legend = c("EQ", "Striatum", "Hippocampus", "MOB", "Cerebellum", "Neocortex", "Frugivorous species", "Folivorous species"), cex = 1, fill = c(colourEQ, colourStriatum, colourHippocampus, colourMOB, colourCerebellum, colourNeocortex, NA, NA), pch=c(NA, NA, NA, NA, NA, NA, 19, 1), border=c("black", "black", "black", "black", "black", "black", "white", "white"), col=c(NA, NA, NA, NA, NA, NA, "black", "black"), bty="n", seg.len=0.75)
-
-```
-
-\clearpage
-
-```{r figresultsevolution, fig.pos='H', include=TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6, fig.cap="The evolution of the Hippocampus and Striatum in frugivorous primates are best fitted by models of trait evolution considering species sympatry | Plotted is the AICc weight, a measure of relative support for a given model, for models not considering species sympatry (BM, OU, EB) or considering species sympatry (MC, DD$_{lin}$, DD$_{exp}$).
-The points represent the average AICc weight obtained (when considering the six models from the same run), while the vertical bars indicate the standard deviation given all tested conditions (see [Models of trait evolution: does species sympatry shape brain size evolution?])."}
-
-layout(mat=rbind(c(1,2,3), c(4,5,6), c(7,7,7)), widths=c(5,5,5), heights=c(5,5,1))
-par(mar=c(3.5, 3, 2, 0.5), mgp=c(2, 0.5, 0), xpd=TRUE)
-#note: 1= second run for frugivory 20%
-#note: _2= first run for frugivory 20%
-
-## EQ
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-mtext(side=2, line=2, at=0.5, text="AICc weight", cex=0.85)
-
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
-
-for(i in 1:6){
-  meanPt <- mean(as.numcharac(summaryEQFrugivory[, ncol(summaryEQFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryEQFrugivory[, ncol(summaryEQFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryEQFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryEQFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryEQFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-
-draw.circle(x=0.3,y=1.1,0.35, col=colourEQ, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="1", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="EQ", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-##-------------
-
-##------------
-#Striatum
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourStriatum)
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.75, xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryStriatumFrugivory[, ncol(summaryStriatumFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryStriatumFrugivory[, ncol(summaryStriatumFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryStriatumFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.35, col=colourStriatum, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="2", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="Striatum", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryStriatumFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryStriatumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-
-##------------
-
-##------------
-
-#Hippocampus
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-# axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryHippocampusFrugivory[, ncol(summaryHippocampusFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryHippocampusFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.35, col=colourHippocampus, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="4", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="Hippocampus", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryHippocampusFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryHippocampusFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-##------------
-
-##-------------
-#MOB
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-mtext(side=2, line=2, at=0.5, text="AICc weight", cex=0.85)
-#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourMOB)
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryMOBFrugivory[, ncol(summaryMOBFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryMOBFrugivory[, ncol(summaryMOBFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryMOBFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.35, col=colourMOB, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="3", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="MOB", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryMOBFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryMOBFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-##------------
-
-##-------------
-#Cerebellum
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourCerebellum)
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.9,  xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryCerebellumFrugivory[, ncol(summaryCerebellumFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryCerebellumFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.35, col=colourCerebellum, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="6", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="Cerebellum", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-#b and r are the rate for density dependance (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryCerebellumFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryCerebellumFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-###----------------------
-
-##-------------
-#Neocortex
-
-plot(
-  x=0, y=0, xlab="", ylab="", cex.sub=1.6,
-  xlim=c(0,7), ylim=c(0,1.2),
-  las=1, type="n", tcl=-0.25, frame.plot=FALSE, 
-  xaxt="n",xaxs="i",yaxs="i", yaxt="n")
-
-rect(xleft=0, xright=3.5, ybottom=0, ytop=1, col=adjustcolor("royalblue", alpha.f=0.2), border=NA)
-rect(xleft=3.5, xright=7, ybottom=0, ytop=1, col=adjustcolor("blue", alpha.f=0.2), border=NA)
-
-addGrid(xmin=0, xmax=7, xintsmall=0.25, xintbig=1, ymin=0, ymax=1, yintsmall=0.05, yintbig=0.2, axisPlot=FALSE)
-#axis(side=2, at=seq(from=0, to=1, by=0.2), labels=seq(from=0, to=1, by=0.2), las=2, tcl=-0.25)
-#segments(x0 = -1, x1 = -1, y0 = 0, y1 = 1, lty = 2, col = colourNeocortex)
-segments(x0 = 3.5, y0=0, x1=3.5, y1=1, lty=2)
-text(x=1:6, y=rep(-0.1, times=6), labels=models, cex=0.75, xpd=TRUE)
-for(i in 1:6){
-
-  meanPt <- mean(as.numcharac(summaryNeocortexFrugivory[, ncol(summaryNeocortexFrugivory)-6+i]))
-  sd <- sd(as.numcharac(summaryNeocortexFrugivory[, ncol(summaryNeocortexFrugivory)-6+i]))
-  #sd <- sd/nrow(summaryNeocortexFrugivory) #error not sd
-  errorBars(location=i, meanPt=meanPt, barValue=sd, refUnit=1, col="black", minValue=0, maxValue=1, horiz=FALSE)
-  points(x=i, y=meanPt, pch=19, col="black", xpd=TRUE)
-
-}
-draw.circle(x=0.3,y=1.1,0.35, col=colourNeocortex, border=NA)
-#text(x=0.3, y=1.1, cex=1.15, labels="5", xpd=TRUE, col="white", font=2)
-text(x=0.75, y=1.1, labels="Neocortex", xpd=TRUE, col="black", font=2, cex=1.15, adj=0)
-
-#b and r are the rate for density dependence (DD) of the speciation rate. If positive, positive DD, otherwise, negative.
-#add their values below:
-
-text(x=c(4,5,6), y=c(-0.2, -0.2),
-     labels=c(
-       "r ~",
-       round(mean(as.numcharac(summaryNeocortexFrugivory$DDlingeo.b)), digit=3),
-       round(mean(as.numcharac(summaryNeocortexFrugivory$DDexpgeo.r)), digit=3)
-     ), cex=0.8, xpd=TRUE)
-
-##-------------
-
-par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
-emptyPlot()
-legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)
-```
-
-\newpage
-
-\beginsupplement
-
-\clearpage
-
-# Appendix
-
-## Data availability
-
-Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Figure \@ref(fig:figdata).
-
-## Data variability
-
-We present below the results of the assessments of data variability depending on the considered thresholds (for frugivory, folivory or overlap) and the data set that is used, specifically related to distribution ranges, or anatomical/behavioural traits.
-
-### Sensitivity to variation in distribution range
+Finer geographic characterization would therefore give too much weight to such anthropogenic effect that recently altered species distribution [e.g.
+evidenced on the North American fauna in @pineda2021mammal].
+
+|   The overlap between a species range and a biogeographic area was used to assess whether the species occupied the area or not.
+We chose overlaps of `r geographicThresholdVector[1]*100` (low threshold) or `r geographicThresholdVector[2]*100`% (high threshold), to consider a species presence within a given area.
+We present now variations that occurred depending on the considered threshold.
 
@@
 
-### Sensitivity to variation in trait value
+## Sensitivity to variation in trait value
 
@@
 ###------
-### CORRELATION
+## CORRELATION
 
@@
 ###------
-### VARIABILITY
+## VARIABILITY
 
@@
 ##----
-## Repeatability of measure
+# Repeatability of measure
 
@@
   addGrid(xmin=1, xmax=ncol(dataForSample_rdcplot), xintsmall=1, xintbig=1, ymin=0, ymax=nrow(dataForSample_rdcplot), yintsmall=1, yintbig=1, colsmall="white", colbig="white", axisPlot=FALSE)
-  #if(p==2){cat('\r\n\r\n')} #Allows to consider plot as a new figure at each step of the loop
-}
-
-```
-
+  #if(p==2){cat('\r\n\r\n')} #Allows to consider plot as a new Fig. at each step of the loop
+}
+
+```
+
+In addition to variability between datasets, we varied thresholds used to classify species diet.
+Illustratively, for example, if a species reached 30% of frugivory, and 65% of folivory (the rest being due, for instance, to insectivory), then, it would be categorized as, “frugivorous” if low thresholds are considered, or as “folivorous” in case high thresholds are considered.
+If we suppose now another species with 30% of frugivory and 50% of folivory, but considered by [@decasien2017primate] as frugivorous, then, the species would be “frugivorous” for low threshold, and still “frugivorous” with high thresholds.
+
+|   Frugivory was prioritized over folivory because we considered that since fruits are a highly palatable food source, it would be the key item that drives the foraging strategy (and associate consequence(s) on brain selection), even if less consumed.
+Additionally, to consider frugivory, we used a lower rate than for folivory for two reasons.
+First, such a static rate does not reflect potential seasonality in fruit-eating [e.g.
+@masi2009western], which is generally shorter, hence a lower overall frugivory rate.
+Second, the frugivory rate is likely to be underestimated in part because primates generally spend more time feeding on leaves than fruits, while rates are often based on relative feeding time, or observation frequency at the individual or group unit of feeding events.
+Finally, the methodology to obtain this rate could additionally vary (e.g.
+in addition to the two aforementioned estimations, one could also rely on the proportion of species targeted for their fruits/leaves).
+For all these reasons, we used two threshold levels (low, `r frugivoryThresholdVector[1]`%, or high, `r frugivoryThresholdVector[2]`%) to classify a species as frugivorous, as well as two threshold levels (low, `r folivoryThresholdVector[1]`%, or high, `r folivoryThresholdVector[2]`%) to classify a species as folivorous.
+
+## Dealing with data uncertainty and parameterisation sensitivity in models of trait evolution
+
+\hfill
+
+In this analysis, uncertainty can stem from two sources.
+First, the evolutionary history (phylogeny, diet, and ranging) was reconstructed based on Bayesian inference.
+They are susceptible to be uncertain at some points.
+Thus, we used a consensus phylogenetic tree from the 10kTrees project, which averages the phylogeny among 1000 possible estimated trees, given that running the models on several trees was too computationally demanding.
+In addition, we repeated diet and ranging history reconstructions `r numberSimulations` times.
+
+|   Second, for each species, trait estimates could vary slightly among datasets (see Fig.
+Appendix Fig.
+S2).
+Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Fig.
+Appendix Fig.
+S2).
+We are aware that this could contribute to blurring results [@Wartel2019; @Hooper2021].
+In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Fig.
+S1) and (ii) to assess the species dietary guild (see Fig.
+Appendix Fig.
+S2) which can cause sensitivity of the results to the chosen parameters.
+To account for these three sources of variability, we refitted several times the six models of trait evolution (BM, OU, EB, MC, DD$_{lin}$ and DD$_{exp}$) with (1) random samples of the dietary and brain traits in case of multiple values available (i.e.
+equal probability for each possible value to be selected), (2) used the low or high threshold for assessing frugivory, folivory, and species sympatry, and (3) various biogeography and dietary evolutionary history reconstructions.
+
+|   Eventually, it means that the results for each model represent the average of `r numberSimulations` (uncertainty on diet/ranging evolutionary reconstructions) x `r randomSampling` (uncertainty in brain/diet rate data) x `r length(geographicThresholdVector)` (geographic overlap threshold defining sympatry) x `r length(frugivoryThresholdVector)` (frugivory threshold) x `r length(folivoryThresholdVector)` (folivory threshold) = `r numberSimulations*randomSampling*length(geographicThresholdVector)*length(frugivoryThresholdVector)*length(folivoryThresholdVector)` sub-models.
+We stopped computations when the optimization of the likelihood was excessively long (> 1 week).
+The final sample size thus was of `r min(totModelsWorked[-2])*10` models that covered all the ranges of tested parameters.
 \clearpage
 
-### Primate diversification rate over time
+## Primate diversification rate over time
+
+Lineage-specific diversification rates were estimated using an updated version of the *ClaDS* algorithm [@maliet2019model] boosted for computational speed based on data augmentation techniques [@maliet2020fast].
+This Bayesian approach considers speciation rate heterogeneity by modelling small shifts in the rate at speciation events.
+In other words, the two new lineages are assumed to inherit new speciation rates that are sampled from a log-normal distribution with an expected mean value $log(\alpha \lambda)$ (where $\lambda$ represents the initial speciation rate and $\alpha$ is a trend parameter), and a standard deviation $\sigma$.
+Three independent chains were run until their convergence was validated by a Gelman-Rubin diagnostic criterion [@gelman1992inference].
+The analysis relied on the use of a consensus tree of primate phylogeny from [@dos2018using].
+The latter provides a robust phylogenetic tree for 367 primate species (while the 10kTrees primate phylogeny has only `r length(phylo_init$tip.label)` species).
+
+|   Such analysis necessarily depends on a prior estimation of the sample representativeness, that is, the fraction of sampled taxa (present in the phylogenetic tree) among all possible existing ones.
+@estrada2017impending estimated that, given current knowledge, the primate clade should be composed of 504 species.
+This means that the current sampling fraction is around 73%.
+We thus parameterized the *ClaDS* algorithm with this value for the estimated sampling fraction.
+Yet, given that the extant number of primate species is subject to controversy, and because the estimated sampling fraction may affect diversification rate estimations, we replicated our analyses with a range of sampling fractions from 95% down to 60%.
+At the end of each run, we extracted the maximum of the *a posteriori* net diversification rate of each extant primate species, as well as the mean diversification rate (given all lineages) through time.
 
@@
 library(strucchange)
-## confidence interval
+# confidence interval
 colnames(aggregatedSpeciationTime.mean) <- c("Time", "Diversification")
@@
 
-## Phylogenetic regressions: results, stability, and assumption
-
-### Model results
+# Phylogenetic regressions: results, stability, and assumption
+
+## Model results
 
@@
 
-### Model stability
+\hfill
+
+###	Model implementation
+
+\hfill
+
+(i)	Effect of sympatry on brain sizes
+
+\hfill
+
+Models were fitted using the “phylolm” function from the *phylolm* package [@phylolm], with the lambda parameter (with $\lambda$ indicating the strength of the phylogenetic signal, where $\lambda$=1  corresponds to Brownian Motion, i.e.
+the maximal influence of the phylogenetic history on the trait evolution) estimated by maximum-likelihood (argument “model” set to “lambda”).
+Bootstrapping over `r repetitionBootstrap` independent replicates was done to obtain confidence intervals.
+Other function parameters were set to default.
+Prior to fitting, covariates were transformed so as to reach more symmetrical distributions when adequate.
+Necessary assumptions on the normal distribution of residuals and homoscedasticity were visually assessed and pointed out no violation (see Appendix [Model assumptions]).
+We did not observe correlation issue among predictors neither [VIF$_{max}$ < 2, @mundry2014statistical].
+
+\hfill
+
+(ii)	Diversification and brain size
+
+\hfill
+
+We could not compute phylogenetic regressions to link diversification and brain traits in frugivorous primates using a frequentist-based approach because it led to a violation of homoscedasticity.
+Instead, we fitted Bayesian phylogenetic regressions using the "MCMCglmm" function of the *MCMCglmm* package [@MCMCglmm].
+Each chain was based on a burnin period of `r burnin` iterations, among a total of `r nitt` iterations, and was sampled every `r thin` iterations.
+We used the least informative priors.
+Fixed priors were let to default (Gaussian distribution of mean 0 and variance $10^{8}$).
+Priors on random effects and residuals were set to follow an inverse-Wishart distribution with a variance at a limit ($V$) of 1, and a degree of belief ($nu$) of 0.02.
+We checked model convergence by fitting three chains, and calculated the Gelman-Rubin criterion [max value < `r round(max(gelmanRubinValues), digit=4)`, @gelman1992inference], as well as checked autocorrelation (max absolute value < `r round(max(valueAutoCorr), digit=2)`) using the respective "gelman.diag" and "autocorr.diag" functions from the *coda* package [@coda].
+In Appendix [Model assumptions], we present traces and distributions of posterior estimates.
+We further checked the quality of the posterior by visually assessing the Q-Q plot of the posterior with that of a Gaussian distribution of mean 0 and sd 1 (see Appendix [Model assumptions]).
+We present the estimate together with the 95% credibility interval centered on the mode (Highest Density Posterior, HDP), together with a MCMC p-value (pMCMC) that corresponds to the probability that the estimate ($\beta$) is positive if the mean estimate ($\hat{\beta}$) is negative (i.e.
+$P(\beta>0|\hat{\beta}<0)$), or if the mean estimate is positive, the probability that the estimate is negative (i.e.
+$P(\beta<0|\hat{\beta}>0)$).
+
+\hfill
+
+(iii) Diversification and sympatry
+
+\hfill
+
+We fitted phylogenetic regression as explained in (i).
+In particular, verification of model assumption and stability pointed out no source of worry (see [Phylogenetic regressions: results, stability, and assumption]).
+
+## Model stability
 
@@
 "sampling fraction" of known species for diversification analyses).
+
+|   To assess frequentist model stability with regards to singular points, we computed the DfBetas (variation in estimates) by discarding one observation at a time of the "standard" dataset used to fit the main model, based on the consensus tree .
+
+|   To assess the sensitivity to (i) the variability in data and (ii) phylogeny uncertainty, we refitted the models using `r repetitionTrees` phylogenetic trees among the 10000 possible trees from the 10kTrees project.
+For each of these trees, we fitted the model `r repetitionModels` times, allowing random sampling for data when we had multiple values (e.g.
+if body mass was provided by different datasets etc.).
+For the diversification analysis specifically, we also assessed the sensitivity to changes in primate sampling fraction by refitting the models for values ranging between 60 to 95% (as specified before), using the "standard" dataset and the consensus tree.
+
+|   The results of these assessments (min-max of estimates) are shown in Appendix [Model stability]. It emphasizes the weak sensitivity of the results.
 
@@
 rownames(summarySensitivityDiversification) <- NULL
-knitr::kable(summarySensitivityDiversification[,-c(3,4,5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction).") %>%
+colnames(summarySensitivityDiversification)[9:11] <- c("Est. min.", "Est.", "Est. max.")
+
+knitr::kable(summarySensitivityDiversification[,-c(3:5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data) or when the sampling fraction varied (Sampling fraction).") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
@@
 knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data)") %>%
+             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas), when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction)") %>%
   kableExtra::kable_styling(latex_options = "striped") %>%
   kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::add_header_above(c("Model:" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction"))
+  kableExtra::add_header_above(c("Model" = 1, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
 
@@
 \newpage
-### Model assumptions
+## Model assumptions
 

### 2022-01-28 Article/Supplementary_material_forsubmission_wordworking.Rmd
Update for submission - Separation Sup mat and Main text - Add Rmd word compilation

--- 2022-01-28 Article/Supplementary_material_forsubmission.Rmd
@@
 knitr::opts_chunk$set(include=FALSE, echo=FALSE, message=FALSE)
-knitr::opts_chunk$set(dpi=300) # Fig. resolution and size out.width = '100%', 
+knitr::opts_chunk$set(dpi=300) # Figure resolution and size out.width = '100%', 
 knitr::opts_chunk$set(fig.pos = 'p'#, fig.align = 'center'
                       ) # Places figures on pages separate from text, centered
-knitr::opts_chunk$set(fig.env="figure") # Latex Fig. environment
-knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R Fig. caption
-```
+knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
+knitr::opts_knit$set(eval.after = "fig.cap") #To insert R code into R figure caption
+```
+
+<!-- TC:ignore -->
 
@@
 
+#Data handling
 library(tidyverse)
+library(huxtable)
+
 #Import own function
@@
 plot(
-  x=0, y=0, xlab="Overlap threshold", ylab="Percentage of species with different biogeographic areas\ncompared to when a 15% overlap is used", 
+  x=0, y=0, xlab="Overlap threshold", ylab="Percentage of species with different biogeographic\nareas compared to when a 15% overlap is used", 
   xlim=c(thresholdPresenceRange[1],thresholdPresenceRange[length(thresholdPresenceRange)]), ylim=c(0,0.4),
@@
 
-|   Second, for each species, trait estimates could vary slightly among datasets (see Fig.
-Appendix Fig.
+|   Second, for each species, trait estimates could vary slightly among datasets (see Appendix Fig.
 S2).
-Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Fig.
-Appendix Fig.
+Particularly, although correlations between measures from the different datasets seem good enough, it existed a variation in absolute measurements (Appendix Fig.
 S2).
@@
 In addition, this study is based on several arbitrary thresholds, namely (i) to assess species sympatry (see Appendix Fig.
-S1) and (ii) to assess the species dietary guild (see Fig.
-Appendix Fig.
+S1) and (ii) to assess the species dietary guild (see Appendix Fig.
 S2) which can cause sensitivity of the results to the chosen parameters.
@@
 
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of relative brain size as a function of sympatry level indices | Left graphics show the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species  is averaged, while the right graphics do the opposite.
+<!-- ```{=latex} -->
+<!-- \begin{figure} -->
+<!-- \centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf} -->
+<!-- \caption{\scriptsize{Phylogenetic regressions of relative brain size as a function of sympatry level indices | Left graphics show the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species  is averaged, while the right graphics do the opposite.
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionGradient}
-\end{figure}
-```
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionGradient} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+
+```{r}
+error_file = magick::image_read("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.pdf", density=500)
+error_file = magick::image_convert(error_file, "png")
+image_write(error_file, path = "C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.png", format = "png")
+```
+
+```{r figRegressionGradient, include=TRUE, fig.width = 7, fig.height = 7, fig.cap= "Phylogenetic regressions of relative brain size as a function of sympatry level indices | Left graphics show the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species  is averaged, while the right graphics do the opposite.
+Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\\% confidence interval is depicted by the transparent grey background."}
+
+knitr::include_graphics("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/selectionGradientPGLS.png", error=TRUE)
+
+```
+
 \clearpage
@@
 
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.7\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent grey background.}}\label{fig:figRegressionDiversification}
-\end{figure}
+<!-- ```{=latex} -->
+<!-- \begin{figure} -->
+<!-- \centering\includegraphics[width=0.7\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf} -->
+<!-- \caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\% highest density posterior is depicted by the transparent grey background.}}\label{fig:figRegressionDiversification} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+
+```{r}
+error_file = magick::image_read("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.pdf", density=500)
+error_file = magick::image_convert(error_file, "png")
+image_write(error_file, path = "C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.png", format = "png")
+```
+
+```{r figRegressionDiversification, include=TRUE, fig.width = 7, fig.height = 7, fig.cap= "Phylogenetic regressions of the net diversification rate as a function of the size of the different brain areas | Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\\% highest density posterior is depicted by the transparent grey background."}
+
+knitr::include_graphics("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationPGLS.png", error=TRUE)
+
 ```
@@
 
-```{=latex}
-\begin{figure}
-\centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf}
-\caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of sympatry level indices | The left graphic depicts the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species is averaged, while the right graphic does the opposite.
+<!-- ```{=latex} -->
+<!-- \begin{figure} -->
+<!-- \centering\includegraphics[width=0.65\linewidth]{C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf} -->
+<!-- \caption{\scriptsize{Phylogenetic regressions of the net diversification rate as a function of sympatry level indices | The left graphic depicts the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species is averaged, while the right graphic does the opposite.
 Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
-The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionDiversificationSympatry}
-\end{figure}
+The model fit is shown with the plain black line and the associated 95\% confidence interval is depicted by the transparent grey background.}}\label{fig:figRegressionDiversificationSympatry} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+
+```{r}
+error_file = magick::image_read("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.pdf", density=500)
+error_file = magick::image_convert(error_file, "png")
+image_write(error_file, path = "C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.png", format = "png")
+```
+
+```{r figRegressionDiversificationSympatry, include=TRUE, fig.width = 7, fig.height = 7, fig.cap= "Phylogenetic regressions of the net diversification rate as a function of sympatry level indices | The left graphic depicts the effect of the number of sympatric species on the brain size, when the effect of the average percentage of overlapping range with sympatric frugivorous species is averaged, while the right graphic does the opposite.
+Raw data are depicted with points, while the segments that link them correspond to the projected phylogenetic tree.
+The model fit is shown with the plain black line and the associated 95\\% confidence interval is depicted by the transparent grey background."}
+
+knitr::include_graphics("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Plots/diversificationAndSympatryPGLS.png", error=TRUE)
+
 ```
@@
 
+# knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
+#              caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down") %>%
+#   kableExtra::kable_styling(latex_options = "HOLD_position") %>%
+#   kableExtra::add_header_above(c("Regression" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3))
+
+summarySensitivityGradient.toPlot <- rbind(colnames(summarySensitivityGradient), summarySensitivityGradient)
+colnames(summarySensitivityGradient.toPlot) <- 1:ncol(summarySensitivityGradient.toPlot)
 rownames(summarySensitivityGradient) <- NULL
-knitr::kable(summarySensitivityGradient, escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
-  kableExtra::add_header_above(c("Regression" = 2, "DfBetas" = 3, "Phylogeny/Data" = 3))
+
+as_huxtable(summarySensitivityGradient.toPlot, add_colnames = FALSE, add_rownames = FALSE) %>%
+  set_caption("Sensitivity analysis of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas) or when varying the used phylogenetic tree and the data sampling (Phylogeny/Data).") %>%
+
+  #Main layout
+  set_bottom_border(row = 1, col = everywhere) %>%
+  set_bold(row = 1, col = everywhere) %>%
+  set_background_color(evens, everywhere, "grey95") %>%
+
+  #Sub-headers
+  insert_row("Regression", "", "DfBetas", "", "", "Phylogeny/Data", "", "", after = 0) %>% 
+  merge_cells(1, 1:2) %>% 
+  merge_cells(1, 3:5) %>% 
+  merge_cells(1, 6:8) %>% 
+  set_align(1, everywhere, "center") %>% 
+  set_bold(1, everywhere) %>%  
+  as_flextable()
+
 ```
@@
 
-knitr::kable(summarySensitivityDiversification[,-c(3:5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data) or when the sampling fraction varied (Sampling fraction).") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
-  kableExtra::add_header_above(c("Regression" = 2, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
+# knitr::kable(summarySensitivityDiversification[,-c(3:5)], escape=TRUE, booktabs = TRUE, #Remove brain 1:3
+#              caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data) or when the sampling fraction varied (Sampling fraction).") %>%
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down") %>%
+#   kableExtra::kable_styling(latex_options = "HOLD_position") %>%
+#   kableExtra::add_header_above(c("Regression" = 2, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
+
+summarySensitivityDiversification.toPlot <- rbind(colnames(summarySensitivityDiversification), summarySensitivityDiversification)
+colnames(summarySensitivityDiversification.toPlot) <- 1:ncol(summarySensitivityDiversification.toPlot)
+
+as_huxtable(summarySensitivityDiversification.toPlot[,-c(3:5)], add_colnames = FALSE, add_rownames = FALSE) %>%
+  set_caption( "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and relative brain sizes | Depicted is the minimum and maximum of estimates when varying the used phylogenetic tree and the data sampling (Phylogeny/Data) or when the sampling fraction varied (Sampling fraction).") %>%
+
+  #Main layout
+  set_bottom_border(row = 1, col = everywhere) %>%
+  set_bold(row = 1, col = everywhere) %>%
+  set_background_color(evens, everywhere, "grey95") %>%
+
+  #Sub-headers
+  insert_row("Regression", "","Phylogeny/Data", "", "", "Sampling fraction", "", "", after = 0) %>% 
+  merge_cells(1, 1:2) %>% 
+  merge_cells(1, 3:5) %>% 
+  merge_cells(1, 6:8) %>% 
+  set_align(1, everywhere, "center") %>% 
+  set_bold(1, everywhere) %>%  
+  as_flextable()
 ```
@@
 summarySensitivitydiversificationAndSympatry[,1] <- gsub("N co-occurrence", "Number of sympatric frugivores", summarySensitivitydiversificationAndSympatry[,1])
-
-knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
-             caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas), when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction)") %>%
-  kableExtra::kable_styling(latex_options = "striped") %>%
-  kableExtra::kable_styling(latex_options="scale_down") %>%
-  kableExtra::add_header_above(c("Model" = 1, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
+# 
+# knitr::kable(summarySensitivitydiversificationAndSympatry, escape=TRUE, booktabs = TRUE,
+#              caption = "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas), when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction)") %>%
+#   kableExtra::kable_styling(latex_options = "striped") %>%
+#   kableExtra::kable_styling(latex_options="scale_down") %>%
+#   kableExtra::add_header_above(c("Model" = 1, "DfBetas" = 3, "Phylogeny/Data" = 3, "Sampling fraction" = 3))
+
+summarySensitivitydiversificationAndSympatry.toPlot <- rbind(colnames(summarySensitivitydiversificationAndSympatry), summarySensitivitydiversificationAndSympatry)
+colnames(summarySensitivitydiversificationAndSympatry.toPlot) <- 1:ncol(summarySensitivitydiversificationAndSympatry.toPlot)
+
+as_huxtable(summarySensitivitydiversificationAndSympatry.toPlot, add_colnames = FALSE, add_rownames = FALSE) %>%
+  set_caption(  "Sensitivity analysis of phylogenetic regressions to assess the relationship between species diversification and sympatry | Depicted is the minimum and maximum of estimates when one observation was removed at a time (DfBetas), when varying the used phylogenetic tree and the data sampling (Phylogeny/Data), or when the sampling fraction varied (Sampling fraction)") %>%
+
+  #Main layout
+  set_bottom_border(row = 1, col = everywhere) %>%
+  set_bold(row = 1, col = everywhere) %>%
+  set_background_color(evens, everywhere, "grey95") %>%
+
+  #Sub-headers
+  insert_row("Regression", "DfBetas", "", "","Phylogeny/Data", "", "", "Sampling fraction", "", "", after = 0) %>%
+  merge_cells(1, 2:4) %>% 
+  merge_cells(1, 5:7) %>% 
+  merge_cells(1, 8:10) %>% 
+  set_align(1, everywhere, "center") %>% 
+  set_bold(1, everywhere) %>%  
+  as_flextable()
 
